### 2019-08-28 ms/ms.tex
begin to make summary

\documentclass[twocolumn]{aastex62}
\emergencystretch=1.em 
\newcommand \figPath{../fig/}
\newcommand \redColor{\color{red}}
\renewcommand\labelenumi{(\roman{enumi})}
\renewcommand\theenumi\labelenumi
%\newcommand{\jcap}{JCAP}

\usepackage{amsmath,amsthm,amsfonts,amssymb,bm}
\usepackage{listings}
\usepackage{multirow}
\usepackage{color}

%\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{epstopdf}
\usepackage{natbib}
\hypersetup{breaklinks}

\begin{document}
\title{}

\begin{abstract}

\end{abstract}

\section{Introduction}

\section{Method}

\subsection{$3$D Weak lensing}

Assuming a flat universe, the lensing convergence at redshift plane $z_s$ is
\begin{equation}\label{lensing_1D_los_continue}
\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2 \Omega_M}{2c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s}(1+z_l) \delta(\chi_l\vec{\theta},\chi_l),
\end{equation}
where $c$ is the speed of light, $z_l$ is the redshift evaluated at comoving distance $\chi_l$. 
$H_0$ and $\Omega_M$ are the Hubble parameter and matter density parameter at redshift equals zero, respectively. 
$\delta(\vec{r})=\rho(\vec{r})/\bar{\rho}-1$ is the matter fluctuation.

The convergence field at redshift ($\kappa$) can be related to the shear field ($\gamma$) at the same redshift plane via a $2$D convolution
\begin{equation}\label{lensing_2D_tv_continue}
\gamma(\vec{\theta}, \chi_s)=\frac{1}{\pi} \int d^2 \theta' D(\vec{\theta}-\vec{\theta}') \kappa(\vec{\theta}',\chi_s),
\end{equation} 
where
\begin{equation}
D(\vec{\theta}) = \frac{1}{(\theta_1-i\theta_2)^2}.
\end{equation}

The shear field ($\gamma$) is pixelized into $N_{zs}$ tomographic bins $\gamma^{1}$,...,$\gamma^{N_{zs}}$ of size $N_{ys} \times N_{xs}$ where $N_{ys}$ and $N_{xs}$ are the number of pixels on the $2$D transverse Cartesian coordinates. Similarly, the density contrast field ($\delta$) to be reconstructed is also binned into $N_{zl}\times N_{yl} \times N_{xl}$ pixels. The discrete shear field and the discrete density contrast field can be viewed as finite size vectors $\gamma_\mu$ and $\delta_\alpha$. The measured shear is related to the matter density contrast by a $2$D transverse convolution (equation (\ref{lensing_2D_tv_continue})) and a $1$D line-of-sight convolution (equation (\ref{lensing_1D_los_continue})), which can be expressed in a matrix notation
\begin{equation}
\gamma_{\mu} = \textbf{P}_{\mu \nu} \textbf{Q}_{\nu \alpha} \delta_{\alpha} + \epsilon_{\mu},
\end{equation}
where $\textbf{P}_{\mu \nu}$ represents the transverse convolution and $\textbf{Q}_{\nu \alpha}$ represents the line-of-sight convolution and $\epsilon_{\mu}$ represents measurement noise including the contributions of shape noise and pixel noise.

\subsection{Sparsity}

\subsection{Wavelets}

\section{Application}
\subsection{Mock shape catalog}

\subsection{HSC shape catalog}

\section{Summary}

\end{document}

### 2019-10-04 python/sparse3D_s16a.py
commit

@@ -66,8 +66,8 @@ class sparse3D_s16aBatchTask(BatchPoolTask):
 
     
     @abortOnError
-    def run(self,Id):
-        fieldList   =  np.load('/work/xiangchong.li/work/S16AFPFS/fieldInfo.npy').item().keys() 
+    def runDataRef(self,Id):
+        fieldList   =  np.load('fieldInfo.npy',allow_pickle=True).item().keys() 
         pool    =   Pool("sparse3D_s16aBatch")
         pool.cacheClear()
         obsDir  =   self.config.obsDir
@@ -86,9 +86,9 @@ class sparse3D_s16aBatchTask(BatchPoolTask):
             self.log.info('stop processing field: %s' %fieldName)
             return
 
-        outDir      =   os.path.join(obsDir,'lambda%.1f'%lbd)
         configName  =   'config_lbd%.1f_%s.ini' %(lbd,fieldName)
-        configName  =   os.path.join(outDir,configName)
+        configName  =   os.path.join(obsDir,configName)
+        
 
         inFname     =   './s16aPre/%s_RG.fits' %fieldName  
         sources     =   pyfits.getdata(inFname)

### 2019-10-04 python/sparseBase.py

@@ -440,11 +440,11 @@ class massmapSparsityTask():
             parser.set('sparse','mu','%s' %self.mu)
         lsst.log.info('mu = %s' %self.mu)
         sigFname    =   os.path.join(self.frameDir,'sigmaAlpha_%s.fits' %self.fieldN)
-        if os.path.exists(sigFname)
+        if os.path.exists(sigFname):
             self.sigmaA =   pyfits.getdata(sigFname) 
             assert self.sigmaA.shape  ==   self.shapeA, 'load wrong noise sigma map'
         else:
-            self.prox_sigmaA(100):
+            self.prox_sigmaA(100)
 
         self.alphaR =   np.zeros(self.shapeA)
         self.deltaR =   np.zeros(self.shapeL)

### 2019-10-04 paper_method_HSCY1/ms.tex
add paper draft

\documentclass[twocolumn]{aastex62}
\emergencystretch=1.em 
\newcommand \figPath{../fig/}
\newcommand \redColor{\color{red}}
\renewcommand\labelenumi{(\roman{enumi})}
\renewcommand\theenumi\labelenumi
%\newcommand{\jcap}{JCAP}

\usepackage{amsmath,amsthm,amsfonts,amssymb,bm}
\usepackage{listings}
\usepackage{multirow}
\usepackage{color}

%\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{epstopdf}
\usepackage{natbib}
\hypersetup{breaklinks}

\begin{document}
\title{FPFS Shear Estimator: Systematic Tests on the First Year Hyper Suprime-Cam Survey}
\author{Xiangchong Li}
\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{Masamune Oguri}
\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
\author{Nobuhiko Katayama}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{Wentao Luo}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{Wenting Wang}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{Jiaxin Han}
\affiliation{Department of Astronomy, School of Physics and Astronomy, Shanghai Jiao Tong University, Shanghai, 200240, China}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{HSC Collaboration}
\noaffiliation
\email{xiangchong.li@ipmu.jp}

%\author{Surhud More}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI),\\
%UTIAS, Tokyo Institutes for Advanced Study, University of Tokyo, Chiba 277-8583, Japan}

\begin{abstract}

\end{abstract}

\section{Introduction}

\section{Mass Map}
\label{sec:kappaMap}

\subsection{Kaiser-Squires reconstruction}
\label{subsec:kappaMap-KS}
Subsequently, the shear field is converted to the convergence field via \citep{massMap-KS1993}
\begin{equation}\label{eq:KS_real}
\kappa(\vec{\theta})=\frac{1}{\pi} \int d^2\theta' \frac{\gamma_t(\vec{\theta'}|\vec{\theta})}{|\vec{\theta}-\vec{\theta'}|^2},
\end{equation}
where $\hat{\gamma}_t(\vec{\theta'}|\vec{\theta})$ is a tangential shear at position $\vec{\theta'}$ computed with respect to the reference position $\vec{\theta}$. The shear-to-convergence relationship is a convolution in two dimensional angular plane. Such convolution is computed in Fourier space with the Fast Fourier Transform (FFT) to reduce the computational time. Shear fields are padded with zero beyond their boundary to avoid the periodic boundary condition assumed in FFT. The complex shear field is denoted as $\gamma(\vec{\theta})=\gamma_1(\vec{\theta})+i\gamma_2(\vec{\theta})$. The Fourier transform of complex shear field and complex kappa field is denoted as $\tilde{\gamma}(\vec{l})$ and $\tilde{\kappa}(\vec{l})$, respectively. Eq. (\ref{eq:KS_real}) can be expressed in Fourier space
\begin{equation}
\tilde{\kappa}(\vec{l})=\pi^{-1}\tilde{\gamma}(\vec{l})\tilde{D}^{*}(\vec{l}) ~~ for ~~\vec{l}\neq\vec{0},
\end{equation}
where $\tilde{D}(\vec{l})$ is the Fourier transform of the convolution kernel in eq. (\ref{eq:KS_real})
\begin{equation}
\tilde{D}(\vec{l})=\pi \frac{l_1^2-l_2^2+2il_1l_2}{|\vec{l}|^2}.
\end{equation}
\break
Then the mass map in configuration space $(\kappa(\vec{\theta}))$ is reconstructed by inverse Fourier transforming $\tilde{\kappa} (\vec{l})$.
Note that the real part of the reconstructed mass map is referred as an E-mode mass map, whereas the imaginary part of the reconstructed mass map is referred as an B-mode mass map which is used to check for certain types of residual systematics in weak lensing measurements.

The relation between $\gamma$ and $\kappa$ is 
\begin{equation}
\gamma(\vec{\theta})=\int D(\vec{\theta}-\vec{\theta}') \kappa(\vec{\theta}') d^2\theta.
\end{equation}
Denote $\gamma$ and $\kappa$ as vectors $\vec{\gamma}$ and $\vec{\kappa}$, respectively. $\vec{\kappa}$ is the mass map to be reconstructed on equally spaced coordinates. $\vec{\gamma}$ is the shear observed from non-equally spaced galaxies. Then the operation of convolution can be denoted as a matrix multiplication
\begin{equation}
\vec{\gamma}=\textbf{D} \vec{\kappa} + \vec{n}.
\end{equation}
And $\vec{\kappa}$ can be determined by minimize
\begin{equation}
\chi^2=(\vec{\gamma}-\textbf{D} \vec{\kappa})^{T}(\vec{\gamma}-\textbf{D} \vec{\kappa}).
\end{equation}
We require 
\begin{equation}
dim\left(\vec{\kappa}\right) \leq dim \left( \vec{\gamma} \right)
\end{equation}

Find an orthogonal vector space and decompose $\vec{\kappa}$ onto the orthogonal space, the decomposition factor are denoted as $\vec{\alpha}$, where
\begin{equation}
\begin{split}\\
\vec{\alpha}&= \bold{\Phi}\vec{\kappa}\\
\vec{\kappa}&=\bold{\Phi}^{-1} \vec{\alpha}
\end{split}
\end{equation} 
If $\vec{\alpha}$ only has a small number of nonzero coefficients,
\begin{equation}
\vec{\gamma}=\textbf{D} \bold{\Phi}^{-1}\vec{\alpha}+\vec{n}
\end{equation}

\begin{equation}
\chi^2=||(\vec{\gamma}-\textbf{D} \bold{\Phi}^{-1}\vec{\alpha})||^2_{2} + \lambda||\vec{\alpha}||_{1}
\end{equation}
\begin{equation}
\begin{split}
||\vec{v}||_{1}&=\sum_i^{N} |v_i|\\
||\vec{v}||^2_{2}&=\sum_i^{N} v_i^2
\end{split}
\end{equation}
\bibliographystyle{aasjournal}
\bibliography{weak_lensing,lensCat,cosmoSim,cmbObs,gglens,shearCor,massMap}

\end{document}

### 2019-10-20 ms_method_HSCY1/ms.tex

--- 2019-10-04 paper_method_HSCY1/ms.tex
@@
 \begin{document}
-\title{FPFS Shear Estimator: Systematic Tests on the First Year Hyper Suprime-Cam Survey}
-\author{Xiangchong Li}
-\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
-\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-University of Tokyo, Kashiwa 277-8583, Japan}
-\author{Masamune Oguri}
-\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
-\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-University of Tokyo, Kashiwa 277-8583, Japan}
-\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
-\author{Nobuhiko Katayama}
-\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-University of Tokyo, Kashiwa 277-8583, Japan}
-\author{Wentao Luo}
-\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-University of Tokyo, Kashiwa 277-8583, Japan}
-\author{Wenting Wang}
-\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-University of Tokyo, Kashiwa 277-8583, Japan}
-\author{Jiaxin Han}
-\affiliation{Department of Astronomy, School of Physics and Astronomy, Shanghai Jiao Tong University, Shanghai, 200240, China}
-\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-University of Tokyo, Kashiwa 277-8583, Japan}
-\author{HSC Collaboration}
-\noaffiliation
-\email{xiangchong.li@ipmu.jp}
-
-%\author{Surhud More}
-%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI),\\
-%UTIAS, Tokyo Institutes for Advanced Study, University of Tokyo, Chiba 277-8583, Japan}
+\title{mass map reconstruction with sparsity method}
+%\author{Xiangchong Li}
+%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
+%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
+%University of Tokyo, Kashiwa 277-8583, Japan}
+%\author{Masamune Oguri}
+%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
+%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
+%University of Tokyo, Kashiwa 277-8583, Japan}
+%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
+%\author{Nobuhiko Katayama}
+%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
+%University of Tokyo, Kashiwa 277-8583, Japan}
+%\author{Wentao Luo}
+%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
+%University of Tokyo, Kashiwa 277-8583, Japan}
+%\author{Wenting Wang}
+%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
+%University of Tokyo, Kashiwa 277-8583, Japan}
+%\author{Jiaxin Han}
+%\affiliation{Department of Astronomy, School of Physics and Astronomy, Shanghai Jiao Tong University, Shanghai, 200240, China}
+%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
+%University of Tokyo, Kashiwa 277-8583, Japan}
+%\author{HSC Collaboration}
+%\noaffiliation
+%\email{xiangchong.li@ipmu.jp}
 
@@
 
-\section{Mass Map}
+\section{The Method}
 \label{sec:kappaMap}

### 2019-11-05 paper_ms_method_HSCY1/ms.tex
add notes and halSim

\documentclass[twocolumn]{aastex62}
\emergencystretch=1.em 
\newcommand \figPath{./}
\newcommand \redColor{\color{red}}
\newcommand{\vecb}[1]{{#1}}
\renewcommand\labelenumi{(\roman{enumi})}
\renewcommand\theenumi\labelenumi
%\newcommand{\jcap}{JCAP}

\usepackage{amsmath,amsthm,amsfonts,amssymb,bm}
\usepackage{listings}
\usepackage{multirow}
\usepackage{color}

%\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{epstopdf}
\usepackage{natbib}
\usepackage{commath}
\hypersetup{breaklinks}

\begin{document}
\title{Sparsity Weak Lensing Mass Reconstruction}
%\author{Xiangchong Li}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Masamune Oguri}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
%\author{Nobuhiko Katayama}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Wentao Luo}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Wenting Wang}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Jiaxin Han}
%\affiliation{Department of Astronomy, School of Physics and Astronomy, Shanghai Jiao Tong University, Shanghai, 200240, China}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{HSC Collaboration}
%\noaffiliation
%\email{xiangchong.li@ipmu.jp}

\begin{abstract}

\end{abstract}

\section{Introduction}
...
\section{The Problem}

\subsection{Density Contrast to Shear}
The lensing distortion $\kappa$ at a position $\vec{x}=(\vec{\theta}$, $\chi_s$) caused by the foreground inhomogeneous density distribution is 
\begin{equation}
\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s} \frac{\delta(\chi_l \vec{\theta},\chi_l)}{a(\chi_l)}
\end{equation}
\citep{massMap-Glimpse3D2014}.
Substitute angular distance $D$ with redshift $z$ and we have
\begin{equation}\label{eq-delta2kappa}
\kappa(\vec{\theta},z_s)=\int_0^{z_s} dz_l \delta_{c}^{-1}(z_l,z_s)\delta(\vec{\theta},z_l).
\end{equation}
we term $\delta_{c}(z_l,z_s)$ as lensing critical density contrast and define it as
\begin{equation}
\delta_{c}^{-1}(z_l,z_s) =
\begin{cases}
\frac{3H_0\Omega_M}{2 c} \frac{\chi_l \chi_{sl} (1+z_l)}{ \chi_s E(z_l)} & (z_s>z_l),\\
0&(z_s \leq z_l).
\end{cases}
\end{equation}

As reported in \citet{massMap-KS1993}, the shear distortion is
\begin{equation}\label{eq-kappa2gamma}
\vecb{\gamma}(\vec{\theta},z_s) = \int \vecb{D}(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s) d^2 \theta,
\end{equation}
where 
\begin{equation}
\begin{split}
\vecb{D}(\vec{\theta})&=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2},\\
\vecb{\gamma}(\vec{\theta})&=\gamma_1(\vec{\theta})+i\gamma_2(\vec{\theta}).
\end{split}
\end{equation}

Combine equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}) and we have
\begin{equation}\label{eq-delta2gamma-z}
\vecb{\gamma}(\vec{\theta},z_s) = \int_0^{z_s} dz_l \frac{\delta_c(z_l,+\infty)}{\delta_{c}(z_l,z_s)} \int d^2 \theta'  \vecb{D}(\vec{\theta}-\vec{\theta'}) \frac{\delta(\vec{\theta'},z_l)}{\delta_c(z_l,+\infty)}.
\end{equation}

\subsection{Photo-$z$ Uncertainty}
Since the redshifts of source galaxies are estimated with a limited number of photometric bands, the estimated redshift of a galaxy suffer from large uncertainty. The probability distribution function (PDF) of a galaxies at position $(\vec{\theta},z_s)$ is denoted as $\mathcal{P}(z|z_s)$.  Note that, in order to simplify the future calculation, we assume the variation of the PDF across the transverse plane is small and neglect the dependency on the transverse position.

Taking the uncertainty of redshift into account, equation (\ref{eq-delta2gamma-z}) changes to
\begin{equation}\label{eq-delta2gamma-poz}
\begin{split}
\gamma(\vec{\theta},z_s) &= \int_0^{z_s} dz_l P(z_l,z_s)\gamma(\vec{\theta},z_l,+\infty),\\
\gamma(\vec{\theta},z_l,+\infty)&= \int d^2 \theta'   Q(\vec{\theta}-\vec{\theta'},z_l) \delta(\vec{\theta'},z_l),
\end{split}
\end{equation}
where $\gamma(\vec{\theta},z_l,+\infty)$ represents shear signal at infinite redshift ($z_s=+\infty$) caused by density contrast at $z_l$, and $P(z_l,z_s)$ is the convolution kernel along line-of-sight and $Q(\vec{\theta},\vec{\theta}',z_l)$ is the convolution kernel along on the transverse plane. These kernels are defined as
\begin{equation}
\begin{split}
P(z_l,z_s)&=\int \frac{\delta_c(z_l,+\infty)}{\delta_{c}(z_l,z)} \mathcal{P}(z|z_s) dz,\\
Q(\vec{\theta},\vec{\theta'},z_l)&=\frac{\vecb{D}(\vec{\theta}-\vec{\theta'})}{\delta_c(z_l,+\infty)}.
\end{split}
\end{equation}
\subsection{Smoothing}
Since the observed galaxies have random irregular (unequally-spaced) distribution, it is necessary to smooth the shear signal in the observation. The smoothing is expressed as follows
\begin{equation}
\gamma_S  (\vec{\theta},z)  = \frac{\sum_i  W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) e_i}{\sum_i W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) R_i},
\end{equation}
where $W(\vec{\theta},z)$ is a $3$-D smoothing kernel. $e_i$, $R_i$, $z_i$ and $\theta_i$ are the ellipticity, response, reshift, transverse position of the `$i$-th' galaxy.
$W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line-of-sight component $W_\times(z)$
\begin{equation}
W(\vec{\theta},z)=W_T(\vec{\theta}) W_\times (z).
\end{equation}
In this paper, we set
\begin{equation}
\begin{split}
W_T(\vec{\theta}) &=\frac{1}{2\pi\beta^2}\exp(-\frac{|\vec{\theta}|}{2\beta^2}),\\
W_\times (z) &= 
\begin{cases}
1/\Delta z& (|z|<\Delta z/2),\\
0& else.
\end{cases}
\end{split}
\end{equation}

With the assumption that the density of response $R$ and the density of galaxy number vary slowly on the smoothing scale, the smoothed shear is 
\begin{equation}\label{eq-smooth-gamma}
\gamma_S(\vec{\theta}_j,z_j)= \int d^2 \theta_s d z_sW(\vec{\theta}_j-\vec{{\theta}}_s,z_j-z_s) \gamma(\vec{\theta}_s,z_s)
\end{equation}

Substitute equation (\ref{eq-delta2gamma-poz}) into equation (\ref{eq-smooth-gamma})
\begin{equation}\label{eq-delta2gamma-smooth}
\begin{split}
\gamma_S(\vec{\theta}_j,z_j) &= \int_0^{z_j} dz_l P_S(z_l,z_j)\gamma_S(\vec{\theta}_j,z_l,+\infty),\\
\gamma_S(\vec{\theta}_j,z_l,+\infty)&= \int d^2 \theta'   Q_S(\vec{\theta}_j,\vec{\theta'},z_l) \delta(\vec{\theta'},z_l),
\end{split}
\end{equation}
and
\begin{equation}
\begin{split}
P_S(z_l,z_j)&=\int  dz_s W_\times (z_j-z_s) \int \frac{\delta_c(z_l,+\infty)}{\delta_{c}(z_l,z)} \mathcal{P}(z|z_s) dz,\\
Q_S(\vec{\theta},\vec{\theta'},z_l)&=\int d^2\theta'' W_T( \vec{\theta} -\vec{\theta''} )  \frac{\vecb{D}(\vec{\theta''}-\vec{\theta'})}{\delta_c(z_l,+\infty)}.
\end{split}
\end{equation}

\subsection{Mask and Noise}
In real observations, the influence of mask and noise should also be taken into account. The final observed shear is 
\begin{equation}\label{eq-delta2gamma-final}
\gamma_o(\vec{\theta},z)=M(\vec{\theta},z) \gamma(\vec{\theta},z) + \epsilon(\vec{\theta},z),
\end{equation}
where $\epsilon$ represents noise typically caused by random shape of intrinsic galaxies and such noise is modeled as white Gaussian noise. $M(\vec{\theta},z_s)$ is the mask function.

We can write equation (\ref{eq-delta2gamma-final}) into 
\begin{equation}\label{eq-delta2gamma-operator-final}
\gamma_o =\mathbf{M}  \mathbf{P} \mathbf{Q} \delta + \epsilon,
\end{equation}
where $\mathbf{M}$,  $\mathbf{P}$ and $\mathbf{Q}$ represent the functional operators $M$, $P$ and $Q$, respectively.

\section{The Method}
\label{sec:kappaMap}

\subsection{Dictionary}
Since many $N$-body simulations have shown the dark matter to be largely distributed in halos connected by filaments,
we assume that the density contrast field can be decomposed into multi-scaled NFW halo \citep{halo-NFW1997ApJ} and point mass at different positions
\begin{equation}
\delta(\vec{x}) = \sum_{s=0}^{N_s} \int d^3 x' \phi_s(\vec{x}-\vec{x}') \alpha_s(\vec{x'})\\
\end{equation}
where $\phi_0$ is $3$-D Dirac delta function representing point mass
\begin{equation}
\phi_0(\vec{x})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
\end{equation}
Since the scale of halo is much less than the reachable redshift resolution, we neglect the depth of halo on the line-of-sight direction as suggested by \citep{massMap-Glimpse3D2014}.
On the transverse plane, the NFW atom is modeled with the surface density profile of NFW halo with scale $\theta_s$ and truncation radius $c \theta_s$ \citep{haloModel-TJ2003-3pt}, where $c$ is generally known as concentration of NFW halo.  Whereas, the NFW atom is modeled with Dirac delta function on the line-of-sight direction
\begin{equation}
\begin{split}
\phi_s(\vec{x}) =&\frac{f }{2 \pi \theta_s^2 } F(|\vec{\theta}|/\theta_s) \delta_D(z),\\
&  (s=1..N_s)
\end{split}
\end{equation}
where
\begin{equation}
F(x)=
\begin{cases}
-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{1}{(1-x^2)^{3/2}} \mathrm{arccosh} (\frac{x^2+c}{x(1+c)}) & (x<1),\\
\frac{\sqrt{c^2-1}}{3(1+c)} (1+\frac{1}{c+1}) & (x=1),\\
-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{1}{(x^2-1)^{3/2}} \mathrm{arccos} (\frac{x^2+c}{x(1+c)}) & (1<x\leq c),\\
0& (x>c).
\end{cases}
\end{equation}
and $f=1/[\ln (1+c)-c/(1+c)]$.

$\alpha_s$ is the corresponding decomposition coefficient of the density contrast field onto our basis atom. The total coefficients set is denoted as $\alpha=\begin{pmatrix}
\alpha_0\\
\alpha_1\\
...\\
\alpha_{N_s}
\end{pmatrix}$, and the total dictionary is $\Phi=\begin{pmatrix}
\phi_0, \phi_1, ..., \phi_{N_s}
\end{pmatrix}$.

We pixelize the parameter space into a $N_\theta \times N_\theta \times N_l$ grid. $N_\theta$ is the number of pixels on the two dimensions of the transverse plane and $N_l$ is the number of pixels on the line-of-sight direction for the lenses. Similarly, $\gamma_o$ is pixelized onto a $N_\theta \times N_\theta \times N_s$ grid, where $N_s$ is the number of pixel on the line-of-sight direction for the sources. 
The pixel size for the two dimensions on the transverse plane is denoted as $\Delta \theta$ and the pixel size for the line-of-sight direction is denoted as $\Delta z$.
Equation (\ref{eq-delta2gamma-operator-final}) changes to 
\begin{equation}\label{eq-alpha2gamma-operator}
\gamma=\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} \alpha +\epsilon.
\end{equation}

\subsection{Loss Function with Constrains}
The loss function is defined as
\begin{equation}\label{eq-lossFun}
L = \norm{\gamma-\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} \alpha}^2_2+\lambda \norm{\alpha}^1_1 + \tau\mathrm{TSV}(\alpha_0),
\end{equation}
where $\norm{\gamma-\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} \alpha}^2_2$ is the normal chi-square, $\norm{\alpha^{N,P}}^1_1$ is the sparsity constrain, and $\mathrm{TSV}(\alpha^P)$ is the Total Squared Variation (TSV) constrain. $\norm{\bullet}_1$ and $\norm{\bullet}_2$ represent $l_1$ norm and $l_2$ norm, respectively.
The $\mathrm{TSV}$ operator is defined as 
\begin{equation}
\begin{split}
\mathrm{TSV}(\alpha_0) =&  \sum_{ijk} \{ (\alpha_0[i,j,k]-\alpha_0[i+1,j,k])^2\\
&+(\alpha_0[i,j,k]-\alpha_0[i,j+1,k])^2\\
&+(\alpha_0[i,j,k]-\alpha_0[i,j,k+1])^2 \},
\end{split}
\end{equation}
where $i=1..N_\theta$, $j=1..N_\theta$, are the pixel indexes for the two dimensions on the transverse plane, $k=1..N_l$ is the pixel index on the line-of-sight direction.

We define 
\begin{equation}
\begin{split}
f(\alpha) &= \norm{\gamma-\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} \alpha}^2_2+ \tau\mathrm{TSV}(\alpha^P)\\
&= \sum_{lm} A_{lm} \alpha_l \alpha_m + \sum_{l}B_{l} \alpha_l +C,
\end{split}
\end{equation}
where $l,m$ go over the indexes of $(i,j,k,s)$.

\subsection{FISTA}
The basic FISTA algorithms is
\begin{equation}
X^{(n+1)}_m=\mathrm{ST}_{\lambda} (\alpha_m -\frac{\mu}{2A_{mm}} \frac{\partial f}{\partial \alpha_m})|_{\alpha^{(n)}_m} ,
\end{equation}
where 
\begin{equation}
\mathrm{ST}_{\lambda} (x) = \mathrm{sign} (x) \max (\abs{x}-\lambda,0)
\end{equation}
is the soft thresholding function.
\begin{equation}
\begin{split}
t^{(n+1)} &= \frac{1+\sqrt{1+4(t^{(n)})^2}}{2},\\
\alpha^{(n+1)}_m&=X^{(n+1)}_m+[\frac{t^{(n)}-1}{t^{(n+1)}}(X^{(n+1)}_m-X^{(n)}_m)],
\end{split}
\end{equation}
with $t^{(0)}=1$ and $X^{(0)}=\alpha^{(0)}$.
\section{Simulation}

\section{Results}
...
\section{Summary}
...
\bibliographystyle{aasjournal}
\bibliography{weak_lensing,lensCat,cosmoSim,cmbObs,gglens,shearCor,massMap,other}

\appendix
\section{General linear LASSO}
Note that the loss function defined in equation (\ref{eq-lossFun}) into 
\begin{equation}
L(\alpha)=f(\alpha) +\lambda \norm{\alpha}^1_1,
\end{equation}
where 
\begin{equation}
f(\vec{\alpha}) = \vec{\alpha}^T \mathbf{A} \vec{\alpha} + \vec{B} \cdot \vec{\alpha} +C.
\end{equation}
Using Einstein notation, we have
\begin{equation}
L(\alpha_i) = A_{ij} \alpha_i \alpha_j + B_{i} \alpha_i + C +\lambda_i \abs{\alpha_i}.
\end{equation}
Set the initial parameter vector is $\vec{\alpha}^{(0)}$. We focus on one specific parameter with index $\mu$ and fix other parameters with indexes $i \neq \mu$
\begin{equation}
L(\alpha_\mu| \alpha^{(0)}_{i\neq\mu})=A_{\mu\mu} \alpha_\mu^2 + (A_{i\mu}\alpha^{(0)}_i+A_{\mu i}\alpha^{(0)}_i +B_\mu) \alpha_\mu +\lambda_\mu \abs{\alpha_\mu} +B_i \alpha^{(0)}_i + \lambda_i \abs{\alpha^{(0)}_i} +C 
\end{equation}
reach its minimum at $\mathrm{ST}_{\lambda} (\alpha_\mu -\frac{\partial_\mu f(\alpha_\mu| \alpha^{(0)}_{i\neq\mu})}{2A_{\mu\mu}}) |_{\alpha_\mu^{(0)}}$,
where $\mathrm{ST}_{\lambda} (x) = \mathrm{sign} (x) \max (\abs{x}-\lambda,0)$ is the soft thresholding function. Then the parameter can be updated
\begin{equation}
\alpha^{(1)}_\mu \leftarrow \mathrm{ST}_{\lambda} (\alpha_\mu -\frac{\partial_\mu f(\alpha_\mu| \alpha^{(0)}_{i\neq\mu})}{2A_{\mu\mu}}) |_{\alpha_\mu^{(0)}}.
\end{equation}
Other parameters are subsequently updated in the same way. The minimum of the loss function can be reached by iterating the parameter update.

\end{document}

### 2019-11-05 python/halSim.py

@@ -1,0 +1,521 @@
+import cosmology
+import scipy.special as spfun
+import astropy.io.fits as pyfits
+
+#important constant
+C_LIGHT=2.99792458e8        # m/s
+GNEWTON=6.67428e-11         # m^3/kg/s^2
+KG_PER_SUN=1.98892e30       # kg/M_solar
+M_PER_PARSEC=3.08568025e16  # m/pc
+
+
+def four_pi_G_over_c_squared():
+    # = 1.5*H0^2/roh_0/c^2
+    # We want it return 4piG/c^2 in unit of Mpc/M_solar 
+    # in unit of m/kg
+    fourpiGoverc2 = 4.0*np.pi*GNEWTON/(C_LIGHT**2)
+    # in unit of pc/M_solar 
+    fourpiGoverc2 *= KG_PER_SUN/M_PER_PARSEC
+    # in unit of Mpc/M_solar
+    fourpiGoverc2 /= 1.e6
+    return fourpiGoverc2   
+
+
+class nfw_lensWB00():
+    """
+    Based on the integral functions of a spherical NFW profile: 
+    Wright & Brainerd(2000, ApJ, 534, 34)
+    
+    @param mass         Mass defined using a spherical overdensity of 200 times the critical density
+                        of the universe, in units of M_solar/h.
+    @param conc         Concentration parameter, i.e., ratio of virial radius to NFW scale radius.
+    @param redshift     Redshift of the halo.
+    @param ra           ra of halo center  [arcsec].
+    @param dec          dec of halo center [arcsec].
+    @param omega_m      Omega_matter to pass to Cosmology constructor. [default: 0.3]
+                        omega_lam is set to 1-omega_matter.
+    """
+    def __init__(self,mass,conc,redshift,ra,dec,omega_m=0.3):
+        self.cosmo=cosmology.Cosmo(h=1,omega_m=omega_m)
+        self.M = float(mass)
+        self.c = float(conc)
+        # \delta_c in equation (2)
+        self.delta_nfw  =200./3*self.c**3/(np.log(1+self.c)-(1.*self.c)/(1+self.c))
+        self.z = float(redshift)
+        # E(z)^{-1}
+        self.ezInv=self.cosmo.Ez_inverse(self.z)
+        # critical density 
+        # in unit of M_solar / Mpc^3
+        rho_cZ   = self.cosmo.rho0()/self.ezInv**2
+        # charateristic matter density within R200 at redshift z
+        # \delta_c \times \rho_c in equation (1),(11)
[…]

### 2019-11-07 python/halSim.py
halolet demo finished

@@ -1,3 +1,4 @@
+import numpy as np
 import cosmology
 import scipy.special as spfun
 import astropy.io.fits as pyfits
@@ -76,7 +77,6 @@ class nfw_lensWB00():
         arcsec2rad = np.pi/180./3600
         self.rs_arcsec = scale/arcsec2rad
         return
-    
     
     
     def __DdRs(self,ra_s,dec_s):
@@ -223,7 +223,6 @@ class nfw_lensWB00():
         DeltaSigma1 = -DeltaSigma*self.__cos2phi(ra_s,dec_s)
         DeltaSigma2 = -DeltaSigma*self.__sin2phi(ra_s,dec_s)
         return DeltaSigma1+1j*DeltaSigma2
-        
         
         
     def lensKernel(self,z_s):
@@ -515,7 +514,94 @@ class nfw_lensTJ03():
         rhoM_ave=self.cosmo.rho_m((z_bin_min+z_bin_max)/2.)
         DaBin=self.cosmo.Da(z_bin_min,z_bin_max)
         return rhoM_ave*DaBin
+    
+
+    def SigmaAtom(self,pix_scale,ngrid):
+        """NFW Atom
+        @param pix_scale    pixel sacle [arcsec]
+        @param ngrid        number of pixels on x and y axis
+        """
+        X   =   (np.arange(ngrid)-ngrid/2.)*pix_scale+self.ra
+        Y   =   (np.arange(ngrid)-ngrid/2.)*pix_scale+self.dec
+        x,y =   np.meshgrid(X,Y)
+        atomReal=self.Sigma(x.ravel(),y.ravel()).reshape((ngrid,ngrid))
+        return atomReal
+
+    def DeltaSigmaAtom(self,pix_scale,ngrid):
+        """NFW Atom
+        @param pix_scale    pixel sacle [arcsec]
+        @param ngrid        number of pixels on x and y axis
+        """
+        X   =   (np.arange(ngrid)-ngrid/2.)*pix_scale+self.ra
+        Y   =   (np.arange(ngrid)-ngrid/2.)*pix_scale+self.dec
+        x,y =   np.meshgrid(X,Y)
+        atomReal=self.DeltaSigma(x.ravel(),y.ravel()).reshape((ngrid,ngrid))
+        return atomReal
+
[…]

### 2019-11-20 python/haloSimOne.py
commi

@@ -1,0 +1,207 @@
+#!/usr/bin/env python
+#
+# LSST Data Management System
+# Copyright 20082014 LSST Corporation.
+#
+# This product includes software developed by the
+# LSST Project (http://www.lsst.org/).
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.    See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the LSST License Statement and
+# the GNU General Public License along with this program.  If not,
+# see <http://www.lsstcorp.org/LegalNotices/>.
+#
+# python lib
+import os
+import fitsio
+import galsim
+import glob
+import numpy as np
+from astropy.table import Table
+from configparser import ConfigParser
+
+# lsst Tasks
+import lsst.pex.config as pexConfig
+import lsst.pipe.base as pipeBase
+from lsst.pipe.base import TaskRunner
+from lsst.ctrl.pool.parallel import BatchPoolTask
+from lsst.ctrl.pool.pool import Pool, abortOnError
+
+class haloSimStampConfig(pexConfig.Config):
+    def setDefaults(self):
+        pexConfig.Config.setDefaults(self)
+    def validate(self):
+        pexConfig.Config.validate(self)
+
+class haloSimStampTask(pipeBase.CmdLineTask):
+    _DefaultName = "haloSimStamp"
+    ConfigClass = haloSimStampConfig
+    def __init__(self,**kwargs):
+        pipeBase.CmdLineTask.__init__(self, **kwargs)
+
+    @pipeBase.timeMethod
+    def run(self,configName,simDir):
+        parser      =   ConfigParser()
+        self.log.info('The configuration file used is:' configName)
+        parser.read(configName)
+
+        # cosmology
+        omega_m     =   parser.getfloat('cosmology','omega_m')
+        omega_l     =   parser.getfloat('cosmology','omega_l')
+        h_cos       =   parser.getfloat('cosmology','h_cos')
+
+        # sources
[…]

### 2020-02-20 bin/haloMultiSimStamp.py
make halolet

@@ -13,13 +13,12 @@ def getS16aZ(nobj):
     pdf     /=  np.sum(pdf)
     cdf     =   np.empty(nbin,dtype=float)
     np.cumsum(pdf,out=cdf)
-              
+
     # Monte Carlo z
     r       =   np.random.random(size=nobj)
     tzmc    =   np.empty(nobj, dtype=float)
     tzmc    =   np.interp(r, cdf, z_bins)
     return tzmc
-
 
 rangHalo=   range(2,3)
 isim    =   5
@@ -34,7 +33,7 @@ ns          =   int(size**2.*ns_per_arcmin+1)
 var_gErr    =   0.25
 x_s         =   np.random.random(ns)*size-size/2.
 y_s         =   np.random.random(ns)*size-size/2.
-z_s         =   getS16aZ(ns)#0.8 
+z_s         =   getS16aZ(ns)#0.8
 kappa_s     =   np.zeros(ns)
 g1_s        =   np.zeros(ns)
 g2_s        =   np.zeros(ns)
@@ -91,8 +90,8 @@ for ngrid in ngList: #(pix)
     g2Map_true  =   np.zeros((ngrid2,ngrid2))
     kMap_true   =   np.zeros((ngrid2,ngrid2))
     kMap_true2  =   np.zeros((ngrid2,ngrid2))# this is the true kMap
-    numMap      =   np.zeros((ngrid2,ngrid2),dtype=np.int)  
-    numMap2     =   np.zeros((ngrid2,ngrid2),dtype=np.int)  
+    numMap      =   np.zeros((ngrid2,ngrid2),dtype=np.int)
+    numMap2     =   np.zeros((ngrid2,ngrid2),dtype=np.int)
     xMin        =   -size
     yMin        =   -size
 
@@ -118,7 +117,6 @@ for ngrid in ngList: #(pix)
                 kMap_true[j,i]  =   kMap_true[j,i]/numMap[j,i]
             if numMap2[j,i]!=0:
                 kMap_true2[j,i]  =   kMap_true2[j,i]/numMap2[j,i]
-
 
     fitsio.write(os.path.join(simDir,'g1Map_grid%s.fits' %(ngrid)),g1Map_true)
     fitsio.write(os.path.join(simDir,'g2Map_grid%s.fits' %(ngrid)),g2Map_true)

### 2020-02-20 bin/testStampOne.py

@@ -1,0 +1,81 @@
+#!/usr/bin/env python
+import os
+import numpy as np
+import astropy.io.fits as pyfits
+from configparser import ConfigParser
+from sparseBase import massmapSparsityTask
+
+def pixelize(simSrc,parser):
+    fieldName   =   parser.get('file','fieldN')
+    pixDir      =   parser.get('file','pixDir')
+    g1Fname     =   os.path.join(pixDir,'g1Map_%s.fits' %fieldName)
+    g2Fname     =   os.path.join(pixDir,'g2Map_%s.fits' %fieldName)
+    nFname      =   os.path.join(pixDir,'nMap_%s.fits'  %fieldName)
+
+    if os.path.exists(nFname):
+        print('Alreadying have pixelized shear field')
+        return
+
+    if parser.has_option('transPlane','raname'):
+        raname  =   parser.get('transPlane','raname')
+    else:
+        raname  =   'ra'
+    if parser.has_option('transPlane','decname'):
+        decname=   parser.get('transPlane','decname')
+    else:
+        decname =   'dec'
+    if parser.has_option('sourceZ','zname'):
+        zname   =   parser.get('sourceZ','zname')
+    else:
+        zname   =   'z'
+    g1name  =   'g1'
+    g2name  =   'g2'
+
+    xMin    =   parser.getfloat('transPlane','xMin')
+    yMin    =   parser.getfloat('transPlane','yMin')
+    scale   =   parser.getfloat('transPlane','scale')
+    ny      =   parser.getint('transPlane'  ,'ny')
+    nx      =   parser.getint('transPlane'  ,'nx')
+    zMin    =   parser.getfloat('sourceZ','zMin')
+    zscale  =   parser.getfloat('sourceZ','zscale')
+    nz      =   parser.getint('sourceZ','nz')
+    shapeS  =   (nz,ny,nx)
+    nSim    =   np.zeros(shapeS)
+    g1Sim   =   np.zeros(shapeS)
+    g2Sim   =   np.zeros(shapeS)
+    for ss in simSrc:
+        ix  =   int((ss[raname]-xMin)//scale)
+        iy  =   int((ss[decname]-yMin)//scale)
+        iz  =   int((ss[zname]-zMin)//zscale)
+        if iz>=0 and iz<nz:
[…]

### 2020-02-20 python/binSplit.py

@@ -39,15 +39,13 @@ class binSplitBatchConfig(pexConfig.Config):
     nSim    =   pexConfig.Field(dtype=int, default=100, doc="number of realization")
     def setDefaults(self):
         pexConfig.Config.setDefaults(self)
-
 class binSplitRunner(TaskRunner):
     @staticmethod
     def getTargetList(parsedCmd, **kwargs):
-        configDir    =  parsedCmd.configDir 
+        configDir    =  parsedCmd.configDir
         ##!NOTE: only try on VVDS
         configList= os.popen('ls %s* |grep VVDS.ini ' %configDir).readlines()
         return [(ref, kwargs) for ref in configList]
-
 def unpickle(factory, args, kwargs):
     """Unpickle something by calling a factory"""
     return factory(*args, **kwargs)
@@ -61,7 +59,7 @@ class binSplitBatchTask(BatchPoolTask):
         """Pickler"""
         return unpickle, (self.__class__, [], dict(config=self.config, name=self._name,
                 parentTask=self._parentTask, log=self.log))
-    
+
     def __init__(self,**kwargs):
         BatchPoolTask.__init__(self, **kwargs)
 
@@ -72,10 +70,10 @@ class binSplitBatchTask(BatchPoolTask):
         parser.read(configName)
         fieldName   =   parser.get('file','fieldN')
         pixDir      =   parser.get('file','pixDir')
-        ##!NOTE: the mock grid file is saved under pix directroy 
-        ##since changing lbd does not require new pixelation 
-        ##changing nframe only change sigmaA and 
-        ##also does not need new pixelation 
+        ##!NOTE: the mock grid file is saved under pix directroy
+        ##since changing lbd does not require new pixelation
+        ##changing nframe only change sigmaA and
+        ##also does not need new pixelation
         ##changing pix_size change shearAll and sigmaA
         ##which need new pixelation
         self.log.info('processing field: %s' %fieldName)
@@ -129,8 +127,8 @@ class binSplitBatchTask(BatchPoolTask):
         zMin    =   parser.getfloat('sourceZ','zMin')
         zscale  =   parser.getfloat('sourceZ','zscale')
         nz      =   parser.getint('sourceZ','nz')
-        shapeS  =   (nz,ny,nx)   
-        nSim    =   np.zeros(shapeS)  
+        shapeS  =   (nz,ny,nx)
+        nSim    =   np.zeros(shapeS)
         g1Sim   =   np.zeros(shapeS)
[…]

### 2020-02-20 python/glInverse2D_s16a.py

@@ -41,37 +41,31 @@ class glInverse2D_s16aBatchConfig(pexConfig.Config):
     def setDefaults(self):
         pexConfig.Config.setDefaults(self)
 
-
 class glInverse2D_s16aRunner(TaskRunner):
     @staticmethod
     def getTargetList(parsedCmd, **kwargs):
-        return [(ref, kwargs) for ref in range(1)] 
-
+        return [(ref, kwargs) for ref in range(1)]
 def unpickle(factory, args, kwargs):
     """Unpickle something by calling a factory"""
     return factory(*args, **kwargs)
-
 class glInverse2D_s16aBatchTask(BatchPoolTask):
     ConfigClass = glInverse2D_s16aBatchConfig
     RunnerClass = glInverse2D_s16aRunner
     _DefaultName = "glInverse2D_s16aBatch"
-
     def __init__(self,**kwargs):
         BatchPoolTask.__init__(self, **kwargs)
-    
     def __reduce__(self):
         """Pickler"""
         return unpickle, (self.__class__, [], dict(config=self.config, name=self._name,
                 parentTask=self._parentTask, log=self.log))
 
-    
     @abortOnError
     def run(self,Id):
         lbd     =   self.config.lambdaR
         glDir   =   './s16a2D/lambda_%s/' % lbd
         if not os.path.exists(glDir):
             os.mkdir(glDir)
-        fieldList   =  np.load('/work/xiangchong.li/work/S16AFPFS/fieldInfo.npy').item().keys() 
+        fieldList   =  np.load('/work/xiangchong.li/work/S16AFPFS/fieldInfo.npy').item().keys()
         pool    =   Pool("glInverse2D_s16aBatch")
         pool.cacheClear()
         pool.storeSet(lbd=lbd)
@@ -99,8 +93,7 @@ class glInverse2D_s16aBatchTask(BatchPoolTask):
         ngrid   =   max(ngridX,ngridY)
         size    =   pix_scale*ngrid
         outDict =   {'raCent':raCen,'decCent':decCen,'size':size,'ngridX':ngridX,'ngridY':ngridY,'ngrid':ngrid}
-        return outDict 
-
+        return outDict
 
     def makeMaskMap(self,raCen,decCen,pix_scale,ngrid,catRG):
         xMin    =   raCen   -   pix_scale*ngrid/2
@@ -115,7 +108,6 @@ class glInverse2D_s16aBatchTask(BatchPoolTask):
         maskMap =   (maskMap>=2).astype(int)
         return maskMap
 
-
[…]

### 2020-02-20 python/glInverse3D_s16a.py

@@ -41,37 +41,31 @@ class glInverse3D_s16aBatchConfig(pexConfig.Config):
     def setDefaults(self):
         pexConfig.Config.setDefaults(self)
 
-
 class glInverse3D_s16aRunner(TaskRunner):
     @staticmethod
     def getTargetList(parsedCmd, **kwargs):
-        return [(ref, kwargs) for ref in range(1)] 
-
+        return [(ref, kwargs) for ref in range(1)]
 def unpickle(factory, args, kwargs):
     """Unpickle something by calling a factory"""
     return factory(*args, **kwargs)
-
 class glInverse3D_s16aBatchTask(BatchPoolTask):
     ConfigClass = glInverse3D_s16aBatchConfig
     RunnerClass = glInverse3D_s16aRunner
     _DefaultName = "glInverse3D_s16aBatch"
-
     def __init__(self,**kwargs):
         BatchPoolTask.__init__(self, **kwargs)
-    
     def __reduce__(self):
         """Pickler"""
         return unpickle, (self.__class__, [], dict(config=self.config, name=self._name,
                 parentTask=self._parentTask, log=self.log))
 
-    
     @abortOnError
     def run(self,Id):
         lbd     =   self.config.lambdaR
         glDir   =   './s16a3D/lambda_%s/' % lbd
         if not os.path.exists(glDir):
             os.mkdir(glDir)
-        fieldList   =  np.load('/work/xiangchong.li/work/S16AFPFS/fieldInfo.npy').item().keys() 
+        fieldList   =  np.load('/work/xiangchong.li/work/S16AFPFS/fieldInfo.npy').item().keys()
         pool    =   Pool("glInverse3D_s16aBatch")
         pool.cacheClear()
         pool.storeSet(lbd=lbd)
@@ -99,8 +93,7 @@ class glInverse3D_s16aBatchTask(BatchPoolTask):
         ngrid   =   max(ngridX,ngridY)
         size    =   pix_scale*ngrid
         outDict =   {'raCent':raCen,'decCent':decCen,'size':size,'ngridX':ngridX,'ngridY':ngridY,'ngrid':ngrid}
-        return outDict 
-
+        return outDict
 
     def makeMaskMap(self,raCen,decCen,pix_scale,ngrid,catRG):
         xMin    =   raCen   -   pix_scale*ngrid/2
@@ -115,7 +108,6 @@ class glInverse3D_s16aBatchTask(BatchPoolTask):
         maskMap =   (maskMap>=2).astype(int)
         return maskMap
 
-
[…]

### 2020-02-20 python/haloSim.py

@@ -11,20 +11,20 @@ M_PER_PARSEC=3.08568025e16  # m/pc
 
 def four_pi_G_over_c_squared():
     # = 1.5*H0^2/roh_0/c^2
-    # We want it return 4piG/c^2 in unit of Mpc/M_solar 
+    # We want it return 4piG/c^2 in unit of Mpc/M_solar
     # in unit of m/kg
     fourpiGoverc2 = 4.0*np.pi*GNEWTON/(C_LIGHT**2)
-    # in unit of pc/M_solar 
+    # in unit of pc/M_solar
     fourpiGoverc2 *= KG_PER_SUN/M_PER_PARSEC
     # in unit of Mpc/M_solar
     fourpiGoverc2 /= 1.e6
-    return fourpiGoverc2   
+    return fourpiGoverc2
 
 class nfw_lensWB00():
     """
-    Based on the integral functions of a spherical NFW profile: 
+    Based on the integral functions of a spherical NFW profile:
     Wright & Brainerd(2000, ApJ, 534, 34)
-    
+
     @param mass         Mass defined using a spherical overdensity of 200 times the critical density
                         of the universe, in units of M_solar/h.
     @param conc         Concentration parameter, i.e., ratio of virial radius to NFW scale radius.
@@ -43,7 +43,7 @@ class nfw_lensWB00():
         self.z = float(redshift)
         # E(z)^{-1}
         self.ezInv=self.cosmo.Ez_inverse(self.z)
-        # critical density 
+        # critical density
         # in unit of M_solar / Mpc^3
         rho_cZ   = self.cosmo.rho0()/self.ezInv**2
         # charateristic matter density within R200 at redshift z
@@ -58,13 +58,13 @@ class nfw_lensWB00():
 
         # First we get the virial radius, which is defined for some spherical overdensity as
         # 3 M / [4 pi (r_vir)^3] = overdensity
-        # Here we have overdensity = 200 * rhocrit, to determine R200 (angular distance). 
-        # The factor of 1.63e-5 comes from the following set of prefactors: 
-        # (3 / (4 pi * 200 * rhocrit))^(1/3), where rhocrit = 2.8e11 h^2 M_solar / Mpc^3. 
[…]

### 2020-02-20 python/halo_wavelet.py

@@ -1,8 +1,34 @@
+import os
 import numpy as np
 import astropy.io.fits as pyfits
 
 class starlet2D():
-    def __init__(self,gen=2,nframe=4,ny=64,nx=64):
+    """
+    A Class for 2D nfwlet transform
+    --------
+
+    Construction Keywords
+    -------
+    nframe  :   number of frames
+    ngrid   :   size of the field (pixel)
+    smooth_scale:   scale radius of Gaussian smoothing kernal (pixel)
+    pltDir  :   whether plot the atoms for demonstration
+
+    Methods
+    --------
+    itransform:
+
+    itranspose:
+
+    transform:
+
+    transpose:
+
+    Examples
+    --------
+    halolet.nfwlet2D(pltDir='plot')
+    """
+    def __init__(self,gen=2,nframe=4,ny=64,nx=64,pltDir=None):
         Coeff_h0 = 3. / 8.;
         Coeff_h1 = 1. / 4.;
         Coeff_h2 = 1. / 16.;
@@ -14,9 +40,13 @@ class starlet2D():
         self.nx=nx
         self.gen=gen
         self.shape=(nframe,ny,nx)
+        if os.path.exists(pltDir):
+            self.pltDir=pltDir
+        else:
+            self.pltDir=None
         self.prepareFrames()
-        
-    def prepareFrames(self,doPlot=False):
+
+    def prepareFrames(self):
         self.frames=np.zeros(self.shape)
         self.aframes=np.zeros(self.shape)
         self.frames[0,0,0]=1
@@ -56,15 +86,14 @@ class starlet2D():
         for iframe in range(self.nframe):
             self.fouframes[iframe,:,:]=np.fft.fft2(self.frames[iframe,:,:]).real
             self.fouaframes[iframe,:,:]=np.fft.fft2(self.aframes[iframe,:,:]).real
-            
-        if doPlot:
-            self.framesShow=np.zeros(self.shape)
-            for iframe in range(self.nframe):
-                self.framesShow[iframe,:,:]=np.fft.fftshift(np.fft.ifft2(self.fouframes[iframe]).real )
-            pyfits.writeto('starlet2-gen%d-nframe%d.fits' %(self.gen,self.nframe), self.frames )
-            pyfits.writeto('starlet2-Fou-gen%d-nframe%d.fits' %(self.gen,self.nframe), self.framesShow)
+
+        if self.pltDir:
[…]

### 2020-02-20 python/halolet.py

@@ -1,0 +1,100 @@
+import os
+import haloSim
+import numpy as np
+import astropy.io.fits as pyfits
+
+class nfwlet2D():
+    """
+    A Class for 2D nfwlet transform
+    --------
+
+    Construction Keywords
+    -------
+    nframe  :   number of frames
+    ngrid   :   size of the field (pixel)
+    smooth_scale:   scale radius of Gaussian smoothing kernal (pixel)
+    pltDir  :   whether plot the atoms for demonstration
+
+    Methods
+    --------
+    itransform:
+
+    itranspose:
+
+
+    Examples
+    --------
+    halolet.nfwlet2D(pltDir='plot')
+    """
+    def __init__(self,nframe=4,ngrid=64,smooth_scale=3,pltDir=None):
+        assert ngrid%2==0,\
+                'Please make sure nx and ny are even numbers'
+        """
+        We force ny=nx, the user should ensure that by padding 0
+        """
+        self.nx=ngrid
+        self.ny=ngrid
+        self.nframe=nframe
+        self.smooth_scale=smooth_scale
+        # shape of output shapelets
+        self.shape2=(ngrid,ngrid)
+        self.shape3=(nframe,ngrid,ngrid)
+        if os.path.exists(pltDir):
+            self.pltDir=pltDir
+        else:
+            self.pltDir=None
+        self.prepareFrames()
+
+    def prepareFrames(self):
+        # Real Space
+        self.fouaframes=np.zeros(self.shape3)
+        self.aframes=np.zeros(self.shape3)
+        # The first frame is Gaussian atom accounting for the smoothing
+        self.fouaframes[0,:,:]=haloSim.GausAtom(sigma=self.smooth_scale,ngrid=self.ny,fou=True)
+        self.aframes[0,:,:]=haloSim.GausAtom(sigma=self.smooth_scale,ngrid=self.ny,fou=False)
+
+        for iframe in range(self.nframe-1):
+            iAtomF=haloSim.haloCS02SigmaAtom(r_s=iframe+1,ngrid=self.ny,c=9.,smooth_scale=self.smooth_scale)
+            self.fouaframes[iframe+1,:,:]=iAtomF
+            self.aframes[iframe+1,:,:]=np.real(np.fft.ifft2(iAtomF))
+
+        if self.pltDir:
+            afname  =   os.path.join(self.pltDir,'nfwAtom-nframe%d.fits' %(self.nframe))
+            pyfits.writeto(afname, self.aframes )
[…]

### 2020-02-20 python/sparse3D.py

@@ -49,7 +49,6 @@ from lsst.ctrl.pool.pool import Pool, abortOnError
 class sparse3DConfig(pexConfig.Config):
     def setDefaults(self):
         pexConfig.Config.setDefaults(self)
-    
     def validate(self):
         pexConfig.Config.validate(self)
 
@@ -74,7 +73,7 @@ class sparse3DTask(pipeBase.CmdLineTask):
         lbd         =   parser.getfloat('sparse','lbd')
         outFname    =   os.path.join(simDir,'kappaMap_3D_lbd%s_m%d_z%d.fits'%(lbd,m_id,z_id))
         if os.path.exists(outFname):
-           massMap  =   pyfits.getdata(outFname) 
+           massMap  =   pyfits.getdata(outFname)
         else:
             sources     =   pyfits.getdata(srcFname)
             sparse3D    =   massmapSparsityTask(sources,parser)
@@ -83,7 +82,7 @@ class sparse3DTask(pipeBase.CmdLineTask):
             pyfits.writeto(outFname,massMap,overwrite=True)
         zyx         =   np.argmax(massMap)
         iz,iy,ix    =   np.unravel_index(zyx,massMap.shape)
-        return (M200,z_cl,ix,iy,iz) 
+        return (M200,z_cl,ix,iy,iz)
 
     @classmethod
     def _makeArgumentParser(cls):
@@ -92,16 +91,12 @@ class sparse3DTask(pipeBase.CmdLineTask):
         doBatch = kwargs.pop("doBatch", False)
         parser = pipeBase.ArgumentParser(name=cls._DefaultName)
         return parser
-
     def writeConfig(self, butler, clobber=False, doBackup=False):
         pass
-
     def writeSchemas(self, butler, clobber=False, doBackup=False):
         pass
-
     def writeMetadata(self, dataRef):
         pass
-
     def writeEupsVersions(self, butler, clobber=False, doBackup=False):
         pass
 
@@ -114,35 +109,30 @@ class sparse3DBatchConfig(pexConfig.Config):
                 doc = 'directory to store exposures')
     def setDefaults(self):
         pexConfig.Config.setDefaults(self)
-    
     def validate(self):
         pexConfig.Config.validate(self)
         if not os.path.exists(self.simDir):
             self.log.info('Do not have %s' %self.simDir)
-    
+
 class sparse3DRunner(TaskRunner):
     @staticmethod
     def getTargetList(parsedCmd, **kwargs):
-        return [(ref, kwargs) for ref in range(1)] 
-
[…]

### 2020-02-20 python/sparse3D_s16a.py

@@ -45,29 +45,24 @@ class sparse3D_s16aBatchConfig(pexConfig.Config):
 class sparse3D_s16aRunner(TaskRunner):
     @staticmethod
     def getTargetList(parsedCmd, **kwargs):
-        return [(ref, kwargs) for ref in range(1)] 
-
+        return [(ref, kwargs) for ref in range(1)]
 def unpickle(factory, args, kwargs):
     """Unpickle something by calling a factory"""
     return factory(*args, **kwargs)
-
 class sparse3D_s16aBatchTask(BatchPoolTask):
     ConfigClass = sparse3D_s16aBatchConfig
     RunnerClass = sparse3D_s16aRunner
     _DefaultName = "sparse3D_s16aBatch"
-
     def __init__(self,**kwargs):
         BatchPoolTask.__init__(self, **kwargs)
-    
     def __reduce__(self):
         """Pickler"""
         return unpickle, (self.__class__, [], dict(config=self.config, name=self._name,
                 parentTask=self._parentTask, log=self.log))
 
-    
     @abortOnError
     def runDataRef(self,Id):
-        fieldList   =  np.load('fieldInfo.npy',allow_pickle=True).item().keys() 
+        fieldList   =  np.load('fieldInfo.npy',allow_pickle=True).item().keys()
         pool    =   Pool("sparse3D_s16aBatch")
         pool.cacheClear()
         obsDir  =   self.config.obsDir
@@ -88,9 +83,8 @@ class sparse3D_s16aBatchTask(BatchPoolTask):
 
         configName  =   'config_lbd%.1f_%s.ini' %(lbd,fieldName)
         configName  =   os.path.join(obsDir,configName)
-        
 
-        inFname     =   './s16aPre/%s_RG.fits' %fieldName  
+        inFname     =   './s16aPre/%s_RG.fits' %fieldName
         sources     =   pyfits.getdata(inFname)
 
         parser      =   ConfigParser()
@@ -98,31 +92,25 @@ class sparse3D_s16aBatchTask(BatchPoolTask):
         sparse3D    =   massmapSparsityTask(sources,parser)
         sparse3D.process()
         sparse3D.write()
-        
+        return
+
     @classmethod
     def _makeArgumentParser(cls, *args, **kwargs):
         kwargs.pop("doBatch", False)
         parser = ArgumentParser(name=cls._DefaultName)
         return parser
-    
     @classmethod
     def writeConfig(self, butler, clobber=False, doBackup=False):
         pass
-    
[…]

### 2020-02-20 python/sparseBase.py

@@ -1,10 +1,14 @@
 import os
 import lsst.log
 import numpy as np
-#NOTE: My version of cosmology
 import cosmology
 import astropy.io.fits as pyfits
-from halo_wavelet import * 
+from halo_wavelet import starlet2D
+from halolet import nfwlet2D
+
+"""
+Useful functions
+"""
 
 def zMeanBin(zMin,dz,nz):
     return np.arange(zMin,zMin+dz*nz,dz)+dz/2.
@@ -27,8 +31,6 @@ def my_thresholding(dum,thresholds):
     dum[mask]=  np.sign(dum[mask])*(abs(dum[mask])-thresholds[mask]**2./abs(dum[mask]))
     return dum
 
-
-
 class massmap_ks2D():
     def __init__(self,ny,nx):
         self.shape   =   (ny,nx)
@@ -47,8 +49,8 @@ class massmap_ks2D():
                     e2phiF[j,i]    =   np.complex((ix**2.-jy**2.),2.*ix*jy)/(ix**2.+jy**2.)
                 else:
                     e2phiF[j,i]    =   1.
-        return e2phiF*np.pi    
-        
+        return e2phiF*np.pi
+
     def itransform(self,gMap,inFou=True,outFou=True):
         assert gMap.shape==self.shape
         if not inFou:
@@ -67,8 +69,6 @@ class massmap_ks2D():
             gOMap    =   np.fft.ifft2(gOMap)
         return gOMap
 
-
-
 class massmap_sparsity_2D():
     def __init__(self,shearR,nMap,nframe=4,lbd=4,doDebug=False):
         self.lbd   = lbd
@@ -77,11 +77,11 @@ class massmap_sparsity_2D():
         self.nframe= nframe
         self.ny    = ny
         self.nx    = nx
-        
+
         #make subtasks
         self.star2D= starlet2D(gen=2,nframe=nframe,ny=ny,nx=nx)
         self.ks2D  = massmap_ks2D(ny,nx)
-        
+
         self.shearR= shearR
         self.nMap  = nMap
         self.mask  = (nMap>0.1).astype(np.int)
@@ -89,14 +89,14 @@ class massmap_sparsity_2D():
         self.doDebug=    doDebug
         if self.doDebug:
             pyfits.writeto('sigmaAlpha.fits',self.sigmaA,overwrite=True)
-        
-        
+
+
         self.alphaR= np.zeros(self.shape)
[…]

### 2020-02-20 python/halo_wavelet.py
commit

@@ -40,10 +40,7 @@ class starlet2D():
         self.nx=nx
         self.gen=gen
         self.shape=(nframe,ny,nx)
-        if os.path.exists(pltDir):
-            self.pltDir=pltDir
-        else:
-            self.pltDir=None
+        self.pltDir=pltDir
         self.prepareFrames()
 
     def prepareFrames(self):

### 2020-02-20 python/halolet.py

@@ -39,10 +39,7 @@ class nfwlet2D():
         # shape of output shapelets
         self.shape2=(ngrid,ngrid)
         self.shape3=(nframe,ngrid,ngrid)
-        if os.path.exists(pltDir):
-            self.pltDir=pltDir
-        else:
-            self.pltDir=None
+        self.pltDir=pltDir
         self.prepareFrames()
 
     def prepareFrames(self):
@@ -87,7 +84,7 @@ class nfwlet2D():
         """
         assert dataIn.shape==(self.ny,self.nx),\
                 'input should have shape2 (ny,nx)'
-        dataOut=np.empty(self.shape)
+        dataOut=np.empty(self.shape3)
         if not inFou:
             dataTmp=np.fft.fft2(dataIn)
         else:

### 2020-02-20 python/sparseBase.py

@@ -430,7 +430,8 @@ class massmapSparsityTask():
         self.shearR     =   g1Map+np.complex128(1j)*g2Map
 
         #make subtasks
-        self.star2D =   starlet2D(gen=2,nframe=self.nframe,ny=self.ny,nx=self.nx)
+        #self.star2D =   starlet2D(gen=2,nframe=self.nframe,ny=self.ny,nx=self.nx)
+        self.star2D =   nfwlet2D(nframe=self.nframe,ngrid=self.nx,smooth_scale=-1)
         self.ks2D   =   massmap_ks2D(self.ny,self.nx)
         if parser.has_option('sparse','mu'):
             self.mu =   parser.getfloat('sparse','mu')

### 2020-03-09 notebook/sparseBase.tex
add demo for sparseBase.py

\documentclass[11pt]{article}

    \usepackage[breakable]{tcolorbox}
    \tcbset{nobeforeafter} % prevents tcolorboxes being placing in paragraphs
    \usepackage{float}
    \floatplacement{figure}{H} % forces figures to be placed at the correct location

    \usepackage[T1]{fontenc}
    % Nicer default font (+ math font) than Computer Modern for most use cases
    \usepackage{mathpazo}

    % Basic figure setup, for now with no caption control since it's done
    % automatically by Pandoc (which extracts ![](path) syntax from Markdown).
    \usepackage{graphicx}
    % We will generate all images so they have a width \maxwidth. This means
    % that they will get their normal width if they fit onto the page, but
    % are scaled down if they would overflow the margins.
    \makeatletter
    \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
    \else\Gin@nat@width\fi}
    \makeatother
    \let\Oldincludegraphics\includegraphics
    % Set max figure width to be 80% of text width, for now hardcoded.
    \renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=.8\maxwidth]{#1}}
    % Ensure that by default, figures have no caption (until we provide a
    % proper Figure object with a Caption API and a way to capture that
    % in the conversion process - todo).
    \usepackage{caption}
    \DeclareCaptionLabelFormat{nolabel}{}
    \captionsetup{labelformat=nolabel}

    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines
    \usepackage{mathrsfs}

    % Colors for the hyperref package
    \definecolor{urlcolor}{rgb}{0,.145,.698}
    \definecolor{linkcolor}{rgb}{.71,0.21,0.01}
    \definecolor{citecolor}{rgb}{.12,.54,.11}

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}
    \definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
    \definecolor{ansi-default-inverse-bg}{HTML}{000000}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Additional commands for more recent versions of Pandoc
    \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
    \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
    \newcommand{\ImportTok}[1]{{#1}}
    \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
    \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
    \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
    \newcommand{\BuiltInTok}[1]{{#1}}
    \newcommand{\ExtensionTok}[1]{{#1}}
    \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
    \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
    \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatibility definitions
    \def\gt{>}
    \def\lt{<}
    \let\Oldtex\TeX
    \let\Oldlatex\LaTeX
    \renewcommand{\TeX}{\textrm{\Oldtex}}
    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
    % Document parameters
    % Document title
    \title{sparseBase}

% Pygments definitions
\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % For linebreaks inside Verbatim environment from package fancyvrb. 
    \makeatletter
        \newbox\Wrappedcontinuationbox 
        \newbox\Wrappedvisiblespacebox 
        \newcommand*\Wrappedvisiblespace {\textcolor{red}{\textvisiblespace}} 
        \newcommand*\Wrappedcontinuationsymbol {\textcolor{red}{\llap{\tiny$\m@th\hookrightarrow$}}} 
        \newcommand*\Wrappedcontinuationindent {3ex } 
        \newcommand*\Wrappedafterbreak {\kern\Wrappedcontinuationindent\copy\Wrappedcontinuationbox} 
        % Take advantage of the already applied Pygments mark-up to insert 
        % potential linebreaks for TeX processing. 
        %        {, <, #, %, $, ' and ": go to next line. 
        %        _, }, ^, &, >, - and ~: stay at end of broken line. 
        % Use of \textquotesingle for straight quote. 
        \newcommand*\Wrappedbreaksatspecials {% 
            \def\PYGZus{\discretionary{\char`\_}{\Wrappedafterbreak}{\char`\_}}% 
            \def\PYGZob{\discretionary{}{\Wrappedafterbreak\char`\{}{\char`\{}}% 
            \def\PYGZcb{\discretionary{\char`\}}{\Wrappedafterbreak}{\char`\}}}% 
            \def\PYGZca{\discretionary{\char`\^}{\Wrappedafterbreak}{\char`\^}}% 
            \def\PYGZam{\discretionary{\char`\&}{\Wrappedafterbreak}{\char`\&}}% 
            \def\PYGZlt{\discretionary{}{\Wrappedafterbreak\char`\<}{\char`\<}}% 
            \def\PYGZgt{\discretionary{\char`\>}{\Wrappedafterbreak}{\char`\>}}% 
            \def\PYGZsh{\discretionary{}{\Wrappedafterbreak\char`\#}{\char`\#}}% 
            \def\PYGZpc{\discretionary{}{\Wrappedafterbreak\char`\%}{\char`\%}}% 
            \def\PYGZdl{\discretionary{}{\Wrappedafterbreak\char`\$}{\char`\$}}% 
            \def\PYGZhy{\discretionary{\char`\-}{\Wrappedafterbreak}{\char`\-}}% 
            \def\PYGZsq{\discretionary{}{\Wrappedafterbreak\textquotesingle}{\textquotesingle}}% 
            \def\PYGZdq{\discretionary{}{\Wrappedafterbreak\char`\"}{\char`\"}}% 
            \def\PYGZti{\discretionary{\char`\~}{\Wrappedafterbreak}{\char`\~}}% 
        } 
        % Some characters . , ; ? ! / are not pygmentized. 
        % This macro makes them "active" and they will insert potential linebreaks 
        \newcommand*\Wrappedbreaksatpunct {% 
            \lccode`\~`\.\lowercase{\def~}{\discretionary{\hbox{\char`\.}}{\Wrappedafterbreak}{\hbox{\char`\.}}}% 
            \lccode`\~`\,\lowercase{\def~}{\discretionary{\hbox{\char`\,}}{\Wrappedafterbreak}{\hbox{\char`\,}}}% 
            \lccode`\~`\;\lowercase{\def~}{\discretionary{\hbox{\char`\;}}{\Wrappedafterbreak}{\hbox{\char`\;}}}% 
            \lccode`\~`\:\lowercase{\def~}{\discretionary{\hbox{\char`\:}}{\Wrappedafterbreak}{\hbox{\char`\:}}}% 
            \lccode`\~`\?\lowercase{\def~}{\discretionary{\hbox{\char`\?}}{\Wrappedafterbreak}{\hbox{\char`\?}}}% 
            \lccode`\~`\!\lowercase{\def~}{\discretionary{\hbox{\char`\!}}{\Wrappedafterbreak}{\hbox{\char`\!}}}% 
            \lccode`\~`\/\lowercase{\def~}{\discretionary{\hbox{\char`\/}}{\Wrappedafterbreak}{\hbox{\char`\/}}}% 
            \catcode`\.\active
            \catcode`\,\active 
            \catcode`\;\active
            \catcode`\:\active
            \catcode`\?\active
            \catcode`\!\active
            \catcode`\/\active 
            \lccode`\~`\~ 	
        }
    \makeatother

    \let\OriginalVerbatim=\Verbatim
    \makeatletter
    \renewcommand{\Verbatim}[1][1]{%
        %\parskip\z@skip
        \sbox\Wrappedcontinuationbox {\Wrappedcontinuationsymbol}%
        \sbox\Wrappedvisiblespacebox {\FV@SetupFont\Wrappedvisiblespace}%
        \def\FancyVerbFormatLine ##1{\hsize\linewidth
            \vtop{\raggedright\hyphenpenalty\z@\exhyphenpenalty\z@
                \doublehyphendemerits\z@\finalhyphendemerits\z@
                \strut ##1\strut}%
        }%
        % If the linebreak is at a space, the latter will be displayed as visible
        % space at end of first line, and a continuation symbol starts next line.
        % Stretch/shrink are however usually zero for typewriter font.
        \def\FV@Space {%
            \nobreak\hskip\z@ plus\fontdimen3\font minus\fontdimen4\font
            \discretionary{\copy\Wrappedvisiblespacebox}{\Wrappedafterbreak}
            {\kern\fontdimen2\font}%
        }%

        % Allow breaks at special characters using \PYG... macros.
        \Wrappedbreaksatspecials
        % Breaks at punctuation characters . , ; ? ! and / need catcode=\active 	
        \OriginalVerbatim[#1,codes*=\Wrappedbreaksatpunct]%
    }
    \makeatother

    % Exact colors from NB
    \definecolor{incolor}{HTML}{303F9F}
    \definecolor{outcolor}{HTML}{D84315}
    \definecolor{cellborder}{HTML}{CFCFCF}
    \definecolor{cellbackground}{HTML}{F7F7F7}

    % prompt
    \newcommand{\prompt}[4]{
        \llap{{\color{#2}[#3]: #4}}\vspace{-1.25em}
    }

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=urlcolor,
      linkcolor=linkcolor,
      citecolor=citecolor,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

    \begin{document}

    \maketitle

    \hypertarget{general-lasso}{%
\section{General LASSO}\label{general-lasso}}

\[L(\vec{x})=\frac{1}{2}(y_{i}-A^{*}_{ij}x_{j})(y_{i}-A_{ik}x_{k})+\frac{\lambda_2}{2}[(D^{1}_{ij} x_{j})(D^{1}_{ik}x_{k})+ (D^{2}_{ij} x_{j})(D^{2}_{ik}x_{k})]+ \lambda_1 \sigma_i |x_i|,\]

where \(x_i\) is the i-th component of real vector \(\vec{x}\),
\(A_{ij}\) and \(D^{1,2}_{ij}\) are the \((i,j)\) component of matrix
\(\mathbf{A}\) and \(\mathbf{D^{1,2}}\). \(A_{ij}\) is complex number
whereas \(D^{1,2}_{ij}\) are real number. \(A^{*}_{ij}\) is used to
denote the conjugate of \(A_{ij}\).

\(\mathbf{A}\) refers to the transformation operator from the real
dictionary field to the observed complex shear field. Note that we do
not consider \(B\) mode so \(x\) is a real vector.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# sparseBase.massmapSparsityTask.__init__}
\CommentTok{## Initialization of the Dictionary Space (A)}
\CommentTok{# 1) Basis vector used to model the Surface Density of halo  }
\ControlFlowTok{if}\NormalTok{ dicname}\OperatorTok{==}\StringTok{'starlet'}\NormalTok{:}
    \ImportTok{from}\NormalTok{ halolet }\ImportTok{import}\NormalTok{ starlet2D}
    \VariableTok{self}\NormalTok{.dict2D }\OperatorTok{=}\NormalTok{   starlet2D(gen}\OperatorTok{=}\DecValTok{2}\NormalTok{,nframe}\OperatorTok{=}\VariableTok{self}\NormalTok{.nframe,ny}\OperatorTok{=}\VariableTok{self}\NormalTok{.ny,nx}\OperatorTok{=}\VariableTok{self}\NormalTok{.nx)}
\ControlFlowTok{elif}\NormalTok{ dicname}\OperatorTok{==}\StringTok{'nfwlet'}\NormalTok{:}
    \ImportTok{from}\NormalTok{ halolet }\ImportTok{import}\NormalTok{ nfwlet2D}
    \VariableTok{self}\NormalTok{.dict2D }\OperatorTok{=}\NormalTok{   nfwlet2D(nframe}\OperatorTok{=}\VariableTok{self}\NormalTok{.nframe,ngrid}\OperatorTok{=}\VariableTok{self}\NormalTok{.nx,smooth_scale}\OperatorTok{=-}\DecValTok{1}\NormalTok{)}
\CommentTok{# 2) From Surface Density of Excess Surface Density}
\VariableTok{self}\NormalTok{.ks2D   }\OperatorTok{=}\NormalTok{   massmap_ks2D(}\VariableTok{self}\NormalTok{.ny,}\VariableTok{self}\NormalTok{.nx)}

\CommentTok{# 3) Lening Kernel: from Excess Surface Density to Shear}

\ControlFlowTok{if} \VariableTok{self}\NormalTok{.nlp}\OperatorTok{<=}\DecValTok{1}\NormalTok{:}
    \VariableTok{self}\NormalTok{.lensKernel }\OperatorTok{=}\NormalTok{   np.ones((}\VariableTok{self}\NormalTok{.nz,}\VariableTok{self}\NormalTok{.nlp))}
\ControlFlowTok{else}\NormalTok{:}
    \VariableTok{self}\NormalTok{.lensKernel }\OperatorTok{=}\NormalTok{   np.zeros((}\VariableTok{self}\NormalTok{.nz,}\VariableTok{self}\NormalTok{.nlp))}
    \ControlFlowTok{for}\NormalTok{ i,zs }\KeywordTok{in} \BuiltInTok{enumerate}\NormalTok{(zsbin):}
        \VariableTok{self}\NormalTok{.lensKernel[i,:]    }\OperatorTok{=}   \VariableTok{self}\NormalTok{.cosmo.deltacritinv(zlbin,zs)}
\end{Highlighting}
\end{Shaded}

    \(\mathbf{D^{1,2}}\) refer to difference operators in two transverse
(ra, dec) directions. \(\lambda_2\) control the amplitude of the Total
Square Variance (TSV) term.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# sparseBase.massmapSparsityTask.gradient_TSV}
\CommentTok{# Definition of D1 and D2}
\NormalTok{difx    }\OperatorTok{=}\NormalTok{   np.roll(}\VariableTok{self}\NormalTok{.alphaR[:,}\DecValTok{0}\NormalTok{,:,:],}\DecValTok{1}\NormalTok{,axis}\OperatorTok{=-}\DecValTok{1}\NormalTok{)}
\NormalTok{difx    }\OperatorTok{=}\NormalTok{   difx}\OperatorTok{-}\VariableTok{self}\NormalTok{.alphaR[:,}\DecValTok{0}\NormalTok{,:,:] }\CommentTok{# D1}
\NormalTok{dify    }\OperatorTok{=}\NormalTok{   np.roll(}\VariableTok{self}\NormalTok{.alphaR[:,}\DecValTok{0}\NormalTok{,:,:],}\DecValTok{1}\NormalTok{,axis}\OperatorTok{=-}\DecValTok{2}\NormalTok{)}
\NormalTok{dify    }\OperatorTok{=}\NormalTok{   dify}\OperatorTok{-}\VariableTok{self}\NormalTok{.alphaR[:,}\DecValTok{0}\NormalTok{,:,:] }\CommentTok{# D2}
\end{Highlighting}
\end{Shaded}

    We separate out the second order terms in the loss function.
\[F(\vec{x})=\frac{1}{2}(y_{i}-A^{*}_{ij}x_{j})(y_{i}-A_{ik}x_{k})+\frac{\lambda_2}{2}[(D^{1}_{ij} x_{j})(D^{1}_{ik}x_{k})+ (D^{2}_{ij} x_{j})(D^{2}_{ik}x_{k})],\]

Then we approach to the minimum of the loss function (\(L(\vec{x})\)) by
iteratively updates each component of \(\vec{x}\)
\[x_{\alpha}^{(n+1)}=x_{\alpha}^{(n)}-S_{\lambda_1 \sigma_{\alpha}}(\frac{\mu\partial_{\alpha}F(\vec{x})}{A_{i\alpha}A_{i\alpha}+4\lambda_2}),\]

where

\[\partial_\alpha F(\vec{x})=-A_{i\alpha}^{*} (y_{i}-A_{ij}x_{j}) + \lambda_2(D^1_{i\alpha}D^1_{ij} x_{j}+ D^2_{i\alpha} D^2_{ij} x_j).\]

\(\mu\) is the step size of the iteration. S\_\{\lambda\} is the soft
thresholding function defined as:

\[S_{\lambda} (x_{\alpha})=\rm{sign}(x_{\alpha}) \rm{max}(|x_{\alpha}| - \lambda,0)\]

    \begin{Shaded}
\begin{Highlighting}[]

\CommentTok{# sparseBase.massmapSparsityTask.gradient}
\CommentTok{# calculate the gradient of the Second order component in loss function }
\CommentTok{# wihch includes Total Square Variance(TSV) and chi2 components}
\NormalTok{gCh2}\OperatorTok{=}\VariableTok{self}\NormalTok{.gradient_chi2()}
\NormalTok{gTSV}\OperatorTok{=}\VariableTok{self}\NormalTok{.gradient_TSV()}

\CommentTok{# sparseBase.massmapSparsityTask.gradient_chi2}
\CommentTok{# calculate the gradient of the chi2 component}
\NormalTok{shearRTmp   }\OperatorTok{=}   \VariableTok{self}\NormalTok{.main_forward(}\VariableTok{self}\NormalTok{.alphaR) }\CommentTok{#A_\{ij\} x_j}
\VariableTok{self}\NormalTok{.shearRRes   }\OperatorTok{=}   \VariableTok{self}\NormalTok{.shearR}\OperatorTok{-}\NormalTok{shearRTmp     }\CommentTok{#y_i-A_\{ij\} x_j}
\NormalTok{dalphaR     }\OperatorTok{=}   \OperatorTok{-}\VariableTok{self}\NormalTok{.main_transpose(}\VariableTok{self}\NormalTok{.shearRRes)}\OperatorTok{/}\FloatTok{2.} \CommentTok{#-A_\{i\textbackslash{}alpha\}(y_i-A_\{ij\} x_j)/2}

\CommentTok{# sparseBase.massmapSparsityTask.gradient_TSV}
\NormalTok{gradx   }\OperatorTok{=}\NormalTok{   np.roll(difx,}\OperatorTok{-}\DecValTok{1}\NormalTok{,axis}\OperatorTok{=-}\DecValTok{1}\NormalTok{)}
\NormalTok{gradx   }\OperatorTok{=}\NormalTok{   gradx}\OperatorTok{-}\NormalTok{difx    }\CommentTok{# (D1)_\{i\textbackslash{}alpha\} (D1)_\{ij\} x_j}
\NormalTok{grady   }\OperatorTok{=}\NormalTok{   np.roll(dify,}\OperatorTok{-}\DecValTok{1}\NormalTok{,axis}\OperatorTok{=-}\DecValTok{2}\NormalTok{)  }
\NormalTok{grady   }\OperatorTok{=}\NormalTok{   grady}\OperatorTok{-}\NormalTok{dify    }\CommentTok{# (D2)_\{i\textbackslash{}alpha\} (D2)_\{ij\} x_j}
\NormalTok{dalphaR[:,}\DecValTok{0}\NormalTok{,:,:]}\OperatorTok{=}\NormalTok{(gradx}\OperatorTok{+}\NormalTok{grady)}\OperatorTok{*}\VariableTok{self}\NormalTok{.lbd2}\OperatorTok{/}\FloatTok{2.}
\end{Highlighting}
\end{Shaded}

    Note that here \(A_{i\alpha} A_{i\alpha}\) should be estimated taking
into account the mask of observed shear field.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# sparseBase.massmapSparsityTask.spectrum_norm}
\CommentTok{# Estimate A_\{i\textbackslash{}alpha\} A_\{i\textbackslash{}alpha\}}
\NormalTok{asquareframe}\OperatorTok{=}\NormalTok{np.zeros((}\VariableTok{self}\NormalTok{.nz,}\VariableTok{self}\NormalTok{.nframe,}\VariableTok{self}\NormalTok{.ny,}\VariableTok{self}\NormalTok{.nx))}
\ControlFlowTok{for}\NormalTok{ iz }\KeywordTok{in} \BuiltInTok{range}\NormalTok{(}\VariableTok{self}\NormalTok{.nz):}
\NormalTok{    maskF}\OperatorTok{=}\NormalTok{np.fft.fft2(}\VariableTok{self}\NormalTok{.mask[iz,:,:])}
    \ControlFlowTok{for}\NormalTok{ iframe }\KeywordTok{in} \BuiltInTok{range}\NormalTok{(}\VariableTok{self}\NormalTok{.nframe):}
\NormalTok{        fun}\OperatorTok{=}\NormalTok{np.}\BuiltInTok{abs}\NormalTok{(}\VariableTok{self}\NormalTok{.ks2D.transform(}\VariableTok{self}\NormalTok{.dict2D.fouaframes[iframe,:,:],outFou}\OperatorTok{=}\VariableTok{False}\NormalTok{))}\OperatorTok{**}\FloatTok{2.}
\NormalTok{        asquareframe[iz,iframe,:,:]}\OperatorTok{=}\NormalTok{np.fft.ifft2(np.fft.fft2(fun).real}\OperatorTok{*}\NormalTok{maskF).real}

\NormalTok{spectrum}\OperatorTok{=}\NormalTok{np.}\BuiltInTok{sum}\NormalTok{(}\VariableTok{self}\NormalTok{.lensKernel[:,:,}\VariableTok{None}\NormalTok{,}\VariableTok{None}\NormalTok{,}\VariableTok{None}\NormalTok{]}\OperatorTok{*}\NormalTok{asquareframe[:,}\VariableTok{None}\NormalTok{,:,:,:],axis}\OperatorTok{=}\DecValTok{0}\NormalTok{)}
\VariableTok{self}\NormalTok{.mu}\OperatorTok{=}\FloatTok{0.1}\OperatorTok{/}\NormalTok{(spectrum}\FloatTok{+4.}\OperatorTok{*}\VariableTok{self}\NormalTok{.lbd2) }\CommentTok{#we chose mu=0.1}
\end{Highlighting}
\end{Shaded}

    \begin{Verbatim}[commandchars=\\\{\}]
Populating the interactive namespace from numpy and matplotlib
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/data1b/work/xiangchong.li/superonionMaster/miniconda3/lib/python3.7/site-
packages/IPython/core/magics/pylab.py:160: UserWarning: pylab import has
clobbered these variables: ['figure', 'logging']
`\%matplotlib` prevents importing * from pylab and numpy
  "\textbackslash{}n`\%matplotlib` prevents importing * from pylab and numpy"
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/lustre2/work/xiangchong.li/massMapSim/stampSim/oneHalo-2D/TSV-lbd1.5
\end{Verbatim}

    \hypertarget{a-simple-simulation}{%
\section{A simple Simulation}\label{a-simple-simulation}}

\(M_{200}=4.41 \times 10^{14} M_{\odot}\)

\(z=0.38\)

\(\sigma_\gamma=0.25\)

\(40\) galaxies per arcmin

    \hypertarget{pixel-frame-only}{%
\section{Pixel frame only}\label{pixel-frame-only}}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{sparseBase_files/sparseBase_10_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \hypertarget{pixel-frame-one-halo-frame}{%
\section{Pixel frame + one halo
frame}\label{pixel-frame-one-halo-frame}}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{sparseBase_files/sparseBase_12_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    % Add a bibliography block to the postdoc

    \end{document}

### 2020-03-09 python/haloSim.py

@@ -568,13 +568,15 @@ def haloCS02SigmaAtom(r_s,ngrid,c=9.,smooth_scale=-1,fou=True):
     atomFou[~mask]=1.+A*(c+c**3/(6*(1 + c))+1/4.*(-2.*c-c**2.-2*np.log(1+c)))*r0**2.
     if smooth_scale>1.:
         atomFou =   atomFou*np.exp(-(rT*smooth_scale)**2./2.)
+    norm = np.sqrt(np.sum(atomFou*np.conj(atomFou)))/ngrid
+    atomFou=atomFou/norm
     if fou:
         return atomFou
     else:
         return np.real(np.fft.ifft2(atomFou))
 
 def GausAtom(sigma,ngrid,fou=True):
-    if sigma>0:
+    if sigma>0.1:
         x,y =   np.meshgrid(np.fft.fftfreq(ngrid),np.fft.fftfreq(ngrid))
         if fou:
             x  *=   (2*np.pi);y*=(2*np.pi)

### 2020-03-09 python/halo_wavelet.py

@@ -1,144 +1,0 @@
-import os
-import numpy as np
-import astropy.io.fits as pyfits
-
-class starlet2D():
-    """
-    A Class for 2D nfwlet transform
-    --------
-
-    Construction Keywords
-    -------
-    nframe  :   number of frames
-    ngrid   :   size of the field (pixel)
-    smooth_scale:   scale radius of Gaussian smoothing kernal (pixel)
-    pltDir  :   whether plot the atoms for demonstration
-
-    Methods
-    --------
-    itransform:
-
-    itranspose:
-
-    transform:
-
-    transpose:
-
-    Examples
-    --------
-    halolet.nfwlet2D(pltDir='plot')
-    """
-    def __init__(self,gen=2,nframe=4,ny=64,nx=64,pltDir=None):
-        Coeff_h0 = 3. / 8.;
-        Coeff_h1 = 1. / 4.;
-        Coeff_h2 = 1. / 16.;
-        ker1D=np.matrix([Coeff_h2,Coeff_h1,Coeff_h0,Coeff_h1,Coeff_h2])
-        self.ker2D=np.array(np.dot(ker1D.T,ker1D))
-        self.nframe=nframe
-        assert ny%2==0 and nx%2==0
-        self.ny=ny
-        self.nx=nx
-        self.gen=gen
-        self.shape=(nframe,ny,nx)
-        self.pltDir=pltDir
-        self.prepareFrames()
-
-    def prepareFrames(self):
-        self.frames=np.zeros(self.shape)
-        self.aframes=np.zeros(self.shape)
-        self.frames[0,0,0]=1
-        self.aframes[0,0,0]=1
-        if self.gen==1:
-            for iframe in range(self.nframe-1):
-                step=int(2**iframe+0.5)
-                #first convolution
-                for j in range(self.ny):
-                    indexJ=(np.arange(j-2*step,j+2*step+1,step)%self.ny)[:,None]
-                    for i in range(self.nx):
-                        indexI=(np.arange(i-2*step,i+2*step+1,step)%self.nx)[None,:]
-                        self.frames[iframe+1,j,i]=np.sum(self.ker2D*self.frames[iframe,indexJ,indexI])
-                #subtraction
-                self.frames[iframe,:,:]=self.frames[iframe,:,:]-self.frames[iframe+1,:,:]
-                self.aframes[iframe+1,0,0]=1
-        elif self.gen==2:
-            for iframe in range(self.nframe-1):
-                step=int(2**iframe+0.5)
[…]

### 2020-03-09 python/halolet.py

@@ -5,6 +5,7 @@ import astropy.io.fits as pyfits
 
 class nfwlet2D():
     """
+    halolet.nfwlet2D
     A Class for 2D nfwlet transform
     --------
 
@@ -17,9 +18,9 @@ class nfwlet2D():
 
     Methods
     --------
-    itransform:
+    itransform: transform from halolet space to observed space
 
-    itranspose:
+    itranspose: transpose of itransform operator
 
 
     Examples
@@ -29,9 +30,7 @@ class nfwlet2D():
     def __init__(self,nframe=4,ngrid=64,smooth_scale=3,pltDir=None):
         assert ngrid%2==0,\
                 'Please make sure nx and ny are even numbers'
-        """
-        We force ny=nx, the user should ensure that by padding 0
-        """
+        # We force ny=nx, the user should ensure that by padding 0
         self.nx=ngrid
         self.ny=ngrid
         self.nframe=nframe
@@ -52,8 +51,8 @@ class nfwlet2D():
 
         for iframe in range(self.nframe-1):
             iAtomF=haloSim.haloCS02SigmaAtom(r_s=iframe+1,ngrid=self.ny,c=9.,smooth_scale=self.smooth_scale)
-            self.fouaframes[iframe+1,:,:]=iAtomF
-            self.aframes[iframe+1,:,:]=np.real(np.fft.ifft2(iAtomF))
+            self.fouaframes[iframe+1,:,:]=iAtomF # Fourier Space
+            self.aframes[iframe+1,:,:]=np.real(np.fft.ifft2(iAtomF)) # Real Space
 
         if self.pltDir:
             afname  =   os.path.join(self.pltDir,'nfwAtom-nframe%d.fits' %(self.nframe))
@@ -68,7 +67,7 @@ class nfwlet2D():
         """
         assert dataIn.shape==self.shape3,\
                 'input should have shape (nframe,ny,nx)'
-        dataOut=np.zeros(self.shape2).astype(np.complex)
+        dataOut=np.zeros(self.shape2,dtype=np.complex128)
         for iframe in range(self.nframe):
             dataTmp=dataIn[iframe,:,:]
             if not inFou:
@@ -85,6 +84,147 @@ class nfwlet2D():
         assert dataIn.shape==(self.ny,self.nx),\
                 'input should have shape2 (ny,nx)'
         dataOut=np.empty(self.shape3)
+        if not inFou:
+            dataTmp=np.fft.fft2(dataIn)
+        else:
[…]

### 2020-03-09 python/sparseBase.py

@@ -17,10 +17,10 @@ def soft_thresholding(dum,thresholds):
     return np.sign(dum)*np.maximum(np.abs(dum)-thresholds,0.)
 
 def firm_thresholding(dum,thresholds):
-    mask    =   (abs(dum)<= thresholds)
+    mask    =   (np.abs(dum)<= thresholds)
     dum[mask]=  0.
-    mask    =   (abs(dum)>thresholds)
-    mask    =   mask&(abs(dum)<= 2*thresholds)
+    mask    =   (np.abs(dum)>thresholds)
+    mask    =   mask&(np.abs(dum)<= 2*thresholds)
     dum[mask]=  np.sign(dum[mask])*(2*np.abs(dum[mask])-thresholds[mask])
     return dum
 
@@ -30,6 +30,44 @@ def my_thresholding(dum,thresholds):
     mask    =   (abs(dum)>thresholds)
     dum[mask]=  np.sign(dum[mask])*(abs(dum[mask])-thresholds[mask]**2./abs(dum[mask]))
     return dum
+
+class massmap_ks2D():
+    def __init__(self,ny,nx):
+        self.shape   =   (ny,nx)
+        self.e2phiF  =   self.e2phiFou(self.shape)
+
+    def e2phiFou(self,shape):
+        ny1,nx1 =   shape
+        e2phiF  =   np.zeros(shape,dtype=complex)
+        for j in range(ny1):
+            jy  =   (j+ny1//2)%ny1-ny1//2
+            jy  =   jy/ny1
+            for i in range(nx1):
+                ix  =   (i+nx1//2)%nx1-nx1//2
+                ix  =   ix/nx1
+                if (i**2+j**2)>0:
+                    e2phiF[j,i]    =   np.complex((ix**2.-jy**2.),2.*ix*jy)/(ix**2.+jy**2.)
+                else:
+                    e2phiF[j,i]    =   1.
+        return e2phiF*np.pi
+
+    def itransform(self,gMap,inFou=True,outFou=True):
+        assert gMap.shape==self.shape
+        if not inFou:
+            gMap =   np.fft.fft2(gMap)
+        kOMap    =   gMap/self.e2phiF*np.pi
+        if not outFou:
+            kOMap    =   np.fft.ifft2(kOMap)
+        return kOMap
+
+    def transform(self,kMap,inFou=True,outFou=True):
+        assert kMap.shape==self.shape
+        if not inFou:
[…]

### 2020-04-19 bin/pixCartesian3DBatchRun.py
pixelization

@@ -10,8 +10,8 @@ from pixel3D import cartesianGrid3D
 raname='raR'
 decname='decR'
 zname='zbest'
-g1name='g1n'
-g2name='g2n'
+g1name='g1R'
+g2name='g2R'
 ngroup=100 # groups in the input fits file
 
 configName  =   'stampSim/HSC-like/process/config.ini'
@@ -23,19 +23,25 @@ def process(isim):
     im = isim//9
     iz = isim%9
     infname='stampSim/HSC-like/stampSim-HSC_like-TJ03-%d,%d-202004021856.fits' %(iz,im)
-    outfname='stampSim/HSC-like/process/pixShear-%d-%d.fits' %(iz,im)
 
     noiTab=pyfits.getdata(infname)
     ng=len(noiTab)//ngroup
 
     pixDatAll=np.zeros((ngroup,)+gridInfo.shape,dtype=np.complex128)
-
     for ig in range(ngroup):
         noiU=noiTab[ig*ng:(ig+1)*ng]
-        val=noiU[g1name]+noiU[g2name]*1j
-        pixDatAll[ig]=gridInfo.pixelize_data(noiU[raname],noiU[decname],noiU[zname],val)
+        val=(noiU[g1name]+noiU['g1n'])+(noiU[g2name]+noiU['g2n'])*1j
+        outcome=gridInfo.pixelize_data(noiU[raname],noiU[decname],noiU[zname],val)
+        pixDatAll[ig]=outcome[0]
 
-    pyfits.writeto(outfname,pixDatAll)
+    outfname1='stampSim/HSC-like/process-equalNum/pixShearR-g1-%d-%d.fits' %(iz,im)
+    outfname2='stampSim/HSC-like/process-equalNum/pixShearR-g2-%d-%d.fits' %(iz,im)
+    pyfits.writeto(outfname1,pixDatAll.real)
+    pyfits.writeto(outfname2,pixDatAll.imag)
+
+    pixNumAll=outcome[1]
+    outfname3='stampSim/HSC-like/process-equalNum/pixNumR-%d-%d.fits' %(iz,im)
+    pyfits.writeto(outfname3,pixNumAll)
     return
 
 if __name__=="__main__":

### 2020-04-19 python/pixel3D.py

@@ -1,7 +1,11 @@
+import os
+import json
+import cosmology
 import numpy as np
 from configparser import ConfigParser
 
 class cartesianGrid3D():
+    # pixel3D.cartesianGrid3D
     def __init__(self,parser):
         # Transverse celestial plane
         unit=parser.get('transPlane','unit')
@@ -16,8 +20,9 @@ class cartesianGrid3D():
         delta=parser.getfloat('transPlane','scale')*ratio
         xmin=parser.getfloat('transPlane','xmin')*ratio
         nx=parser.getint('transPlane','nx')
+        assert nx>=1
         xmax=xmin+delta*(nx+0.1)
-        xbound=np.arange(xmin,xmax,delta)-0.5*delta
+        xbound=np.arange(xmin,xmax,delta)
         xcgrid=(xbound[:-1]+xbound[1:])/2.
         assert len(xcgrid)==nx
         self.xbound=xbound
@@ -25,8 +30,9 @@ class cartesianGrid3D():
         ## dec
         ymin=parser.getfloat('transPlane','ymin')*ratio
         ny=parser.getint('transPlane','ny')
+        assert ny>=1
         ymax=ymin+delta*(ny+0.1)
-        ybound=np.arange(ymin,ymax,delta)-0.5*delta
+        ybound=np.arange(ymin,ymax,delta)
         ycgrid=(ybound[:-1]+ybound[1:])/2.
         assert len(ycgrid)==ny
         self.ybound=ybound
@@ -36,46 +42,118 @@ class cartesianGrid3D():
         self.sigma=parser.getfloat('transPlane','smooth_scale')*ratio
 
         # line-of-signt direction
-        zmin=parser.getfloat('sourceZ','zmin')
-        deltaz=parser.getfloat('sourceZ','zscale')
-        nz=parser.getint('sourceZ','nz')
-        zmax=zmin+deltaz*(nz+0.1)
-        zbound=np.arange(zmin,zmax,deltaz)-0.5*deltaz
+        # background plane
+        if parser.has_option('sourceZ','zbound'):
+            zbound=np.array(json.loads(parser.get('sourceZ','zbound')))
+            nz=len(zbound)-1
+        else:
+            zmin=parser.getfloat('sourceZ','zmin')
+            deltaz=parser.getfloat('sourceZ','zscale')
+            nz=parser.getint('sourceZ','nz')
+            assert nz>=1
+            zmax=zmin+deltaz*(nz+0.1)
[…]

### 2020-04-19 python/haloSim.py
make plot for nfwlet-atom in 1d and 2d

@@ -553,22 +553,26 @@ def haloCS02SigmaAtom(r_s,ngrid,c=9.,smooth_scale=-1,fou=True):
     @param c          truncation ratio (concentration)
     @param fou        in Fourier space
     """
-    A= 1./(np.log(1+c)-c/(1.+c))
     x,y=np.meshgrid(np.fft.fftfreq(ngrid),np.fft.fftfreq(ngrid))
     x*=(2*np.pi);y*=(2*np.pi)
     rT=np.sqrt(x**2+y**2)
-    r=rT*r_s
-    mask=r>0.001
-    atomFou=np.zeros_like(r, dtype=float)
-    r1=r[mask]
-    si1,ci1=spfun.sici((1+c)*r1)
-    si2,ci2=spfun.sici(r1)
-    atomFou[mask]=A*(np.sin(r1)*(si1-si2)-np.sin(c*r1)/(1+c)/r1+np.cos(r1)*(ci1-ci2))
-    r0=r[~mask]
-    atomFou[~mask]=1.+A*(c+c**3/(6*(1 + c))+1/4.*(-2.*c-c**2.-2*np.log(1+c)))*r0**2.
+    if r_s<=0.1:
+        atomFou=np.ones((ngrid,ngrid))
+    else:
+        A= 1./(np.log(1+c)-c/(1.+c))
+        r=rT*r_s
+        mask=r>0.001
+        atomFou=np.zeros_like(r, dtype=float)
+        r1=r[mask]
+        si1,ci1=spfun.sici((1+c)*r1)
+        si2,ci2=spfun.sici(r1)
+        atomFou[mask]=A*(np.sin(r1)*(si1-si2)-np.sin(c*r1)/(1+c)/r1+np.cos(r1)*(ci1-ci2))
+        r0=r[~mask]
+        atomFou[~mask]=1.+A*(c+c**3/(6*(1 + c))+1/4.*(-2.*c-c**2.-2*np.log(1+c)))*r0**2.
     if smooth_scale>.1:
         atomFou =   atomFou*np.exp(-(rT*smooth_scale)**2./2.)
     norm = np.sqrt(np.sum(atomFou*np.conj(atomFou)))/ngrid
+    # Normalize
     atomFou=atomFou/norm
     if fou:
         return atomFou

### 2020-04-20 paper_ms_method_HSCY1/ms.tex
commi
make halolet
commit

@@
 The lensing distortion $\kappa$ at a position $\vec{x}=(\vec{\theta}$, $\chi_s$) caused by the foreground inhomogeneous density distribution is
+
+\begin{figure*}
+ \includegraphics[width=0.95\textwidth]{nfwlet-atom-2D.pdf}
+ \caption{The NFW atom with different scale radius ($r_s$). The first row shows the NFW atoms in Fourier space and the second row shows the NFW atom in Real space.}
+\end{figure*}
+
 \begin{equation}
@@
 \begin{cases}
-\frac{3H_0\Omega_M}{2 c} \frac{\chi_l \chi_{sl} (1+z_l)}{ \chi_s E(z_l)} & (z_s>z_l),\\
+\frac{3H_0\Omega_M}{2 c} \frac{\chi_l \chi_{sl} (1+z_l)}{\chi_{s} E\left(z_l\right)} & (z_s>z_l),\\
 0&(z_s \leq z_l).
@@
 
+\begin{figure}
+ \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
+ \caption{The $1$-D slices of NFW atoms with different scale radius ($r_s=0,1,2,4,8$).}
+\end{figure}
 \subsection{Photo-$z$ Uncertainty}
@@
 Whereas, the NFW atom is modeled with Dirac delta function on the line-of-sight direction
+
 \begin{equation}
@@
 \subsection{Loss Function with Constrains}
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
+ \caption{The source galaxies are binned into $10$ redshift bins according to their mlz best photo-$z$ estimation.
+The blue histogram is the number distribution of the best photo-$z$ estimation.
+The vertical dashed lines are the bounds of bins.
+The galaxies are evenly distributed in each bins.}
+\end{figure}
 The loss function is defined as
@@
 
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
+ \caption{The PDF of photo-$z$ error for $10$ source redshift bins.}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{lensing_efficiency.pdf}
+ \caption{The blue line shows the normalized lensing efficiency for lens bin at $z_{l}=0.51$. The orange line is the normalized lensing efficiency while taking into account the photo-$z$ uncertainty.}
+\end{figure}
 \subsection{FISTA}
@@
 with $t^{(0)}=1$ and $X^{(0)}=\alpha^{(0)}$.
-\section{Simulation}
+
+\section{HSC-like Simulation}
+
+\subsection{Shear Measurement Error}
+\subsection{Photo-$z$ Error}
 
 \section{Results}
-...
+
 \section{Summary}
-...
+
 \bibliographystyle{aasjournal}

### 2020-07-22 paper_ms_method_HSCY1/ms.tex
add figures to latex
commit

@@
 \hypersetup{breaklinks}
+\DeclareMathOperator{\arccosh}{arccosh}
 
@@
 \section{Introduction}
-...
-\section{The Problem}
+Light from distant galaxies is lensed by the foreground inhomogeneous density distribution along the line-of-sight 
+due to the influence of gravity and the shapes of the foreground galaxies are distorted due to the lensing effect. 
+Such effect, which is known as weak lensing, imprints the information of foreground density distribution to the 
+background galaxies and offers a direct probe into the mass density distribution in the universe.
 
-\subsection{Density Contrast to Shear}
-The lensing distortion $\kappa$ at a position $\vec{x}=(\vec{\theta}$, $\chi_s$) caused by the foreground inhomogeneous density distribution is
+This paper is organized as follows. 
+Section \ref{sec:MethodAll} proposes the new method for $3$-D mass map reconstruction. 
+Section \ref{sec:Sim} introduces the realistic simulations we use to test the new method.
+Section \ref{sec:Res} presents the results of our method on the simulations.
+Section \ref{sec:Sum} summarizes and discusses the future development of the method.
+
+\section{Methodology}
+\label{sec:MethodAll}
+
+\subsection{The Problem}
+\subsubsection{Density Contrast to Shear}
+We first review how the foreground density contrast induces the shear distortion on background galaxies.
+The lensing distortion $\kappa$ at a position $\vec{x}=(\vec{\theta}$, $\chi_s$) caused by the foreground 
+inhomogeneous density distribution is
 
@@
 
+\subsubsection{Photo-$z$ Uncertainty}
 \begin{figure}
@@
 \end{figure}
-\subsection{Photo-$z$ Uncertainty}
 Since the redshifts of source galaxies are estimated with a limited number of photometric bands, the estimated redshift of a galaxy suffer from large uncertainty.
@@
 \end{equation}
-\subsection{Smoothing}
+
+\subsubsection{Smoothing}
 Since the observed galaxies have random irregular (unequally-spaced) distribution, it is necessary to smooth the shear signal in the observation. The smoothing is expressed as follows
@@
 
-\subsection{Mask and Noise}
+\subsubsection{Mask and Noise}
 In real observations, the influence of mask and noise should also be taken into account. The final observed shear is
@@
 
-\section{The Method}
+\subsection{The Method}
 \label{sec:kappaMap}
 
-\subsection{Dictionary}
+\subsubsection{Dictionary}
 Since many $N$-body simulations have shown the dark matter to be largely distributed in halos connected by filaments,
@@
 \begin{cases}
--\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{1}{(1-x^2)^{3/2}} \mathrm{arccosh} (\frac{x^2+c}{x(1+c)}) & (x<1),\\
+-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccosh \left(\frac{x^2+c}{x(1+c)}\right)}{(1-x^2)^{3/2}}  & (x<1),\\
 \frac{\sqrt{c^2-1}}{3(1+c)} (1+\frac{1}{c+1}) & (x=1),\\
--\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{1}{(x^2-1)^{3/2}} \mathrm{arccos} (\frac{x^2+c}{x(1+c)}) & (1<x\leq c),\\
+-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccos\left(\frac{x^2+c}{x(1+c)}\right)}{(x^2-1)^{3/2}} & (1<x\leq c),\\
 0& (x>c).
@@
 
-\subsection{Loss Function with Constrains}
+\subsubsection{Loss Function with Constrains}
 \begin{figure}
@@
 \end{figure}
+
 The loss function is defined as
@@
 
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
+ \caption{The PDF of photo-$z$ error for $10$ source redshift bins.}
+\end{figure}
+
 We define
@@
  \centering
- \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
- \caption{The PDF of photo-$z$ error for $10$ source redshift bins.}
+ \includegraphics[width=0.5\textwidth]{lensing_efficiency.pdf}
+ \caption{The blue line shows the normalized lensing efficiency for lens bin at $z_{l}=0.51$. 
+ The orange line is the normalized lensing efficiency while taking into account the photo-$z$ uncertainty. 
+ The green data points show the averaged $\kappa$ field for different redshift bins in the simulation.}
 \end{figure}
 
-\begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{lensing_efficiency.pdf}
- \caption{The blue line shows the normalized lensing efficiency for lens bin at $z_{l}=0.51$. The orange line is the normalized lensing efficiency while taking into account the photo-$z$ uncertainty.}
-\end{figure}
-\subsection{FISTA}
+\subsubsection{FISTA}
 The basic FISTA algorithms is
@@
 is the soft thresholding function.
+
 \begin{equation}
@@
 t^{(n+1)} &= \frac{1+\sqrt{1+4(t^{(n)})^2}}{2},\\
-\alpha^{(n+1)}_m&=X^{(n+1)}_m+[\frac{t^{(n)}-1}{t^{(n+1)}}(X^{(n+1)}_m-X^{(n)}_m)],
+\alpha^{(n+1)}_m& = X^{(n+1)}_m+[\frac{t^{(n)}-1}{t^{(n+1)}}(X^{(n+1)}_m-X^{(n)}_m)].
 \end{split}
 \end{equation}
-with $t^{(0)}=1$ and $X^{(0)}=\alpha^{(0)}$.
+The iteration is initialized with $t^{(0)}=1$ and $X^{(0)}=\alpha^{(0)}$.
 
-\section{HSC-like Simulation}
+\section{Simulation}
+\label{sec:Sim}
+This section simulates lensing shear fields induced by a group of dark matter halos with various halo mass and redshifts.
+HSC-like shape measurement error and photo-$z$ error are added to the shear field.
 
-\subsection{Shear Measurement Error}
-\subsection{Photo-$z$ Error}
+\subsection{Weak Lensing Fields}
+
+We simulate weak lensing shear fields of NFW halos according to \citet{haloModel-TJ2003-3pt} 
+and sample halos in the mass-redshift plane as shown in Figure \ref{fig:mass-redshift}.
+We assume a dependency of the concentration on the mass and the redshift of a halo 
+\begin{equation}
+c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
+\end{equation}
+
+\begin{figure}[!ht]
+ \centering
+ \includegraphics[width=0.45\textwidth]{mass-redshift-sampling.pdf}
+ \caption{The sampling points of halos in the mass-redshift plane.}
+ \label{fig:mass-redshift}
+\end{figure}
+
+\subsection{HSC-like Errors}
+\subsubsection{Shear Measurement Error}
+\begin{figure}[!ht]
+ \centering
+ \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
+ \caption{HSC-like measurement error on the first component of shear ($g_1$).}
+ \label{fig:mass-redshift}
+\end{figure}
+
+\subsubsection{Photo-$z$ Error}
 
 \section{Results}
+\label{sec:Res}
+
+\subsection{Detection Rate}
+
+\subsection{Mass and Redshift Estimation}
 
 \section{Summary}
+\label{sec:Sum}
+
+\begin{figure}[!ht]
+ \centering
+ \includegraphics[width=0.45\textwidth]{noise_std_map_pix.pdf}
+ \caption{The standard deviation map of shear measurement error for the fifth source bin ($0.69 \leq z < 0.80 $).}
+\end{figure}
 

### 2020-07-27 paper_ms_method_HSCY1/ms.tex
commit

@@
 We first review how the foreground density contrast induces the shear distortion on background galaxies.
-The lensing distortion $\kappa$ at a position $\vec{x}=(\vec{\theta}$, $\chi_s$) caused by the foreground 
-inhomogeneous density distribution is
+The lensing distortion $\kappa$ at a comoving distance $\chi_s$ caused by the foreground inhomogeneous 
+density distribution at a comoving distance $\chi_l$ ($\chi_l< \chi_s$) is
 
@@
     \includegraphics[width=0.95\textwidth]{nfwlet-atom-2D.pdf}
- \caption{The NFW atom with different scale radius ($r_s$). The first row shows the NFW atoms in Fourier space and the second row shows the NFW atom in Real space.}
+    \caption{The NFW atom with different scale radius ($r_s$). The first row shows the NFW atoms in Fourier 
+            space and the second row shows the NFW atom in Real space.}
 \end{figure*}
@@
 \begin{equation}
-\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s} \frac{\delta(\chi_l \vec{\theta},\chi_l)}{a(\chi_l)}
+\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s}
+\frac{\delta(\vec{\theta},\chi_l)}{a(\chi_l)},
 \end{equation}
 \citep{massMap-Glimpse3D2014}.
-Substitute angular distance $D$ with redshift $z$ and we have
+where $\chi$ refers to the comoving distance, $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
+at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the matter density parameter, $c$ is the speed 
+of light, and $a(\chi_l)$ is the scale parameter at the lens position.
+
+Substitute comoving distance ($\chi$) with redshift ($z$)
+$z$ and we have
 \begin{equation}\label{eq-delta2kappa}
@@
 \end{equation}
-we term $\delta_{c}(z_l,z_s)$ as lensing critical density contrast and define it as
+We term $\delta_{c}(z_l,z_s)$ as lensing critical density contrast and define it as
 \begin{equation}
@@
 
-As reported in \citet{massMap-KS1993}, the shear distortion is
+As shown in \citet{massMap-KS1993}, the shear distortion is related to the kappa field at the redshift plane as
 \begin{equation}\label{eq-kappa2gamma}
@@
 \end{figure}
-Since the redshifts of source galaxies are estimated with a limited number of photometric bands, the estimated redshift of a galaxy suffer from large uncertainty.
-The probability distribution function (PDF) of a galaxies at position $(\vec{\theta},z_s)$ is denoted as $\mathcal{P}(z|z_s)$.
-Note that, in order to simplify the future calculation, we assume the variation of the PDF across the transverse plane is small and neglect the dependency on the transverse position.
+Since the redshifts of source galaxies in the current large scale survey are estimated with a limited 
+number of photometric bands, the estimated redshift of a single galaxy suffers from large uncertainty. 
+We denote the probability of a galaxies, with photo-$z$ estimated as $z_s$, being  located at redshift 
+$z$ as $\mathcal{P}(z|z_s)$.  Note that, in order to simplify the future calculation, we assume the 
+variation of the PDF across the transverse plane is small and neglect such variation.
 

### 2020-08-11 python/haloSim.py
speed up the code using the correlation matrix of parameter space

@@ -474,7 +474,10 @@ class nfw_lensTJ03():
         return DeltaSigma1+1j*DeltaSigma2
 
     def lensKernel(self,z_s):
-        """Lensing kernel of halo as function of source redshift.
+        """
+        # Note that this lensing kernel is from surface density at lens redshfit
+        # to kappa at source redshift
+        Lensing kernel of halo as function of source redshift.
         @param z_s        redshift of sources.
         """
         # convenience: call with single number

### 2020-08-11 python/pixel3D.py

@@ -4,6 +4,23 @@ import cosmology
 import numpy as np
 from configparser import ConfigParser
 
+C_LIGHT=2.99792458e8        # m/s
+GNEWTON=6.67428e-11         # m^3/kg/s^2
+KG_PER_SUN=1.98892e30       # kg/M_solar
+M_PER_PARSEC=3.08568025e16  # m/pc
+
+
+def four_pi_G_over_c_squared():
+    # = 1.5*H0^2/roh_0/c^2
+    # We want it return 4piG/c^2 in unit of Mpc/M_solar
+    # in unit of m/kg
+    fourpiGoverc2 = 4.0*np.pi*GNEWTON/(C_LIGHT**2)
+    # in unit of pc/M_solar
+    fourpiGoverc2 *= KG_PER_SUN/M_PER_PARSEC
+    # in unit of Mpc/M_solar
+    fourpiGoverc2 /= 1.e6
+    return fourpiGoverc2
+
 class cartesianGrid3D():
     # pixel3D.cartesianGrid3D
     def __init__(self,parser):
@@ -53,6 +70,7 @@ class cartesianGrid3D():
             assert nz>=1
             zmax=zmin+deltaz*(nz+0.1)
             zbound=np.arange(zmin,zmax,deltaz)
+
         zcgrid=(zbound[:-1]+zbound[1:])/2.
         self.zbound=zbound
         self.zcgrid=zcgrid
@@ -89,7 +107,11 @@ class cartesianGrid3D():
             assert self.shape[0]==1
         dataOut=np.zeros(self.shape,v.dtype)
         varOut=np.zeros(self.shape,dtype=float)
-        rsig=int(self.sigma/self.delta*3+1)
+        # sample to 3 times of sigma
+        if self.sigma>0:
+            rsig=int(self.sigma/self.delta*3+1)
+        else:
+            rsig=0.5
         for iz in range(self.shape[0]):
             if z is not None:
                 mskz=(z>=self.zbound[iz])&(z<self.zbound[iz+1])
@@ -104,44 +126,50 @@ class cartesianGrid3D():
                     if not np.sum(mskx)>=1:
                         continue
                     rl2=(x[mskx]-xc)**2.+(y[mskx]-yc)**2.
+                    # convolve with Gaussian kernel
                     wg=1./np.sqrt(2.*np.pi)/self.sigma*np.exp(-rl2/self.sigma**2./2.)
                     wgsum=np.sum(wg)
[…]

### 2020-08-14 paper_ms_method_HSCY1/ms.tex
add talk

@@
 \emergencystretch=1.em
-\newcommand \figPath{./}
-\newcommand \redColor{\color{red}}
-\newcommand{\vecb}[1]{{#1}}
-\renewcommand\labelenumi{(\roman{enumi})}
-\renewcommand\theenumi\labelenumi
-%\newcommand{\jcap}{JCAP}
 
 \usepackage{amsmath,amsthm,amsfonts,amssymb,bm}
+% for big dot
+\makeatletter
+\newcommand*\bigcdot{\mathpalette\bigcdot@{.5}}
+\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
+
 \usepackage{listings}
@@
 \DeclareMathOperator{\arccosh}{arccosh}
+\newcommand \figPath{./}
+\newcommand \redColor{\color{red}}
+\renewcommand\labelenumi{(\roman{enumi})}
+\renewcommand\theenumi\labelenumi
+
+\usepackage{algorithm,algcompatible}
+\DeclareMathOperator*{\argmax}{\arg\!\max}
+\algnewcommand\INPUT{\item[\textbf{Input:}]}
+\algnewcommand\OUTPUT{\item[\textbf{Output:}]}
+
+\makeatother
+%\newcommand{\jcap}{JCAP}
 
 \begin{document}
-\title{Sparsity Weak Lensing Mass Reconstruction}
+\title{Sparsity Weak Lensing $3$- Mass Reconstruction}
 %\author{Xiangchong Li}
@@
 %\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
-%\author{Nobuhiko Katayama}
-%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-%University of Tokyo, Kashiwa 277-8583, Japan}
 %\author{Wentao Luo}
-%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-%University of Tokyo, Kashiwa 277-8583, Japan}
-%\author{Wenting Wang}
-%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-%University of Tokyo, Kashiwa 277-8583, Japan}
-%\author{Jiaxin Han}
-%\affiliation{Department of Astronomy, School of Physics and Astronomy, Shanghai Jiao Tong University, Shanghai, 200240, China}
 %\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
@@
 \section{Introduction}
-Light from distant galaxies is lensed by the foreground inhomogeneous density distribution along the line-of-sight 
-due to the influence of gravity and the shapes of the foreground galaxies are distorted due to the lensing effect. 
-Such effect, which is known as weak lensing, imprints the information of foreground density distribution to the 
-background galaxies and offers a direct probe into the mass density distribution in the universe.
+Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line-of-sight
+due to the influence of gravity and the shapes of the background galaxies are coherently sheared due to the lensing effect.
+Such effect, which is known as weak lensing, imprints the information of foreground mass density distribution to the
+background galaxy images and offers a direct probe into the mass density distribution in the universe \citep[see][for recent 
+reviews]{revKilbinger15,revRachel17}.
+
+Mathematically, the shear field ($\gamma$) measured distant galaxies is a linear mapping of the density contrast ($\delta$)
+\begin{equation}
+ \gamma=\mathbf{T} \delta,
+\end{equation}
+where $\mathbf{T}$ is the transformation operator. The transformation operator ($\mathbf{T}$) includes not only physical lensing
+effect but it also includes observational systematic effects.
+
+In order to fully reconstruct the $3$-D mass density distribution ($\delta$) from the $3$-D shear field ($\gamma$) 
+observed from distorted galaxy images, a premise is take that the density field can be decomposed into a set of models
+\begin{equation}
+ \delta= \mathbf{\Phi} x,
+\end{equation}
+where $\mathbf{\Phi}$ is the transformation operator from the model space to the mass density and $x$ is the projector. 
+In the previous works, Starlets (wavelets transform) and sinusoidial functions (Fourier transform) have been used to 
+modeled the density field .
+
+Subsequently, an ill-posed inverse problem
+\begin{equation}
+\rm{min}_x\{\norm{\gamma - \mathbf{T\Phi} x}_2^2+ C(x)\},
+\end{equation}
+need to be solved to reconstruct the mass density map, where $C(x)$ is the regulation term which makes the ill-posed 
+inversion solvable. The $l^1$ sparsity regulation and the $l^2$ ridge regulation have been applied to the mass density 
+map reversion problem. In their application, the $l^1$ sparsity regulation ($\norm{x}^1_1$) is combined with Starlets modeling 
+\citep{LSS-massMap-Glimpse3D-Leonard2014} and the $l^2$ ridge regulation ($\norm{x}^2_2$) is combined with sinusoidial modeling\footnote{It 
+is also known as Wiener filter.} \citep{LSS-massMap-Wiener-Simon2009}. See \citet{HSC1-massMaps} for a recent application 
+of \citet{LSS-massMap-Wiener-Simon2009} in the Hyper Suprime-Cam Survey \citep{HSC1-data}.
+
+We propose to use NFW halos \citep{halo-NFW1997ApJ} to model the density contrast field and construct the density contrast 
+field with $l^1$ sparsity regulation.
 
 This paper is organized as follows.
-Section \ref{sec:MethodAll} proposes the new method for $3$-D mass map reconstruction. 
+Section \ref{sec:Method} proposes the new method for $3$-D mass map reconstruction.
 Section \ref{sec:Sim} introduces the realistic simulations we use to test the new method.
@@
 \section{Methodology}
-\label{sec:MethodAll}
+\label{sec:Method}
 
-\subsection{The Problem}
-\subsubsection{Density Contrast to Shear}
-We first review how the foreground density contrast induces the shear distortion on background galaxies.
-The lensing distortion $\kappa$ at a comoving distance $\chi_s$ caused by the foreground inhomogeneous 
-density distribution at a comoving distance $\chi_l$ ($\chi_l< \chi_s$) is
+In this section, we first review how the foreground density contrast induces the weak lensing shear distortion on background 
+galaxies in section \ref{subsec:method-delta2shear}.
+After that, we describe several systematic effects which exist in real observation mathematically. The systematic effects 
+include photo-$z$ uncertainty (section \ref{subsec:method-photoz}), smoothing (section \ref{subsec:method-smoothing}),
+mask and noise (section \ref{subsec:method-msknoise}) and pixelation (section \ref{subsec:method-pix}).
+
+Subsequently, we propose a novel method to reconstruct the $3$-D density contrast field from the weak lensing shear 
+distortion field. 
+With the premise that the density field can be decomposed into NFW halos and point masses, we build up a dictionary using 
+NFW models and point mass models in section \ref{subsec:method-dictionary}.
+The models in our dictionary are used to fit the shear field and the optimal fit is determined by minimizing a loss function. 
+As shown in section \ref{subsec:method-lossfun} the loss function is composed of a normal chi-$2$ term, a $l_1$ sparsity 
+constrain and a quadratic total square variance constrain.
+The minimum of the loss function is achieved with the pathwise coordinate descent algorithm in section \ref{subsec:method-pathwise}.
+
+\subsection{Density Contrast to Shear}
+\label{subsec:method-delta2shear}
 
@@
     \includegraphics[width=0.95\textwidth]{nfwlet-atom-2D.pdf}
-    \caption{The NFW atom with different scale radius ($r_s$). The first row shows the NFW atoms in Fourier 
-            space and the second row shows the NFW atom in Real space.}
+    \caption{The NFW models with different scale radius ($r_s$). The first row shows the NFW models in Fourier
+            space and the second row shows the NFW model in Real space.}
 \end{figure*}
 
+The lensing convergence $\kappa$ at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
+density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line-of-sight is
 \begin{equation}
@@
 \end{equation}
-\citep{massMap-Glimpse3D2014}.
+\citep{LSS-massMap-Glimpse3D-Leonard2014}.
 where $\chi$ refers to the comoving distance, $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
@@
 \end{equation}
-We term $\delta_{c}(z_l,z_s)$ as lensing critical density contrast and define it as
+$K(z_l,z_s)$ as the lensing kernel defined as
 \begin{equation}
-\delta_{c}^{-1}(z_l,z_s) =
+K(z_l,z_s) =
 \begin{cases}
@@
 \begin{equation}\label{eq-kappa2gamma}
-\vecb{\gamma}(\vec{\theta},z_s) = \int \vecb{D}(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s) d^2 \theta,
+\gamma^t(\vec{\theta},z_s) = \int  d^2 \theta' D(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s),
 \end{equation}
@@
 \begin{equation}
-\begin{split}
-\vecb{D}(\vec{\theta})&=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2},\\
-\vecb{\gamma}(\vec{\theta})&=\gamma_1(\vec{\theta})+i\gamma_2(\vec{\theta}).
-\end{split}
+D(\vec{\theta})=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2}.
 \end{equation}
+Here we denote the true shear distortion as $\gamma^t$ to distinguish the observed shear signal with systematics which 
+will be introduced in the following subsections.
 
-Combine equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}) and we have
+Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}), the true shear signal is derived as
 \begin{equation}\label{eq-delta2gamma-z}
-\vecb{\gamma}(\vec{\theta},z_s) = \int_0^{z_s} dz_l \frac{\delta_c(z_l,+\infty)}{\delta_{c}(z_l,z_s)} \int d^2 \theta'  \vecb{D}(\vec{\theta}-\vec{\theta'}) \frac{\delta(\vec{\theta'},z_l)}{\delta_c(z_l,+\infty)}.
+\gamma^t(\vec{\theta},z_s) = \int_0^{z_s} \frac{dz_l}{\delta_{c}(z_l,z_s)} \int d^2 \theta' \vec{D}(\vec{\theta}-\vec{\theta'}) \delta(\vec{\theta'},z_l).
 \end{equation}
+Here we define the lensing functional as 
+\begin{equation}
+\mathbf{Q}=\int_0^{z_s} \frac{dz_l}{\delta_{c}(z_l,z_s)} \int d^2 \theta'  \vec{D}(\vec{\theta}-\vec{\theta'}),
+\end{equation}
+then eq. (\ref{eq-delta2gamma-z}) is simplified to $\gamma^t=\mathbf{Q}\delta$.
 
-\subsubsection{Photo-$z$ Uncertainty}
+\subsection{Photo-$z$ Uncertainty}
+\label{subsec:method-photoz}
 \begin{figure}
  \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
- \caption{The $1$-D slices of NFW atoms with different scale radius ($r_s=0,1,2,4,8$).}
+ \caption{The $1$-D slices of NFW models with different scale radius ($r_s=0,1,2,4,8$).}
 \end{figure}
-Since the redshifts of source galaxies in the current large scale survey are estimated with a limited 
-number of photometric bands, the estimated redshift of a single galaxy suffers from large uncertainty. 
-We denote the probability of a galaxies, with photo-$z$ estimated as $z_s$, being  located at redshift 
-$z$ as $\mathcal{P}(z|z_s)$.  Note that, in order to simplify the future calculation, we assume the 
-variation of the PDF across the transverse plane is small and neglect such variation.
 
-Taking the uncertainty of redshift into account, equation (\ref{eq-delta2gamma-z}) changes to
+Since the photometric redshifts of source galaxies in the current large scale survey are estimated with 
+a limited number of photometric bands, the estimated redshift of a single galaxy suffers from large uncertainty.
+We denote the probability of a galaxies, with photo-$z$ estimated as $z_s$, being actually located at redshift
+$z$ as $P(z|z_s)$.  Note that, in order to simplify the future calculation, we assume the variation of the PDF 
+across the transverse plane is small and neglect such variation.
+
+Taking the uncertainty of redshift into account, the shear signal changes to
 \begin{equation}\label{eq-delta2gamma-poz}
-\begin{split}
-\gamma(\vec{\theta},z_s) &= \int_0^{z_s} dz_l P(z_l,z_s)\gamma(\vec{\theta},z_l,+\infty),\\
-\gamma(\vec{\theta},z_l,+\infty)&= \int d^2 \theta'   Q(\vec{\theta}-\vec{\theta'},z_l) \delta(\vec{\theta'},z_l),
-\end{split}
+\gamma^p(\vec{\theta},z) = \int dz_s P(z|z_s) \gamma^t(\vec{\theta},z_s).
 \end{equation}
-where $\gamma(\vec{\theta},z_l,+\infty)$ represents shear signal at infinite redshift ($z_s=+\infty$) caused by density contrast at $z_l$, and $P(z_l,z_s)$ is the convolution kernel along line-of-sight and $Q(\vec{\theta},\vec{\theta}',z_l)$ is the convolution kernel along on the transverse plane.
-These kernels are defined as
+With the definition of photo-$z$ functional
 \begin{equation}
-\begin{split}
-P(z_l,z_s)&=\int \frac{\delta_c(z_l,+\infty)}{\delta_{c}(z_l,z)} \mathcal{P}(z|z_s) dz,\\
-Q(\vec{\theta},\vec{\theta'},z_l)&=\frac{\vecb{D}(\vec{\theta}-\vec{\theta'})}{\delta_c(z_l,+\infty)}.
-\end{split}
+\mathbf{P} = \int dz_s P(z|z_s),
 \end{equation}
+the relation between shear signal and density contrast is $\gamma^p=\mathbf{P} \mathbf{Q} \delta$.
 
-\subsubsection{Smoothing}
-Since the observed galaxies have random irregular (unequally-spaced) distribution, it is necessary to smooth the shear signal in the observation. The smoothing is expressed as follows
+\subsection{Smoothing}
+\label{subsec:method-smoothing}
+
+Since the observed galaxies have random irregular (unequally-spaced) distribution, it is necessary to smooth 
+the shear signal in the observation. The smoothing is expressed as follows
 \begin{equation}
-\gamma_S  (\vec{\theta},z)  = \frac{\sum_i  W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) e_i}{\sum_i W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) R_i},
+\hat{\gamma}  = \frac{\sum_i  W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) e_i}{\sum_i R_i W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) },
 \end{equation}
-where $W(\vec{\theta},z)$ is a $3$-D smoothing kernel. $e_i$, $R_i$, $z_i$ and $\theta_i$ are the ellipticity, response, reshift, transverse position of the `$i$-th' galaxy.
-$W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line-of-sight component $W_\times(z)$
+where $W(\vec{\theta},z)$ is a $3$-D smoothing kernel. $e_i$, $R_i$, $z_i$ and $\theta_i$ are the ellipticity, 
+response, reshift, and transverse position of the `$i$-th' galaxy in the galaxy catalog.
+
+$W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line-of-sight component 
+$W_\times(z)$
 \begin{equation}
@@
 
-With the assumption that the density of response $R$ and the density of galaxy number vary slowly on the smoothing scale, the smoothed shear is
+With the approximation that the density of response $R$ and the density of galaxy number vary slowly on the smoothing scale
+and the fact that $\int d^3r W(\vec{r})=1$, the smoothed shear is
 \begin{equation}\label{eq-smooth-gamma}
-\gamma_S(\vec{\theta}_j,z_j)= \int d^2 \theta_s d z_sW(\vec{\theta}_j-\vec{{\theta}}_s,z_j-z_s) \gamma(\vec{\theta}_s,z_s)
+\gamma^s(\vec{r})= \int d^3 r' W(\vec{r}-\vec{r'}) \gamma^p(\vec{r'})
 \end{equation}
 
-Substitute equation (\ref{eq-delta2gamma-poz}) into equation (\ref{eq-smooth-gamma})
-\begin{equation}\label{eq-delta2gamma-smooth}
-\begin{split}
-\gamma_S(\vec{\theta}_j,z_j) &= \int_0^{z_j} dz_l P_S(z_l,z_j)\gamma_S(\vec{\theta}_j,z_l,+\infty),\\
-\gamma_S(\vec{\theta}_j,z_l,+\infty)&= \int d^2 \theta'   Q_S(\vec{\theta}_j,\vec{\theta'},z_l) \delta(\vec{\theta'},z_l),
-\end{split}
+We define the smoothing functional as
+\begin{equation}
+\mathbf{W} = \int d^3 r' W(\vec{r}-\vec{r'}),
 \end{equation}
-and
+and the relation between shear signal and density contrast is $\gamma^s=\mathbf{W} \mathbf{P} \mathbf{Q} \delta$.
+
+\subsection{Mask and Noise}
+\label{subsec:method-msknoise}
+
+In real observations, the influence of mask and noise should also be taken into account. The final observed shear is
+\begin{equation}\label{eq-delta2gamma-final}
+\gamma(\vec{\theta},z)=M(\vec{\theta},z) \gamma^s(\vec{\theta},z) + \epsilon(\vec{\theta},z),
+\end{equation}
+where $\epsilon$ represents noise typically caused by random shape of intrinsic galaxies and such noise is modeled 
+as uncorrelated Gaussian noise. $M(\vec{\theta},z_s)$ is the mask function.
+
+With the definition of masking functional,
 \begin{equation}
-\begin{split}
-P_S(z_l,z_j)&=\int  dz_s W_\times (z_j-z_s) \int \frac{\delta_c(z_l,+\infty)}{\delta_{c}(z_l,z)} \mathcal{P}(z|z_s) dz,\\
-Q_S(\vec{\theta},\vec{\theta'},z_l)&=\int d^2\theta'' W_T( \vec{\theta} -\vec{\theta''} )  \frac{\vecb{D}(\vec{\theta''}-\vec{\theta'})}{\delta_c(z_l,+\infty)}.
-\end{split}
+\mathbf{M}= \int d^3 r' M(\vec{r'}) \delta_D(\vec{r}-\vec{r'}),
+\end{equation}
+where $\delta_D(\vec{r})$ is $3$-D Dirac delta function, we can write equation (\ref{eq-delta2gamma-final}) into
+\begin{equation}\label{eq-delta2gamma-operator-final}
+\gamma =\mathbf{M} \mathbf{W} \mathbf{P} \mathbf{Q} \delta + \epsilon.
 \end{equation}
 
-\subsubsection{Mask and Noise}
-In real observations, the influence of mask and noise should also be taken into account. The final observed shear is
-\begin{equation}\label{eq-delta2gamma-final}
-\gamma_o(\vec{\theta},z)=M(\vec{\theta},z) \gamma(\vec{\theta},z) + \epsilon(\vec{\theta},z),
+\subsection{Dictionary}
+\label{subsec:method-dictionary}
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
+ \caption{The source galaxies are binned into $10$ redshift bins according to their mlz best photo-$z$ estimation. 
+        The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines 
+        are the bounds of bins. The galaxies are evenly distributed in each bins.}
+\end{figure}
+
+$N$-body simulations show that the dark matter to be largely distributed in halos connected by filaments, therefore,
+we assume that the density contrast field can be decomposed into multi-scaled NFW halo \citep{halo-NFW1997ApJ} and
+point mass at different positions
+\begin{equation}
+\delta(\vec{r}) = \sum_{s=0}^{N} \int d^3 r' \phi_s(\vec{r}-\vec{r'}) x_s(\vec{r'})\\
 \end{equation}
-where $\epsilon$ represents noise typically caused by random shape of intrinsic galaxies and such noise is modeled as white Gaussian noise. $M(\vec{\theta},z_s)$ is the mask function.
-
-We can write equation (\ref{eq-delta2gamma-final}) into
-\begin{equation}\label{eq-delta2gamma-operator-final}
-\gamma_o =\mathbf{M}  \mathbf{P} \mathbf{Q} \delta + \epsilon,
+where $\phi_0$ is $3$-D Dirac delta function to model point masses
+\begin{equation}
+\phi_0(\vec{r})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
 \end{equation}
-where $\mathbf{M}$,  $\mathbf{P}$ and $\mathbf{Q}$ represent the functional operators $M$, $P$ and $Q$, respectively.
-
-\subsection{The Method}
-\label{sec:kappaMap}
-
-\subsubsection{Dictionary}
-Since many $N$-body simulations have shown the dark matter to be largely distributed in halos connected by filaments,
-we assume that the density contrast field can be decomposed into multi-scaled NFW halo \citep{halo-NFW1997ApJ} and point mass at different positions
-\begin{equation}
-\delta(\vec{x}) = \sum_{s=0}^{N_s} \int d^3 x' \phi_s(\vec{x}-\vec{x}') \alpha_s(\vec{x'})\\
-\end{equation}
-where $\phi_0$ is $3$-D Dirac delta function representing point mass
-\begin{equation}
-\phi_0(\vec{x})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
-\end{equation}
-Since the scale of halo is much less than the reachable redshift resolution, we neglect the depth of halo on the line-of-sight direction as suggested by \citep{massMap-Glimpse3D2014}.
-On the transverse plane, the NFW atom is modeled with the surface density profile of NFW halo with scale $\theta_s$ and truncation radius $c \theta_s$ \citep{haloModel-TJ2003-3pt}, where $c$ is generally known as concentration of NFW halo.
-Whereas, the NFW atom is modeled with Dirac delta function on the line-of-sight direction
+Since the scale of halo is much less than the reachable redshift resolution, we neglect the depth of halo on the 
+line-of-sight direction following \citep{LSS-massMap-Glimpse3D-Leonard2014}. On the other hand, in the transverse directions, 
+the surface density profiles of NFW halos with scale $\theta_\alpha$ and truncation radius $c \theta_\alpha$ 
+\citep{haloModel-TJ2003-3pt} are used to model halos, where $c$ is generally known as concentration of NFW halo.
 
@@
 \begin{split}
-\phi_s(\vec{x}) =&\frac{f }{2 \pi \theta_s^2 } F(|\vec{\theta}|/\theta_s) \delta_D(z),\\
-&  (s=1..N_s)
+\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 } F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
+&  (s=1..N)
 \end{split}
@@
 \end{equation}
-and $f=1/[\ln (1+c)-c/(1+c)]$.
+$f=1/[\ln (1+c)-c/(1+c)]$, and $x_\alpha$ is the corresponding projection coefficient of the density contrast
+field onto our basis NFW model.
 
-$\alpha_s$ is the corresponding decomposition coefficient of the density contrast field onto our basis atom. The total coefficients set is denoted as $\alpha=\begin{pmatrix}
-\alpha_0\\
-\alpha_1\\
+We define the projection parameters set as $x=\begin{pmatrix}
+x_{[0]}\\
+x_{[1]}\\
 ...\\
-\alpha_{N_s}
-\end{pmatrix}$, and the total dictionary is $\Phi=\begin{pmatrix}
-\phi_0, \phi_1, ..., \phi_{N_s}
-\end{pmatrix}$.
+x_{[N]}
+\end{pmatrix}$, and the dictionary transforming functional as
+\begin{equation}
+\mathbf{\Phi}=\begin{pmatrix}
+\int d^3r\phi_0(\vec{r}) ~\int d^3r \phi_1(\vec{r})~ ...~\int d^3r \phi_{N}(\vec{r})
+\end{pmatrix}.
+\end{equation}
+Then we write equation (\ref{eq-delta2gamma-operator-final}) into
+\begin{equation}\label{eq-alpha2gamma-operator}
+\gamma=\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} x +\epsilon,
+\end{equation}
+where $\epsilon(\vec{r})$ is the error from the shear measurement which includes contributions from both random
+galaxy orientations and photon noise.
 
-We pixelize the parameter space into a $N_\theta \times N_\theta \times N_l$ grid.
-$N_\theta$ is the number of pixels on the two dimensions of the transverse plane and $N_l$ is the number of pixels on the line-of-sight direction for the lenses.
-Similarly, $\gamma_o$ is pixelized onto a $N_\theta \times N_\theta \times N_s$ grid, where $N_s$ is the number of pixel on the line-of-sight direction for the sources.
-The pixel size for the two dimensions on the transverse plane is denoted as $\Delta \theta$ and the pixel size for the line-of-sight direction is denoted as $\Delta z$.
-Equation (\ref{eq-delta2gamma-operator-final}) changes to
-\begin{equation}\label{eq-alpha2gamma-operator}
-\gamma=\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} \alpha +\epsilon.
+For simplicity, we denote $\mathbf{A}=\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} $ and eq. (\ref{eq-alpha2gamma-operator})
+reduces to 
+\begin{equation}\label{eq-x2gamma-simple}
+\gamma=\mathbf{A} x +\epsilon.
 \end{equation}
 
-\subsubsection{Loss Function with Constrains}
-\begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
- \caption{The source galaxies are binned into $10$ redshift bins according to their mlz best photo-$z$ estimation.
-The blue histogram is the number distribution of the best photo-$z$ estimation.
-The vertical dashed lines are the bounds of bins.
-The galaxies are evenly distributed in each bins.}
-\end{figure}
+\subsection{Pixelization}
+\label{subsec:method-pix}
+We pixelize the smoothed shear field ($\gamma$) into a $N_\theta \times N_\theta \times N_s$ grid, where $N_\theta$ 
+is the number of pixels of two orthogonal axes of the transverse plane and $N_s$ is the number of pixels of the 
+line-of-sight axis. $\gamma_{\alpha}$ is used to denote the value recorded on pixel with index $\alpha$, where $\alpha=
+1..N_\theta \times N_\theta \times N_s$. The grid on the transverse plan is equally spaced so that we can perform the Fast 
+Fourier Transform (FFT) on the transverse plan.
 
-The loss function is defined as
-\begin{equation}\label{eq-lossFun}
-L = \norm{\gamma-\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} \alpha}^2_2+\lambda \norm{\alpha}^1_1 + \tau\mathrm{TSV}(\alpha_0),
+Similarly, we pixelize each frame \footnote{Here we have $N$ dictionary frames in total} of the projector into a $N_\theta 
+\times N_\theta \times N_l$ grid. The pixelization on the transverse plan of each parameter frame is exactly the same as 
+that of the observational frame. $N_l$ is the number of pixels on the line-of-sight axis. $x_{\beta}$ is used to denote the 
+value recorded on pixel with index $\beta$, where $\beta=1..N_\theta \times N_\theta \times N_l \times N$.
+
+With Einstein notation, eq. (\ref{eq-x2gamma-simple}) reduces to
+\begin{equation}
+\gamma_{\alpha} = A_{\alpha\beta} x_{\beta} + \epsilon_{\alpha},
 \end{equation}
-where $\norm{\gamma-\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} \alpha}^2_2$ is the normal chi-square, $\norm{\alpha^{N,P}}^1_1$ is the sparsity constrain, and $\mathrm{TSV}(\alpha^P)$ is the Total Squared Variation (TSV) constrain.
-$\norm{\bullet}_1$ and $\norm{\bullet}_2$ represent $l_1$ norm and $l_2$ norm, respectively.
-The $\mathrm{TSV}$ operator is defined as
-\begin{equation}
-\begin{split}
-\mathrm{TSV}(\alpha_0) =&  \sum_{ijk} \{ (\alpha_0[i,j,k]-\alpha_0[i+1,j,k])^2\\
-&+(\alpha_0[i,j,k]-\alpha_0[i,j+1,k])^2\\
-&+(\alpha_0[i,j,k]-\alpha_0[i,j,k+1])^2 \},
-\end{split}
-\end{equation}
-where $i=1..N_\theta$, $j=1..N_\theta$, are the pixel indexes for the two dimensions on the transverse plane, $k=1..N_l$ is the pixel index on the line-of-sight direction.
+where $\epsilon_{\alpha}$ refers the noise ($\epsilon$) on the pixel of index $\alpha$.
 
+\subsection{Loss Function with Constrains}
+\label{subsec:method-lossfun}
 \begin{figure}
@@
 
-We define
+We define the loss function as
+\begin{equation}\label{eq-lossFun}
+L(x) = \frac{1}{2} \norm{\gamma-\mathbf{A}x}^2_2 + \frac{1}{2}\tau \mathrm{TSV}(x)+\lambda \sigma \norm{x}_1 ,
+\end{equation}
+where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and $l^2$ norm, respectively. 
+$\mathrm{TSV}(x)$ refers to the total square variance of the first dictionary frame, which is defined as
 \begin{equation}
 \begin{split}
-f(\alpha) &= \norm{\gamma-\mathbf{M}\mathbf{P}\mathbf{Q}\mathbf{\Phi} \alpha}^2_2+ \tau\mathrm{TSV}(\alpha^P)\\
-&= \sum_{lm} A_{lm} \alpha_l \alpha_m + \sum_{l}B_{l} \alpha_l +C,
+\mathrm{TSV}(x) =\int d^2 \theta dz (\frac{\partial x}{\partial \theta_1})^2+\int d^2 \theta dz (\frac{\partial x}{\partial \theta_2})^2.
 \end{split}
 \end{equation}
-where $l,m$ go over the indexes of $(i,j,k,s)$.
+The total square variance can be expressed in a quadratic form as
+\begin{equation}
+\mathrm{TSV}(x)=\norm{\frac{\partial x}{\partial \theta_1}}^2_2+\norm{\frac{\partial x}{\partial \theta_2}}^2_2.
+\end{equation}
 
+The $l^1$ term is the sparsity constrain. The TSV term constrains on the smoothness of the mass distribution in the 
+point mass dictionary frame.
+
+The loss function defined on the pixelized data is
+\begin{equation}
+\begin{split}
+L(x)&=\frac{1}{2}(\gamma_{\alpha}-A^{*}_{\alpha\beta}x_{\beta})(\gamma_{\alpha}-A_{\alpha\mu}x_{\mu})\\
+&+\frac{\tau}{2}[(D^{1}_{\alpha\beta} x_{\beta})(D^{1}_{\alpha\mu}x_{\mu})
++ (D^{2}_{\alpha\beta} x_{\beta})(D^{2}_{\alpha\mu}x_{\mu})] \\
+&+ \lambda\sigma_\beta \norm{x_\beta}_1,
+\end{split}
+\end{equation}
+where $\mathbf{D^1}$ and $\mathbf{D^2}$ and difference operator on $\theta_1$ and $\theta_2$ directions, respectively.
+
+\subsection{Pathwise Coordinate Descent Algorithm}
+\label{subsec:method-pathwise}
 \begin{figure}
@@
 
-\subsubsection{FISTA}
-The basic FISTA algorithms is
+The loss function can be separated into a summation of a quadratic term and a $l^1$ term as
 \begin{equation}
-X^{(n+1)}_m=\mathrm{ST}_{\lambda} (\alpha_m -\frac{\mu}{2A_{mm}} \frac{\partial f}{\partial \alpha_m})|_{\alpha^{(n)}_m} ,
+ L(x)=G(x)+\lambda\sigma_{\beta}\norm{x_{\beta}}_1.
 \end{equation}
-where
-\begin{equation}
-\mathrm{ST}_{\lambda} (x) = \mathrm{sign} (x) \max (\abs{x}-\lambda,0)
-\end{equation}
-is the soft thresholding function.
-
+The quadratic term is defined as
 \begin{equation}
 \begin{split}
-t^{(n+1)} &= \frac{1+\sqrt{1+4(t^{(n)})^2}}{2},\\
-\alpha^{(n+1)}_m& = X^{(n+1)}_m+[\frac{t^{(n)}-1}{t^{(n+1)}}(X^{(n+1)}_m-X^{(n)}_m)].
+ G(x)&=\frac{1}{2}(\gamma_{\alpha}-A^{*}_{\alpha\beta}x_{\beta})(\gamma_{\alpha}-A_{\alpha\mu}x_{\mu})\\
+&+\frac{\tau}{2}[(D^{1}_{\alpha\beta} x_{\beta})(D^{1}_{\alpha\mu}x_{\mu})
++ (D^{2}_{\alpha\beta} x_{\beta})(D^{2}_{\alpha\mu}x_{\mu})],
 \end{split}
 \end{equation}
-The iteration is initialized with $t^{(0)}=1$ and $X^{(0)}=\alpha^{(0)}$.
+
+Many algorithms have been proposed to find the minima of this kind of loss function. We base our method on the 
+coordinate descent algorithm \citep{coordinateDescent-Wright2015} which is described as follows.
+Firstly, we initialize the projector as $x^{(1)}=0$. According to the coordinate descent algorithm, we subsequently 
+update the projector ($x$) along the direction of one specific coordinate ($i$) as
+\begin{equation}
+x^{(n+1)}_{i}=\mathrm{ST}_{\lambda\sigma_{i}} (x^{(n)}_{i} -\frac{\partial_i G(x^{(n)})}{A_{\alpha i}A_{\alpha i}+4\tau}), 
+\end{equation}
+where $\mathrm{ST}$ is the soft thresholding function defined as
+\begin{equation}
+\mathrm{ST}_{\lambda} (x) = \mathrm{sign} (x) \max (\abs{x}-\lambda,0),
+\end{equation}
+and the projector along the other coordinates are kept the same. The minima is finally approached by iteratively updating 
+along each coordinate for multiple times.
+
+To simplify the notation, here we define the projector difference for the $n$-th iteration as
+\begin{equation}
+ \Delta x ^{(n)} = -\frac{\bigtriangledown G(x^{(n)})}{A_{\alpha i}A_{\alpha i}+4\tau},
+\end{equation}
+where $\bigtriangledown G(x^{(n)})$ refers to the gradient of quadratic function $G$ at $x^{(n)}$. The signal to noise ratio 
+(SNR) of the projector difference is defined as $s^{(n)}=\Delta x ^{(n)}/\sigma$.
+
+In our algorithm, the coordinate descent algorithm in conducted in a pathwise manner \citep{pathwise-Friedman2007}. 
+We begin with a regulation parameter 
+($\lambda^{(1)}$) which is slightly smaller than the maximum coordinate of $s^{(1)}$ (denoted as $s_{\rm{max}}^{(1)}$) so that 
+in the first iteration, we only update on the coordinate with the maximum SNR. Then, we find the maximum projector difference 
+SNR of the second iteration ($s_{\rm{max}}^{(2)}$) and update the regulation parameter to $\lambda^{(2)}$, where $\lambda^{(2)}$
+is slightly smaller than $s_{\rm{max}}^{(2)}$.
+
+The algorithm is fully described in Algorithm \ref{alg-1}.
+
+\begin{algorithm}[H]
+    \label{alg-1}
+    \caption{Our Algorithm}
+  \begin{algorithmic}[1]
+    \INPUT   $\gamma$: Complex $3$-D array of shear
+    \OUTPUT  $\delta$: $3$-D array of density contrast
+    \STATE \textbf{Initialization} ‎$x^{(1)} = 0$, $\lambda^{(1)} = 100$
+    \WHILE{$i \leq N_{\rm{iter}}$}
+      \STATE 
+      \STATE 
+      \STATE 
+      \STATE 
+    \ENDWHILE
+  \end{algorithmic}
+\end{algorithm}
 
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=0.3\textwidth]{resultExp-tau010.png}
+\includegraphics[width=0.3\textwidth]{resultExp-tau015.png}
+\includegraphics[width=0.3\textwidth]{resultExp-tau020.png}
+\caption{The density map reconstructed for a halo with mass=$3.16\times 10^14 M_{\sun}/h$, $z=0.51$. The left panel shows
+the results with $\tau=0.10$, the middle panel is the result for $\tau=0.15$, the right panel is for $\tau=0.20$.}
+\end{figure*}
+
 \subsection{Detection Rate}
@@
 \bibliographystyle{aasjournal}
-\bibliography{weak_lensing,lensCat,cosmoSim,cmbObs,gglens,shearCor,massMap,other}
+\bibliography{weak_lensing,lensCat,cosmoSim,cmbObs,gglens,shearCor,massMap,other,optimize}
 
 \appendix
-\section{General linear LASSO}
-Note that the loss function defined in equation (\ref{eq-lossFun}) into
-\begin{equation}
-L(\alpha)=f(\alpha) +\lambda \norm{\alpha}^1_1,
-\end{equation}
-where
-\begin{equation}
-f(\vec{\alpha}) = \vec{\alpha}^T \mathbf{A} \vec{\alpha} + \vec{B} \cdot \vec{\alpha} +C.
-\end{equation}
-Using Einstein notation, we have
-\begin{equation}
-L(\alpha_i) = A_{ij} \alpha_i \alpha_j + B_{i} \alpha_i + C +\lambda_i \abs{\alpha_i}.
-\end{equation}
-Set the initial parameter vector is $\vec{\alpha}^{(0)}$. We focus on one specific parameter with index $\mu$ and fix other parameters with indexes $i \neq \mu$
-\begin{equation}
-L(\alpha_\mu| \alpha^{(0)}_{i\neq\mu})=A_{\mu\mu} \alpha_\mu^2 + (A_{i\mu}\alpha^{(0)}_i+A_{\mu i}\alpha^{(0)}_i +B_\mu) \alpha_\mu +\lambda_\mu \abs{\alpha_\mu} +B_i \alpha^{(0)}_i + \lambda_i \abs{\alpha^{(0)}_i} +C
-\end{equation}
-reach its minimum at $\mathrm{ST}_{\lambda} (\alpha_\mu -\frac{\partial_\mu f(\alpha_\mu| \alpha^{(0)}_{i\neq\mu})}{2A_{\mu\mu}}) |_{\alpha_\mu^{(0)}}$,
-where $\mathrm{ST}_{\lambda} (x) = \mathrm{sign} (x) \max (\abs{x}-\lambda,0)$ is the soft thresholding function. Then the parameter can be updated
-\begin{equation}
-\alpha^{(1)}_\mu \leftarrow \mathrm{ST}_{\lambda} (\alpha_\mu -\frac{\partial_\mu f(\alpha_\mu| \alpha^{(0)}_{i\neq\mu})}{2A_{\mu\mu}}) |_{\alpha_\mu^{(0)}}.
-\end{equation}
-Other parameters are subsequently updated in the same way. The minimum of the loss function can be reached by iterating the parameter update.
-
 \end{document}

### 2020-09-30 python/sparseBase.py
prepare to use 20 lens plane

@@ -358,7 +358,7 @@ class massmapSparsityTask():
             normTmp2=   np.sqrt(np.sum(alphaTmp2**2.))
             if normTmp2>norm:
                 norm=normTmp2
-        self.mu    = 1./norm/1.2
+        self.mu    = 1./norm/1.5
         return
 
     def prox_sigmaA(self):

### 2020-09-30 doc/paper_ms_method_HSCY1/ms.tex

\documentclass[twocolumn]{aastex62}
\emergencystretch=1.em

\usepackage{amsmath,amsthm,amsfonts,amssymb,bm}
% for big dot
\makeatletter
\newcommand*\bigcdot{\mathpalette\bigcdot@{.5}}
\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\newcommand{\argmax}{\mathop{\rm arg~max}\limits}
\newcommand{\argmin}{\mathop{\rm arg~min}\limits}

\usepackage{listings}
\usepackage{physics}
\usepackage{multirow}
\usepackage{color}

%\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{epstopdf}
\usepackage{natbib}
\usepackage{commath}
\hypersetup{breaklinks}
\DeclareMathOperator{\arccosh}{arccosh}
\newcommand \figPath{./}
\newcommand \redColor{\color{red}}
\renewcommand\labelenumi{(\roman{enumi})}
\renewcommand\theenumi\labelenumi

\usepackage{algorithm,algcompatible}

%\DeclareMathOperator*{\argmax}{\arg\!\max}
\algnewcommand\INPUT{\item[\textbf{Input:}]}
\algnewcommand\OUTPUT{\item[\textbf{Output:}]}

\makeatother
%\newcommand{\jcap}{JCAP}

\begin{document}
\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction}
%\author{Xiangchong Li}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Masamune Oguri}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
%\author{Wentao Luo}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{HSC Collaboration}
%\noaffiliation
%\email{xiangchong.li@ipmu.jp}

\begin{abstract}
A new method is developed to reconstruct $3$-D density contrast fields from photometric weak lensing shear measurements.
The $3$-D density contrast map is modeled as a superposition of basis atoms. The basis atoms are designed to represent 
the structure of NFW halos which have $2$-D multi-scale NFW surface density profiles on the transverse plane and $1$-D 
Dirac delta functions in the line-of-sight direction. With the prior assumption that the basis atoms have a spare distribution, 
the density field is reconstructed using the adaptive lasso algorithm. The method is tested with realistic simulation 
using HSC-like shape noise and photo-$z$ uncertainties. 
{\redColor{Add descriptions on the outcomes of the test on the simulations.}}
\end{abstract}

\section{Introduction}
Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line-of-sight
due to the influence of gravity. As a result of the light distortion, the shapes of the background galaxies are coherently
sheared. Such effect, which is known as weak lensing, imprints the information of foreground mass density distribution
to the background galaxy images and offers a direct probe into the mass density distribution in our universe
\citep[see][for recent reviews]{revKilbinger15,revRachel17}.

Adopting the thin lens approximation, the expected shear measurements ($\gamma$) on distant galaxies are related to the 
foreground density contrast field ($\delta$) through a linear transformation
\begin{equation} \label{eq-intro-delta2shear}
 \gamma=\mathbf{T} \delta,
\end{equation}
where $\mathbf{T}$ is used to denote the linear transformation operator which includes not only physical lensing effect
but also includes observational systematic effects from the observation (e.g. pixelization and smoothing of shear field in
transverse plane, photo-$z$ uncertainties).

Several large scale surveys target to study the weak lensing effect at high precision level (e.g. HSC \citep{HSC1-data}, KIDS
\citep{KIDS13}, DES \citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, WFIRST \citep{WFIRST15}).

The primary goal of most weak lensing surveys is to constrain the cosmology model through $2$-point correlations. The studies
include galaxy-galaxy lensing which cross correlating the shear field ($\gamma$) with the positions of foreground galaxies
\citep{gglens-GAMA-Han2014,gglens-BossCFHTMore2015,gglens-DES1},
and cosmic shear which auto-correlates the shear measurements
\citep{cosmicShearRealKids450,cosmicShear-DES1,cosmicShear_HSC1_Chiaki2019,cosmicShear_HSC1_Hamana2019}.
Since shear is directly related to the matter distribution as shown in eq. (\ref{eq-intro-delta2shear}), Galaxy-galaxy lensing
probes into the correlation between the matter field and galaxy field, on the other hand, cosmic shear probes into the
auto-correlation of matter field.

Reconstructions of density map from shear measurements also receive considerable interest. $2$-D density map reconstruction 
which reconstructs the integration of mass along the line-of-sight direction has been well studied by the community
\citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016}
and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}.

In order to fully reconstruct the $3$-D mass density distribution ($\delta$) from the tomographic shear observations ($\gamma$),
the density contrast field is modeled as a superposition of basis atoms in a dictionary space
\begin{equation} \label{eq-intro-dict}
 \delta= \mathbf{\Phi} x,
\end{equation}
where $\mathbf{\Phi}$ is the transformation operator from the parameters in the dictionary space to the density contrast 
and $x$ denotes the parameters in the dictionary space. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field
in Fourier space, which is equivalent to model the mass field with sinusoidial functions. On the other hand,
\citet{LSS-massMap-Glimpse3D-Leonard2014} models the mass field with Starlets.

The model parameters are estimated through solving an optimization problem and the estimator is defined as
\begin{equation}
\hat{x}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{T\Phi} x)}_2^2+ \lambda C(x) \right\},
\end{equation}
where $\norm{\Sigma^{-\frac{1}{2}}(\gamma - \mathbf{T\Phi} x)}_2^2$ is the chi-square term\footnote{weighted by the
inverse of the diagonal covariance matrix of error on the shear measurements ($\Sigma$).} measuring
the residuals between the prediction and the data, while $C(x)$ is the regularization term measuring the deviation of
the estimation of the parameter ($x$) from the prior assumptions. Such estimation prefer the parameters that are able
to describe the observations and also align with the prior assumptions. The regularization parameter $\lambda$ adjusts 
the relative weight between the observations and prior assumptions in the optimization process.

\citet{LSS-massMap-Wiener-Simon2009} propose to use the $l^2$ ridge regulation ($C=\norm{x}^2_2$) to find the best-fit 
solution in Fourier space. \citet{HSC1-massMaps} apply the method of \citet{LSS-massMap-Wiener-Simon2009} to the first 
year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}. 
{\redColor{Why we use $l^1$ in this paper, what is the difference between $l^1$ and $l^2$.}}

\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use the $l^1$ lasso regulation ($C=\norm{x}^1_1$) to find the
best-fits solution in a Starlets dictionary space. However, the Starlets functions are not designed to model the 
clumpy mass distributions in the universe and \citet{LSS-massMap-Glimpse3D-Leonard2014} use a greedy descent algorithm 
to find minima of the loss function, which is not guarateed to converge to the global minima ({\redColor{cite..}}).

$N$-body simulations have shown that the dark matter is distributed in halos connected by filaments, and the density 
distribution of a halo follows the NFW profile \citep{halo-NFW1997ApJ}.
We construct a dictionary which is composed of multi-scale NFW atoms and point mass atoms. The multi-scale NFW atoms are used 
to model the structures within halos. They follow multi-scale surface density profiles of NFW halos \citep{haloModel-TJ2003-3pt}
on the transverse plane and Dirac delta function in the line-of-sight direction. By using Dirac delta functions in the 
line-of-sight direction, the depth of halo is neglected \citep{LSS-massMap-Glimpse3D-Leonard2014} since the resolution 
scale of the reconstruction in the line-of-sight direction is much larger than the halo scale.
The point mass atoms are used to model the structures in the filaments and structures smaller than the reachable resolution
on the transverse plane. Furthermore, the point mass atoms make our dictionary space complete.
With the prior assumption that the density contrast field is sparse in the dictionary space, the adaptive lasso regularization
\citep{AdaLASSO-Zou2006} is used to reconstruct a high signal-to-noise-ratio (SNR) density contrast field.

Comparing with \citet{LSS-massMap-Glimpse3D-Leonard2014}, our dictionary space is built up to describe the clumpy mass 
in the universe which has clear physical a motivation. Moreover, we use adaptive lasso which does not rely on any greedy 
descent alorithm, therefore the estimation is guarateed to converge to the global minimum.

This paper is organized as follows.
Section \ref{sec:Method} proposes the new method for $3$-D density map reconstruction.
Section \ref{sec:Sim} introduces the realistic simulations we use to test the new method.
Section \ref{sec:Res} presents the results of our method on the simulations.
Section \ref{sec:Sum} summarizes and discusses the future development of the method.

\section{Methodology}
\label{sec:Method}

In this section, we first review how foreground density distributions induce weak lensing shear distortions on background
galaxies in section \ref{subsec:method-delta2shear}.
Then, we introduce the dictionary space used to model the foreground density map in section \ref{subsec:method-dictionary}.

Subsequently, in section \ref{subsec:method-Systematics} we discuss several systematic effects from observations which include 
photo-$z$ uncertainty (section \ref{subsec:method-photoz}),
smoothing (section \ref{subsec:method-smoothing}),
masking(section \ref{subsec:method-msknoise}),
and pixelization (section \ref{subsec:method-pixel}).

Finally, we find the the sparse solution in section \ref{subsec:method-reversion} using the adaptive lasso algorithm 
\citep{AdaLASSO-Zou2006} optimized with the FISTA alogrithm \citep{FISTA-Beck2009}.

\subsection{Lensing}
\label{subsec:method-delta2shear}

\begin{figure*}
    \includegraphics[width=0.95\textwidth]{nfwlet-atom-2D.pdf}
    \caption{The NFW models with different scale radius ($r_s$). The first row shows the NFW models in Fourier
            space and the second row shows the NFW model in Real space.}
\end{figure*}

The lensing convergence $\kappa$ at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line-of-sight is
\citep{LSS-massMap-Glimpse3D-Leonard2014}
\begin{equation}
\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s}
\frac{\delta(\vec{\theta},\chi_l)}{a(\chi_l)},
\end{equation}
where $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the matter density parameter, $c$ is the speed
of light, and $a(\chi_l)$ is the scale parameter at the lens position.

Substitute comoving distance ($\chi$) with redshift ($z$)
\begin{equation}\label{eq-delta2kappa}
\kappa(\vec{\theta},z_s)=\int_0^{z_s} dz_l K(z_l,z_s)\delta(\vec{\theta},z_l).
\end{equation}
where $K(z_l,z_s)$ is the lensing kernel defined as
\begin{equation}
K(z_l,z_s) =
\begin{cases}
\frac{3H_0\Omega_M}{2 c} \frac{\chi_l \chi_{sl} (1+z_l)}{\chi_{s} E\left(z_l\right)} & (z_s>z_l),\\
0&(z_s \leq z_l).
\end{cases}
\end{equation}

As shown in \citet{massMap-KS1993}, the shear distortion is related to the kappa field at the redshift plane as
\begin{equation}\label{eq-kappa2gamma}
\gamma_L(\vec{\theta},z_s) = \int  d^2 \theta' D(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s),
\end{equation}
where
\begin{equation}
D(\vec{\theta})=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2}.
\end{equation}
Here we denote the physical shear distortions as $\gamma_L$ and we note that the observed shear measurements are the
physical shear distortions influenced by systematics which will be discussed in the following subsections.

Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}), the physical shear signal is derived as
\begin{equation}\label{eq-delta2gammat}
\gamma_L(\vec{\theta},z_s) = \int_0^{z_s} \frac{dz_l}{\delta_{c}(z_l,z_s)} \int d^2 \theta' \vec{D}(\vec{\theta}-\vec{\theta'}) \delta(\vec{\theta'},z_l).
\end{equation}

To simplify the expression, we define the lensing transform operator as
\begin{equation}
\mathbf{Q}=\int_0^{z_s} \frac{dz_l}{\delta_{c}(z_l,z_s)} \int d^2 \theta'  \vec{D}(\vec{\theta}-\vec{\theta'}),
\end{equation}
and eq. (\ref{eq-delta2gammat}) is simplified to
\begin{equation} \label{eq-delta2gammat-simp}
\gamma_L=\mathbf{Q}\delta.
\end{equation}

\subsection{Dictionary}
\label{subsec:method-dictionary}
\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
 \caption{The source galaxies are binned into $10$ redshift bins according to their mlz best photo-$z$ estimation.
        The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines
        are the bounds of bins. The galaxies are evenly distributed in each bins.}
\end{figure}

The density contrast field is modeled as a superposition of basis atoms in the dictionary space $\{\phi_0,\phi_1,...\phi_{N}\}$.
\begin{equation}\label{eq-x2delta}
\delta(\vec{r}) = \sum_{s=0}^{N} \int d^3 r' \phi_s(\vec{r}-\vec{r'}) x_s(\vec{r'}),
\end{equation}
where $\phi_s(\vec{r})$ is the basis vector of the dictionary space, and $x_s$ is the corresponding projection
coefficients of the density contrast field onto the basis vectors.

These basis vectors are composed of multi-scale NFW atoms $\{\phi_1,..,\phi_{N}\}$ and point
mass atoms $\{\phi_0\}$. $\phi_0$ is a $3$-D Dirac delta function
\begin{equation}
\phi_0(\vec{r})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
\end{equation}
on the transverse plane, the NFW atoms ($\{\phi_1,...,\phi_N\}$) follow surface density profiles of NFW halos
\citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and truncation radius $c \theta_\alpha$ ,
where $c$ is known as concentration of NFW halo.
As the scale of halo is much less than the reachable redshift resolution, we neglect the depth of halo on the
line-of-sight direction and set the profiles of NFW atoms in the line-of-sight direction to $1$-D Dirac delta functions
\citep{LSS-massMap-Glimpse3D-Leonard2014}. The NFW atoms are expressed as
\begin{equation}
\begin{split}
\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 } F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
&  (s=1..N)
\end{split}
\end{equation}
where
\begin{equation}
F(x)=
\begin{cases}
-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccosh \left(\frac{x^2+c}{x(1+c)}\right)}{(1-x^2)^{3/2}}  & (x<1),\\
\frac{\sqrt{c^2-1}}{3(1+c)} (1+\frac{1}{c+1}) & (x=1),\\
-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccos\left(\frac{x^2+c}{x(1+c)}\right)}{(x^2-1)^{3/2}} & (1<x\leq c),\\
0& (x>c).
\end{cases}
\end{equation}
$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=9$ for NFW atoms in different scale frames.

To simplify the notation, we define the projection parameters as a column vector:
$x=\begin{pmatrix}
x_{0}\\
x_{1}\\
...\\
x_{N}
\end{pmatrix}$,
and the dictionary transform operator as a row vector:
\begin{equation}
\mathbf{\Phi}=\begin{pmatrix}
\int d^3r\phi_0(\vec{r}) ~\int d^3r \phi_1(\vec{r})~ ...~\int d^3r \phi_{N}(\vec{r})
\end{pmatrix}.
\end{equation}
We substitute eq. (\ref{eq-x2delta}) into eq.(\ref{eq-delta2gammat})
\begin{equation}\label{eq-x2gammat}
\gamma_L=\mathbf{Q}\mathbf{\Phi} x.
\end{equation}

Our prior assumption is that the mass density field is sparse in the dictionary space and we will conduct
adaptive lasso \citep{AdaLASSO-Zou2006} to find a sparse solution of the mass reconstruction problem in the
dictionary space.

We note that the shear measurements are deviated from the physical shear prediction due to the systematics
from observations. The influence of systematics is carefully studied and added to the forward modeling in the
following subsections.

\subsection{Systematics}
\label{subsec:method-Systematics}

\subsubsection{Photo-$z$ Uncertainty}
\label{subsec:method-photoz}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
 \caption{The $1$-D slices of NFW models with different scale radius ($r_s=0,1,2,4,8$).}
\end{figure}

Since the photometric redshifts of source galaxies in the current large scale survey are estimated with
a limited number of photometric bands, the estimated redshifts of galaxies suffer from large uncertainties.
Such uncertainties smear the structure along the line-of-sight direction since a galaxy with a best fit photo-$z$
estimation of $z_s$ has a possibility of being actually located at redshift $z$. Such probability is denoted as $P(z|z_s)$
and the expected shear distortion on this galaxy is
\begin{equation}\label{eq-delta2gamma-poz}
\gamma_L(\vec{\theta},z_s) \rightarrow \int dz_s P(z|z_s) \gamma_L(\vec{\theta},z_s).
\end{equation}
With the definition of photo-$z$ smearing operator
\begin{equation}
\mathbf{P} = \int dz_s P(z|z_s),
\end{equation}
the photo-$z$ uncertainties changes the shear as $\gamma_L \rightarrow \mathbf{Q} \gamma_L$.

\subsubsection{Smoothing}
\label{subsec:method-smoothing}

The observed galaxies have random irregular (unequally-spaced) spacial distribution. To benefit the computational
speed, we smooth the shear measurements from galaxy shapes and pixelise the smoothed measurements onto regular grids.

The smoothing is conducted by convolving the measurements with a smoothing kernel
\begin{equation}
\hat{\gamma}  = \frac{\sum_i  W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) e_i}{\sum_i R_i W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) },
\end{equation}
where $W(\vec{\theta},z)$ is a $3$-D smoothing kernel. $e_i$, $R_i$, $z_i$ and $\theta_i$ are the ellipticity,
response, reshift, and transverse position of the `$i$-th' galaxy in the galaxy catalog.

$W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line-of-sight component
$W_\times(z)$
\begin{equation}
W(\vec{\theta},z)=W_T(\vec{\theta}) W_\times (z).
\end{equation}
In this paper, we set
\begin{equation}
\begin{split}
W_T(\vec{\theta}) &=\frac{1}{2\pi\beta^2}\exp(-\frac{|\vec{\theta}|}{2\beta^2}),\\
W_\times (z) &=
\begin{cases}
1/\Delta z& (|z|<\Delta z/2),\\
0& else.
\end{cases}
\end{split}
\end{equation}

With the approximation that the density of galaxy number vary slowly on the smoothing scale and the fact that
$\int d^3r W(\vec{r})=1$, the smoothing operator is defined as
\begin{equation}
\mathbf{W} = \int d^3 r' W(\vec{r}-\vec{r'}),
\end{equation}
and the relation between shear signal and projections in the dictionary space is
$\gamma_L \rightarrow \mathbf{W} \gamma_L$.

\subsubsection{Masking}
\label{subsec:method-msknoise}

In the forward modeling, normally the shear field has its prediction on any points within a regular region.
However, in real observations, the boundary of the survey, where shear measruements is recorded, is always
irregular. Moreover, there are also many regions are masked out due to the existence of neighboring bright
stars or bad pixels as bight stars and bad pixels are likely to bias the shape measurements.
Therefore, it is necessary to add an mask on the shear field prediction in the forward modeling to match
the prediction with realistic observations. The mask changes the shear prediction as follows
\begin{equation}\label{eq-delta2gamma-final}
\gamma_L(\vec{\theta},z) \rightarrow M(\vec{\theta},z) \gamma_L(\vec{\theta},z),
\end{equation}
$M(\vec{\theta},z_s)$ is the masking function which is defined as
\begin{equation}
 M(\vec{r})=
\begin{cases}
0 & \vec{r}~\rm{resides~in~masked~area}\\
1 & \rm{else}.
\end{cases}
\end{equation}

We define the masking operator as
\begin{equation}
\mathbf{M}= \int d^3 r' M(\vec{r'}) \delta_D(\vec{r}-\vec{r'}),
\end{equation}
where $\delta_D(\vec{r})$ is $3$-D Dirac delta function. The shear is influenced by the masking through
$\gamma_L \rightarrow \mathbf{M} \gamma_L$.

The final observed shear field, taking into account all of the aforementioned systematics from observations,
is
\begin{equation}\label{eq-x2gamma-final}
\gamma =\mathbf{M} \mathbf{W} \mathbf{P} \mathbf{Q} \mathbf{\Phi} x.
\end{equation}
For simplicity, we denote $\mathbf{A}=\mathbf{M} \mathbf{W} \mathbf{P} \mathbf{Q} \mathbf{\Phi} $ and
eq. (\ref{eq-x2gamma-final}) is written as
\begin{equation}\label{eq-x2gamma-simple}
\gamma=\mathbf{A} x.
\end{equation}

\subsubsection{Pixelization}
\label{subsec:method-pixel}
We pixelize the smoothed shear field into a $N_\theta \times N_\theta \times N_s$ grid, where $N_\theta$
is the number of pixels of two orthogonal axes of the transverse plane and $N_s$ is the number of pixels of the
line-of-sight axis. $\gamma_{\alpha}$ is used to denote the value recorded on pixel with index $\alpha$, where $\alpha=
1,...,N_\theta \times N_\theta \times N_s$. The grid on the transverse plan is equally spaced, therefore Fast Fourier
Transform (FFT) can be used to boost the speed of linear operation on the transverse plan.

Similarly, we pixelize each scale frame of the parameter $x$ into a $N_\theta \times N_\theta \times N_l$ grid. 
The pixelization of the parameter $x$ on the transverse plan for each scale frame is exactly the same as the 
pixelization of the smoothed shear field on the transverse plane. $N_l$ is the pixel number of the line-of-sight 
axis. $x_{\beta}$ is used to denote the element of parameter vector $x$ with index $\beta$, where $\beta=1,...
,N_\theta \times N_\theta \times N_l \times N$. The elements of the forward transform matrix $\mathbf{A}$ is denoted 
as $A_{\alpha\beta}$.

We term the column vectors of the transform matrix $\mathbf{A}$ as the effective basis vectors. We note that the effective 
basis vectors have different $l^2$ norm. The $l^2$ norm of the $i'th$ column vectors of the effective basis vectors are 
$\mathcal{N}_{i}=\sum_\alpha A_{i\alpha}A_{i\alpha}$. Before solving the density map inversion problem, we normalize the column
vectors of the transform matrix through
\begin{equation}
\begin{split}
A'_{\alpha\beta}&=A_{\alpha\beta}/\mathcal{N}_{\alpha}^{\frac{1}{2}},\\
x'_{\beta}&=x_{\beta}\mathcal{N}_{\beta}^{\frac{1}{2}}.\\
\end{split}
\end{equation}

\subsection{Density map reversion}
\label{subsec:method-reversion}
\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
 \caption{The PDF of photo-$z$ error for $10$ source redshift bins.}
\end{figure}

\subsubsection{Adaptive lasso}
The lasso algorithm uses $l^1$ penalty as the regularization term and the estimator is defined as
\begin{equation}
\hat{x'}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{A'} x')}_2^2+ \lambda \norm{x'}^1_1\right\},
\end{equation}
where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and $l^2$ norm, respectively. The $l^p$ norm is
defined as
\begin{equation}
\norm{x'}_p=(\sum_{i} |x'|^p_i)^{\frac{1}{p}}.
\end{equation}

Given that the parameters to measure is sparse in the parameter space, the  lasso algorithm can select the parameters 
which are relevant to the measurements and simultaneously estimate the value of the selected parameters. However, it has 
been shown by \citet{AdaLASSO-Zou2006} that when the column vectors of $\mathbf{A'}$ are highly correlated, lasso cannot 
select the related parameters from the parameter space consistently. Moreover, the estimated parameters are biased due to 
the shrinkage process in the lasso regression.

\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different coefficients 
in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. Lasso estimation is performed in the first step 
and achieve a preliminary lasso estimation of parameter ($\hat{x'}^{\rm{lasso}}$). In the second step, the lasso estimation is used 
to weight the penalization on the parameters. With the definition of the adaptive lasso weight 
\begin{equation}
\hat{w}= \frac{1}{\abs{\hat{x'}^{\rm{lasso}}}^\tau},
\end{equation}
here we set the hyper-parameter $\tau$ to $2$, the adaptive lasso estimator is expressed as
\begin{equation}\label{eq-lossFun}
\hat{x'}=\argmin_{x'} \left\{ \frac{1}{2} \norm{\Sigma^{-\frac{1}{2}}(\gamma-\mathbf{A'}x')}^2_2 +
\hat{w}\lambda \norm{x'}^1_1\right\}.
\end{equation}

The loss function can be rewritten with Einstein notation
\begin{equation}
\begin{split}
L(x')&=\frac{1}{2}(\Sigma^{-1})_{\alpha\beta}(\gamma^{*}_{\alpha}-A'^{*}_{\alpha i}x'_{i})
(\gamma_{\beta}-A'_{\beta j}x'_{j})\\
&+ \lambda \hat{w_\beta} \abs{x'_\beta}.
\end{split}
\end{equation}
To simplify the notification, we define the quadruple term in the loss function as $G(x')$:
\begin{equation}
G(x')=\frac{1}{2}\Sigma^{-1}_{\alpha\beta}(\gamma^{*}_{\alpha}-A'^{*}_{\alpha i}x'_{i})
(\gamma_{\beta}-A'_{\beta j}x'_{j}).
\end{equation}

\subsubsection{FISTA}
In this work, we apply the Fast Iterative Soft Thresholding Alorithm (FISTA) of \citet{FISTA-Beck2009} to solve 
the adaptive lasso estimator.

The parameter vector is initialized as $x^{(1)}=0$. According to the FISTA algorithm, we iteratively 
update the elements of the parameter vector ($x$). In the n'th iteration, a temporary update is first calcualted as
\begin{equation}
x'^{(n+1)}_{i}=\mathrm{ST}_{\lambda} \left(x'^{(n)}_{i} -\mu \partial_i G(x'^{(n)})\right),
\end{equation}
where $\mathrm{ST}$ is the soft thresholding function defined as
\begin{equation}
\mathrm{ST}_{\lambda} \left(x'\right) = \mathrm{sign} (x') \max \left(\abs{x'}-\lambda,0\right).
\end{equation}
$\mu$ is the step size of the gradient descent iteration. 
$\partial_i G(x'^{(n)})$ refers to the i'th element of the gradient
vector of $G$ at point $x'^{(n)}$
\begin{equation}
\partial_i G(x'^{(n)})=\Sigma^{-1}_{\alpha\beta}\Re\left(A'^{*}_{\alpha i}(\gamma_{\beta}-A'_{\beta j}x'_{j})\right),
\end{equation}
where $\Re\left( \bullet \right)$ is the function returns the real part of the input function.
The FISTA algorithm requires an additional step amounting to a weighted average between
$x'^{(n+1)}$ and $x'^{(n)}$:
\begin{equation}
\begin{split}
t^{(n+1)}&=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2},\\
x'_{n+1} &\leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)}),
\end{split}
\end{equation}
where the relative weight is initialized as $t^{(1)}=1$.

Note that the FISTA algorithm coverges as long as the gradient descent step size $\mu$ satisfies
\begin{equation}
 0< \mu < \frac{1}{ \norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }},
\end{equation}
where $\norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }$ refers to the spectrum norm of the matrix
$\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$. The spectral norm is estimated using random
vectors. We simulate large number of random vectors with $l^2$ norms equal one with different realizations. Then, 
the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is applied to each random vector and get a 
corresponding transformed random vector. The spectral norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$
is the maximum $l^2$ norm of the transformed vectors.

\subsubsection{The Algorithm}
The algorithm is described in Algorithm \ref{alg-1}.

\begin{algorithm}[H]
\renewcommand{\thealgorithm}{}
\label{alg-1}
\caption{Our Algorithm}
\begin{algorithmic}[1]
\INPUT $\gamma$: Pixelized complex $3$-D array of shear
\OUTPUT  $\delta$: $3$-D array of density contrast
\STATE Normalize column vectors of $\mathbf{A}$
\STATE Estimate step size $\mu$ and $\mathbf{\Sigma}$
\STATE \textbf{Initialization:} ‎
\STATE $x'^{(1)} = 0$ 
\STATE $\hat{w}=1$
\STATE $t^{(1)}=1$,$i=1$, $j=1$
\WHILE{$j \leq 2$}
    \WHILE{$i \leq N_{\rm{iter}}$}
        \STATE $x'^{(n+1)}_{i}=\mathrm{ST}_{\hat{w}\lambda} \left(x'^{(n)}_{i} -\mu \partial_i G(x'^{(n)})\right)$
        \STATE $t^{(n+1)}=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2}$
        \STATE $x'_{n+1} \leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)})$
    \ENDWHILE
\STATE \textbf{Reinitialization:} ‎
\STATE $\hat{w}\leftarrow \abs{\hat{x'}^{\rm{lasso}}}^{-2}$
\STATE $\hat{x'}^{(1)} \leftarrow x'^{(N_{\rm{iter}})}$
\STATE $t^{(1)}\leftarrow1$,$i\leftarrow1$
\ENDWHILE
\STATE $\delta=\mathbf{\Phi}\mathcal{N}^{-\frac{1}{2}}x'^{(N_{\rm{iter}})}$
\end{algorithmic}
\end{algorithm}

\section{Simulation}
\label{sec:Sim}
This section simulates lensing shear fields induced by a group of dark matter halos with various halo mass and redshifts.
HSC-like shape measurement error and photo-$z$ error are added to the shear field.

\subsection{Weak Lensing Fields}

We simulate weak lensing shear fields of NFW halos according to \citet{haloModel-TJ2003-3pt}
and sample halos in the mass-redshift plane as shown in Figure \ref{fig:mass-redshift}.
We assume a dependency of the concentration on the mass and the redshift of a halo as \citep{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}

\begin{figure}[!ht]
 \centering
 \includegraphics[width=0.45\textwidth]{mass-redshift-sampling.pdf}
 \caption{The sampling points of halos in the mass-redshift plane.}
 \label{fig:mass-redshift}
\end{figure}

\subsection{HSC-like Systematic}
\subsubsection{Shear Measurement Error}
\begin{figure}[!ht]
 \centering
 \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
 \caption{HSC-like measurement error on the first component of shear ($g_1$).}
 \label{fig:mass-redshift}
\end{figure}

\subsubsection{Photo-$z$ Error}

\section{Results}
\label{sec:Res}

\begin{figure*}
\centering
\includegraphics[width=0.3\textwidth]{resultExp-tau010.png}
\includegraphics[width=0.3\textwidth]{resultExp-tau015.png}
\includegraphics[width=0.3\textwidth]{resultExp-tau020.png}
\caption{The density map reconstructed for a halo with mass=$3.16\times 10^14 M_{\sun}/h$, $z=0.51$. The left panel shows
the results with $\tau=0.10$, the middle panel is the result for $\tau=0.15$, the right panel is for $\tau=0.20$.}
\end{figure*}

\subsection{Detection}

\subsection{Redshift}

\subsection{Density Map}

\section{Summary}
\label{sec:Sum}

\begin{figure}[!ht]
 \centering
 \includegraphics[width=0.45\textwidth]{noise_std_map_pix.pdf}
 \caption{The standard deviation map of shear measurement error for the fifth source bin ($0.69 \leq z < 0.80 $).}
\end{figure}

\bibliographystyle{aasjournal}
\bibliography{citation}

\appendix
\end{document}

\subsection{Pathwise Coordinate Descent Algorithm}
\label{subsec:method-pathwise}
\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{lensing_efficiency.pdf}
 \caption{The blue line shows the normalized lensing efficiency for lens bin at $z_{l}=0.51$.
 The orange line is the normalized lensing efficiency while taking into account the photo-$z$ uncertainty.
 The green data points show the averaged $\kappa$ field for different redshift bins in the simulation.}
\end{figure}

The loss function can be separated into a summation of a quadratic term and a $l^1$ term as
\begin{equation}
 L(x)=G(x)+\lambda\sigma_{\beta}\norm{x_{\beta}}_1.
\end{equation}
The quadratic term is defined as
\begin{equation}
\begin{split}
 G(x)&=\frac{1}{2}(\gamma_{\alpha}-A^{*}_{\alpha\beta}x_{\beta})(\gamma_{\alpha}-A_{\alpha\mu}x_{\mu})\\
&+\frac{\tau}{2}[(D^{1}_{\alpha\beta} x_{\beta})(D^{1}_{\alpha\mu}x_{\mu})
+ (D^{2}_{\alpha\beta} x_{\beta})(D^{2}_{\alpha\mu}x_{\mu})],
\end{split}
\end{equation}

Many algorithms have been proposed to find the minima of this kind of loss function. We base our method on the
coordinate descent algorithm \citep{coordinateDescent-Wright2015} which is described as follows.
Firstly, we initialize the projector as $x^{(1)}=0$. According to the coordinate descent algorithm, we subsequently
update the projector ($x$) along the direction of one specific coordinate ($i$) as
\begin{equation}
x^{(n+1)}_{i}=\mathrm{ST}_{\lambda\sigma_{i}} (x^{(n)}_{i} -\frac{\partial_i G(x^{(n)})}{A_{\alpha i}A_{\alpha i}+4\tau}),
\end{equation}
where $\mathrm{ST}$ is the soft thresholding function defined as
\begin{equation}
\mathrm{ST}_{\lambda} (x) = \mathrm{sign} (x) \max (\abs{x}-\lambda,0),
\end{equation}
and the projector along the other coordinates are kept the same. The minima is finally approached by iteratively updating
along each coordinate for multiple times.

To simplify the notation, here we define the projector difference for the $n$-th iteration as
\begin{equation}
 \Delta x ^{(n)} = -\frac{\bigtriangledown G(x^{(n)})}{A_{\alpha i}A_{\alpha i}+4\tau},
\end{equation}
where $\bigtriangledown G(x^{(n)})$ refers to the gradient of quadratic function $G$ at $x^{(n)}$. The signal to noise ratio
(SNR) of the projector difference is defined as $s^{(n)}=\Delta x ^{(n)}/\sigma$.

In our algorithm, the coordinate descent algorithm in conducted in a pathwise manner \citep{pathwise-Friedman2007}.
We begin with a regulation parameter
($\lambda^{(1)}$) which is slightly smaller than the maximum coordinate of $s^{(1)}$ (denoted as $s_{\rm{max}}^{(1)}$) so that
in the first iteration, we only update on the coordinate with the maximum SNR. Then, we find the maximum projector difference
SNR of the second iteration ($s_{\rm{max}}^{(2)}$) and update the regulation parameter to $\lambda^{(2)}$, where $\lambda^{(2)}$
is slightly smaller than $s_{\rm{max}}^{(2)}$.

%$\mathrm{TSV}(x)$ refers to the total square variance of the first dictionary frame, which is defined as
%\begin{equation}
%\begin{split}
%\mathrm{TSV}(x) =\int d^2 \theta dz (\frac{\partial x}{\partial \theta_1})^2+\int d^2 \theta dz (\frac{\partial x}{\partial \theta_2})^2.
%\end{split}
%\end{equation}
%The total square variance can be expressed in a quadratic form as
%\begin{equation}
%\mathrm{TSV}(x)=\norm{\frac{\partial x}{\partial \theta_1}}^2_2+\norm{\frac{\partial x}{\partial \theta_2}}^2_2.
%\end{equation}

### 2020-10-03 demo/haloSimStamp.py
use Planck cosmology

@@ -38,21 +38,29 @@ from lsst.ctrl.pool.parallel import BatchPoolTask
 from lsst.ctrl.pool.pool import Pool, abortOnError
 
 class haloSimStampBatchConfig(pexConfig.Config):
-    noiDir  =   pexConfig.Field(dtype=str, default='sims/shapenoise_photoz-202003282257',
-                doc = 'noise and redshift directory name')
-    haloName=   pexConfig.Field(dtype=str, default='sims/haloCat-202009201646.csv',
+    obsDir  =   pexConfig.Field(dtype=str, default='HSC-obs/20200328/',
+                doc = 'obs directory name')
+    haloName=   pexConfig.Field(dtype=str,
+                default='planck-cosmo/nfw-halos/haloCat-202010032144.csv',
                 doc = 'halo catalog file name')
-    configName  =   pexConfig.Field(dtype=str, default='config-pix96-nl15.ini',
+    configName  =   pexConfig.Field(dtype=str,
+                default='planck-cosmo/config-pix96-nl20.ini',
                 doc = 'configuration file name')
-    outDir  =   pexConfig.Field(dtype=str, default='pix96-nl15/',
+    outDir  =   pexConfig.Field(dtype=str,
+                default='planck-cosmo/pix96-ns10/',
                 doc = 'output directory')
+    """
+    outDir  =   pexConfig.Field(dtype=str,
+                default='HSC-obs/20200328/pixes/',
+                doc = 'output directory')
+    """
 
     def setDefaults(self):
         pexConfig.Config.setDefaults(self)
     def validate(self):
         pexConfig.Config.validate(self)
-        assert os.path.isdir(self.noiDir),\
-            'Cannot find noise directory: %s' %self.noiDir
+        assert os.path.isdir(self.obsDir),\
+            'Cannot find observation directory: %s' %self.obsDir
         assert os.path.isfile(self.haloName),\
             'Cannot find halo catalog file: %s' %self.haloName
         assert os.path.isfile(self.configName),\
@@ -87,11 +95,14 @@ class haloSimStampBatchTask(BatchPoolTask):
         #Prepare the pool
         pool=   Pool("haloSimStamp")
         pool.cacheClear()
[…]

### 2020-10-03 demo/makeHaloCat.py

@@ -4,6 +4,9 @@ import haloSim
 import numpy as np
 import astropy.table as astTab
 
+omega_m=0.315   # Planck 2018
+#omega_m=0.3    # Toy model
+
 def main():
     log_m_array=np.linspace(13.3,15.0,8)
     z_array=np.linspace(0.05,0.8,8)
@@ -11,16 +14,17 @@ def main():
     data=[]
     for iz,zh in enumerate(z_array):
         for im,logm in enumerate(log_m_array):
-            z_h=zh+np.random.uniform(-0.02,0.02)
-            log_m=logm+np.random.uniform(-0.05,0.05)
+            z_h =   zh+np.random.uniform(-0.02,0.02)
+            log_m=  logm+np.random.uniform(-0.05,0.05)
 
-            M_200=   10.**(log_m)
-            conc =   6.02*(M_200/1.E13)**(-0.12)*(1.47/(1.+z_h))**(0.16)
-            halo =   haloSim.nfw_lensTJ03(mass=M_200,conc=conc,redshift=z_h,ra=0.,dec=0.)
+            M_200=  10.**(log_m) # in unit of M_solar/h
+            conc =  6.02*(M_200/1.E13)**(-0.12)*(1.47/(1.+z_h))**(0.16)
+            halo =  haloSim.nfw_lensTJ03(mass=M_200,conc=conc,redshift=z_h,\
+                    ra=0.,dec=0.,omega_m=omega_m)
             rs_amin=halo.rs_arcsec/60.
             data.append((iz,im,z_h,log_m,conc,rs_amin))
     tabOut=astTab.Table(rows=data,names=names)
-    tabOut.write('haloCat-202009201646.csv')
+    tabOut.write('haloCat-202010032144.csv')
     return
 
 if __name__ == "__main__":

### 2020-10-03 demo/massMapStamp.py

@@ -40,13 +40,17 @@ from lsst.ctrl.pool.parallel import BatchPoolTask
 from lsst.ctrl.pool.pool import Pool, abortOnError
 
 class massMapStampBatchConfig(pexConfig.Config):
-    haloName=   pexConfig.Field(dtype=str, default='sims/haloCat-202009201646.csv',
+    haloName=   pexConfig.Field(dtype=str, default='planck-cosmo/haloCat-202009201646.csv',
                 doc = 'halo catalog file name')
-    configName  =   pexConfig.Field(dtype=str, default='config-pix96-nl15.ini',
+    configName  =   pexConfig.Field(dtype=str, default='config-pix96-nl20.ini',
                 doc = 'configuration file name')
+    outDir  =   pexConfig.Field(dtype=str, default='HSC-obs/20200328/sparse-f1/',
+                doc = 'output directory')
+    """
     outDir  =   pexConfig.Field(dtype=str, default='sparse-f1/',
                 doc = 'output directory')
-    pixDir  =   pexConfig.Field(dtype=str, default='pix96-nl15/',
+    """
+    pixDir  =   pexConfig.Field(dtype=str, default='HSC-obs/20200328/pixes/',
                 doc = 'output directory')
 
     def setDefaults(self):
@@ -64,7 +68,7 @@ class massMapStampRunner(TaskRunner):
     @staticmethod
     def getTargetList(parsedCmd, **kwargs):
         # number of halos
-        return [(ref, kwargs) for ref in range(64)]
+        return [(ref, kwargs) for ref in range(1)]
 
 def unpickle(factory, args, kwargs):
     """Unpickle something by calling a factory"""
@@ -121,9 +125,12 @@ class massMapStampBatchTask(BatchPoolTask):
         """
         Detect halo
         """
-        names=('iz','iy','ix','value')
-        c,v =   detect3D.local_maxima_3D(delta)
-        src=    Table(data=np.hstack([c,v[:,None]]),names=names)
+        names   =   ('iz','iy','ix','value')
+        c1,v1   =   detect3D.local_maxima_3D(delta)
+        c2,v2   =   detect3D.local_minima_3D(delta)
+        data1   =   np.hstack([c1,v1[:,None]])
+        data2   =   np.hstack([c2,v2[:,None]])
+        src     =   Table(data=np.vstack([data1,data2]),names=names)
[…]

### 2020-10-03 demo/old/haloMultiSimStamp.py

@@ -1,125 +1,0 @@
-#!/usr/bin/env python
-import os
-import fitsio
-import galsim
-import numpy as np
-from astropy.table import Table
-
-def getS16aZ(nobj):
-    z_bins  =   fitsio.read('/work/xiangchong.li/work/S16AStandard/S16A_pz_pdf/mlz/target_wide_s16a_wide12h_9832.0.P.fits',ext=2)['BINS']
-    pdf     =   fitsio.read('/work/xiangchong.li/work/massMapSim/mlz_photoz_pdf_stack.fits')
-    pdf     =   pdf.astype(float)
-    nbin    =   len(pdf)
-    pdf     /=  np.sum(pdf)
-    cdf     =   np.empty(nbin,dtype=float)
-    np.cumsum(pdf,out=cdf)
-
-    # Monte Carlo z
-    r       =   np.random.random(size=nobj)
-    tzmc    =   np.empty(nobj, dtype=float)
-    tzmc    =   np.interp(r, cdf, z_bins)
-    return tzmc
-
-rangHalo=   range(2,3)
-isim    =   5
-simDir  =   './simulation%s/' %(isim)
-if not os.path.exists(simDir):
-    os.mkdir(simDir)
-
-#For sources
-size        =   32 #(arcmin)
-ns_per_arcmin=  40
-ns          =   int(size**2.*ns_per_arcmin+1)
-var_gErr    =   0.25
-x_s         =   np.random.random(ns)*size-size/2.
-y_s         =   np.random.random(ns)*size-size/2.
-z_s         =   getS16aZ(ns)#0.8
-kappa_s     =   np.zeros(ns)
-g1_s        =   np.zeros(ns)
-g2_s        =   np.zeros(ns)
-#Second sources for high resolution true map
-x_s2        =   np.random.random(ns*16)*size-size/2.
-y_s2        =   np.random.random(ns*16)*size-size/2.
-z_s2        =   getS16aZ(ns*16)
-kappa_s2    =   np.zeros(ns*16)
-
-#For halo
-halos   =   []
-omega_m =   0.3
-omega_L =   0.7
-h_cos   =   0.7
-z_cl    =   np.array([0.05,0.26,0.51]) #redshift
-x_cl    =   np.array([0.,5.,-3.])*60. #arcsec
-y_cl    =   np.array([0.,8.,2.])*60.  #arcsec
[…]

### 2020-10-03 demo/old/makeConfigSim.py

@@ -1,93 +1,0 @@
-#!/usr/bin/env python
-import os
-import numpy as np
-from configparser import ConfigParser
-
-
-def addInfoSparse(parser,lbd):
-    #sparse
-    doDebug=    'no'
-    nframe =    4
-    nMax   =    1
-    maxR   =    5
-
-    parser['sparse']={  'doDebug':'%s'%doDebug,
-                        'lbd'   :'%s' %lbd,
-                        'nframe':'%s' %nframe,
-                        'nMax'  :'%s' %nMax,
-                        'maxR'  :'%s' %maxR}
-    #transverse plane
-    unit        =   'arcmin'
-    xMin        =   -24.    #(arcmin)
-    yMin        =   -24.    #(arcmin)
-    scale       =   0.25    #(arcmin/pix)
-    ny          =   192     #pixels
-    nx          =   192     #pixels
-
-    parser['transPlane']={'unit':'%s'  %unit,
-                         'xMin':'%s'  %xMin,
-                         'yMin' :'%s'  %yMin,
-                         'scale':'%s'  %scale,
-                         'ny'   :'%s'  %ny,
-                         'nx'   :'%s'  %nx}
-
-    #lens z axis
-    zlMin       =   0.01
-    zlscale     =   0.05
-    nlp         =   20
-    parser['lensZ']={'zlMin'    :   '%s'  %zlMin,
-                     'zlscale'  :   '%s'  %zlscale,
-                     'nlp'      :   '%s'  %nlp}
-
-    #source z axis
-    nz          =   8
-    if nz!=1:
-        zMin        =   0.05
-        zscale      =   0.25
-    else:
-        zMin    =   0.
-        zscale  =   4.
-    parser['sourceZ']={ 'zMin'  :   '%s'  %zMin,
-                        'zscale':   '%s'  %zscale,
-                        'nz'    :   '%s'  %nz}
-    return parser
-
-
-if __name__=='__main__':
-    simDir  =   'simulation9'
-    if not os.path.exists(simDir):
-        os.mkdir(simDir)
-    lbd     =   8
-    for im,logM in enumerate(np.arange(13,16,0.2)):
-        for iz,z_cl in enumerate(np.arange(0.02,1.04,0.04)):
-            parser      =   ConfigParser()
-            # cosmology
-            omega_m     =   0.3
-            omega_l     =   0.7
-            h_cos       =   0.7
-            parser['cosmology']={'omega_m':'%s'  %omega_m,
-                                'omega_l' :'%s'  %omega_l, 
[…]

### 2020-10-03 demo/pixCartesian3DBatchRun.py

@@ -1,62 +1,0 @@
-#!/usr/bin/env python
-# pixelize data into 3D cartesian coordinates
-import gc
-from multiprocessing import Pool
-from configparser import ConfigParser
-
-import numpy as np
-import astropy.io.fits as pyfits
-from pixel3D import cartesianGrid3D
-
-raname  =   'raR'
-decname =   'decR'
-zname   =   'zbest'
-g1name  =   'g1R'
-g2name  =   'g2R'
-ngroup  =   100  # groups in the input fits file
-
-configName  =   'stampSim/HSC-like/process-equalNum10/config.ini'
-parser      =   ConfigParser()
-parser.read(configName)
-gridInfo    =   cartesianGrid3D(parser)
-
-def pixelize_shear(isim):
-    im  =   isim//9
-    iz  =   isim%9
-    outfname1   =  'stampSim/HSC-like/process-equalNum/pixShearR-g1-%d-%d.fits' %(iz,im)
-    outfname2   =  'stampSim/HSC-like/process-equalNum/pixShearR-g2-%d-%d.fits' %(iz,im)
-    if os.path.isfile(outfname1):
-        print('Already have output for simulation: %d' %isim)
-        return
-
-    infname =   'stampSim/HSC-like/sims/stampSim-HSC_like-TJ03-%d,%d-202004021856.fits' %(iz,im)
-    datTab  =   pyfits.getdata(infname)
-    ng=len(datTab)//ngroup
-
-    pixDatAll=np.zeros((ngroup,)+gridInfo.shape,dtype=np.complex128)
-    for ig in range(ngroup):
-        datU=datTab[ig*ng:(ig+1)*ng]
-        val=(datU[g1name]+datU['g1n'])+(datU[g2name]+datU['g2n'])*1j
-        outcome=gridInfo.pixelize_data(datU[raname],datU[decname],datU[zname],val)
-        pixDatAll[ig]=outcome
-
-    pyfits.writeto(outfname1,pixDatAll.real,overwrite=True)
-    pyfits.writeto(outfname2,pixDatAll.imag,overwrite=True)
-    del pixDatAll
-    del datTab
-    gc.collect()
-    return
-
-def estimate_sigma():
-    infname =   'stampSim/HSC-like/process-equalNum/pixShearR-g1-0-0.fits'
-    data    =   pyfits.getdata(infname)
-    std     =   np.std(data,axis=0)*np.sqrt(2.)
[…]

### 2020-10-03 python/old/haloSimMock.py

@@ -1,202 +1,0 @@
-#!/usr/bin/env python
-#
-# LSST Data Management System
-# Copyright 20082014 LSST Corporation.
-#
-# This product includes software developed by the
-# LSST Project (http://www.lsst.org/).
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.    See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the LSST License Statement and
-# the GNU General Public License along with this program.  If not,
-# see <http://www.lsstcorp.org/LegalNotices/>.
-#
-# python lib
-import os
-import fitsio
-import galsim
-import numpy as np
-from astropy.table import Table
-from configparser import ConfigParser
-
-# lsst Tasks
-import lsst.pex.config as pexConfig
-import lsst.pipe.base as pipeBase
-from lsst.pipe.base import TaskRunner
-from lsst.ctrl.pool.parallel import BatchPoolTask
-from lsst.ctrl.pool.pool import Pool, abortOnError
-
-class haloSimStampConfig(pexConfig.Config):
-    def setDefaults(self):
-        pexConfig.Config.setDefaults(self)
-    def validate(self):
-        pexConfig.Config.validate(self)
-
-class haloSimStampTask(pipeBase.CmdLineTask):
-    _DefaultName = "haloSimStamp"
-    ConfigClass = haloSimStampConfig
-    def __init__(self,**kwargs):
-        pipeBase.CmdLineTask.__init__(self, **kwargs)
-
-    @pipeBase.timeMethod
-    def run(self,configName,simDir):
-        configName  =   configName[:-1]
-        self.log.info(configName)
-        parser      =   ConfigParser()
-        parser.read(os.path.join(simDir,configName))
-        # cosmology
-        omega_m     =   parser.getfloat('cosmology','omega_m')
-        omega_l     =   parser.getfloat('cosmology','omega_l')
-        h_cos       =   parser.getfloat('cosmology','h_cos')
-        # sources
[…]

### 2020-10-03 python/sparseBase.py

@@ -189,7 +189,6 @@ class massmapSparsityTask():
         self.shearRRes   = np.zeros(self.shapeS)# shear residuals
         return
 
-
     def read_pixel_result(self,parser):
         g1fname     =   parser.get('prepare','g1fname')
         g2fname     =   parser.get('prepare','g2fname')
@@ -362,25 +361,27 @@ class massmapSparsityTask():
         return
 
     def prox_sigmaA(self):
-        niter   =   100
-        # A_i\alpha n_i
-        outData     =   np.zeros(self.shapeA)
-        for irun in range(niter):
-            np.random.seed(irun)
-            g1Sim   =   np.random.randn(self.nz,self.ny,self.nx)*self.sigmaS
-            g2Sim   =   np.random.randn(self.nz,self.ny,self.nx)*self.sigmaS
-            shearSim=   (g1Sim+np.complex128(1j)*g2Sim)*self.sigmaSInv**2.
-            alphaRSim=  -self.chi2_transpose(shearSim)
-            outData +=  alphaRSim**2.
+        if True:
+            niter   =   100
+            # A_i\alpha n_i
+            outData     =   np.zeros(self.shapeA)
+            for irun in range(niter):
+                np.random.seed(irun)
+                g1Sim   =   np.random.randn(self.nz,self.ny,self.nx)*self.sigmaS
+                g2Sim   =   np.random.randn(self.nz,self.ny,self.nx)*self.sigmaS
+                shearSim=   (g1Sim+np.complex128(1j)*g2Sim)*self.sigmaSInv**2.
+                alphaRSim=  -self.chi2_transpose(shearSim)
+                outData +=  alphaRSim**2.
 
-        # masked region is assigned with the maximum
-        maskL =   np.all(self.sigmaS>1.e-4,axis=0)
-        for izlp in range(self.nlp):
-            for iframe in range(self.nframe):
-                outData[izlp,iframe][~maskL]=np.max(outData[izlp,iframe])
-
-        # noi std
-        self.sigmaA =   np.sqrt(outData/niter)
+            # masked region is assigned with the maximum
+            maskL =   np.all(self.sigmaS>1.e-4,axis=0)
+            for izlp in range(self.nlp):
+                for iframe in range(self.nframe):
+                    outData[izlp,iframe][~maskL]=np.max(outData[izlp,iframe])
+            # noi std
+            self.sigmaA =   np.sqrt(outData/niter)
+        else:
[…]

### 2020-10-08 demo/massMapStamp.py
now the scripts use the same comoving scale for redshift plane

@@ -27,9 +27,9 @@ import detect3D
 import numpy as np
 import astropy.io.fits as pyfits
 import astropy.io.ascii as pyascii
-from pixel3D import cartesianGrid3D
 from astropy.table import Table,vstack
 from sparseBase import massmapSparsityTask
+from sparseBase import massmapSparsityTaskNew
 from configparser import ConfigParser
 
 # lsst Tasks
@@ -47,7 +47,7 @@ class massMapStampBatchConfig(pexConfig.Config):
                 default='planck-cosmo/config-pix96-nl20.ini',
                 doc = 'configuration file name')
     outDir  =   pexConfig.Field(dtype=str,
-                default='planck-cosmo/sparse-f1-2/',
+                default='planck-cosmo/sparse-f3-3/',
                 doc = 'output directory')
     """
     outDir  =   pexConfig.Field(dtype=str,
@@ -157,14 +157,14 @@ class massMapStampBatchTask(BatchPoolTask):
         outfname3=os.path.join(cache.outDirH,'alphaR-%s-lasso.fits' %pnm)
         outfname4=os.path.join(cache.outDirH,'alphaR-%s-alasso2.fits' %pnm)
         if not (os.path.isfile(outfname1) and os.path.isfile(outfname1)):
-            sparse3D    =   massmapSparsityTask(parser)
+            sparse3D    =   massmapSparsityTaskNew(parser)
             sparse3D.process(1500)
             sparse3D.reconstruct()
             delta1  =   sparse3D.deltaR
             pyfits.writeto(outfname1,delta1)
             pyfits.writeto(outfname3,sparse3D.alphaR)
 
-            w   =   sparse3D.adaptive_lasso_weight(gamma=2.)
+            w   =   sparse3D.adaptive_lasso_weight(gamma=2.,sm_scale=0.)
             sparse3D.fista_gradient_descent(800,w=w)
             sparse3D.reconstruct()
             delta2  =   sparse3D.deltaR
@@ -224,12 +224,15 @@ class massMapStampBatchTask(BatchPoolTask):
         parser.set('prepare','sigmafname',sigmafname)
         parser.set('prepare','lkfname',lkfname)
 
+        parser.set('lensZ','resolve_lim','0.4')
+        parser.set('lensZ','rs_base','0.12')
+
         # Reconstruction Init
-        lbd =   4.
+        lbd =   5.
         tau =   0.
         parser.set('sparse','lbd','%s' %lbd )
[…]

### 2020-10-08 python/detect3D.py

@@ -31,7 +31,7 @@ def local_maxima_3D(data, ordert=2, orderp=1, threshold=1.):
     values = data[mask_local_maxima]
     return coords, values
 
-def local_minima_3D(data, ordert=2, orderp=1, threshold=0.5):
+def local_minima_3D(data, ordert=2, orderp=1, threshold=1.):
     """Detects local minima in a 3D array
 
     Parameters
@@ -46,17 +46,17 @@ def local_minima_3D(data, ordert=2, orderp=1, threshold=0.5):
     Returns
     -------
     coords : ndarray
-        coordinates of the local maxima
+        coordinates of the local minima
     values : ndarray
-        values of the local maxima
+        values of the local minima
     """
     sizet = 1 + 2 * ordert
     sizep = 1 + 2 * orderp
     footprint = np.ones((sizep, sizet, sizet))
     footprint[orderp, ordert, ordert] = 0
 
-    filtered = ndi.maximum_filter(data, footprint=footprint,mode='mirror')
-    mask_local_maxima = (data > filtered)& (data<-threshold)
-    coords = np.asarray(np.where(mask_local_maxima)).T
-    values = data[mask_local_maxima]
+    filtered = ndi.minimum_filter(data, footprint=footprint,mode='mirror')
+    mask_local_minima = (data > filtered)& (data<-threshold)
+    coords = np.asarray(np.where(mask_local_minima)).T
+    values = data[mask_local_minima]
     return coords, values

### 2020-10-08 python/halolet.py

@@ -1,8 +1,51 @@
 import os
+import astropy.io.fits as pyfits
 import haloSim
 import numpy as np
+import cosmology
 
-class nfwHalolet2D():
+def zMeanBin(zMin,dz,nz):
+    return np.arange(zMin,zMin+dz*nz,dz)+dz/2.
+
+class massmap_ks2D():
+    def __init__(self,ny,nx):
+        self.shape   =   (ny,nx)
+        self.e2phiF  =   self.e2phiFou(self.shape)
+
+    def e2phiFou(self,shape):
+        ny1,nx1 =   shape
+        e2phiF  =   np.zeros(shape,dtype=complex)
+        for j in range(ny1):
+            jy  =   (j+ny1//2)%ny1-ny1//2
+            jy  =   jy/ny1
+            for i in range(nx1):
+                ix  =   (i+nx1//2)%nx1-nx1//2
+                ix  =   ix/nx1
+                if (i**2+j**2)>0:
+                    e2phiF[j,i]    =   np.complex((ix**2.-jy**2.),2.*ix*jy)/(ix**2.+jy**2.)
+                else:
+                    e2phiF[j,i]    =   1.
+        return e2phiF*np.pi
+
+    def itransform(self,gMap,inFou=True,outFou=True):
+        assert gMap.shape==self.shape
+        if not inFou:
+            gMap =   np.fft.fft2(gMap)
+        kOMap    =   gMap/self.e2phiF*np.pi
+        if not outFou:
+            kOMap    =   np.fft.ifft2(kOMap)
+        return kOMap
+
+    def transform(self,kMap,inFou=True,outFou=True):
+        assert kMap.shape==self.shape
+        if not inFou:
+            kMap =   np.fft.fft2(kMap)
+        gOMap    =   kMap*self.e2phiF/np.pi
+        if not outFou:
+            gOMap    =   np.fft.ifft2(gOMap)
+        return gOMap
+
+class nfwShearlet2D():
     """
     A Class for 2D nfwlet transform
     Consding the typical scale of the redshift plane
@@ -23,77 +66,139 @@ class nfwHalolet2D():
     Examples
     --------
     """
-    def __init__(self,nframe=2,minframe=0,ngrid=64,smooth_scale=1.5,rs_base=2.5):
-        assert ngrid%2==0,\
-                'Please make sure nx and ny are even numbers'
-        # We force ny=nx, the user should ensure that by padding 0
-        self.nx=ngrid
[…]

### 2020-10-08 python/sparseBase.py

@@ -65,6 +65,379 @@ class massmap_ks2D():
             gOMap    =   np.fft.ifft2(gOMap)
         return gOMap
 
+class massmapSparsityTaskNew():
+    def __init__(self,parser):
+        #display
+        self.display_iframe=0
+        if parser.has_option('file','fieldN'):
+            self.fieldN =   parser.get('file','fieldN')
+        else:
+            self.fieldN =   'test'
+        if parser.has_option('file','outDir'):
+            self.outDir =   parser.get('file','outDir')
+        else:
+            self.outDir =   './'
+
+        #sparse
+        self.aprox_method    =   parser.get('sparse','aprox_method')
+        self.lbd    =   parser.getfloat('sparse','lbd') #   For Sparsity
+        if parser.has_option('sparse','tau'):           #   For Total Square Variance
+            self.tau   =   parser.getfloat('sparse','tau')
+        else:
+            self.tau   =   0.
+        self.nframe     =   parser.getint('sparse','nframe')
+        minframe   =   parser.getint('sparse','minframe')
+        # Do debug?
+        if parser.has_option('sparse','debugList'):
+            self.debugList  =   np.array(json.loads(parser.get('sparse','debugList')))
+            self.debugRatios=[]
+            self.debugDeltas=[]
+            self.debugAlphas=[]
+        else:
+            debugList=[]
+
+        ##transverse plane
+        self.ny     =   parser.getint('transPlane','ny')
+        self.nx     =   parser.getint('transPlane','nx')
+        ##lens z axis
+        self.nlp    =   parser.getint('lensZ','nlp')
+
+        if self.nlp<=1:
+            self.zlMin  =   0.
+            self.zlscale=   1.
+        else:
+            self.zlMin  =   parser.getfloat('lensZ','zlMin')
+            self.zlscale=   parser.getfloat('lensZ','zlscale')
+        self.zlBin      =   zMeanBin(self.zlMin,self.zlscale,self.nlp)
+
+        ##source z axis
+        self.nz     =   parser.getint('sourceZ','nz')
+        if self.nz<=1:
+            self.zMin   =   0.05
+            self.zscale =   2.5
+            self.zsBin      =   zMeanBin(self.zMin,self.zscale,self.nz)
+        else:
[…]

### 2020-10-09 demo/massMapStamp.py
prepare results figures for paper

@@ -31,6 +31,7 @@ from astropy.table import Table,vstack
 from sparseBase import massmapSparsityTask
 from sparseBase import massmapSparsityTaskNew
 from configparser import ConfigParser
+from pixel3D import cartesianGrid3D
 
 # lsst Tasks
 import lsst.pex.config as pexConfig
@@ -49,11 +50,6 @@ class massMapStampBatchConfig(pexConfig.Config):
     outDir  =   pexConfig.Field(dtype=str,
                 default='planck-cosmo/sparse-f3-3/',
                 doc = 'output directory')
-    """
-    outDir  =   pexConfig.Field(dtype=str,
-                default='HSC-obs/20200328/sparse-f1/',
-                doc = 'output directory')
-    """
     pixDir  =   pexConfig.Field(dtype=str,
                 default='planck-cosmo/pix96-ns10/',
                 doc = 'output directory')

### 2020-10-09 python/detect3D.py

@@ -56,7 +56,7 @@ def local_minima_3D(data, ordert=2, orderp=1, threshold=1.):
     footprint[orderp, ordert, ordert] = 0
 
     filtered = ndi.minimum_filter(data, footprint=footprint,mode='mirror')
-    mask_local_minima = (data > filtered)& (data<-threshold)
+    mask_local_minima = (data < filtered)& (data<-threshold)
     coords = np.asarray(np.where(mask_local_minima)).T
     values = data[mask_local_minima]
     return coords, values

### 2020-10-10 doc/paper_ms_method_HSCY1/ms.tex
add figures to paper

@@
 \begin{abstract}
-A new method is developed to reconstruct $3$-D density contrast fields from photometric weak lensing shear measurements.
-The $3$-D density contrast map is modeled as a superposition of basis atoms. The basis atoms are designed to represent 
-the structure of NFW halos which have $2$-D multi-scale NFW surface density profiles on the transverse plane and $1$-D 
-Dirac delta functions in the line-of-sight direction. With the prior assumption that the basis atoms have a spare distribution, 
-the density field is reconstructed using the adaptive lasso algorithm. The method is tested with realistic simulation 
-using HSC-like shape noise and photo-$z$ uncertainties. 
+A new method is developed to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
+The $3$-D density contrast maps is modeled as a summation of basis atoms which are designed to represent the profiles of 
+multi-scale NFW halos. The NFW atoms have $2$-D multi-scale NFW surface density profiles on the transverse plane and 
+$1$-D Dirac delta functions in the line-of-sight direction. With the sparsity prior assumption, the density field 
+is reconstructed using an oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using HSC-like 
+shape noise and photo-$z$ uncertainties.
 {\redColor{Add descriptions on the outcomes of the test on the simulations.}}
@@
 \section{Introduction}
+
+\begin{figure*}[!ht]
+    \includegraphics[width=0.98\textwidth]{nfwlet-atom-2D.pdf}
+    \caption{The smoothed basis atoms with different scale radius ($r_s$). The first row shows the smoothed basis atoms in 
+            Fourier space and the second row shows the smoothed basis atoms in Real space. The smoothing kernel is Gaussian
+            with scale of $1.5$ pixels.} \label{fig-atoms2D}
+\end{figure*}
+
+\begin{figure}
+ \includegraphics[width=0.45\textwidth]{nfwlet-atom-1D.pdf}
+ \caption{The $1$-D slices for smoothed basis atoms at $x=0$. The corresponding $2$-D profiles are shown in Figure 
+            \ref{fig-atoms2D}.}
+\end{figure}
+
 Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line-of-sight
@@
 where $\mathbf{T}$ is used to denote the linear transformation operator which includes not only physical lensing effect
-but also includes observational systematic effects from the observation (e.g. pixelization and smoothing of shear field in
+but also observational systematic effects from the observation (e.g. pixelization and smoothing of shear field in
 transverse plane, photo-$z$ uncertainties).
@@
 Reconstructions of density map from shear measurements also receive considerable interest. $2$-D density map reconstruction 
-which reconstructs the integration of mass along the line-of-sight direction has been well studied by the community
+which recover an integration of projected mass along the line-of-sight has been well studied within the community
 \citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016}
-and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}.
+and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However, the 
+reconstruction of $3$-D mass map is still a challenging task.
 
 In order to fully reconstruct the $3$-D mass density distribution ($\delta$) from the tomographic shear observations ($\gamma$),
-the density contrast field is modeled as a superposition of basis atoms in a dictionary space
+the density contrast field is modeled as a summation of basis atoms in a model dictionary
 \begin{equation} \label{eq-intro-dict}
@@
 where $\mathbf{\Phi}$ is the transformation operator from the parameters in the dictionary space to the density contrast 
-and $x$ denotes the parameters in the dictionary space. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field
+and $x$ denotes the parameters. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field
 in Fourier space, which is equivalent to model the mass field with sinusoidial functions. On the other hand,
-\citet{LSS-massMap-Glimpse3D-Leonard2014} models the mass field with Starlets.
+\citet{LSS-massMap-Glimpse3D-Leonard2014} models the mass field with Starlets \citep{Starlet-Starck2015}.
 
@@
 
-\citet{LSS-massMap-Wiener-Simon2009} propose to use the $l^2$ ridge regulation ($C=\norm{x}^2_2$) to find the best-fit 
+\citet{LSS-massMap-Wiener-Simon2009} propose to use the $l^2$ ridge regulation ($C=\norm{x}^2_2$) to find a sparse 
 solution in Fourier space. \citet{HSC1-massMaps} apply the method of \citet{LSS-massMap-Wiener-Simon2009} to the first 
@@
 
-\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use the $l^1$ lasso regulation ($C=\norm{x}^1_1$) to find the
-best-fits solution in a Starlets dictionary space. However, the Starlets functions are not designed to model the 
-clumpy mass distributions in the universe and \citet{LSS-massMap-Glimpse3D-Leonard2014} use a greedy descent algorithm 
-to find minima of the loss function, which is not guarateed to converge to the global minima ({\redColor{cite..}}).
+\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version of $l^1$ lasso regulation ($C=\norm{x}^1_1$) 
+to find a sparse solution in the Starlets dictionary space \citep{Starlet-Starck2015}. However, the Starlets functions are 
+not designed to model the profile of clumpy mass in the universe. Moreover, \citet{LSS-massMap-Glimpse3D-Leonard2014} 
+apply a greedy coordinate descent algorithm, which selects the steepest coordinate in each iteration, find the minima of 
+a non-convex loss function. However, the stability of the non-convex optimization has not been fully discussed.
 
 $N$-body simulations have shown that the dark matter is distributed in halos connected by filaments, and the density 
-distribution of a halo follows the NFW profile \citep{halo-NFW1997ApJ}.
-We construct a dictionary which is composed of multi-scale NFW atoms and point mass atoms. The multi-scale NFW atoms are used 
-to model the structures within halos. They follow multi-scale surface density profiles of NFW halos \citep{haloModel-TJ2003-3pt}
-on the transverse plane and Dirac delta function in the line-of-sight direction. By using Dirac delta functions in the 
-line-of-sight direction, the depth of halo is neglected \citep{LSS-massMap-Glimpse3D-Leonard2014} since the resolution 
-scale of the reconstruction in the line-of-sight direction is much larger than the halo scale.
-The point mass atoms are used to model the structures in the filaments and structures smaller than the reachable resolution
-on the transverse plane. Furthermore, the point mass atoms make our dictionary space complete.
+profile of a single halo follows the NFW function \citep{halo-NFW1997ApJ}.
+We construct a dictionary which is composed of multi-scale NFW atoms. The multi-scale NFW atoms are used to model the 
+profiles of halos. The atoms follow multi-scale surface density profiles of NFW functions \citep{haloModel-TJ2003-3pt}
+on the transverse plane.
+The depth of halo is neglected \citep{LSS-massMap-Glimpse3D-Leonard2014} since the resolution scale of the reconstruction 
+in the line-of-sight direction is much larger than the halo scale. Therefore, the Dirac delta function is used to model the
+atoms' profile in the line-of-sight direction. 
 With the prior assumption that the density contrast field is sparse in the dictionary space, the adaptive lasso regularization
@@
 
-Comparing with \citet{LSS-massMap-Glimpse3D-Leonard2014}, our dictionary space is built up to describe the clumpy mass 
-in the universe which has clear physical a motivation. Moreover, we use adaptive lasso which does not rely on any greedy 
-descent alorithm, therefore the estimation is guarateed to converge to the global minimum.
+Comparing with \citet{LSS-massMap-Glimpse3D-Leonard2014}, our dictionary is built up to describe the clumpy mass 
+in the universe which has a clear physical motivation. Furthermore, the adaptive lasso algorithm is full convex and 
+can be optimized with the FISTA algorithm \citep{FISTA-Beck2009} without relying on any greedy coordinate descent approaches. 
+The stability of this convex optimization has been well studied.
 
@@
 
-In this section, we first review how foreground density distributions induce weak lensing shear distortions on background
-galaxies in section \ref{subsec:method-delta2shear}.
-Then, we introduce the dictionary space used to model the foreground density map in section \ref{subsec:method-dictionary}.
+We first review the lensing process in section \ref{subsec:method-delta2shear}.
+Then, we introduce the dictionary used to model the foreground density maps in section \ref{subsec:method-dictionary}.
 
-Subsequently, in section \ref{subsec:method-Systematics} we discuss several systematic effects from observations which include 
-photo-$z$ uncertainty (section \ref{subsec:method-photoz}),
+Subsequently, in section \ref{subsec:method-Systematics}, we discuss several systematic effects from observations which 
+include photo-$z$ uncertainty (section \ref{subsec:method-photoz}),
 smoothing (section \ref{subsec:method-smoothing}),
@@
 
-\begin{figure*}
-    \includegraphics[width=0.95\textwidth]{nfwlet-atom-2D.pdf}
-    \caption{The NFW models with different scale radius ($r_s$). The first row shows the NFW models in Fourier
-            space and the second row shows the NFW model in Real space.}
-\end{figure*}
-
-The lensing convergence $\kappa$ at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
+The lensing convergence map at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
 density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line-of-sight is
@@
 \begin{equation}\label{eq-delta2gammat}
-\gamma_L(\vec{\theta},z_s) = \int_0^{z_s} \frac{dz_l}{\delta_{c}(z_l,z_s)} \int d^2 \theta' \vec{D}(\vec{\theta}-\vec{\theta'}) \delta(\vec{\theta'},z_l).
+\gamma_L(\vec{\theta},z_s) = \int_0^{z_s} dz_l K(z_l,z_s) \int d^2 \theta' \vec{D}(\vec{\theta}-\vec{\theta'}) \delta(\vec{\theta'},z_l).
 \end{equation}
@@
 \begin{equation}
-\mathbf{Q}=\int_0^{z_s} \frac{dz_l}{\delta_{c}(z_l,z_s)} \int d^2 \theta'  \vec{D}(\vec{\theta}-\vec{\theta'}),
+\mathbf{Q}=\int_0^{z_s} dz_l K(z_l,z_s) \int d^2 \theta'  \vec{D}(\vec{\theta}-\vec{\theta'}),
 \end{equation}
@@
 \label{subsec:method-dictionary}
-\begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
- \caption{The source galaxies are binned into $10$ redshift bins according to their mlz best photo-$z$ estimation.
-        The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines
-        are the bounds of bins. The galaxies are evenly distributed in each bins.}
-\end{figure}
 
-The density contrast field is modeled as a superposition of basis atoms in the dictionary space $\{\phi_0,\phi_1,...\phi_{N}\}$.
+The density contrast field is modeled as a summation of basis atoms in the dictionary space $\{\phi_0,\phi_1,...\phi_{N}\}$.
 \begin{equation}\label{eq-x2delta}
@@
 \label{subsec:method-photoz}
+
 \begin{figure}
- \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
- \caption{The $1$-D slices of NFW models with different scale radius ($r_s=0,1,2,4,8$).}
+ \centering
+ \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
+ \caption{The source galaxies are binned into $10$ redshift bins according to their mlz best photo-$z$ estimation.
+        The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines
+        are the bounds of bins. The galaxies are evenly distributed in each bins.}
 \end{figure}
@@
 \citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different coefficients 
-in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. Lasso estimation is performed in the first step 
-and achieve a preliminary lasso estimation of parameter ($\hat{x'}^{\rm{lasso}}$). In the second step, the lasso estimation is used 
-to weight the penalization on the parameters. With the definition of the adaptive lasso weight 
+in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. First, Lasso estimation is performed in the first 
+step and achieve a preliminary lasso estimation of parameter ($\hat{x'}^{\rm{lasso}}$). In the second step, the lasso estimation 
+is used to weight the penalization on the parameters. With the definition of the adaptive lasso weight 
 \begin{equation}
@@
 \label{sec:Sim}
-This section simulates lensing shear fields induced by a group of dark matter halos with various halo mass and redshifts.
-HSC-like shape measurement error and photo-$z$ error are added to the shear field.
+
+This section simulates lensing shear fields induced by a group of dark matter halos with various halo masses and redshifts.
+Then the shear distortions are applied to HSC mock catalogs with different realizations of HSC-like shape noises and photo-$z$
+uncertainties.
+
+The $\Lambda$CDM cosmology used for the simulations is from the best fitting result of the final full-mission Planck observation 
+of the cosmic microwave background (CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$, $\Omega_\Lambda=0.685$
+\citep{cmb-Planck2018-Cosmology}.
 
@@
 
+We sample halos in two dimensional (mass, redshift) plane. The two dimensional plane is divided into eight redshift bins 
+times eight mass bins. The input redshifts and masses are shifted by random values for each halo, respectively.
+
 We simulate weak lensing shear fields of NFW halos according to \citet{haloModel-TJ2003-3pt}
-and sample halos in the mass-redshift plane as shown in Figure \ref{fig:mass-redshift}.
-We assume a dependency of the concentration on the mass and the redshift of a halo as \citep{c-M_Magneticum-Ragagnin2019}
+We assume a dependency of the concentration on the mass and the redshift of a halo 
+\citet[equation (2)]{c-M_Magneticum-Ragagnin2019}
 \begin{equation}
@@
 
-\begin{figure}[!ht]
- \centering
- \includegraphics[width=0.45\textwidth]{mass-redshift-sampling.pdf}
- \caption{The sampling points of halos in the mass-redshift plane.}
- \label{fig:mass-redshift}
-\end{figure}
-
-\subsection{HSC-like Systematic}
-\subsubsection{Shear Measurement Error}
+\subsection{HSC mock Catalog}
 \begin{figure}[!ht]
@@
 
-\subsubsection{Photo-$z$ Error}
+For each galaxy, we randomly assign its redshift following the MLZ photo-$z$ probability distribution function 
+\citep{HSC1-photoz} of the galaxy. The shear values are obtained from the all-sky weak lensing maps at two adjacent 
+redshift slices with linearly interpolation.
 
@@
 
+We develope a novel method to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
+Our method models $3$-D density contrast maps as a summation of NFW atoms with multiple comoving radius and point mass atoms
+in the $3$-D space binned with photometric redshift. The NFW atoms are used to model the mass in isolated halos and the 
+point mass atoms are used to model the structures close to the resolution limit of the reconstruction.
+
+With the prior assumption that the basis atoms sparsely distributes in the $3$-D space, the density field is reconstructed 
+using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006} which has the oracle properties.
+
+The method is tested with realistic simulations using HSC-like shape noise and photo-$z$ uncertainties.
+
+\begin{figure*}[!ht]
+ \centering
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f1-1.pdf}
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
+ \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
+point mass atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
+\end{figure*}
+
+\begin{figure*}[!ht]
+ \centering
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f3-1.pdf}
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
+ \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
+NFW atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
+\end{figure*}
+
+\begin{figure*}[!ht]
+ \centering
+ \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
+ \caption{The left panel shows the stacked distribution of deviations of detected peak positions 
+ from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane and the 
+ $y$-axis is for the deviation of the redshift. The peaks inside the dashed black box are regarded as true detections. The 
+ right panel focus on the deviation of detected peaks in the line-of-sight direction. The $x$-axis shows the input redshifts 
+ and the $y$-axis is the redshift of the detected peak. The cross symbols show the average redshift of detected peak for 
+ halos with different input redshift and mass and the error-bars are the scatter of the corresponding peak redshifts. All 
+ of the results in this figure are based on the NFW atoms.}
+\end{figure*}
+
+\begin{figure}[!ht]
+ \centering
+ \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
+ \caption{The histograms of detected peak values for all of the halo and error realizations. The dotted lines with different 
+ colors are for the results of reconstruction with NFW atoms dictionary penalized with different regularization parameter 
+ $\lambda$.}
+\end{figure}
+
+\clearpage
 \bibliographystyle{aasjournal}

### 2020-10-11 demo/massMapStamp.py
add figures to demonstrate it is necessary to use oracle algorithms

@@ -220,8 +220,8 @@ class massMapStampBatchTask(BatchPoolTask):
         parser.set('prepare','sigmafname',sigmafname)
         parser.set('prepare','lkfname',lkfname)
 
-        parser.set('lensZ','resolve_lim','0.4')
-        parser.set('lensZ','rs_base','0.12')
+        parser.set('lensZ','resolve_lim','0.4') #pix
+        parser.set('lensZ','rs_base','0.12')    #Mpc/h
 
         # Reconstruction Init
         lbd =   5.

### 2020-10-20 demo/haloSimStamp.py
analysis on noise

@@ -70,7 +70,9 @@ class haloSimStampRunner(TaskRunner):
     @staticmethod
     def getTargetList(parsedCmd, **kwargs):
         # number of halos
-        return [(ref, kwargs) for ref in range(64)]
+        #idRange=range(64)
+        idRange=[10000000]
+        return [(ref, kwargs) for ref in idRange]
 
 def unpickle(factory, args, kwargs):
     """Unpickle something by calling a factory"""
@@ -98,13 +100,22 @@ class haloSimStampBatchTask(BatchPoolTask):
         pool.storeSet(obsDir=self.config.obsDir)
         pool.storeSet(haloName=self.config.haloName)
         pool.storeSet(configName=self.config.configName)
-        ss  =   pyascii.read(self.config.haloName)[Id]
-        outDirH =   os.path.join(self.config.outDir,'halo%d%d'%(ss['iz'],ss['im']))
+        if Id<5e4:
+            # halo field
+            ss  =   pyascii.read(self.config.haloName)[Id]
+            iz  =   ss['iz']
+            im  =   ss['im']
+            self.pixelize_Sigma(ss)
+        else:
+            # Noise field
+            ss  =   None
+            iz  =   800
+            im  =   800
+        pool.storeSet(ss=ss)
+        outDirH =   os.path.join(self.config.outDir,'halo%d%d'%(iz,im))
         if not os.path.isdir(outDirH):
             os.mkdir(outDirH)
         pool.storeSet(outDirH=outDirH)
-        pool.storeSet(ss=ss)
-        self.pixelize_Sigma(ss)
         pool.map(self.process,range(100))
         return
 
@@ -122,9 +133,11 @@ class haloSimStampBatchTask(BatchPoolTask):
         M_200   =   10.**(ss['log10_M200'])
         conc    =   ss['conc']
         zh      =   ss['zh']
+        # TJ03 halo
         halo    =   haloSim.nfw_lensTJ03(mass=M_200,conc=conc,\
                     redshift=zh,ra=0.,dec=0.,omega_m=omega_m)
         """
+        # WB00 halo
         halo    =   haloSim.nfw_lensWB00(mass=M_200,conc=conc,\
                     redshift=zh,ra=0.,dec=0.,omega_m=omega_m)
         """
@@ -150,28 +163,6 @@ class haloSimStampBatchTask(BatchPoolTask):
         @param ss       halo source
         """
 
[…]

### 2020-10-20 demo/massMapStamp.py

@@ -48,7 +48,7 @@ class massMapStampBatchConfig(pexConfig.Config):
                 default='planck-cosmo/config-pix96-nl20.ini',
                 doc = 'configuration file name')
     outDir  =   pexConfig.Field(dtype=str,
-                default='planck-cosmo/sparse-f3-3/',
+                default='planck-cosmo/sparse-f3-3/', # -1/2/3 (lbd=3.5/4/5)
                 doc = 'output directory')
     pixDir  =   pexConfig.Field(dtype=str,
                 default='planck-cosmo/pix96-ns10/',
@@ -69,7 +69,9 @@ class massMapStampRunner(TaskRunner):
     @staticmethod
     def getTargetList(parsedCmd, **kwargs):
         # number of halos
-        return [(ref, kwargs) for ref in range(64)]
+        #idRange=range(64)
+        idRange=[10000000]
+        return [(ref, kwargs) for ref in idRange]
 
 def unpickle(factory, args, kwargs):
     """Unpickle something by calling a factory"""
@@ -97,14 +99,21 @@ class massMapStampBatchTask(BatchPoolTask):
         pool.storeSet(haloName=self.config.haloName)
         pool.storeSet(configName=self.config.configName)
         pool.storeSet(pixDir=self.config.pixDir)
-        ss  =   pyascii.read(self.config.haloName)[Id]
-        iz  =   ss['iz']
-        im  =   ss['im']
+        if Id<5e4:
+            # halo field
+            ss  =   pyascii.read(self.config.haloName)[Id]
+            iz  =   ss['iz']
+            im  =   ss['im']
+        else:
+            # Noise field
+            ss  =   None
+            iz  =   800
+            im  =   800
+        pool.storeSet(ss=ss)
         outDirH =   os.path.join(self.config.outDir,'halo%d%d'%(iz,im))
         if not os.path.isdir(outDirH):
             os.mkdir(outDirH)
         pool.storeSet(outDirH=outDirH)
-        pool.storeSet(ss=ss)
         resList =   pool.map(self.process,range(100))
         resList =   [x for x in resList if x is not None]
 
@@ -144,9 +153,13 @@ class massMapStampBatchTask(BatchPoolTask):
         Reconstruct density map
         """
         ss  =   cache.ss
-        iz  =   ss['iz']
-        im  =   ss['im']
[…]

### 2020-10-22 demo/makeNoiseCat.py
add code to make noise catalog (was in notebook)

@@ -1,0 +1,100 @@
+#!/usr/bin/env python
+
+import os
+import gc
+import numpy as np
+import astropy.table as astTab
+import astropy.io.fits as pyfits
+
+datDir  =   "/work/xiangchong.li/work/S16ACatalogs/"
+tn      =   '9347.fits'
+
+def rotCatalog(e1, e2, phi=None):
+    if phi  ==  None:
+        phi = 2.0 * np.pi * np.random.rand(len(e1))
+    cs = np.cos(phi)
+    ss = np.sin(phi)
+    e1_rot = e1 * cs + e2 * ss
+    e2_rot = (-1.0) * e1 * ss + e2 * cs
+    return e1_rot, e2_rot
+
+def measShear(cdata):
+    e1      =   cdata['ishape_hsm_regauss_e1']
+    e2      =   cdata['ishape_hsm_regauss_e2']
+    m_b     =   cdata['ishape_hsm_regauss_derived_shear_bias_m']
+    c1_b    =   cdata['ishape_hsm_regauss_derived_shear_bias_c1']
+    c2_b    =   cdata['ishape_hsm_regauss_derived_shear_bias_c2']
+    weight  =   cdata['ishape_hsm_regauss_derived_shape_weight']
+    w_A     =   np.sum(weight)
+    m_bA    =   np.sum(m_b*weight)/w_A
+    Res_A   =   1.-np.sum(cdata['ishape_hsm_regauss_derived_rms_e']**2.*weight)/w_A
+    g1      =   1./(1.+m_bA)*(e1/2./Res_A-c1_b)
+    g2      =   1./(1.+m_bA)*(e2/2./Res_A-c2_b)
+    #t       =   1./(1.+m_bA)/2./Res_A
+    #weight  =   weight/(t**2.)
+    return g1,g2
+
+
+def main():
+    # read the data from S16A
+    pfn =   os.path.join(datDir,'S16AStandardCalibrated/tract/%s_pofz.fits' %tn.split('.')[0])
+    cfn =   os.path.join(datDir,'S16AStandardCalibrated/tract/%s' %tn)
+    cdata=  pyfits.getdata(cfn)
+    pdata=  pyfits.getdata(pfn)['PDF']
+    assert len(pdata)==len(cdata)
+
+    # mask the catalog data
+    ra      =   cdata['coord_ra']*180/np.pi-np.average(cdata['coord_ra'])*180/np.pi
[…]

### 2020-10-22 demo/massMapStamp.py

@@ -48,7 +48,7 @@ class massMapStampBatchConfig(pexConfig.Config):
                 default='planck-cosmo/config-pix96-nl20.ini',
                 doc = 'configuration file name')
     outDir  =   pexConfig.Field(dtype=str,
-                default='planck-cosmo/sparse-f3-3/', # -1/2/3 (lbd=3.5/4/5)
+                default='planck-cosmo/sparse-f3-2/',
                 doc = 'output directory')
     pixDir  =   pexConfig.Field(dtype=str,
                 default='planck-cosmo/pix96-ns10/',
@@ -243,7 +243,7 @@ class massMapStampBatchTask(BatchPoolTask):
         parser.set('lensZ','rs_base','0.12')    #Mpc/h
 
         # Reconstruction Init
-        lbd =   5.0
+        lbd =   4.0
         tau =   0.
         parser.set('sparse','lbd','%s' %lbd )
         parser.set('sparse','aprox_method','fista' )

### 2020-10-23 demo/haloSimStamp.py
add function to plot for both noise peaks and field peaks

@@ -116,7 +116,7 @@ class haloSimStampBatchTask(BatchPoolTask):
         if not os.path.isdir(outDirH):
             os.mkdir(outDirH)
         pool.storeSet(outDirH=outDirH)
-        pool.map(self.process,range(100))
+        pool.map(self.process,range(100,1000))
         return
 
     def pixelize_Sigma(self,ss):

### 2020-10-23 demo/makeNoiseCat.py

@@ -12,10 +12,10 @@ tn      =   '9347.fits'
 def rotCatalog(e1, e2, phi=None):
     if phi  ==  None:
         phi = 2.0 * np.pi * np.random.rand(len(e1))
-    cs = np.cos(phi)
-    ss = np.sin(phi)
-    e1_rot = e1 * cs + e2 * ss
-    e2_rot = (-1.0) * e1 * ss + e2 * cs
+    cs      =   np.cos(phi)
+    ss      =   np.sin(phi)
+    e1_rot  =   e1 * cs + e2 * ss
+    e2_rot  =   (-1.0) * e1 * ss + e2 * cs
     return e1_rot, e2_rot
 
 def measShear(cdata):
@@ -51,8 +51,13 @@ def main():
     pdata   =   pdata[mask]
     ra      =   ra[mask]
     dec     =   dec[mask]
-    raR     =   np.random.rand(len(ra))-0.5
-    decR    =   np.random.rand(len(dec))-0.5
+    if os.path.exists('HSC-obs/20200328/cats/sim0.fits'):
+        data0=  pyfits.getdata('HSC-obs/20200328/cats/sim0.fits')
+        raR =   data0['raR']
+        decR=   data0['decR']
+    else:
+        raR     =   np.random.rand(len(ra))-0.5
+        decR    =   np.random.rand(len(dec))-0.5
     zBest   =   cdata['mlz_photoz_best']
     g1,g2   =   measShear(cdata)
 
@@ -61,7 +66,6 @@ def main():
     poz_bins=pyfits.getdata(bfn)['BINS']
     nobj, nbin = pdata.shape
     assert len(poz_bins)==nbin
-
 
     pdata   =   pdata.astype(float)
     pdata   /=  np.sum(pdata,axis=1).reshape(nobj, 1)
@@ -75,12 +79,12 @@ def main():
         print('processing mock: %d' %imock)
         np.random.seed(imock)
         tableMock   =   astTab.Table(data=np.empty((nobj,len(names))),names=names)
-        tzmc  =   np.empty(nobj, dtype=float)
+        tzmc        =   np.empty(nobj, dtype=float)
         # Monte Carlo z
-        r     =   np.random.random(size=nobj)
+        r           =   np.random.random(size=nobj)
         for i in range(nobj):
             tzmc[i] =   np.interp(r[i], cdf[i], poz_bins)
-        g1n,g2n =   rotCatalog(g1,g2)
+        g1n,g2n     =   rotCatalog(g1,g2)
[…]

### 2020-10-23 demo/massMapStamp.py

@@ -48,7 +48,7 @@ class massMapStampBatchConfig(pexConfig.Config):
                 default='planck-cosmo/config-pix96-nl20.ini',
                 doc = 'configuration file name')
     outDir  =   pexConfig.Field(dtype=str,
-                default='planck-cosmo/sparse-f3-2/',
+                default='planck-cosmo/sparse-f3-3/',
                 doc = 'output directory')
     pixDir  =   pexConfig.Field(dtype=str,
                 default='planck-cosmo/pix96-ns10/',
@@ -114,7 +114,7 @@ class massMapStampBatchTask(BatchPoolTask):
         if not os.path.isdir(outDirH):
             os.mkdir(outDirH)
         pool.storeSet(outDirH=outDirH)
-        resList =   pool.map(self.process,range(100))
+        resList =   pool.map(self.process,range(1000))
         resList =   [x for x in resList if x is not None]
 
         # peak catalogs list
@@ -165,7 +165,7 @@ class massMapStampBatchTask(BatchPoolTask):
         outfname2=os.path.join(cache.outDirH,'deltaR-%s-alasso2.fits' %pnm)
         outfname3=os.path.join(cache.outDirH,'alphaR-%s-lasso.fits' %pnm)
         outfname4=os.path.join(cache.outDirH,'alphaR-%s-alasso2.fits' %pnm)
-        if not (os.path.isfile(outfname1) and os.path.isfile(outfname1)):
+        if not (os.path.isfile(outfname1) and os.path.isfile(outfname2)):
             sparse3D    =   massmapSparsityTaskNew(parser)
             sparse3D.process(1500)
             sparse3D.reconstruct()
@@ -243,7 +243,7 @@ class massMapStampBatchTask(BatchPoolTask):
         parser.set('lensZ','rs_base','0.12')    #Mpc/h
 
         # Reconstruction Init
-        lbd =   4.0
+        lbd =   5.0
         tau =   0.
         parser.set('sparse','lbd','%s' %lbd )
         parser.set('sparse','aprox_method','fista' )

### 2020-10-23 doc/paper_ms_method_HSCY1/ms.tex
paper update

@@
 \begin{document}
-\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction}
+\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction: 
+Reducing the line-of-sight smearing.}
 %\author{Xiangchong Li}
@@
 A new method is developed to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
-The $3$-D density contrast maps is modeled as a summation of basis atoms which are designed to represent the profiles of 
-multi-scale NFW halos. The NFW atoms have $2$-D multi-scale NFW surface density profiles on the transverse plane and 
-$1$-D Dirac delta functions in the line-of-sight direction. With the sparsity prior assumption, the density field 
-is reconstructed using an oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using HSC-like 
-shape noise and photo-$z$ uncertainties.
+The $3$-D density contrast maps is modeled as a summation of NFW basis atoms which have $2$-D multi-scale NFW surface 
+density profiles on the transverse plane and $1$-D Dirac delta functions in the line-of-sight direction. With the prior 
+assumption that the density fields can be sparsely represented by the NFW basis atoms, it is reconstructed using an 
+oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape noise and 
+photo-$z$ uncertainty.
 {\redColor{Add descriptions on the outcomes of the test on the simulations.}}
@@
 
-\begin{figure*}[!ht]
-    \includegraphics[width=0.98\textwidth]{nfwlet-atom-2D.pdf}
-    \caption{The smoothed basis atoms with different scale radius ($r_s$). The first row shows the smoothed basis atoms in 
-            Fourier space and the second row shows the smoothed basis atoms in Real space. The smoothing kernel is Gaussian
-            with scale of $1.5$ pixels.} \label{fig-atoms2D}
+\begin{figure*}[!t]
+    \includegraphics[width=1.\textwidth]{nfwlet-atom-2D.pdf}
+    \caption{The smoothed basis atoms. The first row shows the smoothed basis atoms in Fourier space 
+            and the second row shows the smoothed basis atoms in Real space. 
+            The first column is point mass atom and the other columns are multi-scale NFW atoms.
+            The smoothing kernel is Gaussian with scale of $1.5$ pixels.} \label{fig-atoms2D}
 \end{figure*}
@@
 \begin{figure}
- \includegraphics[width=0.45\textwidth]{nfwlet-atom-1D.pdf}
+ \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
  \caption{The $1$-D slices for smoothed basis atoms at $x=0$. The corresponding $2$-D profiles are shown in Figure 
-            \ref{fig-atoms2D}.}
+        \ref{fig-atoms2D}.} \label{fig-atoms1D}
 \end{figure}
@@
 
-Adopting the thin lens approximation, the expected shear measurements ($\gamma$) on distant galaxies are related to the 
+The expected shear measurements ($\gamma$) on distant galaxies are related to the 
 foreground density contrast field ($\delta$) through a linear transformation
@@
 where $\mathbf{T}$ is used to denote the linear transformation operator which includes not only physical lensing effect
-but also observational systematic effects from the observation (e.g. pixelization and smoothing of shear field in
-transverse plane, photo-$z$ uncertainties).
+but also systematic effects from observations (e.g. pixelization and smoothing of shear field in
+transverse plane, photo-$z$ uncertainty).
 
@@
 which recover an integration of projected mass along the line-of-sight has been well studied within the community
-\citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016}
+\citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
 and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However, the 
@@
 
-In order to fully reconstruct the $3$-D mass density distribution ($\delta$) from the tomographic shear observations ($\gamma$),
+In order to fully reconstruct the $3$-D mass density distribution ($\delta$) from the photometric shear observations ($\gamma$),
 the density contrast field is modeled as a summation of basis atoms in a model dictionary
@@
 
-The model parameters are estimated through solving an optimization problem and the estimator is defined as
+The projection coefficients are estimated through optimizing a loss function with regularization. The estimator is
+generally defined as
 \begin{equation}
@@
 the residuals between the prediction and the data, while $C(x)$ is the regularization term measuring the deviation of
-the estimation of the parameter ($x$) from the prior assumptions. Such estimation prefer the parameters that are able
+the estimation of the parameter ($x$) from the prior assumptions. Such estimation prefers the parameters that are able
 to describe the observations and also align with the prior assumptions. The regularization parameter $\lambda$ adjusts 
@@
 
-\citet{LSS-massMap-Wiener-Simon2009} propose to use the $l^2$ ridge regulation ($C=\norm{x}^2_2$) to find a sparse 
-solution in Fourier space. \citet{HSC1-massMaps} apply the method of \citet{LSS-massMap-Wiener-Simon2009} to the first 
-year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}. 
-{\redColor{Why we use $l^1$ in this paper, what is the difference between $l^1$ and $l^2$.}}
+\citet{LSS-massMap-Wiener-Simon2009} propose to use the Wiener filter, which is also known as $l^2$ ridge regulation 
+($C=\norm{x}^2_2$), to find a solution in Fourier space. \citet{HSC1-massMaps} apply the method of 
+\citet{LSS-massMap-Wiener-Simon2009} to the first year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}. 
+However, the density maps reconstructed by this method suffer from a smearing along the line-of-sight direction with 
+a standard deviation of $\sigma_z=0.2 \sim 0.3$.
 
 \citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version of $l^1$ lasso regulation ($C=\norm{x}^1_1$) 
-to find a sparse solution in the Starlets dictionary space \citep{Starlet-Starck2015}. However, the Starlets functions are 
-not designed to model the profile of clumpy mass in the universe. Moreover, \citet{LSS-massMap-Glimpse3D-Leonard2014} 
-apply a greedy coordinate descent algorithm, which selects the steepest coordinate in each iteration, find the minima of 
-a non-convex loss function. However, the stability of the non-convex optimization has not been fully discussed.
+to find a sparse solution in the Starlets dictionary space \citep{Starlet-Starck2015}. \citet{LSS-massMap-Glimpse3D-Leonard2014}
+apply a greedy coordinate descent algorithm, which selects the steepest coordinate in each iteration, to find the minima 
+of a non-convex loss function penalized with the firm thresholding function. \citet{LSS-massMap-Glimpse3D-Leonard2014} 
+significantly reduce the smearing along the line-of-sight, however, the stability of the non-convex optimization and
+greedy coordinate descent algorithm has not been fully justified. Moreover, the Starlets functions are not designed to 
+model the profile of clumpy mass in the universe.
 
@@
 profile of a single halo follows the NFW function \citep{halo-NFW1997ApJ}.
-We construct a dictionary which is composed of multi-scale NFW atoms. The multi-scale NFW atoms are used to model the 
-profiles of halos. The atoms follow multi-scale surface density profiles of NFW functions \citep{haloModel-TJ2003-3pt}
-on the transverse plane.
-The depth of halo is neglected \citep{LSS-massMap-Glimpse3D-Leonard2014} since the resolution scale of the reconstruction 
-in the line-of-sight direction is much larger than the halo scale. Therefore, the Dirac delta function is used to model the
-atoms' profile in the line-of-sight direction. 
-With the prior assumption that the density contrast field is sparse in the dictionary space, the adaptive lasso regularization
-\citep{AdaLASSO-Zou2006} is used to reconstruct a high signal-to-noise-ratio (SNR) density contrast field.
+We construct a dictionary with multi-scale NFW atoms.  The atoms follow multi-scale surface density profiles of NFW 
+functions \citep{haloModel-TJ2003-3pt} on the transverse plane. We follow \citet{LSS-massMap-Glimpse3D-Leonard2014} 
+to neglect the depth of halos since the resolution scale of the reconstruction in the line-of-sight direction is much 
+larger than the scales of halos. Therefore, we set the profile of the NFW atoms in the line-of-sight as the Dirac delta 
+function. The multi-scale NFW atoms are used to model the profiles of halos which is assumed to be sparsely distributed 
+in the universe. With the sparsity prior, the adaptive lasso regularization \citep{AdaLASSO-Zou2006} is used to reconstruct 
+the density field. We find that, in contrast to the standard lasso estimator which smears the structure along the line-of-sight,
+the addaptive lasso is able to significantly reduce the smearing effect.
 
 Comparing with \citet{LSS-massMap-Glimpse3D-Leonard2014}, our dictionary is built up to describe the clumpy mass 
-in the universe which has a clear physical motivation. Furthermore, the adaptive lasso algorithm is full convex and 
-can be optimized with the FISTA algorithm \citep{FISTA-Beck2009} without relying on any greedy coordinate descent approaches. 
-The stability of this convex optimization has been well studied.
+in the universe which has a clear physical motivation. Furthermore, the adaptive lasso algorithm is strictly convex and 
+can be directly optimized with the FISTA algorithm \citep{FISTA-Beck2009} without relying on any greedy coordinate 
+descent approaches.  The stability of this convex optimization has been well studied.
 
@@
 Section \ref{sec:Method} proposes the new method for $3$-D density map reconstruction.
-Section \ref{sec:Sim} introduces the realistic simulations we use to test the new method.
-Section \ref{sec:Res} presents the results of our method on the simulations.
+Section \ref{sec:Test} Tests our algorithm on HSC-like simulations.
 Section \ref{sec:Sum} summarizes and discusses the future development of the method.
@@
 \label{sec:Method}
+
+\begin{figure}[!t]
+ \centering
+ \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
+ \caption{The source galaxies are binned into $10$ redshift bins according to their MLZ best photo-$z$ estimation.
+        The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines
+        are the bounds of bins. The galaxies are evenly distributed in each bins.} \label{fig-bestpz}
+\end{figure}
 
@@
 
-Finally, we find the the sparse solution in section \ref{subsec:method-reversion} using the adaptive lasso algorithm 
+Finally, we find the sparse solution in section \ref{subsec:method-reconstruction} using the adaptive lasso algorithm 
 \citep{AdaLASSO-Zou2006} optimized with the FISTA alogrithm \citep{FISTA-Beck2009}.
@@
 
+\begin{figure}[!t]
+ \centering
+ \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
+ \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.}\label{fig-pdfpz}
+\end{figure}
+
 The lensing convergence map at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
 density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line-of-sight is
-\citep{LSS-massMap-Glimpse3D-Leonard2014}
 \begin{equation}
@@
 
-Substitute comoving distance ($\chi$) with redshift ($z$)
+Substitute comoving distance ($\chi$) with redshift ($z$), we have
 \begin{equation}\label{eq-delta2kappa}
@@
 \frac{3H_0\Omega_M}{2 c} \frac{\chi_l \chi_{sl} (1+z_l)}{\chi_{s} E\left(z_l\right)} & (z_s>z_l),\\
-0&(z_s \leq z_l).
+0&(z_s \leq z_l),
 \end{cases}
 \end{equation}
+where $E(z)$ is the Hubble parameter as a function of redshift, in units of $H_0$.
 
-As shown in \citet{massMap-KS1993}, the shear distortion is related to the kappa field at the redshift plane as
+\begin{figure*}[!t]
+ \centering
+ \includegraphics[width=1.\textwidth]{lensing_kernel.pdf}
+ \caption{The left panel shows the lensing kernels for five different lens redshifts. The dashed lines are the 
+        kernels for spectroscopic redshift which assumes that the redshifts of source galaxies are precisely 
+        estimated. The solid lines are for photometric redshifts which accounts for the influence of photometric 
+        redshift uncertainty. The other two panels show the correlation between lensing kernels of different 
+        lens redshifts. The middle panel is for spectroscopic redshift and the right panel is for photometric 
+        redshifts. The lensing kernels are normalized so that the diagonal elements of the correlation matrices
+        equal one.}\label{fig-corlensKer}
+\end{figure*}
+
+As shown in \citet{massMap-KS1993}, the shear field is related to the kappa field at the same redshift plane
+via
 \begin{equation}\label{eq-kappa2gamma}
@@
 \end{equation}
-Here we denote the physical shear distortions as $\gamma_L$ and we note that the observed shear measurements are the
-physical shear distortions influenced by systematics which will be discussed in the following subsections.
+Here we denote the physical shear distortion field as $\gamma_L$ and we note that the final observed shear measurements 
+are also physical shear distortions influenced by systematic errors from observatins. The systematic error will be discussed 
+in Section \ref{subsec:method-Systematics}.
 
-Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}), the physical shear signal is derived as
+Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}), the expectation of lensing shear signal is 
 \begin{equation}\label{eq-delta2gammat}
@@
 
-The density contrast field is modeled as a summation of basis atoms in the dictionary space $\{\phi_0,\phi_1,...\phi_{N}\}$.
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=0.42\textwidth]{delta-3-7-pz-nn-lasso.png}
+\includegraphics[width=0.42\textwidth]{delta-3-7-pz-nn-alasso.png}
+\caption{The result of density map reconstruction with standard lasso (left) and adaptive lasso (right). The input density 
+        map is from a NFW halo with mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso reconstruction 
+        smear the density field along the line-of-sight direction. Noises on shear measurements are neglected in the 
+        simulation.} \label{fig-lassoVsadaLasso}
+\end{figure*}
+
+The density contrast field is modeled as a summation of basis atoms in the dictionary 
 \begin{equation}\label{eq-x2delta}
-\delta(\vec{r}) = \sum_{s=0}^{N} \int d^3 r' \phi_s(\vec{r}-\vec{r'}) x_s(\vec{r'}),
+\delta(\vec{r}) = \sum_{s=1}^{N} \int d^3 r' \phi_s(\vec{r}-\vec{r'}) x_s(\vec{r'}),
 \end{equation}
-where $\phi_s(\vec{r})$ is the basis vector of the dictionary space, and $x_s$ is the corresponding projection
-coefficients of the density contrast field onto the basis vectors.
+where $\phi_s(\vec{r})$ are the basis atoms of the dictionary. The basis atoms have `$N$' different scales and the atoms
+in each scale frame are shifted by $\vec{r'}$ to form basis at different positions. $x_s(\vec{r'})$ is the projection 
+coefficients of the density contrast field onto the basis atoms.
 
-These basis vectors are composed of multi-scale NFW atoms $\{\phi_1,..,\phi_{N}\}$ and point
-mass atoms $\{\phi_0\}$. $\phi_0$ is a $3$-D Dirac delta function
-\begin{equation}
-\phi_0(\vec{r})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
-\end{equation}
-on the transverse plane, the NFW atoms ($\{\phi_1,...,\phi_N\}$) follow surface density profiles of NFW halos
+These basis atoms are constructed with multi-scale NFW atoms which are denoted as $\{\phi_1,...,\phi_N\}$.
+On the transverse plane, the NFW atoms follow surface density profiles of NFW halos
 \citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and truncation radius $c \theta_\alpha$ ,
-where $c$ is known as concentration of NFW halo.
-As the scale of halo is much less than the reachable redshift resolution, we neglect the depth of halo on the
-line-of-sight direction and set the profiles of NFW atoms in the line-of-sight direction to $1$-D Dirac delta functions
-\citep{LSS-massMap-Glimpse3D-Leonard2014}. The NFW atoms are expressed as
+where $c$ is the concentration of NFW halos.
+As the scales of halos are much less than the reachable redshift resolution, we neglect the depth of halo on the
+line-of-sight direction and set the profiles of NFW atoms in the line-of-sight direction to $1$-D Dirac delta 
+functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. 
+The multi-scale NFW atoms are defined as
 \begin{equation}
@@
 \end{equation}
-$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=9$ for NFW atoms in different scale frames.
+$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for NFW atoms in different scale frames.
 
@@
 
-Our prior assumption is that the mass density field is sparse in the dictionary space and we will conduct
-adaptive lasso \citep{AdaLASSO-Zou2006} to find a sparse solution of the mass reconstruction problem in the
-dictionary space.
+In this paper dictionary constructed with point mass atoms is used to compare with the dictionary of multi-scale atoms.
+The point mass atoms is a $3$-D Dirac function defined as follows
+\begin{equation}
+\phi_{\rm{PM}}(\vec{r})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
+\end{equation}
 
-We note that the shear measurements are deviated from the physical shear prediction due to the systematics
-from observations. The influence of systematics is carefully studied and added to the forward modeling in the
-following subsections.
+The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the transverse plane are shown in Figure 
+\ref{fig-atoms2D}. The $1$-D slices of the profiles are demonstrated in Fiugre \ref{fig-atoms1D}. Note that these profiles 
+are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The smoothing operator is described in 
+Section \ref{subsec:method-smoothing} and the pixelization operator is described in Section \ref{subsec:method-pixel}.
 
@@
 
+The observed shear measurements are deviated from the physical shear prediction due to the systematic 
+errors from observations. The influence of systematics is carefully studied and incorporated into the forward 
+modeling in this section.
+
 \subsubsection{Photo-$z$ Uncertainty}
@@
 
-\begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
- \caption{The source galaxies are binned into $10$ redshift bins according to their mlz best photo-$z$ estimation.
-        The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines
-        are the bounds of bins. The galaxies are evenly distributed in each bins.}
-\end{figure}
-
-Since the photometric redshifts of source galaxies in the current large scale survey are estimated with
-a limited number of photometric bands, the estimated redshifts of galaxies suffer from large uncertainties.
-Such uncertainties smear the structure along the line-of-sight direction since a galaxy with a best fit photo-$z$
-estimation of $z_s$ has a possibility of being actually located at redshift $z$. Such probability is denoted as $P(z|z_s)$
-and the expected shear distortion on this galaxy is
+The photometric redshifts of source galaxies in the current large scale survey are estimated with a limited number of 
+board photometric bands (e.g. $9$ bands for KIDS$+$VIKING survey, $5$ bands for DES survey and HSC survey). As a result, 
+the estimated redshifts of galaxies suffer from much larger uncertainties, comparing with redshifts estimated with 
+spectroscopic observations. Such photo-$z$ uncertainty smears the lensing kernels statistically since a galaxy with a 
+best fit photo-$z$ estimation of $z_s$ has possibilities of being actually located at different redshifts ($z$).
+The probability function for the photo-$z$ uncertainty is denoted as $P(z|z_s)$ and the expected shear distortion on 
+the galaxy is
 \begin{equation}\label{eq-delta2gamma-poz}
@@
 \end{equation}
-the photo-$z$ uncertainties changes the shear as $\gamma_L \rightarrow \mathbf{Q} \gamma_L$.
+the photo-$z$ uncertainty changes the shear as $\gamma_L \rightarrow \mathbf{Q} \gamma_L$.
+
+Figure \ref{fig-bestpz} shows the histogram of the best MLZ photo-$z$ estimation \cite{HSC1-photoz} for galaxies in tract 
+9347 of HSC S16A data release \citep{HSC1-data}. These Galaxies are divided into ten source galaxy bins according to the 
+photo-$z$ best estimation and the boundaries of the bins are shown as vertical dash lines in Figure \ref{fig-bestpz}.
+Figure \ref{fig-pdfpz} shows the average probability density functions (PDFs) in each redshift bin.
+
+The left panel of Figure \ref{fig-corlensKer} shows the lensing kernels for lenses at five different redshifts as functions 
+of source galaxy redshfit bins. The dashed lines are the lensing kernel for spectroscopic redshfits with neglectable redshift 
+uncertainty. The solid lines are the lensing kernel for photometric redshifts with redshift uncertainties shown in Figure 
+\ref{fig-pdfpz}. The middle and right panels show the correlation between lensing kernels for lenses at different redshifts. 
+The middle panel is for spect-$z$ and the right panel is for photo-$z$.
+
+The photo-$z$ uncertainties smear the shapes of lensing kernels. As demonstrated by the dashed lines in the left panel of 
+Figure \ref{fig-corlensKer}, the lensing kernels converge to zero for source redshifts lower than the lens redshift, if the 
+uncertainties on the source galaxy redshift estimations are neglectable. However, as demonstrated by the solid lines in the 
+same panel, for the source redshifts with large photo-$z$ uncertainties, the lensing kernels do not converge to zero at 
+redshifts lower than the lens redshift. This is because the galaxies with photo-$z$ estimations lower than the lens redshifts 
+may be actually located at higher redshifts due to the photo-$z$ uncertainties.
+Comparing the correlation matrices shown in the middle panel and the right panel of Figure \ref{fig-corlensKer}, we conclude 
+that the smearings of lensing kernels due to photo-$z$ uncertainties increase the correlations between lensing kernels at 
+different lens plane.
 
@@
 
-The observed galaxies have random irregular (unequally-spaced) spacial distribution. To benefit the computational
-speed, we smooth the shear measurements from galaxy shapes and pixelise the smoothed measurements onto regular grids.
+\begin{figure}[!t]
+ \centering
+ \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
+ \caption{The Histogram of HSC-like shear measurement error (including errors from shape noise and photon noise) on the 
+        first component of shear ($g_1$).}
+ \label{fig:mass-redshift}
+\end{figure}
 
-The smoothing is conducted by convolving the measurements with a smoothing kernel
+The observed galaxies have random irregular (unequally-spaced) spacial distribution. In order boost the computational
+speed, we smooth the shear measurements from galaxy shapes and pixelize the smoothed measurements onto regular grids.
+After the pixelization, the fast Fourier transform (FFT) can be directly conducted on the transverse plane in each 
+source redshift bin.
+
+The smoothing is conducted by convolving the shear measurements with a smoothing kernel
 \begin{equation}
-\hat{\gamma}  = \frac{\sum_i  W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) e_i}{\sum_i R_i W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) },
+\gamma_{\rm{sm}} (\vec{\theta})  = \frac{\sum_i  W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) \gamma_i}{\sum_i W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) },
 \end{equation}
-where $W(\vec{\theta},z)$ is a $3$-D smoothing kernel. $e_i$, $R_i$, $z_i$ and $\theta_i$ are the ellipticity,
-response, reshift, and transverse position of the `$i$-th' galaxy in the galaxy catalog.
+where $W(\vec{\theta},z)$ is a $3$-D smoothing kernel. $\gamma_i$, $z_i$ and $\theta_i$ are the shear,
+photometric reshift, and transverse position of the `$i$-th' galaxy in the catalog.
 
@@
 \end{equation}
-In this paper, we set
+In this paper, we use an isotropic $2$-D Gaussian kernel and a $1$-D top-hat kernel to smooth the measurements in the 
+transverse plane and the line-of-sight direction, the smoothing kernel is 
 \begin{equation}
@@
 
-With the approximation that the density of galaxy number vary slowly on the smoothing scale and the fact that
-$\int d^3r W(\vec{r})=1$, the smoothing operator is defined as
+With the approximation that the density of galaxy number ($n(\vec{r})$) varies slowly on the smoothing scale, 
+since $\int d^3r W(\vec{r})=1$, the smoothed galaxy number density which is defined as
+$$n_{\rm{sm}}(\vec{r})=\sum_i W(\vec{\theta}-\vec{\theta_i},z-z_i),$$
+equals the number density. Therefore, we have $n_{\rm{sm}}(\vec{r})=n(\vec{r})$.
+We note that the smooth approximation of the galaxy density does not hold near the boundary of the survey as
+the galaxy number drop to zero outside of the boundary.
+
+The smoothing operator is defined as
 \begin{equation}
@@
 \end{equation}
-and the relation between shear signal and projections in the dictionary space is
-$\gamma_L \rightarrow \mathbf{W} \gamma_L$.
+and the smoothing procedure influence the shear signal through
+\begin{equation}
+\gamma_L \rightarrow \mathbf{W} \gamma_L.
+\end{equation}
+
+As we will discussed in Section \ref{subsec:method-pixel}, the smoothed shear field is pixelized into an equally spaced
+grids. Another widely used scheme is to directly average the shear measurements located in each pixel. Such scheme is 
+equivalent to an equal-space sampling of the shear field smoothed with a $3$-D top-hat kernel with the same scale as 
+the pixels.
+
+\begin{figure}[!t]
+ \centering
+ \includegraphics[width=0.45\textwidth]{noise_std_map_pix.pdf}
+ \caption{The standard deviation map of shear measurement error for the fifth source bin ($0.69 \leq z < 0.80 $).}
+\end{figure}
 
@@
 
-In the forward modeling, normally the shear field has its prediction on any points within a regular region.
-However, in real observations, the boundary of the survey, where shear measruements is recorded, is always
-irregular. Moreover, there are also many regions are masked out due to the existence of neighboring bright
-stars or bad pixels as bight stars and bad pixels are likely to bias the shape measurements.
-Therefore, it is necessary to add an mask on the shear field prediction in the forward modeling to match
-the prediction with realistic observations. The mask changes the shear prediction as follows
+\begin{figure*}[!t]
+ \centering
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f3-1.pdf}
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
+ \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
+NFW atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
+\end{figure*}
+
+In real observations, shear measurements are available in a finite region of the sky and the boundary of the region is
+always irregular. Moreover, there are also many isolated sub-regions do not have shear measurements due to the existence 
+of neighboring bright stars or bad pixels.
+
+We define the masking window function according to the smoothed number density of the galaxies as follows
+\begin{equation}
+ M(\vec{r})=
+\begin{cases}
+0 & n_{\rm{sm}}>1,\\
+1 & \rm{else}.
+\end{cases}
+\end{equation}
+The mask changes the shear measurements as
 \begin{equation}\label{eq-delta2gamma-final}
@@
 \end{equation}
-$M(\vec{\theta},z_s)$ is the masking function which is defined as
-\begin{equation}
- M(\vec{r})=
-\begin{cases}
-0 & \vec{r}~\rm{resides~in~masked~area}\\
-1 & \rm{else}.
-\end{cases}
-\end{equation}
-
 We define the masking operator as
@@
 \label{subsec:method-pixel}
+
+\begin{figure*}[!t]
+ \centering
+ \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
+ \caption{The left panel shows the stacked distribution of deviations of detected peak positions 
+ from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane and the 
+ $y$-axis is for the deviation of the redshift. The peaks inside the dashed black box are regarded as true detections. The 
+ right panel focus on the deviation of detected peaks in the line-of-sight direction. The $x$-axis shows the input redshifts 
+ and the $y$-axis is the redshift of the detected peak. The cross symbols show the average redshift of detected peak for 
+ halos with different input redshift and mass and the error-bars are the scatter of the corresponding peak redshifts. All 
+ of the results in this figure are based on the NFW atoms.}
+\end{figure*}
+
 We pixelize the smoothed shear field into a $N_\theta \times N_\theta \times N_s$ grid, where $N_\theta$
@@
 line-of-sight axis. $\gamma_{\alpha}$ is used to denote the value recorded on pixel with index $\alpha$, where $\alpha=
-1,...,N_\theta \times N_\theta \times N_s$. The grid on the transverse plan is equally spaced, therefore Fast Fourier
-Transform (FFT) can be used to boost the speed of linear operation on the transverse plan.
+1...N_\theta \times N_\theta \times N_s$. The grids on the transverse plans are equally spaced, therefore fast Fourier
+transform (FFT) can be used to boost the speed of linear operation on the transverse plan.
 
 Similarly, we pixelize each scale frame of the parameter $x$ into a $N_\theta \times N_\theta \times N_l$ grid. 
-The pixelization of the parameter $x$ on the transverse plan for each scale frame is exactly the same as the 
-pixelization of the smoothed shear field on the transverse plane. $N_l$ is the pixel number of the line-of-sight 
-axis. $x_{\beta}$ is used to denote the element of parameter vector $x$ with index $\beta$, where $\beta=1,...
-,N_\theta \times N_\theta \times N_l \times N$. The elements of the forward transform matrix $\mathbf{A}$ is denoted 
+The pixelization of the parameter field $x$ on the transverse plan for each scale frame is the same as the 
+pixelization of the smoothed shear field on the transverse plane. $N_l$ is the number of the line-of-sight planes. 
+$x_{\beta}$ is used to denote the element of the projected vector $x$ with index $\beta$, where $\beta=1...
+N_\theta \times N_\theta \times N_l \times N$. The elements of the forward transform matrix $\mathbf{A}$ is denoted 
 as $A_{\alpha\beta}$.
 
-We term the column vectors of the transform matrix $\mathbf{A}$ as the effective basis vectors. We note that the effective 
-basis vectors have different $l^2$ norm. The $l^2$ norm of the $i'th$ column vectors of the effective basis vectors are 
-$\mathcal{N}_{i}=\sum_\alpha A_{i\alpha}A_{i\alpha}$. Before solving the density map inversion problem, we normalize the column
-vectors of the transform matrix through
+We term the column vectors of the transform matrix $\mathbf{A}$ as the effective basis atoms. We note that the effective 
+basis atoms have different $l^2$ norm. The $l^2$ norm of the $i'th$ column vectors of the effective basis atoms are 
+$\mathcal{N}_{i}=\sum_\alpha A_{i\alpha}A_{i\alpha}$. Before solving the density map reconstruction problem, we normalize 
+the column
+vectors of the transform matrix through the following rescaling
 \begin{equation}
@@
 
-\subsection{Density map reversion}
-\label{subsec:method-reversion}
-\begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
- \caption{The PDF of photo-$z$ error for $10$ source redshift bins.}
-\end{figure}
+\subsection{Density map reconstruction}
+\label{subsec:method-reconstruction}
 
 \subsubsection{Adaptive lasso}
+
 The lasso algorithm uses $l^1$ penalty as the regularization term and the estimator is defined as
 \begin{equation}
-\hat{x'}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{A'} x')}_2^2+ \lambda \norm{x'}^1_1\right\},
+\hat{x'}^{\rm{lasso}}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{A'} x')}_2^2+ \lambda_{\rm{ls}} \norm{x'}^1_1\right\},
 \end{equation}
@@
 \begin{equation}
-\norm{x'}_p=(\sum_{i} |x'|^p_i)^{\frac{1}{p}}.
+\norm{x'}_p=(\sum_{i} |x'|^p_i)^{\frac{1}{p}},
 \end{equation}
+and $\lambda_{ls}$ is the penalization parameter for the preliminary lasso estimation.
 
-Given that the parameters to measure is sparse in the parameter space, the  lasso algorithm can select the parameters 
-which are relevant to the measurements and simultaneously estimate the value of the selected parameters. However, it has 
-been shown by \citet{AdaLASSO-Zou2006} that when the column vectors of $\mathbf{A'}$ are highly correlated, lasso cannot 
-select the related parameters from the parameter space consistently. Moreover, the estimated parameters are biased due to 
-the shrinkage process in the lasso regression.
+Given that the parameters to measure is sparse, the lasso algorithm selects the parameters which are relevant to the 
+measurements and simultaneously estimate the value of the selected parameters. However, it has been shown by 
+\citet{AdaLASSO-Zou2006} that when the column vectors of the projection matrix $\mathbf{A'}$ are highly correlated, 
+lasso cannot select the relevant parameters from the parameter space consistently. Moreover, the estimated parameters 
+are biased due to the shrinkage process in the lasso regression. For the density map reconstruction problem, the effective
+basis vectors are highly correlated since as shown in Figure \ref{fig-corlensKer}, the lensing kernels for lenses at 
+different redshifts are highly correlated. Therefore, the lasso algorithm cannot select the consistent sparse model 
+from the dictionary, which is demonstrated by the left figure of Figure \ref{fig-lassoVsadaLasso}.
 
-\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different coefficients 
-in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. First, Lasso estimation is performed in the first 
-step and achieve a preliminary lasso estimation of parameter ($\hat{x'}^{\rm{lasso}}$). In the second step, the lasso estimation 
-is used to weight the penalization on the parameters. With the definition of the adaptive lasso weight 
+\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different parameters
+in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. First, lasso is used to estimate the parameters and
+the preliminary lasso estimation is denoted as $\hat{x'}^{\rm{lasso}}$. In the second step, the preliminary lasso estimation 
+is used to weight the penalization. The weight on penalty is defined as
 \begin{equation}
@@
 \end{equation}
-here we set the hyper-parameter $\tau$ to $2$, the adaptive lasso estimator is expressed as
+here we set the hyper-parameter $\tau$ to $2$. 
+The adaptive lasso estimator is expressed as
 \begin{equation}\label{eq-lossFun}
 \hat{x'}=\argmin_{x'} \left\{ \frac{1}{2} \norm{\Sigma^{-\frac{1}{2}}(\gamma-\mathbf{A'}x')}^2_2 +
-\hat{w}\lambda \norm{x'}^1_1\right\}.
+\hat{w}\lambda_{\rm{als}} \norm{x'}^1_1\right\}.
 \end{equation}
+Here $\lambda_{\rm{als}}$ is the penalization parameter for adaptive lasso which does not need to be the same as the 
+penalization parameter for the preliminary lasso estimation ($\lambda_{\rm{ls}}$).
 
@@
 (\gamma_{\beta}-A'_{\beta j}x'_{j})\\
-&+ \lambda \hat{w_\beta} \abs{x'_\beta}.
+&+ \lambda_{\rm{als}} \hat{w_\beta} \abs{x'_\beta}.
 \end{split}
@@
 \subsubsection{FISTA}
+
+\begin{figure}[!t]
+ \centering
+ \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
+ \caption{The histograms of detected peak values for all of the halo and error realizations. The dotted lines with different 
+ colors are for the results of reconstruction with NFW atoms dictionary penalized with different regularization parameter 
+ $\lambda$.}
+\end{figure}
+
 In this work, we apply the Fast Iterative Soft Thresholding Alorithm (FISTA) of \citet{FISTA-Beck2009} to solve 
@@
 
-The parameter vector is initialized as $x^{(1)}=0$. According to the FISTA algorithm, we iteratively 
+The parameters are initialized as $x_i^{(1)}=0$. According to the FISTA algorithm, we iteratively 
 update the elements of the parameter vector ($x$). In the n'th iteration, a temporary update is first calcualted as
@@
 \STATE $x'^{(1)} = 0$ 
-\STATE $\hat{w}=1$
+\STATE $\hat{w}=1$, $\lambda=\lambda_{\rm{ls}}$
 \STATE $t^{(1)}=1$,$i=1$, $j=1$
@@
         \STATE $x'_{n+1} \leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)})$
+        \STATE $i=i+1$
     \ENDWHILE
 \STATE \textbf{Reinitialization:} ‎
-\STATE $\hat{w}\leftarrow \abs{\hat{x'}^{\rm{lasso}}}^{-2}$
-\STATE $\hat{x'}^{(1)} \leftarrow x'^{(N_{\rm{iter}})}$
-\STATE $t^{(1)}\leftarrow1$,$i\leftarrow1$
+\STATE $\hat{w}=\abs{\hat{x'}^{\rm{lasso}}}^{-2}$, $\lambda=\lambda_{\rm{als}}$
+\STATE $\hat{x'}^{(1)} = x'^{(N_{\rm{iter}})}$
+\STATE $t^{(1)}=1$, $i=1$
+\STATE $j=j+1$
 \ENDWHILE
@@
 
-\section{Simulation}
-\label{sec:Sim}
+\section{Tests}
+\label{sec:Test}
 
-This section simulates lensing shear fields induced by a group of dark matter halos with various halo masses and redshifts.
-Then the shear distortions are applied to HSC mock catalogs with different realizations of HSC-like shape noises and photo-$z$
-uncertainties.
+\begin{figure*}[!ht]
+ \centering
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f1-1.pdf}
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
+ \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
+point mass atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
+\end{figure*}
+
+In this section, we simulate weak lensing shear fields induced by a group of halos with various halo masses 
+and redshifts. The shear distortion fields are applied to HSC mock catalogs with different realizations of HSC-like shape 
+noises and photo-$z$ uncertainties (Section \ref{subsec:Sims}).
+
+Then, we test our algorithm on the simulations with two different setups of the algorithm. The first setup uses dictionary
+constructed with NFW atoms (Section \ref{subsec:test-nfw}) and the second setup uses dictionary constructed with point mass 
+atoms (Section \ref{subsec:test-pm}).
 
@@
 
-\subsection{Weak Lensing Fields}
+\subsection{Simulations}
+\label{subsec:Sims}
 
-We sample halos in two dimensional (mass, redshift) plane. The two dimensional plane is divided into eight redshift bins 
-times eight mass bins. The input redshifts and masses are shifted by random values for each halo, respectively.
-
-We simulate weak lensing shear fields of NFW halos according to \citet{haloModel-TJ2003-3pt}
-We assume a dependency of the concentration on the mass and the redshift of a halo 
-\citet[equation (2)]{c-M_Magneticum-Ragagnin2019}
+We sample halos in two dimensional redshift-mass plane. The redshift-mass plane is evenly divided into eight redshift bins
+and eight mass bins. The input redshifts and masses are shifted by random values for each halo from the centers 
+of the bins.
+The concentration of the NFW halo is a function of the halo's mass and redshift according to 
+\citet{c-M_Magneticum-Ragagnin2019}
 \begin{equation}
@@
 \end{equation}
+The weak lensing shear fields of these NFW halos are simulated according to \citet{haloModel-TJ2003-3pt}. The shear 
+distortions are applied to galaxy catalogs with HSC-like shape noise and photo-$z$ uncertainty.
 
-\subsection{HSC mock Catalog}
-\begin{figure}[!ht]
+The galay catalogs are simulated with the HSC S16A shape catalog \citep{HSC1-catalog}. 
+We uses galaxies in a one square degree region at the center of tract 9347 \citep{HSC1-data}.
+By randomly rotating the galaxies in the shape catalog, we simulate HSC-like shear estimation errors 
+with different realizations.
+The positions of the galaxies are randomized so that the galaxies homogeneously distributed in a one square degree 
+stamp.
+For each galaxy, we randomly assign its redshift following the MLZ photo-$z$ probability distribution function 
+\citep{HSC1-photoz} of the galaxy.
+
+\subsection{NFW atoms}
+\label{subsec:test-nfw}
+
+\begin{figure*}[!t]
 \centering
- \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
- \caption{HSC-like measurement error on the first component of shear ($g_1$).}
- \label{fig:mass-redshift}
-\end{figure}
-
-For each galaxy, we randomly assign its redshift following the MLZ photo-$z$ probability distribution function 
-\citep{HSC1-photoz} of the galaxy. The shear values are obtained from the all-sky weak lensing maps at two adjacent 
-redshift slices with linearly interpolation.
-
-\section{Results}
-\label{sec:Res}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.3\textwidth]{resultExp-tau010.png}
-\includegraphics[width=0.3\textwidth]{resultExp-tau015.png}
-\includegraphics[width=0.3\textwidth]{resultExp-tau020.png}
-\caption{The density map reconstructed for a halo with mass=$3.16\times 10^14 M_{\sun}/h$, $z=0.51$. The left panel shows
-the results with $\tau=0.10$, the middle panel is the result for $\tau=0.15$, the right panel is for $\tau=0.20$.}
+\includegraphics[width=0.42\textwidth]{delta-1-7-pz-wn-PM-falsepeakproblem.png}
+\includegraphics[width=0.42\textwidth]{delta-1-7-pz-wn-NFW-falsepeakproblem.png}
+\caption{The result of density map reconstruction with  Point Mass atoms (left) and  NFW atoms (right). The input density 
+        map is from a NFW halo with mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The reconstruction 
+        with point mass atoms has many false peaks at different redshfits.
+        } \label{fig-lassoVsadaLasso}
 \end{figure*}
 
-\subsection{Detection}
+In this subsection, we test the performance of our algorithm with the default setup which model the matter density
+field with multi-scale NFW atoms. The dictionary space is constructed with NFW atom with NFW scale radius set to
+three different comoving distances which are 0.12 Mpc/h, 0.24 Mpc/h, 0.36 Mpc/h. The truncation radius is set to
+four times of the scale radius.
+We test the algorithm with regularization parameter for the preliminary lasso is set to $3.5$ and $5.0$. The 
+regularization parameter for the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\gamma+1}$.
 
-\subsection{Redshift}
+\subsection{Point mass atoms}
+\label{subsec:test-pm}
+In this subsection, we test the performance of our algorithm with another setup which model the matter density
+field with point mass atoms.
+The dictionary space is constructed with point mass atoms in each lens redshift plane.
+We also test the algorithm with regularization parameter for the preliminary lasso is set to $3.5$ and $5.0$. The 
+regularization parameter for the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.
 
-\subsection{Density Map}
+Inspired by \citet{structureAdaLasso-Pramanik2020}, which propose to incorporate external group information into 
+different penalization weights for the regression coefficients by setting the penalization weights for adaptive lasso
+for model coefficients in the same group to the same value, we use a smoothed weight for adaptive lasso. The preliminary
+lasso estimation is smoothed with a top-hat filter of comoving scale 0.25 Mpc/h, which is denoted as 
+$\hat{x}^{\rm{ls}}_{\rm{sm}}$ and the penalization weights are set to $1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\gamma$.
 
@@
 \label{sec:Sum}
-
-\begin{figure}[!ht]
- \centering
- \includegraphics[width=0.45\textwidth]{noise_std_map_pix.pdf}
- \caption{The standard deviation map of shear measurement error for the fifth source bin ($0.69 \leq z < 0.80 $).}
-\end{figure}
 
@@
 
-\begin{figure*}[!ht]
- \centering
- \includegraphics[width=0.95\textwidth]{detfalseRate_f1-1.pdf}
- \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
- \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
-point mass atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
-\end{figure*}
-
-\begin{figure*}[!ht]
- \centering
- \includegraphics[width=0.95\textwidth]{detfalseRate_f3-1.pdf}
- \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
- \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
-NFW atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
-\end{figure*}
-
-\begin{figure*}[!ht]
- \centering
- \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
- \caption{The left panel shows the stacked distribution of deviations of detected peak positions 
- from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane and the 
- $y$-axis is for the deviation of the redshift. The peaks inside the dashed black box are regarded as true detections. The 
- right panel focus on the deviation of detected peaks in the line-of-sight direction. The $x$-axis shows the input redshifts 
- and the $y$-axis is the redshift of the detected peak. The cross symbols show the average redshift of detected peak for 
- halos with different input redshift and mass and the error-bars are the scatter of the corresponding peak redshifts. All 
- of the results in this figure are based on the NFW atoms.}
-\end{figure*}
-
-\begin{figure}[!ht]
- \centering
- \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
- \caption{The histograms of detected peak values for all of the halo and error realizations. The dotted lines with different 
- colors are for the results of reconstruction with NFW atoms dictionary penalized with different regularization parameter 
- $\lambda$.}
-\end{figure}
-
-\clearpage
 \bibliographystyle{aasjournal}

### 2020-10-24 demo/massMapStamp.py
fix a bug in noise simulation; did not keep the position the same for each realization

@@ -48,7 +48,7 @@ class massMapStampBatchConfig(pexConfig.Config):
                 default='planck-cosmo/config-pix96-nl20.ini',
                 doc = 'configuration file name')
     outDir  =   pexConfig.Field(dtype=str,
-                default='planck-cosmo/sparse-f3-3/',
+                default='planck-cosmo/sparse-f3-3-2/',
                 doc = 'output directory')
     pixDir  =   pexConfig.Field(dtype=str,
                 default='planck-cosmo/pix96-ns10/',

### 2020-10-25 doc/paper_ms_method_HSCY1/ms.tex
update to high resolution figures with mayavi

@@
 A new method is developed to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
-The $3$-D density contrast maps is modeled as a summation of NFW basis atoms which have $2$-D multi-scale NFW surface 
+The $3$-D density contrast maps are modeled as a summation of the NFW basis atoms which have $2$-D multi-scale NFW surface 
 density profiles on the transverse plane and $1$-D Dirac delta functions in the line-of-sight direction. With the prior 
@@
 photo-$z$ uncertainty.
-{\redColor{Add descriptions on the outcomes of the test on the simulations.}}
+Our findings are summarized as folllows: 1) The global minima solution of the standard lasso algorithm suffers from a
+smear of structure in the line-of-sight direction even in the absence of shape nosie.
+2) The global minima solution of addaptive lasso algorithm significantly removes the line-of-sight smear of structure.
 \end{abstract}
@@
 \centering
-\includegraphics[width=0.42\textwidth]{delta-3-7-pz-nn-lasso.png}
-\includegraphics[width=0.42\textwidth]{delta-3-7-pz-nn-alasso.png}
+\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-lasso.pdf}
+\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-alasso.pdf}
 \caption{The result of density map reconstruction with standard lasso (left) and adaptive lasso (right). The input density 
@@
 \centering
-\includegraphics[width=0.42\textwidth]{delta-1-7-pz-wn-PM-falsepeakproblem.png}
-\includegraphics[width=0.42\textwidth]{delta-1-7-pz-wn-NFW-falsepeakproblem.png}
+\includegraphics[width=0.49\textwidth]{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
+\includegraphics[width=0.49\textwidth]{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
 \caption{The result of density map reconstruction with  Point Mass atoms (left) and  NFW atoms (right). The input density 

### 2020-10-26 doc/paper_ms_method_HSCY1/ms.tex
more mayavi figures, proofread to finish meth section

@@
 \usepackage{color}
+\usepackage{graphicx,subfigure}
+\renewcommand\thesubfigure{(\roman{subfigure})}
 
-%\usepackage{subfigure}
 \usepackage{textcomp}
@@
 \DeclareMathOperator{\arccosh}{arccosh}
-\newcommand \figPath{./}
 \newcommand \redColor{\color{red}}
@@
 due to the influence of gravity. As a result of the light distortion, the shapes of the background galaxies are coherently
-sheared. Such effect, which is known as weak lensing, imprints the information of foreground mass density distribution
+distorted. Such effect, which is known as weak lensing, imprints the information of foreground mass density distribution
 to the background galaxy images and offers a direct probe into the mass density distribution in our universe
@@
 
-Reconstructions of density map from shear measurements also receive considerable interest. $2$-D density map reconstruction 
-which recover an integration of projected mass along the line-of-sight has been well studied within the community
-\citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
+The reconstruction of density map from shear measurements also receive considerable interest as it reaches the nonlinear scales. 
+$2$-D density map reconstruction which recover an integration of projected mass along the line-of-sight has been well studied 
+within the community \citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
 and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However, the 
@@
 
-The projection coefficients are estimated through optimizing a loss function with regularization. The estimator is
+The projection coefficients are estimated through optimizing a regularized loss function. The estimator is
 generally defined as
@@
 \end{equation}
-where $\norm{\Sigma^{-\frac{1}{2}}(\gamma - \mathbf{T\Phi} x)}_2^2$ is the chi-square term\footnote{weighted by the
-inverse of the diagonal covariance matrix of error on the shear measurements ($\Sigma$).} measuring
+where $\norm{\Sigma^{-\frac{1}{2}}(\gamma - \mathbf{T\Phi} x)}_2^2$ is the $l^2$ chi-square term\footnote{weighted by 
+the inverse of the diagonal covariance matrix of error on the shear measurements ($\Sigma$).} measuring
 the residuals between the prediction and the data, while $C(x)$ is the regularization term measuring the deviation of
-the estimation of the parameter ($x$) from the prior assumptions. Such estimation prefers the parameters that are able
-to describe the observations and also align with the prior assumptions. The regularization parameter $\lambda$ adjusts 
-the relative weight between the observations and prior assumptions in the optimization process.
+the estimation of the parameter ($x$) from the prior assumptions. The $l^p$ norm is defined as
+\begin{equation}
+\norm{x}_p=(\sum_{i} |x|^p_i)^{\frac{1}{p}}.
+\end{equation}
+Such estimation prefers the parameters that are able to describe the observations and also align with the prior assumptions. 
+The regularization parameter $\lambda$ adjusts the relative weight between the observations and prior assumptions in the 
+optimization process.
 
 \citet{LSS-massMap-Wiener-Simon2009} propose to use the Wiener filter, which is also known as $l^2$ ridge regulation 
-($C=\norm{x}^2_2$), to find a solution in Fourier space. \citet{HSC1-massMaps} apply the method of 
+($C=\norm{x}^2_2$), to find a regularized solution in Fourier space. \citet{HSC1-massMaps} apply the method of 
 \citet{LSS-massMap-Wiener-Simon2009} to the first year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}. 
@@
 
-Finally, we find the sparse solution in section \ref{subsec:method-reconstruction} using the adaptive lasso algorithm 
-\citep{AdaLASSO-Zou2006} optimized with the FISTA alogrithm \citep{FISTA-Beck2009}.
+Finally, we solve the mass reconstruction problem in section \ref{subsec:method-reconstruction} using the adaptive lasso 
+algorithm \citep{AdaLASSO-Zou2006} optimized with the FISTA alogrithm \citep{FISTA-Beck2009}.
 
@@
 Here we denote the physical shear distortion field as $\gamma_L$ and we note that the final observed shear measurements 
-are also physical shear distortions influenced by systematic errors from observatins. The systematic error will be discussed 
+are also physical shear distortions influenced by systematic errors from observatins. The systematic errors will be discussed 
 in Section \ref{subsec:method-Systematics}.
@@
 \centering
-\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-lasso.pdf}
-\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-alasso.pdf}
+\subfigure[lasso]{\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-lasso.pdf}}
+\subfigure[adaptive lasso]{\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-alasso.pdf}}
 \caption{The result of density map reconstruction with standard lasso (left) and adaptive lasso (right). The input density 
         map is from a NFW halo with mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso reconstruction 
-        smear the density field along the line-of-sight direction. Noises on shear measurements are neglected in the 
-        simulation.} \label{fig-lassoVsadaLasso}
+        smear the density field along the line-of-sight direction (vertical direction in the plots). Noises on shear measurements 
+        are neglected in this simulation.} \label{fig-lassoVsadaLasso}
 \end{figure*}
@@
 \end{equation}
-where $\phi_s(\vec{r})$ are the basis atoms of the dictionary. The basis atoms have `$N$' different scales and the atoms
+where $\phi_s(\vec{r})$ are the basis atoms of the dictionary. The basis atoms have `$N$' different scale frames and the atoms
 in each scale frame are shifted by $\vec{r'}$ to form basis at different positions. $x_s(\vec{r'})$ is the projection 
@@
 
-These basis atoms are constructed with multi-scale NFW atoms which are denoted as $\{\phi_1,...,\phi_N\}$.
+We propose to use multi-scale NFW atoms, denoted as $\{\phi_1,...,\phi_N\}$, as our dictionary basi.
 On the transverse plane, the NFW atoms follow surface density profiles of NFW halos
@@
 
-In this paper dictionary constructed with point mass atoms is used to compare with the dictionary of multi-scale atoms.
+In this paper, dictionary constructed with point mass atoms is used to compare with the dictionary of multi-scale atoms.
 The point mass atoms is a $3$-D Dirac function defined as follows
@@
 \ref{fig-atoms2D}. The $1$-D slices of the profiles are demonstrated in Fiugre \ref{fig-atoms1D}. Note that these profiles 
-are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The smoothing operator is described in 
-Section \ref{subsec:method-smoothing} and the pixelization operator is described in Section \ref{subsec:method-pixel}.
+are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The smoothing operation is discussed in 
+Section \ref{subsec:method-smoothing} and the pixelization operation is discussed in Section \ref{subsec:method-pixel}.
 
@@
 The photometric redshifts of source galaxies in the current large scale survey are estimated with a limited number of 
-board photometric bands (e.g. $9$ bands for KIDS$+$VIKING survey, $5$ bands for DES survey and HSC survey). As a result, 
-the estimated redshifts of galaxies suffer from much larger uncertainties, comparing with redshifts estimated with 
-spectroscopic observations. Such photo-$z$ uncertainty smears the lensing kernels statistically since a galaxy with a 
-best fit photo-$z$ estimation of $z_s$ has possibilities of being actually located at different redshifts ($z$).
-The probability function for the photo-$z$ uncertainty is denoted as $P(z|z_s)$ and the expected shear distortion on 
-the galaxy is
+board photometric bands (e.g. $9$ bands for KIDS$+$VIKING survey \citep{KIDS_VIKING-Hildebrant2020}, $5$ bands for DES 
+survey and HSC survey). As a result, the estimated redshifts of galaxies suffer from much larger uncertainties, compared 
+with redshifts estimated with spectroscopic observations. Such photo-$z$ uncertainty smears the lensing kernels statistically 
+since a galaxy with a best fit photo-$z$ estimation of $z_s$ has possibilities of being actually located at different 
+redshifts ($z$). The probability function for the photo-$z$ uncertainty is denoted as $P(z|z_s)$ and the expected shear 
+distortion on the galaxy is
 \begin{equation}\label{eq-delta2gamma-poz}
-\gamma_L(\vec{\theta},z_s) \rightarrow \int dz_s P(z|z_s) \gamma_L(\vec{\theta},z_s).
+\int dz_s P(z|z_s) \gamma_L(\vec{\theta},z_s).
 \end{equation}
@@
 \end{equation}
-the photo-$z$ uncertainty changes the shear as $\gamma_L \rightarrow \mathbf{Q} \gamma_L$.
+the photo-$z$ uncertainty changes the shear as 
+\begin{equation}
+\gamma_L \rightarrow \mathbf{Q} \gamma_L,
+\end{equation}
+where we use $\rightarrow$ to denote the changes of shear by the systematic operator.
 
@@
 photo-$z$ best estimation and the boundaries of the bins are shown as vertical dash lines in Figure \ref{fig-bestpz}. 
-Figure \ref{fig-pdfpz} shows the average probability density functions (PDFs) in each redshift bin.
+Figure \ref{fig-pdfpz} shows the average probability density function (PDF) in for galaxies in each redshift bin.
 
@@
 uncertainty. The solid lines are the lensing kernel for photometric redshifts with redshift uncertainties shown in Figure 
-\ref{fig-pdfpz}. The middle and right panels show the correlation between lensing kernels for lenses at different redshifts. 
-The middle panel is for spect-$z$ and the right panel is for photo-$z$.
+\ref{fig-pdfpz}. 
+As shown by the dashed lines in the left panel of Figure \ref{fig-corlensKer}, the lensing kernels converge to zero for source 
+redshifts lower than the lens redshift, if the uncertainties on the source galaxy redshift estimations are neglectable. However,
+as demonstrated by the solid lines in the same panel, for the source redshifts with large photo-$z$ uncertainties, the lensing 
+kernels do not converge to zero at redshifts lower than the lens redshift. This is because the galaxies with photo-$z$ estimations 
+lower than the lens redshifts may be actually located at higher redshifts due to the photo-$z$ uncertainties.
 
-The photo-$z$ uncertainties smear the shapes of lensing kernels. As demonstrated by the dashed lines in the left panel of 
-Figure \ref{fig-corlensKer}, the lensing kernels converge to zero for source redshifts lower than the lens redshift, if the 
-uncertainties on the source galaxy redshift estimations are neglectable. However, as demonstrated by the solid lines in the 
-same panel, for the source redshifts with large photo-$z$ uncertainties, the lensing kernels do not converge to zero at 
-redshifts lower than the lens redshift. This is because the galaxies with photo-$z$ estimations lower than the lens redshifts 
-may be actually located at higher redshifts due to the photo-$z$ uncertainties.
+The middle and right panels show the correlation between lensing kernels for lenses at different redshifts. The middle panel is for 
+spect-$z$ and the right panel is for photo-$z$.
+As demonstrated in the middle panel, the lensing kernels are highly correlated even though the redshfit estimation is precise.
 Comparing the correlation matrices shown in the middle panel and the right panel of Figure \ref{fig-corlensKer}, we conclude 
-that the smearings of lensing kernels due to photo-$z$ uncertainties increase the correlations between lensing kernels at 
-different lens plane.
+that the photo-$z$ uncertainties further increase the correlations between lensing kernels at different lens plane.
 
@@
 With the approximation that the density of galaxy number ($n(\vec{r})$) varies slowly on the smoothing scale, 
-since $\int d^3r W(\vec{r})=1$, the smoothed galaxy number density which is defined as
-$$n_{\rm{sm}}(\vec{r})=\sum_i W(\vec{\theta}-\vec{\theta_i},z-z_i),$$
-equals the number density. Therefore, we have $n_{\rm{sm}}(\vec{r})=n(\vec{r})$.
-We note that the smooth approximation of the galaxy density does not hold near the boundary of the survey as
-the galaxy number drop to zero outside of the boundary.
+as $\int d^3r W(\vec{r})=1$, the smoothed galaxy number density which is defined as
+\begin{equation}\label{eq-numDesSmooth}
+n_{\rm{sm}}(\vec{r})=\sum_i W(\vec{\theta}-\vec{\theta_i},z-z_i),
+\end{equation}
+equals the galaxy number density: $n_{\rm{sm}}(\vec{r})=n(\vec{r})$.
+We note that the galaxy number density experience a steep drop on the boundary of the survey, therefore the 
+smoothed galaxy number density does not equal the galaxy number density close the the boundary of the survey.
 
@@
 
-As we will discussed in Section \ref{subsec:method-pixel}, the smoothed shear field is pixelized into an equally spaced
-grids. Another widely used scheme is to directly average the shear measurements located in each pixel. Such scheme is 
-equivalent to an equal-space sampling of the shear field smoothed with a $3$-D top-hat kernel with the same scale as 
-the pixels.
+As we will discussed in Section \ref{subsec:method-pixel}, the smoothed shear field is pixelized into equally spaced
+grids. We note that another widely used scheme is to directly average the shear measurements located in each pixel. 
+Such scheme is equivalent to an equal-space sampling of the shear field smoothed with a $3$-D top-hat kernel with the 
+same scale as the pixels.
 
@@
 In real observations, shear measurements are available in a finite region of the sky and the boundary of the region is
-always irregular. Moreover, there are also many isolated sub-regions do not have shear measurements due to the existence 
-of neighboring bright stars or bad pixels.
+always irregular. Moreover, there are also many isolated sub-regions near the bright stars are masked out since the light
+from bright stars tends to influence the shear measurements on neighboring galaxies.
 
-We define the masking window function according to the smoothed number density of the galaxies as follows
+We define the masking window function according to the smoothed number density (defined in eq. (\ref{eq-numDesSmooth})) of 
+the galaxies as follows
 \begin{equation}
@@
 \end{equation}
-The mask changes the shear measurements as
+The mask changes the shear measurements though
 \begin{equation}\label{eq-delta2gamma-final}
@@
 1...N_\theta \times N_\theta \times N_s$. The grids on the transverse plans are equally spaced, therefore fast Fourier
-transform (FFT) can be used to boost the speed of linear operation on the transverse plan.
+transform (FFT) can be used to boost the speed of linear operation on the transverse plan, whereas the grids in the 
+line-of-sight direction follow equal number binning as shown in Figure \ref{fig-bestpz}.
 
 Similarly, we pixelize each scale frame of the parameter $x$ into a $N_\theta \times N_\theta \times N_l$ grid. 
-The pixelization of the parameter field $x$ on the transverse plan for each scale frame is the same as the 
-pixelization of the smoothed shear field on the transverse plane. $N_l$ is the number of the line-of-sight planes. 
-$x_{\beta}$ is used to denote the element of the projected vector $x$ with index $\beta$, where $\beta=1...
-N_\theta \times N_\theta \times N_l \times N$. The elements of the forward transform matrix $\mathbf{A}$ is denoted 
-as $A_{\alpha\beta}$.
+The pixelization of the parameter field $x$ on the transverse plan for each scale frame is exactly the same as the 
+pixelization of the smoothed shear field on the transverse plane. Whereas the parameter field is pixelized into equal 
+spaced grids in the line-of-sight direction. Here, we use $N_l$ to denote the number of the lens planes and $x_{\beta}$ to 
+denote the element of the parameter with index $\beta$, where $\beta=1...N_\theta \times N_\theta \times N_l \times N$. 
+The corresponding pixelized elements of the forward transform matrix $\mathbf{A}$ is denoted as $A_{\alpha\beta}$.
 
-We term the column vectors of the transform matrix $\mathbf{A}$ as the effective basis atoms. We note that the effective 
-basis atoms have different $l^2$ norm. The $l^2$ norm of the $i'th$ column vectors of the effective basis atoms are 
+We term the column vectors of the forward transform matrix $\mathbf{A}$ as the effective basis atoms. We note that the 
+effective basis atoms have different $l^2$ norm. The $l^2$ norm of the $i'th$ column vectors of the effective basis atoms are 
 $\mathcal{N}_{i}=\sum_\alpha A_{i\alpha}A_{i\alpha}$. Before solving the density map reconstruction problem, we normalize 
@@
 
-The lasso algorithm uses $l^1$ penalty as the regularization term and the estimator is defined as
+The lasso algorithm uses $l^1$ norm of parameters as the regularization term and the estimator is defined as
 \begin{equation}
@@
 \end{equation}
-where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and $l^2$ norm, respectively. The $l^p$ norm is
-defined as
-\begin{equation}
-\norm{x'}_p=(\sum_{i} |x'|^p_i)^{\frac{1}{p}},
-\end{equation}
-and $\lambda_{ls}$ is the penalization parameter for the preliminary lasso estimation.
+where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and $l^2$ norm, respectively.
+$\lambda_{ls}$ denotes the penalization parameter for the lasso estimation.
 
-Given that the parameters to measure is sparse, the lasso algorithm selects the parameters which are relevant to the 
-measurements and simultaneously estimate the value of the selected parameters. However, it has been shown by 
+The lasso algorithm selects the parameters which are relevant to the measurements and simultaneously estimate the value of 
+the selected parameters. However, it has been shown by 
 \citet{AdaLASSO-Zou2006} that when the column vectors of the projection matrix $\mathbf{A'}$ are highly correlated, 
 lasso cannot select the relevant parameters from the parameter space consistently. Moreover, the estimated parameters 
-are biased due to the shrinkage process in the lasso regression. For the density map reconstruction problem, the effective
-basis vectors are highly correlated since as shown in Figure \ref{fig-corlensKer}, the lensing kernels for lenses at 
-different redshifts are highly correlated. Therefore, the lasso algorithm cannot select the consistent sparse model 
-from the dictionary, which is demonstrated by the left figure of Figure \ref{fig-lassoVsadaLasso}.
+are biased due to the shrinkage process in the lasso regression. We note that, for the density map reconstruction problem, 
+the effective basis vectors are highly correlated since, as shown in Figure \ref{fig-corlensKer}, the lensing kernels for 
+lenses at different redshifts are highly correlated. Therefore, the lasso algorithm cannot select the consistent mass in  
+the line-of-sight direction and the reconstructed mass sufferes from smears in the line-of-sight direction even in the 
+absence of noise on shear measurements. 
+Figure \ref{fig-lassoVsadaLasso} shows the reconstructions of the mass map of a single halo with halo mass equals 
+$M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The noises on shear measurements are not included. The left panel of 
+Figure \ref{fig-lassoVsadaLasso} is the reconstruction with lasso algorithm which shows a significant smear along the line-of-sight.
 
 \citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different parameters
-in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. First, lasso is used to estimate the parameters and
-the preliminary lasso estimation is denoted as $\hat{x'}^{\rm{lasso}}$. In the second step, the preliminary lasso estimation 
-is used to weight the penalization. The weight on penalty is defined as
+in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. In the first step, lasso is used to estimate the 
+parameters and the preliminary lasso estimation is denoted as $\hat{x'}^{\rm{lasso}}$. In the second step, the preliminary 
+lasso estimation is used to weight the penalization. The weight on penalty is defined as
 \begin{equation}
@@
 \end{equation}
-To simplify the notification, we define the quadruple term in the loss function as $G(x')$:
+To simplify the notification in future, we define the quadruple term in the loss function as $G(x')$:
 \begin{equation}
@@
 where $\norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }$ refers to the spectrum norm of the matrix
-$\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$. The spectral norm is estimated using random
-vectors. We simulate large number of random vectors with $l^2$ norms equal one with different realizations. Then, 
-the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is applied to each random vector and get a 
-corresponding transformed random vector. The spectral norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$
+$\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$. The spectral norm is estimated by simulating a large number of 
+random vectors with $l^2$ norms equal one with different realizations. Then, the matrix operator 
+$\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is applied to each random vector and get a corresponding transformed 
+random vector. The spectral norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$
 is the maximum $l^2$ norm of the transformed vectors.
@@
 \subsubsection{The Algorithm}
+
 The algorithm is described in Algorithm \ref{alg-1}.
@@
 \centering
-\includegraphics[width=0.49\textwidth]{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
-\includegraphics[width=0.49\textwidth]{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
+\subfigure[Point Mass: $\lambda=3.5$]{\includegraphics[width=0.45\textwidth]{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}}
+\subfigure[NFW: $\lambda=3.5$]{\includegraphics[width=0.45\textwidth]{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}}
+\subfigure[Point Mass: $\lambda=5.0$]{\includegraphics[width=0.45\textwidth]{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}}
+\subfigure[NFW: $\lambda=5.0$]{\includegraphics[width=0.45\textwidth]{delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}}
 \caption{The result of density map reconstruction with  Point Mass atoms (left) and  NFW atoms (right). The input density 
-        map is from a NFW halo with mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The reconstruction 
-        with point mass atoms has many false peaks at different redshfits.
+        map is from a NFW halo with mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. 
         } \label{fig-lassoVsadaLasso}
@@
 four times of the scale radius.
-We test the algorithm with regularization parameter for the preliminary lasso is set to $3.5$ and $5.0$. The 
+We test the algorithm with different regularization parameters for the preliminary lasso set to $3.5$ and $5.0$. The 
 regularization parameter for the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\gamma+1}$.

### 2020-10-26 doc/paper_ms_method_HSCY1/ms.tex
some detailed modification

@@
 \title{Sparsity Weak Lensing $3$-D Density Map Reconstruction:
-Reducing the line-of-sight smearing.}
+Reducing the line of sight smearing.}
 %\author{Xiangchong Li}
@@
 \begin{abstract}
-A new method is developed to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
+A new method is developed to reconstruct $3$-D density contrast maps from photometric weak-lensing shear measurements.
 The $3$-D density contrast maps are modeled as a summation of the NFW basis atoms which have $2$-D multi-scale NFW surface
-density profiles on the transverse plane and $1$-D Dirac delta functions in the line-of-sight direction. With the prior 
+density profiles on the transverse plane and $1$-D Dirac delta functions in the line of sight direction. With the prior
 assumption that the density fields can be sparsely represented by the NFW basis atoms, it is reconstructed using an
@@
 Our findings are summarized as folllows: 1) The global minima solution of the standard lasso algorithm suffers from a
-smear of structure in the line-of-sight direction even in the absence of shape nosie.
-2) The global minima solution of addaptive lasso algorithm significantly removes the line-of-sight smear of structure.
+smear of structure in the line of sight direction even in the absence of shape nosie.
+2) The global minima solution of addaptive lasso algorithm significantly removes the line of sight smear of structure.
 \end{abstract}
@@
 
-Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line-of-sight
+Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line of sight
 due to the influence of gravity. As a result of the light distortion, the shapes of the background galaxies are coherently
-distorted. Such effect, which is known as weak lensing, imprints the information of foreground mass density distribution
+distorted. Such effect, which is known as weak-lensing, imprints the information of foreground mass density distribution
 to the background galaxy images and offers a direct probe into the mass density distribution in our universe
@@
 
-Several large scale surveys target to study the weak lensing effect at high precision level (e.g. HSC \citep{HSC1-data}, KIDS
+Several large scale surveys target to study the weak-lensing effect at high precision level (e.g. HSC \citep{HSC1-data}, KIDS
 \citep{KIDS13}, DES \citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, WFIRST \citep{WFIRST15}).
 
-The primary goal of most weak lensing surveys is to constrain the cosmology model through $2$-point correlations. The studies
+The primary goal of most weak-lensing surveys is to constrain the cosmology model through $2$-point correlations. The studies
 include galaxy-galaxy lensing which cross correlating the shear field ($\gamma$) with the positions of foreground galaxies
@@
 The reconstruction of density map from shear measurements also receive considerable interest as it reaches the nonlinear scales.
-$2$-D density map reconstruction which recover an integration of projected mass along the line-of-sight has been well studied 
+$2$-D density map reconstruction which recover an integration of projected mass along the line of sight has been well studied
 within the community \citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
@@
 ($C=\norm{x}^2_2$), to find a regularized solution in Fourier space. \citet{HSC1-massMaps} apply the method of
-\citet{LSS-massMap-Wiener-Simon2009} to the first year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}. 
-However, the density maps reconstructed by this method suffer from a smearing along the line-of-sight direction with 
+\citet{LSS-massMap-Wiener-Simon2009} to the first-year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}.
+However, the density maps reconstructed by this method suffer from a smearing along the line of sight direction with
 a standard deviation of $\sigma_z=0.2 \sim 0.3$.
@@
 of a non-convex loss function penalized with the firm thresholding function. \citet{LSS-massMap-Glimpse3D-Leonard2014}
-significantly reduce the smearing along the line-of-sight, however, the stability of the non-convex optimization and
+significantly reduce the smearing along the line of sight, however, the stability of the non-convex optimization and
 greedy coordinate descent algorithm has not been fully justified. Moreover, the Starlets functions are not designed to
@@
 functions \citep{haloModel-TJ2003-3pt} on the transverse plane. We follow \citet{LSS-massMap-Glimpse3D-Leonard2014}
-to neglect the depth of halos since the resolution scale of the reconstruction in the line-of-sight direction is much 
-larger than the scales of halos. Therefore, we set the profile of the NFW atoms in the line-of-sight as the Dirac delta 
+to neglect the depth of halos since the resolution scale of the reconstruction in the line of sight direction is much
+larger than the scales of halos. Therefore, we set the profile of the NFW atoms in the line of sight as the Dirac delta
 function. The multi-scale NFW atoms are used to model the profiles of halos which is assumed to be sparsely distributed
 in the universe. With the sparsity prior, the adaptive lasso regularization \citep{AdaLASSO-Zou2006} is used to reconstruct
-the density field. We find that, in contrast to the standard lasso estimator which smears the structure along the line-of-sight,
+the density field. We find that, in contrast to the standard lasso estimator which smears the structure along the line of sight,
 the addaptive lasso is able to significantly reduce the smearing effect.
@@
 This paper is organized as follows.
-Section \ref{sec:Method} proposes the new method for $3$-D density map reconstruction.
-Section \ref{sec:Test} Tests our algorithm on HSC-like simulations.
-Section \ref{sec:Sum} summarizes and discusses the future development of the method.
+In Section \ref{sec:Method}, we propose the new method for $3$-D density map reconstruction.
+In Section \ref{sec:Test}, we test the novel algorithm on HSC-like simulations.
+In Section \ref{sec:Sum}, we summarize and discuss the future development of the method.
 
@@
 The lensing convergence map at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
-density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line-of-sight is
+density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line of sight is
 \begin{equation}
@@
         map is from a NFW halo with mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso reconstruction
-        smear the density field along the line-of-sight direction (vertical direction in the plots). Noises on shear measurements 
+        smear the density field along the line of sight direction (vertical direction in the plots). Noises on shear measurements
         are neglected in this simulation.} \label{fig-lassoVsadaLasso}
@@
 As the scales of halos are much less than the reachable redshift resolution, we neglect the depth of halo on the
-line-of-sight direction and set the profiles of NFW atoms in the line-of-sight direction to $1$-D Dirac delta 
+line of sight direction and set the profiles of NFW atoms in the line of sight direction to $1$-D Dirac delta
 functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}.
@@
 
-$W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line-of-sight component
+$W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line of sight component
 $W_\times(z)$
@@
 In this paper, we use an isotropic $2$-D Gaussian kernel and a $1$-D top-hat kernel to smooth the measurements in the
-transverse plane and the line-of-sight direction, the smoothing kernel is 
+transverse plane and the line of sight direction, the smoothing kernel is
 \begin{equation}
@@
  $y$-axis is for the deviation of the redshift. The peaks inside the dashed black box are regarded as true detections. The
- right panel focus on the deviation of detected peaks in the line-of-sight direction. The $x$-axis shows the input redshifts 
+ right panel focus on the deviation of detected peaks in the line of sight direction. The $x$-axis shows the input redshifts
  and the $y$-axis is the redshift of the detected peak. The cross symbols show the average redshift of detected peak for
@@
 is the number of pixels of two orthogonal axes of the transverse plane and $N_s$ is the number of pixels of the
-line-of-sight axis. $\gamma_{\alpha}$ is used to denote the value recorded on pixel with index $\alpha$, where $\alpha=
+line of sight axis. $\gamma_{\alpha}$ is used to denote the value recorded on pixel with index $\alpha$, where $\alpha=
 1...N_\theta \times N_\theta \times N_s$. The grids on the transverse plans are equally spaced, therefore fast Fourier
 transform (FFT) can be used to boost the speed of linear operation on the transverse plan, whereas the grids in the
-line-of-sight direction follow equal number binning as shown in Figure \ref{fig-bestpz}.
+line of sight direction follow equal number binning as shown in Figure \ref{fig-bestpz}.
 
@@
 pixelization of the smoothed shear field on the transverse plane. Whereas the parameter field is pixelized into equal
-spaced grids in the line-of-sight direction. Here, we use $N_l$ to denote the number of the lens planes and $x_{\beta}$ to 
+spaced grids in the line of sight direction. Here, we use $N_l$ to denote the number of the lens planes and $x_{\beta}$ to
 denote the element of the parameter with index $\beta$, where $\beta=1...N_\theta \times N_\theta \times N_l \times N$.
@@
 lenses at different redshifts are highly correlated. Therefore, the lasso algorithm cannot select the consistent mass in
-the line-of-sight direction and the reconstructed mass sufferes from smears in the line-of-sight direction even in the 
+the line of sight direction and the reconstructed mass sufferes from smears in the line of sight direction even in the
 absence of noise on shear measurements.
@@
 $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The noises on shear measurements are not included. The left panel of
-Figure \ref{fig-lassoVsadaLasso} is the reconstruction with lasso algorithm which shows a significant smear along the line-of-sight.
+Figure \ref{fig-lassoVsadaLasso} is the reconstruction with lasso algorithm which shows a significant smear along the line of sight.
 
@@
 
-In this section, we simulate weak lensing shear fields induced by a group of halos with various halo masses 
+In this section, we simulate weak-lensing shear fields induced by a group of halos with various halo masses
 and redshifts. The shear distortion fields are applied to HSC mock catalogs with different realizations of HSC-like shape
@@
 \end{equation}
-The weak lensing shear fields of these NFW halos are simulated according to \citet{haloModel-TJ2003-3pt}. The shear 
+The weak-lensing shear fields of these NFW halos are simulated according to \citet{haloModel-TJ2003-3pt}. The shear
 distortions are applied to galaxy catalogs with HSC-like shape noise and photo-$z$ uncertainty.
@@
 
-We develope a novel method to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
+We develope a novel method to reconstruct $3$-D density contrast maps from photometric weak-lensing shear measurements.
 Our method models $3$-D density contrast maps as a summation of NFW atoms with multiple comoving radius and point mass atoms

### 2020-10-27 doc/paper_ms_method_HSCY1/ms.tex
update the figures in paper

@@
 \hypersetup{breaklinks}
+
 \DeclareMathOperator{\arccosh}{arccosh}
@@
 \usepackage{algorithm,algcompatible}
+\usepackage[-]{callouts}
 
@@
 \algnewcommand\OUTPUT{\item[\textbf{Output:}]}
+
+\newcommand{\includezraphics}[1]{
+\begin{annotate}{
+\includegraphics[width=0.43\textwidth]{#1}}{0.45}
+\arrow { -6., -4}{ -6., 4}
+\note {-6.,4.5}{$\huge{z}$}
+\end{annotate}
+}
 
@@
 density profiles on the transverse plane and $1$-D Dirac delta functions in the line of sight direction. With the prior
-assumption that the density fields can be sparsely represented by the NFW basis atoms, it is reconstructed using an
-oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape noise and
+assumption that the density fields can be sparsely represented by the NFW basis atoms, the density fields are reconstructed 
+using an oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape noise and
 photo-$z$ uncertainty.
@@
     \includegraphics[width=1.\textwidth]{nfwlet-atom-2D.pdf}
-    \caption{The smoothed basis atoms. The first row shows the smoothed basis atoms in Fourier space
-            and the second row shows the smoothed basis atoms in Real space.
-            The first column is point mass atom and the other columns are multi-scale NFW atoms.
-            The smoothing kernel is Gaussian with scale of $1.5$ pixels.} \label{fig-atoms2D}
+    \caption{The smoothed pixelized basis atoms. The upper row shows the basis atoms in Fourier space
+            and the lower row shows the basis atoms in Real space.
+            The leftmost column is point mass atom and the other columns are multi-scale NFW atoms.
+            The smoothing kernel is Gaussian with standard deviation of $1.5$ pixels.} \label{fig-atoms2D}
 \end{figure*}
@@
  \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
- \caption{The $1$-D slices for smoothed basis atoms at $x=0$. The corresponding $2$-D profiles are shown in Figure
-        \ref{fig-atoms2D}.} \label{fig-atoms1D}
+ \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The corresponding $2$-D profiles are 
+        shown in Figure \ref{fig-atoms2D}.} \label{fig-atoms1D}
 \end{figure}
@@
 The primary goal of most weak-lensing surveys is to constrain the cosmology model through $2$-point correlations. The studies
-include galaxy-galaxy lensing which cross correlating the shear field ($\gamma$) with the positions of foreground galaxies
+include galaxy$-$galaxy lensing which cross correlating the shear field ($\gamma$) with the positions of foreground galaxies
 \citep{gglens-GAMA-Han2014,gglens-BossCFHTMore2015,gglens-DES1},
@@
 \citep{cosmicShearRealKids450,cosmicShear-DES1,cosmicShear_HSC1_Chiaki2019,cosmicShear_HSC1_Hamana2019}.
-Since shear is directly related to the matter distribution as shown in eq. (\ref{eq-intro-delta2shear}), Galaxy-galaxy lensing
+Since shear is directly related to the matter distribution as shown in eq. (\ref{eq-intro-delta2shear}), Galaxy$-$galaxy lensing
 probes into the correlation between the matter field and galaxy field, on the other hand, cosmic shear probes into the
@@
 \end{equation}
-where $\mathbf{\Phi}$ is the transformation operator from the parameters in the dictionary space to the density contrast
+where $\mathbf{\Phi}$ is the transformation operator from the projection parameters to the density contrast,
 and $x$ denotes the parameters. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field
@@
         The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines
-        are the bounds of bins. The galaxies are evenly distributed in each bins.} \label{fig-bestpz}
+        are the boundaries of the bins. The galaxies are equal-number binned.} \label{fig-bestpz}
 \end{figure}
@@
 \centering
-\subfigure[lasso]{\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-lasso.pdf}}
-\subfigure[adaptive lasso]{\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-alasso.pdf}}
+\subfigure[lasso]{\includezraphics{delta-3-7-pz-nn-lasso.pdf}}
+\subfigure[adaptive lasso]{\includezraphics{delta-3-7-pz-nn-alasso.pdf}}
 \caption{The result of density map reconstruction with standard lasso (left) and adaptive lasso (right). The input density
@@
 
-Figure \ref{fig-bestpz} shows the histogram of the best MLZ photo-$z$ estimation \cite{HSC1-photoz} for galaxies in tract
-9347 of HSC S16A data release \citep{HSC1-data}. These Galaxies are divided into ten source galaxy bins according to the
-photo-$z$ best estimation and the boundaries of the bins are shown as vertical dash lines in Figure \ref{fig-bestpz}.
-Figure \ref{fig-pdfpz} shows the average probability density function (PDF) in for galaxies in each redshift bin.
+Figure \ref{fig-bestpz} shows the histogram of the best Machine Learning and photo-Z \citep[MLZ]{MLZ-TPZ2013} photometric redshift estimation 
+from \cite{HSC1-photoz} for galaxies in the tract 9347 of the HSC S16A data release \citep{HSC1-data}. These Galaxies are divided 
+into ten source galaxy bins according to the photo-$z$ best estimation and the boundaries of the bins are shown as vertical dash 
+lines in Figure \ref{fig-bestpz}. Figure \ref{fig-pdfpz} shows the average probability density function (PDF) in for galaxies 
+in each redshift bin.
 
@@
  \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
- \caption{The Histogram of HSC-like shear measurement error (including errors from shape noise and photon noise) on the
-        first component of shear ($g_1$).}
+ \caption{The histograms of the HSC-like shear measurement error (including both from shape noise and from photon noise) 
+        on the first component of shear ($g_1$) for galaxies (blue lines) and smoothed pixels (orange lines). The solid
+        steps are the sampled histograms, and the dashed lines are the normalized gaussian distributions which have the
+        same standard deviations as the corresponding histograms.}
  \label{fig:mass-redshift}
@@
  \includegraphics[width=0.45\textwidth]{noise_std_map_pix.pdf}
- \caption{The standard deviation map of shear measurement error for the fifth source bin ($0.69 \leq z < 0.80 $).}
+ \caption{The standard deviation pixel map of the HSC-like shear measurement error for the fifth source galaxy bin 
+        ($0.69 \leq z < 0.80 $).}
 \end{figure}
@@
  \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
- \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
-NFW atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
+ \caption{The upper panels show the halo detection rate and the number of false peaks per square degree for mass map 
+ reconstruction with NFW atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
 \end{figure*}
@@
  \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
- \caption{The left panel shows the stacked distribution of deviations of detected peak positions
- from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane and the
- $y$-axis is for the deviation of the redshift. The peaks inside the dashed black box are regarded as true detections. The
- right panel focus on the deviation of detected peaks in the line of sight direction. The $x$-axis shows the input redshifts
- and the $y$-axis is the redshift of the detected peak. The cross symbols show the average redshift of detected peak for
- halos with different input redshift and mass and the error-bars are the scatter of the corresponding peak redshifts. All
- of the results in this figure are based on the NFW atoms.}
+ \caption{The left panel shows the stacked $2$-D distribution of the deviations of detected peak positions
+ from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane, and 
+ the $y$-axis is for the deviation of the redshift. For each simulatin, the peaks inside the dashed black box with the
+ minimal deviations (in unit of pixel) are defined as true detections. 
+ The right panel focuses on the deviation of detected peaks in the line of sight direction. The $x$-axis is the input 
+ halo redshifts, and the $y$-axis is the redshift of the detected peak. The `$\cross$' denotes the average redshift of 
+ detected peaks for each halo over different realizations, and the error-bars are the scatters of the corresponding peak 
+ redshifts. All of the results in this figure are based on the NFW dictionary with $\lambda=3.5$.}
 \end{figure*}
@@
 \STATE Estimate step size $\mu$ and $\mathbf{\Sigma}$
-\STATE \textbf{Initialization:} ‎
+\STATE \textbf{Initialization:}
 \STATE $x'^{(1)} = 0$
@@
     \ENDWHILE
-\STATE \textbf{Reinitialization:} ‎
+\STATE \textbf{Reinitialization:}
 \STATE $\hat{w}=\abs{\hat{x'}^{\rm{lasso}}}^{-2}$, $\lambda=\lambda_{\rm{als}}$
@@
  \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
- \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
-point mass atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
+ \caption{The upper panels show the halo detection rate and the number of false peak per square degree for mass map 
+ reconstruction with point mass atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
 \end{figure*}
@@
 stamp.
-For each galaxy, we randomly assign its redshift following the MLZ photo-$z$ probability distribution function
-\citep{HSC1-photoz} of the galaxy.
+For each galaxy, we randomly assign its redshift following the MLZ photo-$z$ probability distribution function from
+\citep{HSC1-photoz}.
 
@@
 \centering
-\subfigure[Point Mass: $\lambda=3.5$]{\includegraphics[width=0.45\textwidth]{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}}
-\subfigure[NFW: $\lambda=3.5$]{\includegraphics[width=0.45\textwidth]{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}}
-\subfigure[Point Mass: $\lambda=5.0$]{\includegraphics[width=0.45\textwidth]{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}}
-\subfigure[NFW: $\lambda=5.0$]{\includegraphics[width=0.45\textwidth]{delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}}
-\caption{The result of density map reconstruction with  Point Mass atoms (left) and  NFW atoms (right). The input density
+\subfigure[Point Mass: $\lambda=3.5$]{\includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}}
+\subfigure[NFW: $\lambda=3.5$]{\includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}}
+\subfigure[Point Mass: $\lambda=5.0$]{\includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}}
+\subfigure[NFW: $\lambda=5.0$]{\includezraphics{delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}}
+\caption{The results of density maps reconstruction with Point Mass atoms (left) and  NFW atoms (right) with 
+        $\lambda=3.5$ (upper) and $\lambda=5.0$ (lower). The input density
         map is from a NFW halo with mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$.

### 2020-10-29 doc/paper_ms_method_HSCY1/ms.tex
update the draft of paper

@@
 assumption that the density fields can be sparsely represented by the NFW basis atoms, the density fields are reconstructed 
-using an oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape noise and
-photo-$z$ uncertainty.
-Our findings are summarized as folllows: 1) The global minima solution of the standard lasso algorithm suffers from a
-smear of structure in the line of sight direction even in the absence of shape nosie.
-2) The global minima solution of addaptive lasso algorithm significantly removes the line of sight smear of structure.
+using an oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape estimation
+error and photo-$z$ uncertainty.
+Our findings are summarized as folllows: 
+1) The solution of the standard lasso algorithm suffers from a smear of structure 
+in the line of sight direction even in the absence of shape nosie, and the addaptive lasso algorithm significantly removes 
+the line of sight smear of structure. 
+2) The algorithm is able to detect halo with minimal mass limits of $10^{13.5} M_{\odot}/h$, $10^{14.3} M_{\odot}/h$, 
+$10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.9$) redshifts, respectively.
+3) The estimated redshift of the halos detected from the reconstructed mass maps are
+lower than the true redshfit by about $0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshfit bias is below 
+$0.5\%$ for halos at $0.4<z\leq 0.85$.
 \end{abstract}
@@
             and the lower row shows the basis atoms in Real space.
-            The leftmost column is point mass atom and the other columns are multi-scale NFW atoms.
+            The leftmost column is the point mass atom and the other columns are the multi-scale NFW atoms.
             The smoothing kernel is Gaussian with standard deviation of $1.5$ pixels.} \label{fig-atoms2D}
@@
 The expected shear measurements ($\gamma$) on distant galaxies are related to the
-foreground density contrast field ($\delta$) through a linear transformation
+foreground density contrast field ($\delta$) through a linear transformation:
 \begin{equation} \label{eq-intro-delta2shear}
@@
 In order to fully reconstruct the $3$-D mass density distribution ($\delta$) from the photometric shear observations ($\gamma$),
-the density contrast field is modeled as a summation of basis atoms in a model dictionary
+the density contrast field is modeled as a summation of basis atoms in a model dictionary:
 \begin{equation} \label{eq-intro-dict}
@@
 \end{equation}
-where $\mathbf{\Phi}$ is the transformation operator from the projection parameters to the density contrast,
+where $\mathbf{\Phi}$ is the transformation operator from the projection coefficient field to the density contrast,
 and $x$ denotes the parameters. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field
@@
 profile of a single halo follows the NFW function \citep{halo-NFW1997ApJ}.
-We construct a dictionary with multi-scale NFW atoms.  The atoms follow multi-scale surface density profiles of NFW
-functions \citep{haloModel-TJ2003-3pt} on the transverse plane. We follow \citet{LSS-massMap-Glimpse3D-Leonard2014}
+We construct a dictionary with the multi-scale NFW atoms.  The atoms follow multi-scale surface density profiles of the 
+NFW functions \citep{haloModel-TJ2003-3pt} on the transverse plane. We follow \citet{LSS-massMap-Glimpse3D-Leonard2014}
 to neglect the depth of halos since the resolution scale of the reconstruction in the line of sight direction is much
@@
  \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
- \caption{The source galaxies are binned into $10$ redshift bins according to their MLZ best photo-$z$ estimation.
-        The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines
-        are the boundaries of the bins. The galaxies are equal-number binned.} \label{fig-bestpz}
+ \caption{The source galaxies are binned into $10$ redshift bins according to their Machine Learning and photo-Z (MLZ) 
+        best photo-$z$ estimation. The blue histogram is the normalized number distribution of the best photo-$z$ estimation. 
+        The vertical dashed lines are the boundaries of the bins. The galaxies are equal-number binned.} \label{fig-bestpz}
 \end{figure}
@@
 \subfigure[adaptive lasso]{\includezraphics{delta-3-7-pz-nn-alasso.pdf}}
-\caption{The result of density map reconstruction with standard lasso (left) and adaptive lasso (right). The input density
+\caption{The results of density map reconstructions with standard lasso (left) and adaptive lasso (right). The input density
         map is from a NFW halo with mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso reconstruction
-        smear the density field along the line of sight direction (vertical direction in the plots). Noises on shear measurements
-        are neglected in this simulation.} \label{fig-lassoVsadaLasso}
+        smear the density field along the line of sight direction (vertical direction in the plots). The vertical direction
+        is the line of sight direction, and the lower boundaries and upper boundaries of the boxes are $0.01$ and $0.85$, 
+        respectively. Noises on galaxy shape measurements are neglected in this simulation.} \label{fig-lassoVsadaLasso}
 \end{figure*}
 
-The density contrast field is modeled as a summation of basis atoms in the dictionary
+The density contrast field is modeled as a summation of basis atoms in the dictionary:
 \begin{equation}\label{eq-x2delta}
@@
 
-We propose to use multi-scale NFW atoms, denoted as $\{\phi_1,...,\phi_N\}$, as our dictionary basi.
-On the transverse plane, the NFW atoms follow surface density profiles of NFW halos
+We propose to use the multi-scale NFW atoms, denoted as $\{\phi_1,...,\phi_N\}$, as the basis atoms of our dictionary .
+On the transverse plane, the NFW atoms follow surface density profiles of the NFW halos
 \citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and truncation radius $c \theta_\alpha$ ,
-where $c$ is the concentration of NFW halos.
+where $c$ is the concentration of the NFW halos.
 As the scales of halos are much less than the reachable redshift resolution, we neglect the depth of halo on the
-line of sight direction and set the profiles of NFW atoms in the line of sight direction to $1$-D Dirac delta
+line of sight direction and set the profiles of the NFW atoms in the line of sight direction to $1$-D Dirac delta
 functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}.
@@
 \end{equation}
-$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for NFW atoms in different scale frames.
+$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for the NFW atoms in different scale frames.
 
-To simplify the notation, we define the projection parameters as a column vector:
+To simplify the notation, we define the projection coefficients as a column vector:
 $x=\begin{pmatrix}
@@
 \end{equation}
-We substitute eq. (\ref{eq-x2delta}) into eq.(\ref{eq-delta2gammat})
+We substitute eq. (\ref{eq-x2delta}) into eq.(\ref{eq-delta2gammat}) and get
 \begin{equation}\label{eq-x2gammat}
@@
 \end{equation}
-With the definition of photo-$z$ smearing operator
+With the definition of photo-$z$ smearing operator:
 \begin{equation}
@@
  \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
- \caption{The histograms of the HSC-like shear measurement error (including both from shape noise and from photon noise) 
+ \caption{The histograms of the HSC-like shape measurement error (including both from shape noise and from photon noise) 
         on the first component of shear ($g_1$) for galaxies (blue lines) and smoothed pixels (orange lines). The solid
@@
         same standard deviations as the corresponding histograms.}
- \label{fig:mass-redshift}
+ \label{fig-noiseHistogram}
 \end{figure}
@@
 
-The smoothing is conducted by convolving the shear measurements with a smoothing kernel
+The smoothing is conducted by convolving the shear measurements with a smoothing kernel:
 \begin{equation}
@@
 $W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line of sight component
-$W_\times(z)$
+$W_\times(z)$ as
 \begin{equation}
@@
 \end{equation}
+In this paper, we set $\beta=1.\arcmin5$.
 
@@
  \includegraphics[width=0.45\textwidth]{noise_std_map_pix.pdf}
- \caption{The standard deviation pixel map of the HSC-like shear measurement error for the fifth source galaxy bin 
-        ($0.69 \leq z < 0.80 $).}
+ \caption{The standard deviation pixel map of the HSC-like shape measurement error for the fifth source galaxy bin 
+        ($0.69 \leq z < 0.80 $).
+        } \label{fig-noistdmap}
 \end{figure}
@@
  \centering
- \includegraphics[width=0.95\textwidth]{detfalseRate_f3-1.pdf}
- \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
- \caption{The upper panels show the halo detection rate and the number of false peaks per square degree for mass map 
- reconstruction with NFW atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
+ \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
+ \caption{The left panel shows the stacked $2$-D distribution of the deviations of detected peak positions
+ from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane, and 
+ the $y$-axis is for the deviation of the redshift. For each box, the positive peaks inside the dashed black box with 
+ the minimal offset from the input halo (in unit of pixel) is taken as a true detection. 
+ The right panel focuses on the deviation of detected peaks in the line of sight direction. The $x$-axis is the input 
+ halo redshifts, and the $y$-axis is the redshift of the detected peak. The `$\cross$' denotes the average redshift of 
+ detected peaks for each halo over different noise realizations, and the error-bars are the uncertainties of the average
+ redshifts. The deep gray area is for the relative redshfit bias less than $0.05$, and the light gray area is for the 
+ relative redshift bias less than $0.5$. These results in this figure are based on the NFW dictionary with $\lambda=3.5$.
+ } \label{fig-detoffsets}
 \end{figure*}
@@
 We define the masking window function according to the smoothed number density (defined in eq. (\ref{eq-numDesSmooth})) of
-the galaxies as follows
+the galaxies:
 \begin{equation}
@@
  \centering
- \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
- \caption{The left panel shows the stacked $2$-D distribution of the deviations of detected peak positions
- from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane, and 
- the $y$-axis is for the deviation of the redshift. For each simulatin, the peaks inside the dashed black box with the
- minimal deviations (in unit of pixel) are defined as true detections. 
- The right panel focuses on the deviation of detected peaks in the line of sight direction. The $x$-axis is the input 
- halo redshifts, and the $y$-axis is the redshift of the detected peak. The `$\cross$' denotes the average redshift of 
- detected peaks for each halo over different realizations, and the error-bars are the scatters of the corresponding peak 
- redshifts. All of the results in this figure are based on the NFW dictionary with $\lambda=3.5$.}
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f3-1.pdf}
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
+ \caption{The upper panels show the halo detection rate and the number of false peaks per square degree for mass map 
+        reconstructed with the NFW atoms. The penalization parameter is set to $\lambda=3.5$ for the upper panels. 
+        The low panels show the results for $\lambda=5.0$. 
+        } \label{fig-detFalsRateNFW}
 \end{figure*}
@@
 We pixelize the smoothed shear field into a $N_\theta \times N_\theta \times N_s$ grid, where $N_\theta$
-is the number of pixels of two orthogonal axes of the transverse plane and $N_s$ is the number of pixels of the
-line of sight axis. $\gamma_{\alpha}$ is used to denote the value recorded on pixel with index $\alpha$, where $\alpha=
-1...N_\theta \times N_\theta \times N_s$. The grids on the transverse plans are equally spaced, therefore fast Fourier
-transform (FFT) can be used to boost the speed of linear operation on the transverse plan, whereas the grids in the
-line of sight direction follow equal number binning as shown in Figure \ref{fig-bestpz}.
+is the number of pixels for the two orthogonal axes of the transverse plane and $N_s$ is the number of pixels for the
+line of sight axis. $\gamma_{\alpha}$ denotes the smoothed shear measurements recorded on the pixel with index $\alpha$, 
+where $\alpha=1...N_\theta \times N_\theta \times N_s$. The grids on the transverse plans are equally spaced with a pixel
+size of $1\arcmin$.
+Fast Fourier transform (FFT) can be used to boost the speed of linear operation on the transverse plan, whereas the grids 
+in the line of sight direction follow equal number binning as shown in Figure \ref{fig-bestpz}.
 
-Similarly, we pixelize each scale frame of the parameter $x$ into a $N_\theta \times N_\theta \times N_l$ grid.
-The pixelization of the parameter field $x$ on the transverse plan for each scale frame is exactly the same as the
-pixelization of the smoothed shear field on the transverse plane. Whereas the parameter field is pixelized into equal
-spaced grids in the line of sight direction. Here, we use $N_l$ to denote the number of the lens planes and $x_{\beta}$ to
-denote the element of the parameter with index $\beta$, where $\beta=1...N_\theta \times N_\theta \times N_l \times N$.
-The corresponding pixelized elements of the forward transform matrix $\mathbf{A}$ is denoted as $A_{\alpha\beta}$.
+Similarly, we pixelize each scale frame of the projection coefficient field $x$ into a $N_\theta \times N_\theta \times N_l$ 
+grid. The pixelization on the transverse plan for each scale frame is exactly the same as that of the smoothed shear field 
+on the transverse plane. Whereas the projection coefficient field is pixelized into equal spaced grids in the line of sight 
+direction ranging from redshfit $0.01$ to redshift $0.85$. Here, we use $N_l$ to denote the number of the lens planes and 
+$x_{\beta}$ to denote the element of the projection parameter with index $\beta$, where 
+$\beta=1...N_\theta \times N_\theta \times N_l \times N$. The corresponding pixelized elements of the forward transform 
+matrix $\mathbf{A}$ is denoted as $A_{\alpha\beta}$.
 
@@
 the column
-vectors of the transform matrix through the following rescaling
+vectors of the transform matrix through a rescaling:
 \begin{equation}
@@
 
-The lasso algorithm uses $l^1$ norm of parameters as the regularization term and the estimator is defined as
+The standard lasso algorithm uses the $l^1$ norm of the projection coefficient field as the regularization and the estimator is 
+defined as
 \begin{equation}
@@
 the selected parameters. However, it has been shown by
-\citet{AdaLASSO-Zou2006} that when the column vectors of the projection matrix $\mathbf{A'}$ are highly correlated,
+\citet{AdaLASSO-Zou2006} that when the column vectors of the transforming matrix $\mathbf{A'}$ are highly correlated,
 lasso cannot select the relevant parameters from the parameter space consistently. Moreover, the estimated parameters
 are biased due to the shrinkage process in the lasso regression. We note that, for the density map reconstruction problem,
-the effective basis vectors are highly correlated since, as shown in Figure \ref{fig-corlensKer}, the lensing kernels for
+the column vectors are highly correlated because, as shown in Figure \ref{fig-corlensKer}, the lensing kernels for
 lenses at different redshifts are highly correlated. Therefore, the lasso algorithm cannot select the consistent mass in
@@
 Figure \ref{fig-lassoVsadaLasso} shows the reconstructions of the mass map of a single halo with halo mass equals
-$M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The noises on shear measurements are not included. The left panel of
-Figure \ref{fig-lassoVsadaLasso} is the reconstruction with lasso algorithm which shows a significant smear along the line of sight.
+$M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The noises on shear measurements are not included in the simulation. 
+The left panel of Figure \ref{fig-lassoVsadaLasso} is the reconstruction with lasso algorithm which shows a significant smear 
+along the line of sight.
 
-\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different parameters
-in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. In the first step, lasso is used to estimate the
-parameters and the preliminary lasso estimation is denoted as $\hat{x'}^{\rm{lasso}}$. In the second step, the preliminary
-lasso estimation is used to weight the penalization. The weight on penalty is defined as
+\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different projection 
+coefficients in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. In the first step, lasso is used to 
+estimate the parameters and the preliminary estimated outcome of lasso is denoted as $\hat{x'}^{\rm{lasso}}$. In the second 
+step, the preliminary lasso estimation is used to weight the penalization. The weight on penalty is defined as
 \begin{equation}
@@
 
-The loss function can be rewritten with Einstein notation
+The loss function can be rewritten with the Einstein notation:
 \begin{equation}
@@
  \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
- \caption{The histograms of detected peak values for all of the halo and error realizations. The dotted lines with different
- colors are for the results of reconstruction with NFW atoms dictionary penalized with different regularization parameter
- $\lambda$.}
+ \caption{The histograms of detected peak values from all of the simulations. The solid lines with different colors 
+        are the results of reconstructions with the NFW dictionary penalized with different regularization parameter:
+        $\lambda=3.5,4.0,5.0$. The dashed lines are the results of reconstructions from pure noise fields.
+        }\label{fig-peakHist}
 \end{figure}
 
-In this work, we apply the Fast Iterative Soft Thresholding Alorithm (FISTA) of \citet{FISTA-Beck2009} to solve
-the adaptive lasso estimator.
+In this work, we apply the Fast Iterative Soft Thresholding Alorithm (FISTA) of \citet{FISTA-Beck2009} to find the global minia
+of the adaptive lasso loss function.
 
-The parameters are initialized as $x_i^{(1)}=0$. According to the FISTA algorithm, we iteratively
-update the elements of the parameter vector ($x$). In the n'th iteration, a temporary update is first calcualted as
+The coefficients are initialized as $x_i^{(1)}=0$. According to the FISTA algorithm, we iteratively update the elements of the 
+projection coefficient field ($x$). In the $n$'th iteration, a temporary update is first calcualted as
 \begin{equation}
@@
 $\mu$ is the step size of the gradient descent iteration.
-$\partial_i G(x'^{(n)})$ refers to the i'th element of the gradient
-vector of $G$ at point $x'^{(n)}$
+$\partial_i G(x'^{(n)})$ refers to the $i$'th element of the gradient
+vector of $G$ at point $x'^{(n)}$:
 \begin{equation}
@@
 $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$. The spectral norm is estimated by simulating a large number of
-random vectors with $l^2$ norms equal one with different realizations. Then, the matrix operator
-$\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is applied to each random vector and get a corresponding transformed
-random vector. The spectral norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$
-is the maximum $l^2$ norm of the transformed vectors.
+random vectors with $l^2$ norms equal one with different realizations. The matrix operator 
+$\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is subsequently applied to each random vector and get a corresponding 
+transformed vector. The spectral norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is the maximum $l^2$ 
+norm of the transformed vectors.
 
@@
 
-\begin{figure*}[!ht]
+\begin{figure*}[!t]
 \centering
- \includegraphics[width=0.95\textwidth]{detfalseRate_f1-1.pdf}
- \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
- \caption{The upper panels show the halo detection rate and the number of false peak per square degree for mass map 
- reconstruction with point mass atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
+\subfigure[NFW: $\lambda=3.5$]{\includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}}
+\subfigure[Point Mass: $\lambda=3.5$]{\includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}}
+\subfigure[NFW: $\lambda=5.0$]{\includezraphics{delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}}
+\subfigure[Point Mass: $\lambda=5.0$]{\includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}}
+\caption{The results of density maps reconstruction with the point mass dictionary (left) and the NFW dictionary (right) 
+        with $\lambda=3.5$ (upper) and $\lambda=5.0$ (lower). The input density map is from a NFW halo with mass 
+        $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The vertical direction is the line of sight 
+        direction, and the lower boundaries and upper boundaries of the boxes are $0.01$ and $0.85$, respectively.
+        } \label{fig-NFWvsPM}
 \end{figure*}
@@
 In this section, we simulate weak-lensing shear fields induced by a group of halos with various halo masses
-and redshifts. The shear distortion fields are applied to HSC mock catalogs with different realizations of HSC-like shape
-noises and photo-$z$ uncertainties (Section \ref{subsec:Sims}).
+and redshifts. The shear fields are used to distort the HSC mock shape catalogs with different realizations of the 
+HSC-like shape measurement error and photo-$z$ uncertainty (Section \ref{subsec:Sims}).
 
-Then, we test our algorithm on the simulations with two different setups of the algorithm. The first setup uses dictionary
-constructed with NFW atoms (Section \ref{subsec:test-nfw}) and the second setup uses dictionary constructed with point mass
-atoms (Section \ref{subsec:test-pm}).
+Then, we test our algorithm on the simulations with different setups of the regularization parameter. We also compare the 
+results of our algorithm which uses the NFW dictionary (Section \ref{subsec:test-nfw}) with the results from the setup using
+the point mass dictionary (Section \ref{subsec:test-pm}).
 
@@
 
-We sample halos in two dimensional redshift-mass plane. The redshift-mass plane is evenly divided into eight redshift bins
-and eight mass bins. The input redshifts and masses are shifted by random values for each halo from the centers
-of the bins.
-The concentration of the NFW halo is a function of the halo's mass and redshift according to
+We sample halos in a two dimensional redshift-mass plane. The redshift-mass plane is evenly divided into eight redshift bins
+and eight mass bins. The input redshifts and masses are shifted by random values for each halo from the centers of the bins.
+The concentration of the NFW halo is set to as a function of the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
 \citet{c-M_Magneticum-Ragagnin2019}
@@
 The weak-lensing shear fields of these NFW halos are simulated according to \citet{haloModel-TJ2003-3pt}. The shear
-distortions are applied to galaxy catalogs with HSC-like shape noise and photo-$z$ uncertainty.
+distortions are applied to one hundred realizations of galaxy catalogs with the HSC-like shape measurement error and photo-$z$ 
+uncertainty.
 
@@
 We uses galaxies in a one square degree region at the center of tract 9347 \citep{HSC1-data}.
-By randomly rotating the galaxies in the shape catalog, we simulate HSC-like shear estimation errors
-with different realizations.
-The positions of the galaxies are randomized so that the galaxies homogeneously distributed in a one square degree
-stamp.
+The positions of the galaxies are randomized so that the galaxies statistically have a homogeneous distribution in a one square 
+degree stamp.
 For each galaxy, we randomly assign its redshift following the MLZ photo-$z$ probability distribution function from
+By randomly rotating the galaxies in the shape catalog, we simulate the HSC-like shape estimation error with different realizations.
+The histogram of the first component of the HSC-like shape estimation error on galaxy
+level is shown in Figure \ref{fig-noiseHistogram}. 
+The corresponding histogram after the procedure of smoothing and pixelization is also shown in \ref{fig-noiseHistogram}, 
+and the standard deviation map of the noise is demonstrated in Figure \ref{fig-noistdmap}.
 \citep{HSC1-photoz}.
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[!ht]
  \centering
-\subfigure[Point Mass: $\lambda=3.5$]{\includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}}
-\subfigure[NFW: $\lambda=3.5$]{\includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}}
-\subfigure[Point Mass: $\lambda=5.0$]{\includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}}
-\subfigure[NFW: $\lambda=5.0$]{\includezraphics{delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}}
-\caption{The results of density maps reconstruction with Point Mass atoms (left) and  NFW atoms (right) with 
-        $\lambda=3.5$ (upper) and $\lambda=5.0$ (lower). The input density
-        map is from a NFW halo with mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$.
-        } \label{fig-lassoVsadaLasso}
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f1-1.pdf}
+ \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
+ \caption{The upper panels show the halo detection rate and the number of false peak per square degree for mass map 
+        reconstructed with the point mass dictionary. The penalization paramter is set to $\lambda=3.5$ for the upper panels. 
+        The lower panels show the results for $\lambda=5.0$. 
+        }\label{fig-detFalsRatePM}
 \end{figure*}
 
-In this subsection, we test the performance of our algorithm with the default setup which model the matter density
-field with multi-scale NFW atoms. The dictionary space is constructed with NFW atom with NFW scale radius set to
-three different comoving distances which are 0.12 Mpc/h, 0.24 Mpc/h, 0.36 Mpc/h. The truncation radius is set to
-four times of the scale radius.
-We test the algorithm with different regularization parameters for the preliminary lasso set to $3.5$ and $5.0$. The
-regularization parameter for the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\gamma+1}$.
+In this subsection, we test the performance of our algorithm with the default setup which models the matter density
+field with multi-scale NFW atoms. The dictionary is constructed with NFW atom with three frames of different scale radius. 
+The NFW scale radius is set to comoving distances of $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc, respectively. 
+The truncation radius (concentration) is set to four times of the scale radius for the atoms in the dictionary. We test the 
+algorithm with different regularization parameters for the preliminary lasso ranging from $3.5$ to $5.0$. The regularization 
+parameter for the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\gamma+1}$.
+
+In this paper, we do not go beyound the resolution limit defined by the Gaussian smoothing kernel with scale radius equals 
+$1.\arcmin 5$ and the pixel scale equals $1\arcmin$. Therefore, we also smooth the reconstruced density with the same 
+Gaussian kernel in each lens redshift plane.
+
+After the reconstruction of each density field, we detect the peaks on the density map. The stacked $2$-D histogram from all of
+the simulated boxes for the offsets of the detected peak positions from the input halo is demonstrated in the left panel of 
+Figure \ref{fig-detoffsets}. For each simulation, we find the positive peak closest to the input position (in unit of pixel), and
+if the cloest peak lay inside the region denoted with dashed lines in the left panel of Figure \ref{fig-detoffsets}, we take it
+as a true detection of the input halo. Whereas, other detected peaks, which includes both positive and negative peaks, are taken as 
+false peak detections. The right panel of Figure \ref{fig-detoffsets} shows the average redshift of true detections for each halo.
+The estimated redshift are lower than the true redshfit by about $0.03$ for halos at low redshifts ($z\leq 0.4$). For halos at 
+$0.4<z\leq 0.85$, the relative redshfit bias is below $0.5\%$.
+
+Figure \ref{fig-detFalsRateNFW} shows the detection rate (left panels) and the number of false peaks per square degree (right panel) 
+for each simulated halo. The figure include results of different penalization parameters: $\lambda=3.5$ (upper panel) 
+and $\lambda=5.0$ (lower panel).
+We find that with the increase of the penalization parameter, the detection rate decreases. On the other hand, the number of false 
+peaks also decreases.
+Figure \ref{fig-peakHist} shows the histograms, which is normalized by the number of simulations, for all of the detected peaks 
+with different penalization parameters. We also plot the corresponding histograms for peaks detected from pure noise fields for 
+comparison. From the left panels of Figure \ref{fig-NFWvsPM}, which show the $3$-D density maps reconstructed with different 
+penalization parameters for a halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$ , we also find that the number 
+of false detections significantly decreases as the penalization parameter increases.
 
@@
 \label{subsec:test-pm}
-In this subsection, we test the performance of our algorithm with another setup which model the matter density
-field with point mass atoms.
-The dictionary space is constructed with point mass atoms in each lens redshift plane.
-We also test the algorithm with regularization parameter for the preliminary lasso is set to $3.5$ and $5.0$. The
-regularization parameter for the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.
 
+In this subsection, we show the results for the setup which subsitutes the default NFW dictionary with the point mass dictionary, 
+as a comparison with the default setup.
+The regularization parameter for the preliminary lasso is set to $3.5$ and $5.0$. 
 Inspired by \citet{structureAdaLasso-Pramanik2020}, which propose to incorporate external group information into
-different penalization weights for the regression coefficients by setting the penalization weights for adaptive lasso
-for model coefficients in the same group to the same value, we use a smoothed weight for adaptive lasso. The preliminary
-lasso estimation is smoothed with a top-hat filter of comoving scale 0.25 Mpc/h, which is denoted as
+different adaptive lasso penalization weights by setting the penalization weights for projection coefficients in 
+the same group to the average of the adaptive weights in the same group, we smooth the preliminary lasso estimation 
+in each lens redshfit bins with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc, which is denoted as 
 $\hat{x}^{\rm{ls}}_{\rm{sm}}$ and the penalization weights are set to $1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\gamma$. 
+The regularization parameter for the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.
+
+As we have done on the reconstructions from NFW dictionary, we smooth the reconstruced density maps with the Gaussian 
+kernel (scale radius equals $1.\arcmin 5$) in each lens redshift plane.
+
+Figure \ref{fig-detFalsRatePM} shows the detection rate (left panels) and the number of false peaks per square degree (right panel) 
+for each simulated halo. The figure include results of different penalization parameters: $\lambda=3.5$ (upper panel) 
+and $\lambda=5.0$ (lower panel). The right panels of Figure \ref{fig-NFWvsPM} show the $3$-D density maps reconstructed with 
+different penalization parameters for a halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. Comparing with
+the results for the NFW dictionary, we find that the number of false peaks for the point mass dictionary is much larger than that 
+of the NFW dictionary. As demonstrated in the right panels of Figure \ref{fig-NFWvsPM}, the reconstructions with the point 
+mass dictionary tend to assign masses to different redshfits in the neighboring region of the halo center. Since the profies
+of NFW atoms are consistent with the input halo profiles, the reconstruced structures from the NFW dictionary are sparser than
+those from the point mass dictionary.
 
@@
 
-We develope a novel method to reconstruct $3$-D density contrast maps from photometric weak-lensing shear measurements.
-Our method models $3$-D density contrast maps as a summation of NFW atoms with multiple comoving radius and point mass atoms
-in the $3$-D space binned with photometric redshift. The NFW atoms are used to model the mass in isolated halos and the
-point mass atoms are used to model the structures close to the resolution limit of the reconstruction.
+We develope a novel method to reconstruct $3$-D density contrast maps from weak-lensing shear measurements and photometric
+redshift estimations.
+Our method models $3$-D density contrast maps as a summation of NFW atoms with multiple comoving radius. 
+With the prior assumption that the basis atoms sparsely distributes in the $3$-D space, the density field is reconstructed
+using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}.
 
-With the prior assumption that the basis atoms sparsely distributes in the $3$-D space, the density field is reconstructed
-using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006} which has the oracle properties.
-
-The method is tested with realistic simulations using HSC-like shape noise and photo-$z$ uncertainties.
+The method is tested with realistic simulations using HSC-like shape estimation error and photo-$z$ uncertainty. The results
+are summarized as follows:
+\begin{enumerate}
+ \item The solution of the standard lasso algorithm suffers from a smear of structure in the line of sight direction even in 
+    the absence of shape nosie, and the addaptive lasso algorithm significantly removes the line of sight smear of structure. 
+ \item The algorithm is able to detect halo with minimal mass limits of $10^{13.5} M_{\odot}/h$, $10^{14.3} M_{\odot}/h$, 
+    $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.9$) redshifts, respectively.
+ \item The estimated redshift of the halos detected from the reconstructed mass maps are lower than the true redshfit by about 
+    $0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshfit bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$. 
+\end{enumerate}
 
@@
 
-\appendix
 \end{document}
-
-\subsection{Pathwise Coordinate Descent Algorithm}
-\label{subsec:method-pathwise}
-\begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{lensing_efficiency.pdf}
- \caption{The blue line shows the normalized lensing efficiency for lens bin at $z_{l}=0.51$.
- The orange line is the normalized lensing efficiency while taking into account the photo-$z$ uncertainty.
- The green data points show the averaged $\kappa$ field for different redshift bins in the simulation.}
-\end{figure}
-
-The loss function can be separated into a summation of a quadratic term and a $l^1$ term as
-\begin{equation}
- L(x)=G(x)+\lambda\sigma_{\beta}\norm{x_{\beta}}_1.
-\end{equation}
-The quadratic term is defined as
-\begin{equation}
-\begin{split}
- G(x)&=\frac{1}{2}(\gamma_{\alpha}-A^{*}_{\alpha\beta}x_{\beta})(\gamma_{\alpha}-A_{\alpha\mu}x_{\mu})\\
-&+\frac{\tau}{2}[(D^{1}_{\alpha\beta} x_{\beta})(D^{1}_{\alpha\mu}x_{\mu})
-+ (D^{2}_{\alpha\beta} x_{\beta})(D^{2}_{\alpha\mu}x_{\mu})],
-\end{split}
-\end{equation}
-
-Many algorithms have been proposed to find the minima of this kind of loss function. We base our method on the
-coordinate descent algorithm \citep{coordinateDescent-Wright2015} which is described as follows.
-Firstly, we initialize the projector as $x^{(1)}=0$. According to the coordinate descent algorithm, we subsequently
-update the projector ($x$) along the direction of one specific coordinate ($i$) as
-\begin{equation}
-x^{(n+1)}_{i}=\mathrm{ST}_{\lambda\sigma_{i}} (x^{(n)}_{i} -\frac{\partial_i G(x^{(n)})}{A_{\alpha i}A_{\alpha i}+4\tau}),
-\end{equation}
-where $\mathrm{ST}$ is the soft thresholding function defined as
-\begin{equation}
-\mathrm{ST}_{\lambda} (x) = \mathrm{sign} (x) \max (\abs{x}-\lambda,0),
-\end{equation}
-and the projector along the other coordinates are kept the same. The minima is finally approached by iteratively updating
-along each coordinate for multiple times.
-
-To simplify the notation, here we define the projector difference for the $n$-th iteration as
-\begin{equation}
- \Delta x ^{(n)} = -\frac{\bigtriangledown G(x^{(n)})}{A_{\alpha i}A_{\alpha i}+4\tau},
-\end{equation}
-where $\bigtriangledown G(x^{(n)})$ refers to the gradient of quadratic function $G$ at $x^{(n)}$. The signal to noise ratio
-(SNR) of the projector difference is defined as $s^{(n)}=\Delta x ^{(n)}/\sigma$.
-
-In our algorithm, the coordinate descent algorithm in conducted in a pathwise manner \citep{pathwise-Friedman2007}.
-We begin with a regulation parameter
-($\lambda^{(1)}$) which is slightly smaller than the maximum coordinate of $s^{(1)}$ (denoted as $s_{\rm{max}}^{(1)}$) so that
-in the first iteration, we only update on the coordinate with the maximum SNR. Then, we find the maximum projector difference
-SNR of the second iteration ($s_{\rm{max}}^{(2)}$) and update the regulation parameter to $\lambda^{(2)}$, where $\lambda^{(2)}$
-is slightly smaller than $s_{\rm{max}}^{(2)}$.
-
-%$\mathrm{TSV}(x)$ refers to the total square variance of the first dictionary frame, which is defined as
-%\begin{equation}
-%\begin{split}
-%\mathrm{TSV}(x) =\int d^2 \theta dz (\frac{\partial x}{\partial \theta_1})^2+\int d^2 \theta dz (\frac{\partial x}{\partial \theta_2})^2.
-%\end{split}
-%\end{equation}
-%The total square variance can be expressed in a quadratic form as
-%\begin{equation}
-%\mathrm{TSV}(x)=\norm{\frac{\partial x}{\partial \theta_1}}^2_2+\norm{\frac{\partial x}{\partial \theta_2}}^2_2.
-%\end{equation}

### 2020-11-27 doc/paper_ms_method_HSCY1/ms.tex
correct typo in the ms.tex

@@
 \begin{abstract}
-A new method is developed to reconstruct $3$-D density contrast maps from photometric weak-lensing shear measurements.
-The $3$-D density contrast maps are modeled as a summation of the NFW basis atoms which have $2$-D multi-scale NFW surface
-density profiles on the transverse plane and $1$-D Dirac delta functions in the line of sight direction. With the prior
-assumption that the density fields can be sparsely represented by the NFW basis atoms, the density fields are reconstructed 
-using an oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape estimation
-error and photo-$z$ uncertainty.
-Our findings are summarized as folllows: 
-1) The solution of the standard lasso algorithm suffers from a smear of structure 
-in the line of sight direction even in the absence of shape nosie, and the addaptive lasso algorithm significantly removes 
-the line of sight smear of structure. 
-2) The algorithm is able to detect halo with minimal mass limits of $10^{13.5} M_{\odot}/h$, $10^{14.3} M_{\odot}/h$, 
-$10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.9$) redshifts, respectively.
-3) The estimated redshift of the halos detected from the reconstructed mass maps are
-lower than the true redshfit by about $0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshfit bias is below 
-$0.5\%$ for halos at $0.4<z\leq 0.85$.
+A new method is developed to reconstruct $3$-D density contrast maps from
+photometric weak-lensing shear measurements. The $3$-D density contrast maps
+are modeled as a summation of the NFW basis atoms, which have $2$-D multi-scale
+NFW surface density profiles on the transverse plane and $1$-D Dirac delta
+functions in the line of sight direction. With the prior assumption that the
+density fields have a sparse spatial distribution, the density fields are
+reconstructed using an oracle algorithm: adaptive lasso. Our method is tested
+with realistic simulations using the HSC-like shape estimation error and
+photo-$z$ uncertainty.  Our findings are summarized as follows: 1) The lasso
+solution suffers from a smear of structure in the line of sight direction even
+in the absence of shape noise. The adaptive lasso algorithm significantly
+removes the line of sight smear of structure.  2) The algorithm is able to
+detect halo with minimal mass limits of $10^{13.5} M_{\odot}/h$, $10^{14.3}
+M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq
+z< 0.6$) and high ($0.6\leq z< 0.9$) redshifts, respectively.  3) The estimated
+redshift of the halos detected from the reconstructed mass maps are lower than
+the true redshift by about $0.03$ for halos at low redshifts ($z\leq 0.4$). The
+relative redshift bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$.
 \end{abstract}
@@
 
-\begin{figure*}[!t]
-    \includegraphics[width=1.\textwidth]{nfwlet-atom-2D.pdf}
-    \caption{The smoothed pixelized basis atoms. The upper row shows the basis atoms in Fourier space
-            and the lower row shows the basis atoms in Real space.
-            The leftmost column is the point mass atom and the other columns are the multi-scale NFW atoms.
-            The smoothing kernel is Gaussian with standard deviation of $1.5$ pixels.} \label{fig-atoms2D}
+\begin{figure*}[!t] \includegraphics[width=1.\textwidth]{nfwlet-atom-2D.pdf}
+    \caption{The smoothed pixelized basis atoms. The upper row shows the basis
+        atoms in Fourier space, and the lower row shows the basis atoms in Real
+        space.  The leftmost column is the point mass atom, and the other
+        columns are the multi-scale NFW atoms.  The smoothing kernel is
+        Gaussian with a standard deviation of $1.5$ pixels.
+        } \label{fig-atoms2D}
 \end{figure*}
@@
 
-Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line of sight
-due to the influence of gravity. As a result of the light distortion, the shapes of the background galaxies are coherently
-distorted. Such effect, which is known as weak-lensing, imprints the information of foreground mass density distribution
-to the background galaxy images and offers a direct probe into the mass density distribution in our universe
-\citep[see][for recent reviews]{revKilbinger15,revRachel17}.
+Light from distant galaxies is distorted by the intervening inhomogeneous
+density distribution along the line of sight due to the gravity's influence.
+As a result of the light distortion, the shapes of the background galaxies are
+coherently distorted. Such effect, which is known as weak-lensing, imprints the
+information of foreground mass density distribution to the background galaxy
+images and offers a direct probe into the mass density distribution in our
+universe \citep[see][for recent reviews]{revKilbinger15,revRachel17}.
 
-The expected shear measurements ($\gamma$) on distant galaxies are related to the
-foreground density contrast field ($\delta$) through a linear transformation:
-\begin{equation} \label{eq-intro-delta2shear}
- \gamma=\mathbf{T} \delta,
-\end{equation}
-where $\mathbf{T}$ is used to denote the linear transformation operator which includes not only physical lensing effect
-but also systematic effects from observations (e.g. pixelization and smoothing of shear field in
-transverse plane, photo-$z$ uncertainty).
+The expected shear measurements ($\gamma$) on distant galaxies are related to
+the foreground density contrast field ($\delta$) through a linear
+transformation: \begin{equation} \label{eq-intro-delta2shear} \gamma=\mathbf{T}
+\delta, \end{equation} where $\mathbf{T}$ is used to denote the linear
+transformation operator, which includes not only physical lensing effect but
+also systematic effects from observations (e.g., pixelization and smoothing of
+the shear field in the transverse plane, photo-$z$ uncertainty).
 
-Several large scale surveys target to study the weak-lensing effect at high precision level (e.g. HSC \citep{HSC1-data}, KIDS
-\citep{KIDS13}, DES \citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, WFIRST \citep{WFIRST15}).
+Several large-scale surveys target to study the weak-lensing effect at high
+precision level (e.g., HSC \citep{HSC1-data}, KIDS \citep{KIDS13}, DES
+\citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, WFIRST
+\citep{WFIRST15}).
 
-The primary goal of most weak-lensing surveys is to constrain the cosmology model through $2$-point correlations. The studies
-include galaxy$-$galaxy lensing which cross correlating the shear field ($\gamma$) with the positions of foreground galaxies
-\citep{gglens-GAMA-Han2014,gglens-BossCFHTMore2015,gglens-DES1},
-and cosmic shear which auto-correlates the shear measurements
+The primary goal of most weak-lensing surveys is to constrain the cosmology
+model through $2$-point correlations. The studies include galaxy$-$galaxy
+lensing, which cross-correlating the shear field ($\gamma$) with the positions
+of foreground galaxies
+\citep{gglens-GAMA-Han2014,gglens-BossCFHTMore2015,gglens-DES1}, and cosmic
+shear which auto-correlates the shear measurements
 \citep{cosmicShearRealKids450,cosmicShear-DES1,cosmicShear_HSC1_Chiaki2019,cosmicShear_HSC1_Hamana2019}.
-Since shear is directly related to the matter distribution as shown in eq. (\ref{eq-intro-delta2shear}), Galaxy$-$galaxy lensing
-probes into the correlation between the matter field and galaxy field, on the other hand, cosmic shear probes into the
-auto-correlation of matter field.
+Since the shear is directly related to the foreground matter distribution as
+shown in eq.  (\ref{eq-intro-delta2shear}), Galaxy$-$galaxy lensing probes into
+the correlation between the matter field and galaxy field. On the other hand,
+cosmic shear probes into the auto-correlation of matter field.
 
@@
 within the community \citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
-and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However, the
+and applied to large-scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However, the
 reconstruction of $3$-D mass map is still a challenging task.
 
-In order to fully reconstruct the $3$-D mass density distribution ($\delta$) from the photometric shear observations ($\gamma$),
-the density contrast field is modeled as a summation of basis atoms in a model dictionary:
+To fully reconstruct the $3$-D mass density distribution ($\delta$) from the
+photometric shear observations ($\gamma$), the density contrast field is
+modeled as a summation of basis atoms in a model dictionary:
 \begin{equation} \label{eq-intro-dict}
@@
 \end{equation}
-where $\mathbf{\Phi}$ is the transformation operator from the projection coefficient field to the density contrast,
-and $x$ denotes the parameters. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field
-in Fourier space, which is equivalent to model the mass field with sinusoidial functions. On the other hand,
-\citet{LSS-massMap-Glimpse3D-Leonard2014} models the mass field with Starlets \citep{Starlet-Starck2015}.
+where $\mathbf{\Phi}$ is the transformation operator from the projection
+coefficient field to the density contrast, and $x$ denotes the parameters.
+\citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field in Fourier
+space, which is equivalent to model the mass field with sinusoidal functions.
+On the other hand, \citet{LSS-massMap-Glimpse3D-Leonard2014} models the mass
+field with Starlets \citep{Starlet-Starck2015}.
 
-The projection coefficients are estimated through optimizing a regularized loss function. The estimator is
-generally defined as
+The projection coefficients are estimated by optimizing a regularized loss
+function. The estimator is generally defined as
 \begin{equation}
@@
 \end{equation}
-where $\norm{\Sigma^{-\frac{1}{2}}(\gamma - \mathbf{T\Phi} x)}_2^2$ is the $l^2$ chi-square term\footnote{weighted by
-the inverse of the diagonal covariance matrix of error on the shear measurements ($\Sigma$).} measuring
-the residuals between the prediction and the data, while $C(x)$ is the regularization term measuring the deviation of
-the estimation of the parameter ($x$) from the prior assumptions. The $l^p$ norm is defined as
+where $\norm{\Sigma^{-\frac{1}{2}}(\gamma - \mathbf{T\Phi} x)}_2^2$ is the
+$l^2$ chi-square term\footnote{weighted by the inverse of the diagonal
+covariance matrix of the error on the shear measurements ($\Sigma$).} measuring
+the residuals between the prediction and the data, while $C(x)$ is the
+regularization term measuring the deviation of the estimation of the parameter
+($x$) from the prior assumptions. The $l^p$ norm is defined as
 \begin{equation}
@@
 \end{equation}
-Such estimation prefers the parameters that are able to describe the observations and also align with the prior assumptions.
-The regularization parameter $\lambda$ adjusts the relative weight between the observations and prior assumptions in the
-optimization process.
+Such estimation prefers the parameters that are able to describe the
+observations and align with the prior assumptions.  The regularization
+parameter $\lambda$ adjusts the relative weight between the observations and
+prior assumptions in the optimization process.
 
-\citet{LSS-massMap-Wiener-Simon2009} propose to use the Wiener filter, which is also known as $l^2$ ridge regulation
-($C=\norm{x}^2_2$), to find a regularized solution in Fourier space. \citet{HSC1-massMaps} apply the method of
-\citet{LSS-massMap-Wiener-Simon2009} to the first-year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}.
-However, the density maps reconstructed by this method suffer from a smearing along the line of sight direction with
-a standard deviation of $\sigma_z=0.2 \sim 0.3$.
+\citet{LSS-massMap-Wiener-Simon2009} propose to use the Wiener filter, which is
+also known as $l^2$ ridge regulation ($C=\norm{x}^2_2$), to find a regularized
+solution in Fourier space. \citet{HSC1-massMaps} apply the method of
+\citet{LSS-massMap-Wiener-Simon2009} to the first-year data of the Hyper
+Suprime-Cam Survey \citep{HSC1-data}.  However, the density maps reconstructed
+by this method suffer from smearing along the line of sight direction with a
+standard deviation of $\sigma_z=0.2 \sim 0.3$.
 
-\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version of $l^1$ lasso regulation ($C=\norm{x}^1_1$)
-to find a sparse solution in the Starlets dictionary space \citep{Starlet-Starck2015}. \citet{LSS-massMap-Glimpse3D-Leonard2014}
-apply a greedy coordinate descent algorithm, which selects the steepest coordinate in each iteration, to find the minima
-of a non-convex loss function penalized with the firm thresholding function. \citet{LSS-massMap-Glimpse3D-Leonard2014}
-significantly reduce the smearing along the line of sight, however, the stability of the non-convex optimization and
-greedy coordinate descent algorithm has not been fully justified. Moreover, the Starlets functions are not designed to
-model the profile of clumpy mass in the universe.
+\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version
+of $l^1$ lasso regulation ($C=\norm{x}^1_1$) to find a sparse solution in the
+Starlets dictionary space \citep{Starlet-Starck2015}.
+\citet{LSS-massMap-Glimpse3D-Leonard2014} apply a greedy coordinate descent
+algorithm, which selects the steepest coordinate in each iteration, to find the
+minima of a non-convex loss function penalized with the firm thresholding
+function. \citet{LSS-massMap-Glimpse3D-Leonard2014} significantly reduce the
+smearing along the line of sight. However, the stability of the non-convex
+optimization and greedy coordinate descent algorithm has not been fully
+justified. Moreover, the Starlets functions are not designed to model the
+profile of clumpy mass in the universe.
 
-$N$-body simulations have shown that the dark matter is distributed in halos connected by filaments, and the density
-profile of a single halo follows the NFW function \citep{halo-NFW1997ApJ}.
-We construct a dictionary with the multi-scale NFW atoms.  The atoms follow multi-scale surface density profiles of the 
-NFW functions \citep{haloModel-TJ2003-3pt} on the transverse plane. We follow \citet{LSS-massMap-Glimpse3D-Leonard2014}
-to neglect the depth of halos since the resolution scale of the reconstruction in the line of sight direction is much
-larger than the scales of halos. Therefore, we set the profile of the NFW atoms in the line of sight as the Dirac delta
-function. The multi-scale NFW atoms are used to model the profiles of halos which is assumed to be sparsely distributed
-in the universe. With the sparsity prior, the adaptive lasso regularization \citep{AdaLASSO-Zou2006} is used to reconstruct
-the density field. We find that, in contrast to the standard lasso estimator which smears the structure along the line of sight,
-the addaptive lasso is able to significantly reduce the smearing effect.
+$N$-body simulations have shown that the dark matter is distributed in halos
+connected by filaments, and the density profile of a single halo follows the
+NFW function \citep{halo-NFW1997ApJ}.  We construct a model dictionary with the
+multi-scale NFW atoms.  The atoms follow multi-scale surface density profiles
+of the NFW functions \citep{haloModel-TJ2003-3pt} on the transverse plane.
+Following \citet{LSS-massMap-Glimpse3D-Leonard2014}, we neglect the depth of
+halos since the resolution scale of the reconstruction in the line of sight
+direction is much larger than the halo scale. Therefore, we set the NFW atoms'
+profile in the line of sight direction as the Dirac delta function.  Moreover,
+we assume that the halos are sparsely distributed in the universe.  With the
+sparsity prior, the adaptive lasso regularization \citep{AdaLASSO-Zou2006} is
+used to reconstruct the density field.  In contrast to the lasso
+estimator that smears the structure along the line of sight, the adaptive lasso
+can significantly reduce the smearing effect.
 
-Comparing with \citet{LSS-massMap-Glimpse3D-Leonard2014}, our dictionary is built up to describe the clumpy mass
-in the universe which has a clear physical motivation. Furthermore, the adaptive lasso algorithm is strictly convex and
-can be directly optimized with the FISTA algorithm \citep{FISTA-Beck2009} without relying on any greedy coordinate
-descent approaches. The stability of this convex optimization has been well studied.
+Compared with \citet{LSS-massMap-Glimpse3D-Leonard2014}, our dictionary is
+built up to describe the clumpy mass in the universe with a clear physical
+motivation. Furthermore, the adaptive lasso algorithm is strictly convex and
+can be directly optimized with the FISTA algorithm \citep{FISTA-Beck2009}
+without relying on any greedy coordinate descent approaches. The stability of
+this convex optimization has been well studied.
 
 This paper is organized as follows.
-In Section \ref{sec:Method}, we propose the new method for $3$-D density map reconstruction.
+In Section \ref{sec:Method}, we propose the new method for $3$-D density map
+reconstruction.
 In Section \ref{sec:Test}, we test the novel algorithm on HSC-like simulations.
-In Section \ref{sec:Sum}, we summarize and discuss the future development of the method.
+In Section \ref{sec:Sum}, we summarize and discuss the future development of
+the method.
 
@@
  \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
- \caption{The source galaxies are binned into $10$ redshift bins according to their Machine Learning and photo-Z (MLZ) 
-        best photo-$z$ estimation. The blue histogram is the normalized number distribution of the best photo-$z$ estimation. 
-        The vertical dashed lines are the boundaries of the bins. The galaxies are equal-number binned.} \label{fig-bestpz}
+ \caption{The source galaxies are binned into $10$ redshift bins according to
+         their Machine Learning and photo-Z (MLZ) best photo-$z$ estimation. The
+         blue histogram is the normalized number distribution of the best photo-$z$
+         estimation. The vertical dashed lines are the boundaries of the redshift bins.
+         The galaxies are equal-number binned.
+        } \label{fig-bestpz}
 \end{figure}
@@
 We first review the lensing process in section \ref{subsec:method-delta2shear}.
-Then, we introduce the dictionary used to model the foreground density maps in section \ref{subsec:method-dictionary}.
+Then, we introduce the dictionary used to model the foreground density maps in
+section \ref{subsec:method-dictionary}.
 
-Subsequently, in section \ref{subsec:method-Systematics}, we discuss several systematic effects from observations which
-include photo-$z$ uncertainty (section \ref{subsec:method-photoz}),
-smoothing (section \ref{subsec:method-smoothing}),
-masking(section \ref{subsec:method-msknoise}),
+Subsequently, in section \ref{subsec:method-Systematics}, we discuss several
+systematic effects from observations which include photo-$z$ uncertainty
+(section \ref{subsec:method-photoz}), smoothing (section
+\ref{subsec:method-smoothing}), masking(section \ref{subsec:method-msknoise}),
 and pixelization (section \ref{subsec:method-pixel}).
 
-Finally, we solve the mass reconstruction problem in section \ref{subsec:method-reconstruction} using the adaptive lasso
-algorithm \citep{AdaLASSO-Zou2006} optimized with the FISTA alogrithm \citep{FISTA-Beck2009}.
+Finally, we solve the mass reconstruction problem in section
+\ref{subsec:method-reconstruction} using the adaptive lasso algorithm
+\citep{AdaLASSO-Zou2006} optimized with the FISTA algorithm
+\citep{FISTA-Beck2009}.
 
@@
  \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
- \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.}\label{fig-pdfpz}
+ \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.
+        }\label{fig-pdfpz}
 \end{figure}
 
-The lensing convergence map at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
-density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line of sight is
+The lensing convergence map at the comoving distance $\chi_s$ caused by the
+foreground inhomogeneous density distribution at the comoving distance $\chi_l$
+($\chi_l< \chi_s$) along the line of sight is
 \begin{equation}
@@
 where $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
-at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the matter density parameter, $c$ is the speed
-of light, and $a(\chi_l)$ is the scale parameter at the lens position.
+at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the
+matter density parameter, $c$ is the speed of light, and $a(\chi_l)$ is the
+scale parameter at the lens position.
 
-Substitute comoving distance ($\chi$) with redshift ($z$), we have
+After substituting comoving distance ($\chi$) with redshift ($z$), we have
 \begin{equation}\label{eq-delta2kappa}
@@
  \includegraphics[width=1.\textwidth]{lensing_kernel.pdf}
- \caption{The left panel shows the lensing kernels for five different lens redshifts. The dashed lines are the
-        kernels for spectroscopic redshift which assumes that the redshifts of source galaxies are precisely
-        estimated. The solid lines are for photometric redshifts which accounts for the influence of photometric
-        redshift uncertainty. The other two panels show the correlation between lensing kernels of different
-        lens redshifts. The middle panel is for spectroscopic redshift and the right panel is for photometric
-        redshifts. The lensing kernels are normalized so that the diagonal elements of the correlation matrices
-        equal one.}\label{fig-corlensKer}
+ \caption{The left panel shows the lensing kernels for five different lens
+         redshifts. The dashed lines are the kernels for spectroscopic redshift,
+         which assumes that the source galaxies' redshifts are precisely
+         estimated. The solid lines are for photometric redshifts, which
+         accounts for the influence of photometric redshift uncertainty. The
+         other two panels show the correlation between lensing kernels of
+         different lens redshifts. The middle panel is for spectroscopic
+         redshift, and the right panel is for photometric redshifts. The
+         lensing kernels are normalized so that the diagonal elements of the
+         correlation matrices equal one.
+        }\label{fig-corlensKer}
 \end{figure*}
 
-As shown in \citet{massMap-KS1993}, the shear field is related to the kappa field at the same redshift plane
-via
+As shown in \citet{massMap-KS1993}, the shear field is related to the kappa
+field at the same redshift plane via
 \begin{equation}\label{eq-kappa2gamma}
@@
 \end{equation}
-Here we denote the physical shear distortion field as $\gamma_L$ and we note that the final observed shear measurements
-are also physical shear distortions influenced by systematic errors from observatins. The systematic errors will be discussed
-in Section \ref{subsec:method-Systematics}.
+Here we denote the physical shear distortion field as $\gamma_L$ and we note
+that the final observed shear measurements are also physical shear distortions
+influenced by systematic errors from observatins. The systematic errors will be
+discussed in Section \ref{subsec:method-Systematics}.
 
-Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}), the expectation of lensing shear signal is
+Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}),
+the expectation of lensing shear signal is
 \begin{equation}\label{eq-delta2gammat}
@@
 \subfigure[adaptive lasso]{\includezraphics{delta-3-7-pz-nn-alasso.pdf}}
-\caption{The results of density map reconstructions with standard lasso (left) and adaptive lasso (right). The input density
-        map is from a NFW halo with mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso reconstruction
-        smear the density field along the line of sight direction (vertical direction in the plots). The vertical direction
-        is the line of sight direction, and the lower boundaries and upper boundaries of the boxes are $0.01$ and $0.85$, 
-        respectively. Noises on galaxy shape measurements are neglected in this simulation.} \label{fig-lassoVsadaLasso}
+\caption{The density map reconstructions with the lasso (left) and the adaptive
+        lasso (right) algorithms. The input density map is from a NFW halo with
+        mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso
+        reconstruction smears the density field along the line of sight
+        direction (vertical direction in the plots).  The vertical direction is
+        the line of sight direction, and the lower boundaries and upper
+        boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively. Noises
+        on galaxy shape measurements are neglected in this simulation.
+        } \label{fig-lassoVsadaLasso}
 \end{figure*}
 
-The density contrast field is modeled as a summation of basis atoms in the dictionary:
+The density contrast field is modeled as a summation of basis atoms in the
+dictionary:
 \begin{equation}\label{eq-x2delta}
@@
 \end{equation}
-where $\phi_s(\vec{r})$ are the basis atoms of the dictionary. The basis atoms have `$N$' different scale frames and the atoms
-in each scale frame are shifted by $\vec{r'}$ to form basis at different positions. $x_s(\vec{r'})$ is the projection
-coefficients of the density contrast field onto the basis atoms.
+where $\phi_s(\vec{r})$ are the basis atoms of the dictionary. The basis atoms
+have `$N$' different scale frames, and the atoms in each scale frame are
+shifted by $\vec{r'}$ to form models at different spatial positions.
+$x_s(\vec{r'})$ is the projection coefficients of the density contrast field
+onto the basis atoms.
 
-We propose to use the multi-scale NFW atoms, denoted as $\{\phi_1,...,\phi_N\}$, as the basis atoms of our dictionary .
-On the transverse plane, the NFW atoms follow surface density profiles of the NFW halos
-\citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and truncation radius $c \theta_\alpha$ ,
-where $c$ is the concentration of the NFW halos.
-As the scales of halos are much less than the reachable redshift resolution, we neglect the depth of halo on the
-line of sight direction and set the profiles of the NFW atoms in the line of sight direction to $1$-D Dirac delta
-functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}.
-The multi-scale NFW atoms are defined as
+We propose to use the multi-scale NFW atoms, denoted as
+$\{\phi_1,...,\phi_N\}$, as the basis atoms of our dictionary.  On the
+transverse plane, the NFW atoms follow surface density profiles of the NFW
+halos \citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and
+truncation radius $c \theta_\alpha$ , where $c$ is the concentration of the NFW
+halos.  As the scales of halos are much smaller than the reachable redshift
+resolution, we neglect the depth of halo on the line of sight direction and set
+the NFW atoms' profiles in the line of sight direction to $1$-D Dirac delta
+functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. The
+multi-scale NFW atoms are defined as
 \begin{equation}
 \begin{split}
-\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 } F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
+\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 }
+F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
 &  (s=1..N)
@@
 \begin{cases}
--\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccosh \left(\frac{x^2+c}{x(1+c)}\right)}{(1-x^2)^{3/2}}  & (x<1),\\
+-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccosh
+\left(\frac{x^2+c}{x(1+c)}\right)}{(1-x^2)^{3/2}}  & (x<1),\\
 \frac{\sqrt{c^2-1}}{3(1+c)} (1+\frac{1}{c+1}) & (x=1),\\
--\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccos\left(\frac{x^2+c}{x(1+c)}\right)}{(x^2-1)^{3/2}} & (1<x\leq c),\\
+-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} +
+\frac{\arccos\left(\frac{x^2+c}{x(1+c)}\right)}{(x^2-1)^{3/2}} & (1<x\leq c),\\
 0& (x>c).
@@
 \end{equation}
-$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for the NFW atoms in different scale frames.
+$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for the NFW atoms in
+different scale frames.
 
-To simplify the notation, we define the projection coefficients as a column vector:
+To simplify the notation, we compress the projection coefficients into a column
+vector:
 $x=\begin{pmatrix}
@@
 \end{pmatrix}$,
-and the dictionary transform operator as a row vector:
+and compress the dictionary transform operator to a row vector:
 \begin{equation}
@@
 
-In this paper, dictionary constructed with point mass atoms is used to compare with the dictionary of multi-scale atoms.
-The point mass atoms is a $3$-D Dirac function defined as follows
+In this paper, a dictionary constructed with point mass atoms is used to
+compare with the dictionary of multi-scale atoms.  The point mass atoms is a
+$3$-D Dirac function defined as follows
 \begin{equation}
@@
 
-The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the transverse plane are shown in Figure
-\ref{fig-atoms2D}. The $1$-D slices of the profiles are demonstrated in Fiugre \ref{fig-atoms1D}. Note that these profiles
-are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The smoothing operation is discussed in
-Section \ref{subsec:method-smoothing} and the pixelization operation is discussed in Section \ref{subsec:method-pixel}.
+The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the
+transverse plane are shown in Figure \ref{fig-atoms2D}. The $1$-D slices of the
+profiles are demonstrated in Figure \ref{fig-atoms1D}. Note that these profiles
+are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The
+smoothing operation is discussed in Section \ref{subsec:method-smoothing}, and
+the pixelization operation is discussed in Section \ref{subsec:method-pixel}.
 
@@
 
-The observed shear measurements are deviated from the physical shear prediction due to the systematic
-errors from observations. The influence of systematics is carefully studied and incorporated into the forward
-modeling in this section.
+The observed shear measurements are deviated from the physical shear prediction
+due to the systematic errors from observations. The influence of systematics is
+carefully studied and incorporated into the forward modeling in this section.
 
@@
 
-The photometric redshifts of source galaxies in the current large scale survey are estimated with a limited number of
-board photometric bands (e.g. $9$ bands for KIDS$+$VIKING survey \citep{KIDS_VIKING-Hildebrant2020}, $5$ bands for DES
-survey and HSC survey). As a result, the estimated redshifts of galaxies suffer from much larger uncertainties, compared
-with redshifts estimated with spectroscopic observations. Such photo-$z$ uncertainty smears the lensing kernels statistically
-since a galaxy with a best fit photo-$z$ estimation of $z_s$ has possibilities of being actually located at different
-redshifts ($z$). The probability function for the photo-$z$ uncertainty is denoted as $P(z|z_s)$ and the expected shear
-distortion on the galaxy is
+The photometric redshifts of source galaxies in the current large-scale survey
+are estimated with a limited number of board photometric bands (e.g., $9$ bands
+for KIDS$+$VIKING survey \citep{KIDS_VIKING-Hildebrant2020}, $5$ bands for DES
+survey and HSC survey). As a result, the estimated redshifts of galaxies suffer
+from much larger uncertainties than redshifts estimated with spectroscopic
+observations. Such photo-$z$ uncertainty smears the lensing kernels
+statistically since a galaxy with a best fit photo-$z$ estimation of $z_s$ has
+possibilities of being actually located at different redshifts ($z$).  The
+probability function for the photo-$z$ uncertainty is denoted as $P(z|z_s)$,
+and the expected shear distortion on the galaxy is
 \begin{equation}\label{eq-delta2gamma-poz}
@@
 \end{equation}
-where we use $\rightarrow$ to denote the changes of shear by the systematic operator.
+where we use $\rightarrow$ to denote the changes of shear by the systematic
+operator.
 
-Figure \ref{fig-bestpz} shows the histogram of the best Machine Learning and photo-Z \citep[MLZ]{MLZ-TPZ2013} photometric redshift estimation 
-from \cite{HSC1-photoz} for galaxies in the tract 9347 of the HSC S16A data release \citep{HSC1-data}. These Galaxies are divided 
-into ten source galaxy bins according to the photo-$z$ best estimation and the boundaries of the bins are shown as vertical dash 
-lines in Figure \ref{fig-bestpz}. Figure \ref{fig-pdfpz} shows the average probability density function (PDF) in for galaxies 
-in each redshift bin.
+Figure \ref{fig-bestpz} shows the histogram of the best Machine Learning and
+photo-Z \citep[MLZ]{MLZ-TPZ2013} photometric redshift estimation from
+\cite{HSC1-photoz} for galaxies in the tract 9347 of the HSC S16A data release
+\citep{HSC1-data}. These Galaxies are divided into ten source galaxy bins
+according to the photo-$z$ best estimation, and the boundaries of the bins are
+shown as vertical dashed lines in Figure \ref{fig-bestpz}. Figure \ref{fig-pdfpz}
+shows the average probability density function (PDF) for galaxies in each
+redshift bin.
 
-The left panel of Figure \ref{fig-corlensKer} shows the lensing kernels for lenses at five different redshifts as functions
-of source galaxy redshfit bins. The dashed lines are the lensing kernel for spectroscopic redshfits with neglectable redshift
-uncertainty. The solid lines are the lensing kernel for photometric redshifts with redshift uncertainties shown in Figure
-\ref{fig-pdfpz}.
-As shown by the dashed lines in the left panel of Figure \ref{fig-corlensKer}, the lensing kernels converge to zero for source
-redshifts lower than the lens redshift, if the uncertainties on the source galaxy redshift estimations are neglectable. However,
-as demonstrated by the solid lines in the same panel, for the source redshifts with large photo-$z$ uncertainties, the lensing
-kernels do not converge to zero at redshifts lower than the lens redshift. This is because the galaxies with photo-$z$ estimations
-lower than the lens redshifts may be actually located at higher redshifts due to the photo-$z$ uncertainties.
+The left panel of Figure \ref{fig-corlensKer} shows the lensing kernels for
+lenses at five different redshifts as functions of source galaxy redshift bins.
+The dashed lines are the lensing kernel for spectroscopic redshifts with
+neglectable redshift uncertainty. The solid lines are the lensing kernel for
+photometric redshifts with redshift uncertainties shown in Figure
+\ref{fig-pdfpz}.  As shown by the dashed lines in the left panel of Figure
+\ref{fig-corlensKer}, the lensing kernels converge to zero for source redshifts
+lower than the lens redshift if the uncertainties on the source galaxy
+redshift estimations are neglectable. However, as demonstrated by the solid
+lines in the same panel, for the source redshifts with large photo-$z$
+uncertainties, the lensing kernels do not converge to zero at redshifts lower
+than the lens redshift. This is because the galaxies with photo-$z$ estimations
+lower than the lens redshifts may be actually located at higher redshifts due
+to the photo-$z$ uncertainties.
 
-The middle and right panels show the correlation between lensing kernels for lenses at different redshifts. The middle panel is for
-spect-$z$ and the right panel is for photo-$z$.
-As demonstrated in the middle panel, the lensing kernels are highly correlated even though the redshfit estimation is precise.
-Comparing the correlation matrices shown in the middle panel and the right panel of Figure \ref{fig-corlensKer}, we conclude
-that the photo-$z$ uncertainties further increase the correlations between lensing kernels at different lens plane.
+The middle and right panels show the correlation between lensing kernels for
+lenses at different redshifts. The middle panel is for spect-$z$, and the right
+panel is for photo-$z$.  As demonstrated in the middle panel, the lensing
+kernels are highly correlated even though the redshift estimation is precise.
+Comparing the correlation matrices shown in the middle panel and the right
+panel of Figure \ref{fig-corlensKer}, we conclude that the photo-$z$
+uncertainties further increase the correlations between lensing kernels at
+different lens plane.
 
@@
  \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
- \caption{The histograms of the HSC-like shape measurement error (including both from shape noise and from photon noise) 
-        on the first component of shear ($g_1$) for galaxies (blue lines) and smoothed pixels (orange lines). The solid
-        steps are the sampled histograms, and the dashed lines are the normalized gaussian distributions which have the
-        same standard deviations as the corresponding histograms.}
+ \caption{The histograms of the HSC-like shape measurement error (including
+         both from shape noise and from photon noise) on the first component of
+         shear ($g_1$) for galaxies (blue lines) and smoothed pixels (orange
+         lines). The solid steps are the sampled histograms, and the dashed
+         lines are the normalized Gaussian distributions that have the same
+         standard deviations as the corresponding histograms.
+        }
  \label{fig-noiseHistogram}
@@
 
-The observed galaxies have random irregular (unequally-spaced) spacial distribution. In order boost the computational
-speed, we smooth the shear measurements from galaxy shapes and pixelize the smoothed measurements onto regular grids.
-After the pixelization, the fast Fourier transform (FFT) can be directly conducted on the transverse plane in each
-source redshift bin.
+The observed galaxies have random irregular (unequally-spaced) spatial
+distribution. To boost the computational speed, we smooth the shear
+measurements from galaxy shapes and pixelize the smoothed measurements onto
+regular grids.  After the pixelization, the fast Fourier transform (FFT) can be
+directly conducted on the transverse plane in each source redshift bin.
 
-The smoothing is conducted by convolving the shear measurements with a smoothing kernel:
+The smoothing is conducted by convolving the shear measurements with a
+smoothing kernel:
 \begin{equation}
-\gamma_{\rm{sm}} (\vec{\theta})  = \frac{\sum_i  W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) \gamma_i}{\sum_i W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) },
+\gamma_{\rm{sm}} (\vec{\theta})  = \frac{\sum_i
+W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) \gamma_i}{\sum_i
+W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) },
 \end{equation}
-where $W(\vec{\theta},z)$ is a $3$-D smoothing kernel. $\gamma_i$, $z_i$ and $\theta_i$ are the shear,
-photometric reshift, and transverse position of the `$i$-th' galaxy in the catalog.
+where $W(\vec{\theta},z)$ is a $3$-D smoothing kernel. $\gamma_i$, $z_i$ and
+$\theta_i$ are the shear, photometric reshift, and transverse position of the
+`$i$-th' galaxy in the catalog.
 
-$W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line of sight component
+$W(\vec{\theta},z)$ can be decomposed into a transverse component
+$W_T(\vec{\theta})$ and a line of sight component
 $W_\times(z)$ as
@@
 \end{equation}
-In this paper, we use an isotropic $2$-D Gaussian kernel and a $1$-D top-hat kernel to smooth the measurements in the
-transverse plane and the line of sight direction, the smoothing kernel is
+In this paper, we use an isotropic $2$-D Gaussian kernel and a $1$-D top-hat
+kernel to smooth the measurements in the transverse plane and the line of sight
+direction. These components of the smoothing kernel are
 \begin{equation}
@@
 
-With the approximation that the density of galaxy number ($n(\vec{r})$) varies slowly on the smoothing scale,
-as $\int d^3r W(\vec{r})=1$, the smoothed galaxy number density which is defined as
+Since the smoothing kernel is normalized by definition:
+\begin{equation}
+\int d^3r W(\vec{r})=1,
+\end{equation}
+with the approximation that the density of galaxy number - $n(\vec{r})$ -
+varies slowly at the smoothing scale, the
+smoothed galaxy number density:
 \begin{equation}\label{eq-numDesSmooth}
@@
 equals the galaxy number density: $n_{\rm{sm}}(\vec{r})=n(\vec{r})$.
-We note that the galaxy number density experience a steep drop on the boundary of the survey, therefore the
-smoothed galaxy number density does not equal the galaxy number density close the the boundary of the survey.
+We note that the galaxy number density experience a steep drop on the boundary
+of the survey, therefore the smoothed galaxy number density does not equal the
+galaxy number density close to the boundary of the survey.
 
@@
 
-As we will discussed in Section \ref{subsec:method-pixel}, the smoothed shear field is pixelized into equally spaced
-grids. We note that another widely used scheme is to directly average the shear measurements located in each pixel.
-Such scheme is equivalent to an equal-space sampling of the shear field smoothed with a $3$-D top-hat kernel with the
-same scale as the pixels.
+As we will discuss in Section \ref{subsec:method-pixel}, the smoothed shear
+field is pixelized into equally spaced grids. We note that another widely used
+scheme is to average the shear measurements in each pixel.  Such a scenario is
+equivalent to resampling the shear field smoothed with a $3$-D top-hat kernel
+with the same scale as the pixels.
 
@@
  \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
- \caption{The left panel shows the stacked $2$-D distribution of the deviations of detected peak positions
- from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane, and 
- the $y$-axis is for the deviation of the redshift. For each box, the positive peaks inside the dashed black box with 
- the minimal offset from the input halo (in unit of pixel) is taken as a true detection. 
- The right panel focuses on the deviation of detected peaks in the line of sight direction. The $x$-axis is the input 
- halo redshifts, and the $y$-axis is the redshift of the detected peak. The `$\cross$' denotes the average redshift of 
- detected peaks for each halo over different noise realizations, and the error-bars are the uncertainties of the average
- redshifts. The deep gray area is for the relative redshfit bias less than $0.05$, and the light gray area is for the 
- relative redshift bias less than $0.5$. These results in this figure are based on the NFW dictionary with $\lambda=3.5$.
+ \caption{The left panel shows the stacked $2$-D distribution of the deviations
+     of detected peak positions from the centers of the corresponding input
+     halos. The $x$-axis is for the deviated distance in the transverse plane,
+     and the $y$-axis is for the deviation of the redshift. For each
+     simulation, the positive peak inside the dashed black box with the
+     minimal offset (in the pixel unit) from the input halo's position is
+     taken as a true detection. The right panel focuses on the deviation of
+     detected peaks in the line of sight direction. The $x$-axis is the input
+     halo redshifts, and the $y$-axis is the redshift of the detected peak. The
+     `$\cross$' denotes the average redshift of detected peaks for each halo
+     over different noise realizations, and the error-bars are the
+     uncertainties of the average redshifts. The deep gray area is for the
+     relative redshift bias less than $0.05$, and the light gray area is for
+     the relative redshift bias less than $0.5$. These results in this figure
+     are based on the NFW dictionary with $\lambda=3.5$.
      } \label{fig-detoffsets}
@@
 
-In real observations, shear measurements are available in a finite region of the sky and the boundary of the region is
-always irregular. Moreover, there are also many isolated sub-regions near the bright stars are masked out since the light
-from bright stars tends to influence the shear measurements on neighboring galaxies.
+In real observations, shear measurements are available in a finite region of
+the sky, and the boundary of the region is always irregular. Moreover, many
+isolated sub-regions near the bright stars are masked out since the light from
+bright stars tends to influence the shear measurements on neighboring galaxies.
 
-We define the masking window function according to the smoothed number density (defined in eq. (\ref{eq-numDesSmooth})) of
-the galaxies:
+We define the masking window function according to the smoothed number density
+(defined in eq. (\ref{eq-numDesSmooth})) of the galaxies:
 \begin{equation}
@@
 \end{equation}
-where $\delta_D(\vec{r})$ is $3$-D Dirac delta function. The shear is influenced by the masking through
+where $\delta_D(\vec{r})$ is $3$-D Dirac delta function. The shear is
+influenced by the masking by
 $\gamma_L \rightarrow \mathbf{M} \gamma_L$.
 
-The final observed shear field, taking into account all of the aforementioned systematics from observations,
-is
+The final observed shear field, taking into account all of the systematics as
+mentioned above from observations, is
 \begin{equation}\label{eq-x2gamma-final}
@@
 \end{equation}
-For simplicity, we denote $\mathbf{A}=\mathbf{M} \mathbf{W} \mathbf{P} \mathbf{Q} \mathbf{\Phi} $ and
+For simplicity, we denote $\mathbf{A}=\mathbf{M} \mathbf{W} \mathbf{P}
+\mathbf{Q} \mathbf{\Phi} $ and
 eq. (\ref{eq-x2gamma-final}) is written as
@@
  \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
- \caption{The upper panels show the halo detection rate and the number of false peaks per square degree for mass map 
-        reconstructed with the NFW atoms. The penalization parameter is set to $\lambda=3.5$ for the upper panels. 
-        The low panels show the results for $\lambda=5.0$. 
+ \caption{The upper panels show the halo detection rate and the number of false
+     peaks per square degree for mass map reconstructed with the NFW atoms. The
+     penalization parameter is set to $\lambda=3.5$ for the upper panels.  The
+     low panels show the results for $\lambda=5.0$.
         } \label{fig-detFalsRateNFW}
@@
 
-We pixelize the smoothed shear field into a $N_\theta \times N_\theta \times N_s$ grid, where $N_\theta$
-is the number of pixels for the two orthogonal axes of the transverse plane and $N_s$ is the number of pixels for the
-line of sight axis. $\gamma_{\alpha}$ denotes the smoothed shear measurements recorded on the pixel with index $\alpha$, 
-where $\alpha=1...N_\theta \times N_\theta \times N_s$. The grids on the transverse plans are equally spaced with a pixel
-size of $1\arcmin$.
-Fast Fourier transform (FFT) can be used to boost the speed of linear operation on the transverse plan, whereas the grids 
-in the line of sight direction follow equal number binning as shown in Figure \ref{fig-bestpz}.
+We pixelize the smoothed shear field into an $N_\theta \times N_\theta \times
+N_s$ grid, where $N_\theta$ is the number of pixels for the two orthogonal axes
+of the transverse plane and $N_s$ is the number of pixels for the line of sight
+axis. $\gamma_{\alpha}$ denotes the smoothed shear measurements recorded on the
+pixel with index $\alpha$, where $\alpha=1...N_\theta \times N_\theta \times
+N_s$. The grids on the transverse planes are equally spaced with a pixel size of
+$1\arcmin$.  Fast Fourier transform (FFT) can be used to boost the speed of
+linear operation on the transverse plane, whereas the grids in the line of sight
+direction follow equal number binning as shown in Figure \ref{fig-bestpz}.
 
-Similarly, we pixelize each scale frame of the projection coefficient field $x$ into a $N_\theta \times N_\theta \times N_l$ 
-grid. The pixelization on the transverse plan for each scale frame is exactly the same as that of the smoothed shear field 
-on the transverse plane. Whereas the projection coefficient field is pixelized into equal spaced grids in the line of sight 
-direction ranging from redshfit $0.01$ to redshift $0.85$. Here, we use $N_l$ to denote the number of the lens planes and 
-$x_{\beta}$ to denote the element of the projection parameter with index $\beta$, where 
-$\beta=1...N_\theta \times N_\theta \times N_l \times N$. The corresponding pixelized elements of the forward transform 
-matrix $\mathbf{A}$ is denoted as $A_{\alpha\beta}$.
+Similarly, we pixelize each scale frame of the projection coefficient field $x$
+into an $N_\theta \times N_\theta \times N_l$ grid. The pixelization on the
+transverse plane for each scale frame is the same as that of the
+smoothed shear field on the transverse plane. At the same time, the projection
+coefficient field is pixelized into equal spaced grids in the line of sight
+direction ranging from redshift $0.01$ to redshift $0.85$. Here, we use $N_l$
+to denote the number of the lens planes and $x_{\beta}$ to denote the
+projection parameter indexed as $\beta$, where $\beta=1...N_\theta \times
+N_\theta \times N_l \times N$. The corresponding pixelized elements of the
+forward transform matrix $\mathbf{A}$ is denoted as $A_{\alpha\beta}$.
 
-We term the column vectors of the forward transform matrix $\mathbf{A}$ as the effective basis atoms. We note that the
-effective basis atoms have different $l^2$ norm. The $l^2$ norm of the $i'th$ column vectors of the effective basis atoms are
-$\mathcal{N}_{i}=\sum_\alpha A_{i\alpha}A_{i\alpha}$. Before solving the density map reconstruction problem, we normalize
-the column
-vectors of the transform matrix through a rescaling:
+We term the column vectors of the forward transform matrix $\mathbf{A}$ as the
+effective basis atoms. We note that the effective basis atoms have different
+$l^2$ norm. The $l^2$ norm of the $i'th$ column vectors of the effective basis
+atoms are $\mathcal{N}_{i}=\sum_\alpha A_{i\alpha}A_{i\alpha}$. Before solving
+the density map reconstruction problem, we normalize the column vectors of the
+transform matrix through a rescaling:
 \begin{equation}
@@
 
-The standard lasso algorithm uses the $l^1$ norm of the projection coefficient field as the regularization and the estimator is 
-defined as
+The lasso algorithm uses $l^1$ norm of the projection coefficient field as to
+regularize the modeling, and the estimator is defined as
 \begin{equation}
@@
 \end{equation}
-where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and $l^2$ norm, respectively.
-$\lambda_{ls}$ denotes the penalization parameter for the lasso estimation.
+where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and
+$l^2$ norm, respectively.  $\lambda_{ls}$ denotes the penalization parameter
+for the lasso estimation.
 
-The lasso algorithm selects the parameters which are relevant to the measurements and simultaneously estimate the value of
-the selected parameters. However, it has been shown by
-\citet{AdaLASSO-Zou2006} that when the column vectors of the transforming matrix $\mathbf{A'}$ are highly correlated,
-lasso cannot select the relevant parameters from the parameter space consistently. Moreover, the estimated parameters
-are biased due to the shrinkage process in the lasso regression. We note that, for the density map reconstruction problem,
-the column vectors are highly correlated because, as shown in Figure \ref{fig-corlensKer}, the lensing kernels for
-lenses at different redshifts are highly correlated. Therefore, the lasso algorithm cannot select the consistent mass in
-the line of sight direction and the reconstructed mass sufferes from smears in the line of sight direction even in the
-absence of noise on shear measurements.
-Figure \ref{fig-lassoVsadaLasso} shows the reconstructions of the mass map of a single halo with halo mass equals
-$M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The noises on shear measurements are not included in the simulation. 
-The left panel of Figure \ref{fig-lassoVsadaLasso} is the reconstruction with lasso algorithm which shows a significant smear 
-along the line of sight.
+The lasso algorithm selects the parameters relevant to the measurements and
+simultaneously estimates the value of the selected parameters.  However, it has
+been shown by \citet{AdaLASSO-Zou2006} that when the column vectors of the
+transforming matrix $\mathbf{A'}$ are highly correlated, the lasso cannot
+select the relevant parameters from the parameter space consistently.
+Moreover, the estimated parameters are biased due to the shrinkage in the lasso
+regression. We note that, for the density map reconstruction problem, the
+column vectors are highly correlated because, as shown in Figure
+\ref{fig-corlensKer}, the lensing kernels for lenses at different redshifts are
+highly correlated. Therefore, the lasso algorithm cannot select the consistent
+mass in the line of sight direction, and the reconstructed mass suffers from
+smears in the line of sight direction even in the absence of noise on shear
+measurements.  Figure \ref{fig-lassoVsadaLasso} shows the reconstructions of a
+single halo's mass map with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$
+at redshift $0.35$. The noises on shear measurements are not included in the
+simulation.  The left panel of Figure \ref{fig-lassoVsadaLasso} is the
+reconstruction with the lasso algorithm, which shows a significant smear along
+the line of sight.
 
-\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different projection 
-coefficients in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. In the first step, lasso is used to 
-estimate the parameters and the preliminary estimated outcome of lasso is denoted as $\hat{x'}^{\rm{lasso}}$. In the second 
-step, the preliminary lasso estimation is used to weight the penalization. The weight on penalty is defined as
+\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm, which uses
+adaptive weights to penalize different projection coefficients in the $l^1$
+penalty. The adaptive lasso algorithm is a two-steps process. In the first
+step, the lasso is used to estimate the parameters, and the preliminary
+estimation of the lasso is denoted as $\hat{x'}^{\rm{lasso}}$. In the second
+step, the preliminary lasso estimation is used to weight the penalization. The
+weight on penalty is defined as
 \begin{equation}
@@
 \end{equation}
-here we set the hyper-parameter $\tau$ to $2$.
-The adaptive lasso estimator is expressed as
+where we set the hyper-parameter $\tau$ to $2$.  The adaptive lasso estimator is
+expressed as
 \begin{equation}\label{eq-lossFun}
@@
 \end{equation}
-Here $\lambda_{\rm{als}}$ is the penalization parameter for adaptive lasso which does not need to be the same as the
-penalization parameter for the preliminary lasso estimation ($\lambda_{\rm{ls}}$).
+Here, $\lambda_{\rm{als}}$ is the penalization parameter for the adaptive
+lasso.  We note that $\lambda_{\rm{als}}$ does not need to be the same as the
+penalization parameter for the preliminary lasso estimation
+($\lambda_{\rm{ls}}$).
 
-The loss function can be rewritten with the Einstein notation:
+We rewrite the loss function with the Einstein notation:
 \begin{equation}
@@
 \end{equation}
-To simplify the notification in future, we define the quadruple term in the loss function as $G(x')$:
+To simplify the notification in future, we define the quadruple term in the
+loss function as $G(x')$:
 \begin{equation}
-G(x')=\frac{1}{2}\Sigma^{-1}_{\alpha\beta}(\gamma^{*}_{\alpha}-A'^{*}_{\alpha i}x'_{i})
-(\gamma_{\beta}-A'_{\beta j}x'_{j}).
+G(x')=\frac{1}{2}\Sigma^{-1}_{\alpha\beta}(\gamma^{*}_{\alpha}-A'^{*}_{\alpha
+i}x'_{i}) (\gamma_{\beta}-A'_{\beta j}x'_{j}).
 \end{equation}
@@
  \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
- \caption{The histograms of detected peak values from all of the simulations. The solid lines with different colors 
-        are the results of reconstructions with the NFW dictionary penalized with different regularization parameter:
-        $\lambda=3.5,4.0,5.0$. The dashed lines are the results of reconstructions from pure noise fields.
+ \caption{The histograms of detected peak values from all of the simulations.
+     The solid lines with different colors are the results of reconstructions
+     with the NFW dictionary penalized with different regularization parameter:
+     $\lambda=3.5,4.0,5.0$. The dashed lines are the results of reconstructions
+     from pure noise fields.
     }\label{fig-peakHist}
@@
 
-In this work, we apply the Fast Iterative Soft Thresholding Alorithm (FISTA) of \citet{FISTA-Beck2009} to find the global minia
-of the adaptive lasso loss function.
+In this work, we apply the Fast Iterative Soft Thresholding Algorithm (FISTA) of
+\citet{FISTA-Beck2009} to find the global minima of the adaptive lasso's loss
+function.
 
-The coefficients are initialized as $x_i^{(1)}=0$. According to the FISTA algorithm, we iteratively update the elements of the 
-projection coefficient field ($x$). In the $n$'th iteration, a temporary update is first calcualted as
+The coefficients are initialized as $x_i^{(1)}=0$. According to the FISTA
+algorithm, we iteratively update the projection coefficient field ($x$). In the
+$n$'th iteration, a temporary update is first calculated as
 \begin{equation}
@@
 \end{equation}
-$\mu$ is the step size of the gradient descent iteration.
-$\partial_i G(x'^{(n)})$ refers to the $i$'th element of the gradient
-vector of $G$ at point $x'^{(n)}$:
+$\mu$ is the step size of the gradient descent iteration.  $\partial_i
+G(x'^{(n)})$ refers to the $i$'th element of the gradient vector of $G$ at
+point $x'^{(n)}$:
 \begin{equation}
@@
 \end{equation}
-where $\Re\left( \bullet \right)$ is the function returns the real part of the input function.
-The FISTA algorithm requires an additional step amounting to a weighted average between
+where $\Re\left( \bullet \right)$ is the function returns the real part of the
+input function. The FISTA algorithm requires an additional step amounting to a
+weighted average between
 $x'^{(n+1)}$ and $x'^{(n)}$:
@@
 
-Note that the FISTA algorithm coverges as long as the gradient descent step size $\mu$ satisfies
+Note that the FISTA algorithm converges as long as the gradient descent step
+size $\mu$ satisfies
 \begin{equation}
@@
 \end{equation}
-where $\norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }$ refers to the spectrum norm of the matrix
-$\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$. The spectral norm is estimated by simulating a large number of
-random vectors with $l^2$ norms equal one with different realizations. The matrix operator 
-$\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is subsequently applied to each random vector and get a corresponding 
-transformed vector. The spectral norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is the maximum $l^2$ 
-norm of the transformed vectors.
+where $\norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }$ refers to
+the spectrum norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1}
+\mathbf{A}$. The spectral norm is estimated by simulating a large number of
+random vectors with $l^2$ norms equal one with different realizations. The
+matrix operator $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is
+subsequently applied to each random vector and get a corresponding transformed
+vector. The spectral norm of the matrix $\mathbf{A^{\dagger}}
+\mathbf{\Sigma}^{-1} \mathbf{A}$ is determined as the maximum $l^2$ norm of the
+transformed vectors.
 
@@
 \centering
-\subfigure[NFW: $\lambda=3.5$]{\includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}}
-\subfigure[Point Mass: $\lambda=3.5$]{\includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}}
-\subfigure[NFW: $\lambda=5.0$]{\includezraphics{delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}}
-\subfigure[Point Mass: $\lambda=5.0$]{\includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}}
-\caption{The results of density maps reconstruction with the point mass dictionary (left) and the NFW dictionary (right) 
-        with $\lambda=3.5$ (upper) and $\lambda=5.0$ (lower). The input density map is from a NFW halo with mass 
-        $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The vertical direction is the line of sight 
-        direction, and the lower boundaries and upper boundaries of the boxes are $0.01$ and $0.85$, respectively.
+\subfigure[NFW: $\lambda=3.5$]{
+        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
+        }
+\subfigure[Point Mass: $\lambda=3.5$]{
+        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
+        }
+\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
+        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
+        }
+\subfigure[Point Mass: $\lambda=5.0$]{
+        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
+        }
+\caption{The results of density maps reconstruction with the point mass
+    dictionary (left) and the NFW dictionary (right) with $\lambda=3.5$ (upper)
+    and $\lambda=5.0$ (lower). The input density map is from a NFW halo with
+    mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The
+    vertical direction is the line of sight direction, and the lower boundaries
+    and upper boundaries of the boxes are $0.01$ and $0.85$, respectively.
         } \label{fig-NFWvsPM}
@@
 
-In this section, we simulate weak-lensing shear fields induced by a group of halos with various halo masses
-and redshifts. The shear fields are used to distort the HSC mock shape catalogs with different realizations of the 
-HSC-like shape measurement error and photo-$z$ uncertainty (Section \ref{subsec:Sims}).
+This section simulates weak-lensing shear fields induced by a group of halos
+with various halo masses and redshifts. The shear fields are used to distort
+the HSC mock shape catalogs with different realizations of the HSC-like shape
+measurement error and photo-$z$ uncertainty (Section \ref{subsec:Sims}).
 
-Then, we test our algorithm on the simulations with different setups of the regularization parameter. We also compare the 
-results of our algorithm which uses the NFW dictionary (Section \ref{subsec:test-nfw}) with the results from the setup using
-the point mass dictionary (Section \ref{subsec:test-pm}).
+Then, we test our algorithm using the simulations with different setups of the
+regularization parameter. We also compare the results of our algorithm, which
+uses the NFW dictionary (Section \ref{subsec:test-nfw}), with the point mass
+dictionary (Section \ref{subsec:test-pm}).
 
-The $\Lambda$CDM cosmology used for the simulations is from the best fitting result of the final full-mission Planck observation
-of the cosmic microwave background (CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$, $\Omega_\Lambda=0.685$
-\citep{cmb-Planck2018-Cosmology}.
+The $\Lambda$CDM cosmology used for the simulations is from the best fitting
+result of the final full-mission Planck observation of the cosmic microwave
+background (CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$,
+$\Omega_\Lambda=0.685$ \citep{cmb-Planck2018-Cosmology}.
 
@@
 
-We sample halos in a two dimensional redshift-mass plane. The redshift-mass plane is evenly divided into eight redshift bins
-and eight mass bins. The input redshifts and masses are shifted by random values for each halo from the centers of the bins.
-The concentration of the NFW halo is set to as a function of the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
+We sample halos in a two-dimensional redshift-mass plane. The redshift-mass
+plane is evenly divided into eight redshift bins and eight mass bins. We
+randomly shift the input halo redshifts and halo masses from the bins' centers
+by a small amount. The concentration of the NFW halo is set to as a function of
+the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
 \citet{c-M_Magneticum-Ragagnin2019}
@@
 \end{equation}
-The weak-lensing shear fields of these NFW halos are simulated according to \citet{haloModel-TJ2003-3pt}. The shear
-distortions are applied to one hundred realizations of galaxy catalogs with the HSC-like shape measurement error and photo-$z$ 
-uncertainty.
+The weak-lensing shear fields of these NFW halos are simulated according to
+\citet{haloModel-TJ2003-3pt}. The shear distortions are applied to one hundred
+realizations of galaxy catalogs with the HSC-like shape measurement error and
+photo-$z$ uncertainty.
 
-The galay catalogs are simulated with the HSC S16A shape catalog \citep{HSC1-catalog}.
-We uses galaxies in a one square degree region at the center of tract 9347 \citep{HSC1-data}.
-The positions of the galaxies are randomized so that the galaxies statistically have a homogeneous distribution in a one square 
-degree stamp.
-For each galaxy, we randomly assign its redshift following the MLZ photo-$z$ probability distribution function from
-By randomly rotating the galaxies in the shape catalog, we simulate the HSC-like shape estimation error with different realizations.
-The histogram of the first component of the HSC-like shape estimation error on galaxy
-level is shown in Figure \ref{fig-noiseHistogram}. 
-The corresponding histogram after the procedure of smoothing and pixelization is also shown in \ref{fig-noiseHistogram}, 
-and the standard deviation map of the noise is demonstrated in Figure \ref{fig-noistdmap}.
-\citep{HSC1-photoz}.
+The galaxy catalogs are simulated using the HSC S16A shape catalog
+\citep{HSC1-catalog}.  We use galaxies in a one square degree region at the
+center of tract 9347 \citep{HSC1-data}.  The galaxies' positions are randomized
+to have a homogeneous distribution statistically in the one-square
+degree stamp. We randomly assign its redshift for each galaxy following the
+MLZ photo-$z$ probability distribution function from By randomly rotating the
+galaxies in the shape catalog, we simulate the HSC-like shape estimation error
+with different realizations.  The histogram of the first component of the
+HSC-like shape estimation error on galaxy level is shown in Figure
+\ref{fig-noiseHistogram}.  The corresponding histogram of the shape error on
+the pixel level after smoothing and pixelization is also shown in
+\ref{fig-noiseHistogram}, and the standard deviation map of the noise is
+demonstrated in Figure \ref{fig-noistdmap}.  \citep{HSC1-photoz}.
 
@@
  \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
- \caption{The upper panels show the halo detection rate and the number of false peak per square degree for mass map 
-        reconstructed with the point mass dictionary. The penalization paramter is set to $\lambda=3.5$ for the upper panels. 
-        The lower panels show the results for $\lambda=5.0$. 
+ \caption{The upper panels show the halo detection rate and the number of false
+     peak per square degree for mass map reconstructed with the point mass
+     dictionary. The penalization paramter is set to $\lambda=3.5$ for the
+     upper panels.  The lower panels show the results for $\lambda=5.0$.
         }\label{fig-detFalsRatePM}
@@
 
-In this subsection, we test the performance of our algorithm with the default setup which models the matter density
-field with multi-scale NFW atoms. The dictionary is constructed with NFW atom with three frames of different scale radius. 
-The NFW scale radius is set to comoving distances of $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc, respectively. 
-The truncation radius (concentration) is set to four times of the scale radius for the atoms in the dictionary. We test the 
-algorithm with different regularization parameters for the preliminary lasso ranging from $3.5$ to $5.0$. The regularization 
-parameter for the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\gamma+1}$.
+In this subsection, we test the performance of our algorithm with the default
+setup that models the matter density field with multi-scale NFW atoms. The
+dictionary is constructed with three frames of different comoving scale radius:
+$0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc.  The
+truncation radius (concentration) is set to four times the scale radius for
+the atoms in the dictionary. We test the algorithm with different
+regularization parameters for the preliminary lasso ranging from $3.5$ to
+$5.0$. The regularization parameter for the adaptive lasso is set to
+$\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\gamma+1}$.
 
-In this paper, we do not go beyound the resolution limit defined by the Gaussian smoothing kernel with scale radius equals 
-$1.\arcmin 5$ and the pixel scale equals $1\arcmin$. Therefore, we also smooth the reconstruced density with the same 
+This paper does not go beyond the resolution limit defined by the Gaussian
+smoothing kernel with the scale: $1.\arcmin 5$ and the pixel scale
+that equals $1\arcmin$. We smooth the reconstructed density with the same
 Gaussian kernel in each lens redshift plane.
 
-After the reconstruction of each density field, we detect the peaks on the density map. The stacked $2$-D histogram from all of
-the simulated boxes for the offsets of the detected peak positions from the input halo is demonstrated in the left panel of 
-Figure \ref{fig-detoffsets}. For each simulation, we find the positive peak closest to the input position (in unit of pixel), and
-if the cloest peak lay inside the region denoted with dashed lines in the left panel of Figure \ref{fig-detoffsets}, we take it
-as a true detection of the input halo. Whereas, other detected peaks, which includes both positive and negative peaks, are taken as 
-false peak detections. The right panel of Figure \ref{fig-detoffsets} shows the average redshift of true detections for each halo.
-The estimated redshift are lower than the true redshfit by about $0.03$ for halos at low redshifts ($z\leq 0.4$). For halos at 
-$0.4<z\leq 0.85$, the relative redshfit bias is below $0.5\%$.
+After the reconstruction of each density field, we detect the peaks on the
+density map. The stacked $2$-D histogram from all of the simulated boxes for
+the offsets of the detected peak positions from the input halo is demonstrated
+in the left panel of Figure \ref{fig-detoffsets}. For each simulation, we find
+the positive peak closest to the input position (in the pixel unit), and if the
+closest peak lay inside the region denoted with the dashed box in the left
+panel of Figure \ref{fig-detoffsets}, we take it as a true detection of the
+input halo. Other detected peaks, which include both positive and negative
+peaks, are taken as false peak detections. The right panel of Figure
+\ref{fig-detoffsets} shows the average redshift of true detections for each
+halo.  The estimated redshifts are lower than the true redshifts by about
+$0.03$ for halos in the low-redshift range ($z\leq 0.4$). For halos at
+$0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.
 
-Figure \ref{fig-detFalsRateNFW} shows the detection rate (left panels) and the number of false peaks per square degree (right panel) 
-for each simulated halo. The figure include results of different penalization parameters: $\lambda=3.5$ (upper panel) 
-and $\lambda=5.0$ (lower panel).
-We find that with the increase of the penalization parameter, the detection rate decreases. On the other hand, the number of false 
-peaks also decreases.
-Figure \ref{fig-peakHist} shows the histograms, which is normalized by the number of simulations, for all of the detected peaks 
-with different penalization parameters. We also plot the corresponding histograms for peaks detected from pure noise fields for 
-comparison. From the left panels of Figure \ref{fig-NFWvsPM}, which show the $3$-D density maps reconstructed with different 
-penalization parameters for a halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$ , we also find that the number 
-of false detections significantly decreases as the penalization parameter increases.
+Figure \ref{fig-detFalsRateNFW} shows the detection rate (left panels) and the
+number of false peaks per square degree (right panel) for each simulated halo.
+The figure include results of different penalization parameters: $\lambda=3.5$
+(upper panel) and $\lambda=5.0$ (lower panel).  We find that with the increase
+of the penalization parameter, the detection rate decreases. On the other hand,
+the number of false peaks also decreases.  Figure \ref{fig-peakHist} shows the
+histograms, which are normalized by the number of simulations, for all
+detected peaks with different penalization parameters. We also plot the
+corresponding histograms for peaks detected from pure noise fields for
+comparison. From the left panels of Figure \ref{fig-NFWvsPM}, which show the
+$3$-D density maps reconstructed with different penalization parameters for a
+halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$ , we also
+find that the number of false detections significantly decreases as the
+penalization parameter increases.
 
@@
 
-In this subsection, we show the results for the setup which subsitutes the default NFW dictionary with the point mass dictionary, 
-as a comparison with the default setup.
-The regularization parameter for the preliminary lasso is set to $3.5$ and $5.0$. 
-Inspired by \citet{structureAdaLasso-Pramanik2020}, which propose to incorporate external group information into
-different adaptive lasso penalization weights by setting the penalization weights for projection coefficients in 
-the same group to the average of the adaptive weights in the same group, we smooth the preliminary lasso estimation 
-in each lens redshfit bins with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc, which is denoted as 
-$\hat{x}^{\rm{ls}}_{\rm{sm}}$ and the penalization weights are set to $1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\gamma$. 
-The regularization parameter for the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.
+In this subsection, we show the results for the setup, which substitutes the
+default NFW dictionary with the point mass dictionary, to compare with the
+default setup.  The regularization parameter for the preliminary lasso is set
+to $3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
+propose to incorporate external group information into different adaptive lasso
+penalization weights by setting the penalization weights for projection
+coefficients in the same group to the average of the adaptive weights in this
+group, we smooth the preliminary lasso estimation in each lens redshift bins
+with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc, which is denoted as
+$\hat{x}^{\rm{ls}}_{\rm{sm}}$ and the penalization weights are set to
+$1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\gamma$.  The regularization parameter for
+the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.
 
-As we have done on the reconstructions from NFW dictionary, we smooth the reconstruced density maps with the Gaussian 
-kernel (scale radius equals $1.\arcmin 5$) in each lens redshift plane.
+As we have done on the NFW dictionary's reconstruction, we smooth the
+reconstructed density maps with the Gaussian kernel (scale radius equals
+$1.\arcmin 5$) in each lens redshift plane.
 
-Figure \ref{fig-detFalsRatePM} shows the detection rate (left panels) and the number of false peaks per square degree (right panel) 
-for each simulated halo. The figure include results of different penalization parameters: $\lambda=3.5$ (upper panel) 
-and $\lambda=5.0$ (lower panel). The right panels of Figure \ref{fig-NFWvsPM} show the $3$-D density maps reconstructed with 
-different penalization parameters for a halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. Comparing with
-the results for the NFW dictionary, we find that the number of false peaks for the point mass dictionary is much larger than that 
-of the NFW dictionary. As demonstrated in the right panels of Figure \ref{fig-NFWvsPM}, the reconstructions with the point 
-mass dictionary tend to assign masses to different redshfits in the neighboring region of the halo center. Since the profies
-of NFW atoms are consistent with the input halo profiles, the reconstruced structures from the NFW dictionary are sparser than
-those from the point mass dictionary.
+Figure \ref{fig-detFalsRatePM} shows the detection rate (left panels) and the
+number of false peaks per square degree (right panel) for each simulated halo.
+The figure includes results of different penalization parameters: $\lambda=3.5$
+(upper panel) and $\lambda=5.0$ (lower panel). The right panels of Figure
+\ref{fig-NFWvsPM} show the $3$-D density maps reconstructed with different
+penalization parameters for a halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$
+at redshift $0.164$. Comparing with the results for the NFW dictionary, we find
+that the number of false peaks for the point mass dictionary is much larger
+than that of the NFW dictionary. As demonstrated in the right panels of Figure
+\ref{fig-NFWvsPM}, the reconstructions with the point mass dictionary tend to
+assign masses to different redshifts in the neighboring region of the halo
+center. Since the NFW atoms' profiles are more consistent with the input halo
+profiles than the point mass profiles, the reconstructed structures from the
+NFW dictionary are sparser than those from the point mass dictionary.
 
@@
 
-We develope a novel method to reconstruct $3$-D density contrast maps from weak-lensing shear measurements and photometric
-redshift estimations.
-Our method models $3$-D density contrast maps as a summation of NFW atoms with multiple comoving radius. 
-With the prior assumption that the basis atoms sparsely distributes in the $3$-D space, the density field is reconstructed
+We develop a novel method to reconstruct $3$-D density contrast maps from
+weak-lensing shear measurements and photometric redshift estimations.  Our
+method models $3$-D density contrast maps as summations of NFW atoms with
+difference comoving radius.  With the prior assumption that the clumpy mass
+sparsely distributes in the $3$-D space, the density field is reconstructed
 using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}.
 
-The method is tested with realistic simulations using HSC-like shape estimation error and photo-$z$ uncertainty. The results
-are summarized as follows:
+The method is tested with realistic simulations using HSC-like shape estimation
+error and HSC-like photo-$z$ uncertainty. The results are summarized as follows:
 \begin{enumerate}
- \item The solution of the standard lasso algorithm suffers from a smear of structure in the line of sight direction even in 
-    the absence of shape nosie, and the addaptive lasso algorithm significantly removes the line of sight smear of structure. 
- \item The algorithm is able to detect halo with minimal mass limits of $10^{13.5} M_{\odot}/h$, $10^{14.3} M_{\odot}/h$, 
-    $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.9$) redshifts, respectively.
- \item The estimated redshift of the halos detected from the reconstructed mass maps are lower than the true redshfit by about 
-    $0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshfit bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$. 
+ \item The solution of the lasso algorithm suffers from a smear of structure in
+     the line of sight direction even in the absence of shape noise, and the
+     adaptive lasso algorithm significantly removes the line of sight smear of
+     structure.
+ \item The algorithm is able to detect halo with minimal mass
+     limits of $10^{13.5} M_{\odot}/h$, $10^{14.3} M_{\odot}/h$, $10^{15.0}
+     M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high
+     ($0.6\leq z< 0.9$) redshifts, respectively.
+ \item The estimated redshift
+     of the halos detected from the reconstructed mass maps are lower than the
+     true redshift by about $0.03$ for halos at low redshifts ($z\leq 0.4$).
+     The relative redshift bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$.
 \end{enumerate}

### 2020-11-28 doc/paper_ms_method_HSCY1/ms.tex
updating ms

@@
 \newcommand \redColor{\color{red}}
+
 \renewcommand\labelenumi{(\roman{enumi})}
@@
 Reducing the line of sight smearing.}
-%\author{Xiangchong Li}
-%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
-%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-%University of Tokyo, Kashiwa 277-8583, Japan}
+\author{Xiangchong Li}
+\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
+\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
+University of Tokyo, Kashiwa 277-8583, Japan}
 %\author{Masamune Oguri}
@@
  \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
- \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The corresponding $2$-D profiles are
-        shown in Figure \ref{fig-atoms2D}.} \label{fig-atoms1D}
+    \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The
+        corresponding $2$-D profiles are shown in Figure \ref{fig-atoms2D}.
+        }
+ \label{fig-atoms1D}
 \end{figure}
@@
 algorithm, which selects the steepest coordinate in each iteration, to find the
-minima of a non-convex loss function penalized with the firm thresholding
+minimum of a non-convex loss function penalized with the firm thresholding
 function. \citet{LSS-massMap-Glimpse3D-Leonard2014} significantly reduce the
@@
 Here we denote the physical shear distortion field as $\gamma_L$ and we note
-that the final observed shear measurements are also physical shear distortions
-influenced by systematic errors from observatins. The systematic errors will be
-discussed in Section \ref{subsec:method-Systematics}.
+that the final observed shear measurements are influenced by systematic errors
+from observations. The systematic errors will be discussed in Section
+\ref{subsec:method-Systematics}.
 
@@
 
-The lasso algorithm uses $l^1$ norm of the projection coefficient field as to
+The lasso algorithm uses $l^1$ norm of the projection coefficient field to
 regularize the modeling, and the estimator is defined as
@@
 regression. We note that, for the density map reconstruction problem, the
-column vectors are highly correlated because, as shown in Figure
-\ref{fig-corlensKer}, the lensing kernels for lenses at different redshifts are
-highly correlated. Therefore, the lasso algorithm cannot select the consistent
-mass in the line of sight direction, and the reconstructed mass suffers from
-smears in the line of sight direction even in the absence of noise on shear
-measurements.  Figure \ref{fig-lassoVsadaLasso} shows the reconstructions of a
-single halo's mass map with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$
-at redshift $0.35$. The noises on shear measurements are not included in the
-simulation.  The left panel of Figure \ref{fig-lassoVsadaLasso} is the
-reconstruction with the lasso algorithm, which shows a significant smear along
-the line of sight.
+column vectors are highly correlated even in the absence of photometric
+redshift uncertainties because, as shown in Figure \ref{fig-corlensKer}, the
+lensing kernels for lenses at different redshifts are highly correlated.
+Therefore, the lasso algorithm cannot select the consistent mass in the line of
+sight direction, and the reconstructed mass suffers from smears in the line of
+sight direction even in the absence of noise on shear measurements.  Figure
+\ref{fig-lassoVsadaLasso} shows the reconstructions of a single halo's mass map
+with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$.
+The noises on shear measurements are not included in the simulation.  The left
+panel of Figure \ref{fig-lassoVsadaLasso} is the reconstruction with the lasso
+algorithm, which shows a significant smear along the line of sight.
 
@@
      The solid lines with different colors are the results of reconstructions
-     with the NFW dictionary penalized with different regularization parameter:
+     with the NFW dictionary penalized with different regularization parameters:
      $\lambda=3.5,4.0,5.0$. The dashed lines are the results of reconstructions
@@
 
-In this work, we apply the Fast Iterative Soft Thresholding Algorithm (FISTA) of
-\citet{FISTA-Beck2009} to find the global minima of the adaptive lasso's loss
-function.
-
-The coefficients are initialized as $x_i^{(1)}=0$. According to the FISTA
-algorithm, we iteratively update the projection coefficient field ($x$). In the
-$n$'th iteration, a temporary update is first calculated as
+\citet{FISTA-Beck2009} proposed the Fast Iterative Soft Thresholding Algorithm
+(FISTA) to solve the lasso problem.  Since the lasso's loss function and the
+adaptive lasso's loss function only differ in their penalization terms. The
+FISTA is also applicable to the adaptive lasso problem. We apply the FISTA to
+solve the preliminary lasso estimation and the final adaptive lasso estimation.
+
+Here we start from the lasso preliminary estimation. The coefficients are
+initialized as $x_i^{(1)}=0$. According to the FISTA algorithm, we iteratively
+update the projection coefficient field ($x$). In the $n$'th iteration, a
+temporary update is first calculated as
 \begin{equation}
@@
 \end{equation}
+The soft thresholding is a part of the lasso algorithm. It selects the
+estimations with amplitude larger than $\lambda$, and shrink the estimations by
+$\lambda$.
 $\mu$ is the step size of the gradient descent iteration.  $\partial_i
@@
 where $\Re\left( \bullet \right)$ is the function returns the real part of the
-input function. The FISTA algorithm requires an additional step amounting to a
+input function. The FISTA algorithm requires an additional update amounting to a
 weighted average between
@@
 t^{(n+1)}&=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2},\\
-x'_{n+1} &\leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)}),
+x'^{(n+1)} &\leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)}),
 \end{split}
@@
 
-Note that the FISTA algorithm converges as long as the gradient descent step
-size $\mu$ satisfies
+The FISTA algorithm converges as long as the gradient descent step size $\mu$
+satisfies
 \begin{equation}
@@
 
-\subsubsection{The Algorithm}
-
-The algorithm is described in Algorithm \ref{alg-1}.
+As summarized in Algorithm \ref{alg-1}, we first initial the projection
+coefficients as zero and use the FISTA algorithm to find the global minimum of
+the lasso loss function. Such a global minimum is the preliminary estimation.
+We then use the preliminary lasso estimation to weight the coefficients and
+construct the adaptive lasso loss function. Finally, we set the preliminary
+lasso estimation as the warm start of the adaptive lasso estimation and use the
+FISTA algorithm again to find the adaptive lasso loss function's global minimum,
+which is the final solution.
 
@@
     \WHILE{$i \leq N_{\rm{iter}}$}
+        \STATE \# soft thresholding
         \STATE $x'^{(n+1)}_{i}=\mathrm{ST}_{\hat{w}\lambda} \left(x'^{(n)}_{i} -\mu \partial_i G(x'^{(n)})\right)$
+        \STATE \# FISTA algorithm
         \STATE $t^{(n+1)}=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2}$
-        \STATE $x'_{n+1} \leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)})$
+        \STATE $x'^{(n+1)} \leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)})$
         \STATE $i=i+1$
@@
     vertical direction is the line of sight direction, and the lower boundaries
-    and upper boundaries of the boxes are $0.01$ and $0.85$, respectively.
+    and upper boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively.
         } \label{fig-NFWvsPM}
@@
 randomly shift the input halo redshifts and halo masses from the bins' centers
-by a small amount. The concentration of the NFW halo is set to as a function of
+by a small amount. The concentration of the NFW halo is set as a function of
 the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
@@
 setup that models the matter density field with multi-scale NFW atoms. The
-dictionary is constructed with three frames of different comoving scale radius:
-$0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc.  The
-truncation radius (concentration) is set to four times the scale radius for
-the atoms in the dictionary. We test the algorithm with different
-regularization parameters for the preliminary lasso ranging from $3.5$ to
-$5.0$. The regularization parameter for the adaptive lasso is set to
-$\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\gamma+1}$.
+dictionary is constructed with three frames of different NFW comoving scale
+radius: $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc.  The
+truncation radius (concentration) is set to four times the scale radius for the
+atoms in the dictionary.
+
+We test the algorithm with different regularization parameters for the
+preliminary lasso estimation which range from $3.5$ to $5.0$. The
+regularization parameter for the adaptive lasso is set to
+$\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\tau+1}$.
+Here, we note that both the preliminary lasso estimation and the final adaptive
+estimation select the modes with signal to noise ratios (SNRs) greater than
+$\lambda_{\rm{ls}}$ in each iteration. While the final adaptive lasso
+estimation further enhances the growth of the modes with preliminary
+estimations greater than $\lambda_{\rm{ls}}$.
 
@@
 
-After the reconstruction of each density field, we detect the peaks on the
-density map. The stacked $2$-D histogram from all of the simulated boxes for
-the offsets of the detected peak positions from the input halo is demonstrated
-in the left panel of Figure \ref{fig-detoffsets}. For each simulation, we find
-the positive peak closest to the input position (in the pixel unit), and if the
-closest peak lay inside the region denoted with the dashed box in the left
-panel of Figure \ref{fig-detoffsets}, we take it as a true detection of the
-input halo. Other detected peaks, which include both positive and negative
-peaks, are taken as false peak detections. The right panel of Figure
-\ref{fig-detoffsets} shows the average redshift of true detections for each
-halo.  The estimated redshifts are lower than the true redshifts by about
-$0.03$ for halos in the low-redshift range ($z\leq 0.4$). For halos at
-$0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.
+We detect the peaks on the density map after the reconstruction. The stacked
+$2$-D histogram, from all of the simulations, for the offsets of the detected
+peak positions from the input halos' positions is shown in the left panel of
+Figure \ref{fig-detoffsets}.
+
+For each simulation, we find the positive peak closest to the input position
+(in the pixel unit), and if the closest peak lay inside the region denoted with
+the dashed box in the left panel of Figure \ref{fig-detoffsets}, we take it as
+a true peak detection of the input halo. Other detected peaks, which include both
+positive and negative peaks, are taken as false peaks. The right
+panel of Figure \ref{fig-detoffsets} shows the average redshift of true
+detections for each halo. The estimated redshifts are lower than the true
+redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
+For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.
 
@@
 of the penalization parameter, the detection rate decreases. On the other hand,
-the number of false peaks also decreases.  Figure \ref{fig-peakHist} shows the
-histograms, which are normalized by the number of simulations, for all
-detected peaks with different penalization parameters. We also plot the
-corresponding histograms for peaks detected from pure noise fields for
-comparison. From the left panels of Figure \ref{fig-NFWvsPM}, which show the
-$3$-D density maps reconstructed with different penalization parameters for a
-halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$ , we also
-find that the number of false detections significantly decreases as the
-penalization parameter increases.
+the number of false peaks also decreases.
+
+Figure \ref{fig-peakHist} shows the histograms, which are normalized by the
+number of simulations, for all detected peaks with different penalization
+parameters. We also plot the corresponding histograms for peaks detected from
+pure noise fields for comparison. From the left panels of Figure
+\ref{fig-NFWvsPM}, which show the $3$-D density maps reconstructed with
+different penalization parameters for a halo with $M_{200}=10^{15.02}
+~h^{-1}M_{\odot}$ at redshift $0.164$ , we also find that the number of false
+peaks significantly decreases as the penalization parameter increases.
 
@@
 coefficients in the same group to the average of the adaptive weights in this
-group, we smooth the preliminary lasso estimation in each lens redshift bins
-with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc, which is denoted as
-$\hat{x}^{\rm{ls}}_{\rm{sm}}$ and the penalization weights are set to
-$1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\gamma$.  The regularization parameter for
-the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.
+group, we smooth the preliminary lasso estimation in each lens redshift bin
+with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc. The smoothed
+preliminary lasso estimation is denoted as $\hat{x}^{\rm{ls}}_{\rm{sm}}$, and
+the penalization weights are set to $1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.
+The regularization parameter for the adaptive lasso is set to
+$\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.
 
@@
 Figure \ref{fig-detFalsRatePM} shows the detection rate (left panels) and the
-number of false peaks per square degree (right panel) for each simulated halo.
-The figure includes results of different penalization parameters: $\lambda=3.5$
-(upper panel) and $\lambda=5.0$ (lower panel). The right panels of Figure
-\ref{fig-NFWvsPM} show the $3$-D density maps reconstructed with different
-penalization parameters for a halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$
-at redshift $0.164$. Comparing with the results for the NFW dictionary, we find
-that the number of false peaks for the point mass dictionary is much larger
-than that of the NFW dictionary. As demonstrated in the right panels of Figure
-\ref{fig-NFWvsPM}, the reconstructions with the point mass dictionary tend to
-assign masses to different redshifts in the neighboring region of the halo
-center. Since the NFW atoms' profiles are more consistent with the input halo
-profiles than the point mass profiles, the reconstructed structures from the
-NFW dictionary are sparser than those from the point mass dictionary.
+number of false peaks per square degree (right panel) for each setup of halo
+mass and redshift.
+This figure includes results of different penalization parameters:
+$\lambda=3.5$ (upper panel) and $\lambda=5.0$ (lower panel). The right panels
+of Figure \ref{fig-NFWvsPM} show the $3$-D density maps reconstructed with
+different penalization parameters for a halo with $M_{200}=10^{15.02}
+~h^{-1}M_{\odot}$ at redshift $0.164$.
+Comparing with the results of the NFW dictionary, we find that the number of
+false peaks in the mass map reconstructed with the point mass dictionary is
+much larger than the NFW dictionary.
+
+As demonstrated in the right panels of Figure \ref{fig-NFWvsPM}, the mass
+reconstructions with the point mass dictionary tend to assign masses to
+several different redshift bins in the neighboring region of the halo center.
+While the NFW dictionary produces consistent mass reconstructions.
+Since the NFW atoms' profiles are more consistent with the mass profiles of the
+input halos than the profile of a point mass, there are less false structures
+reconstructed with the NFW dictionary.
 
@@
 
+\section*{Acknowledgements}
+We thank Yin Li and Jiaxin Han for useful discussion.
+
+This work was supported by Global Science Graduate Course (GSGC) program of
+University of Tokyo and JSPS KAKENHI (JP19J22222).
 \bibliographystyle{aasjournal}

### 2020-11-28 doc/paper_ms_method_HSCY1/ms.tex
update ms

@@
 Reducing the line of sight smearing.}
-\author{Xiangchong Li}
-\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
-\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-University of Tokyo, Kashiwa 277-8583, Japan}
+%\author{Xiangchong Li}
+%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
+%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
+%University of Tokyo, Kashiwa 277-8583, Japan}
 %\author{Masamune Oguri}
@@
         columns are the multi-scale NFW atoms.  The smoothing kernel is
-        Gaussian with a standard deviation of $1.5$ pixels.
+        Gaussian with a standard dev
+        iation of $1.5$ pixels.
         } \label{fig-atoms2D}
@@
 
-Light from distant galaxies is distorted by the intervening inhomogeneous
-density distribution along the line of sight due to the gravity's influence.
+Weak lensing refers to the phenomenon that light from distant galaxies is
+distorted by the intervening inhomogeneous density distribution along the line
+of sight due to gravity's influence.
 As a result of the light distortion, the shapes of the background galaxies are
-coherently distorted. Such effect, which is known as weak-lensing, imprints the
-information of foreground mass density distribution to the background galaxy
-images and offers a direct probe into the mass density distribution in our
-universe \citep[see][for recent reviews]{revKilbinger15,revRachel17}.
+coherently distorted. The lensing effect imprints the information of
+foreground mass density distribution to the background galaxy images and offers
+a direct probe into the mass density distribution in our universe
+\citep[see][for recent reviews]{revKilbinger15,revRachel17}.
 
@@
 
-Several large-scale surveys target to study the weak-lensing effect at high
+Several large-scale surveys target to study the weak-lensing effect at a high
 precision level (e.g., HSC \citep{HSC1-data}, KIDS \citep{KIDS13}, DES
-\citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, WFIRST
+\citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, NGRST
 \citep{WFIRST15}).
@@
 sparsity prior, the adaptive lasso regularization \citep{AdaLASSO-Zou2006} is
-used to reconstruct the density field.  In contrast to the lasso
+used to reconstruct the density field.  We find that, in contrast to the lasso
 estimator that smears the structure along the line of sight, the adaptive lasso
@@
      The solid lines with different colors are the results of reconstructions
-     with the NFW dictionary penalized with different regularization parameters:
-     $\lambda=3.5,4.0,5.0$. The dashed lines are the results of reconstructions
-     from pure noise fields.
+     with the NFW dictionary penalized with different regularization
+     parameters: $\lambda=3.5,4.0,5.0$. The dashed lines are the corresponding
+     results of reconstructions from pure noise fields.
     }\label{fig-peakHist}
+ \includegraphics[width=0.45\textwidth]{detfalse_threshold.pdf}
+ \caption{Number of detections for true peaks (solid lines) and false
+     peaks (dashed lines) as functions of selection thresholds.
+     The lines with different colors are the results of reconstructions
+     with the NFW dictionary penalized with different regularization
+     parameters: $\lambda=3.5,4.0,5.0$.
+    }\label{fig-detfalse_threshold}
 \end{figure}
 
-\citet{FISTA-Beck2009} proposed the Fast Iterative Soft Thresholding Algorithm
+\citet{FISTA-Beck2009} propose the Fast Iterative Soft Thresholding Algorithm
 (FISTA) to solve the lasso problem.  Since the lasso's loss function and the
@@
 FISTA is also applicable to the adaptive lasso problem. We apply the FISTA to
-solve the preliminary lasso estimation and the final adaptive lasso estimation.
+solve both the preliminary lasso estimation and the final adaptive lasso
+estimation.
 
@@
 initialized as $x_i^{(1)}=0$. According to the FISTA algorithm, we iteratively
-update the projection coefficient field ($x$). In the $n$'th iteration, a
-temporary update is first calculated as
+update the projection coefficient field ($x$). Taking the $n$'th iteration as
+an example, a temporary update is first calculated as
 \begin{equation}
@@
 
+We note that when detecting galaxy clusters from the weak lensing mass maps in
+real observations\citep{HSC1-massMap-cluster}, peaks greater than an ad-hoc
+threshold is chosen as galaxy cluster candidates to suppress the number of
+false detection. Figure \ref{fig-detfalse_threshold} shows the numbers of true
+detections and false detections as functions of detection thresholds.
+
 \subsection{Point mass atoms}
@@
 
+We will apply the method to the shear measurements of the HSC survey
+\citep{HSC1-catalog,FPFSHSC1-Li2020} to perform galaxy cluster detection in our
+future work.
+
 \section*{Acknowledgements}
-We thank Yin Li and Jiaxin Han for useful discussion.
+We thank Yin Li and Jiaxin Han for useful discussions.
 

### 2020-12-02 doc/paper_ms_method_HSCY1/ms.tex
add detection vs thresholds(post-construction)

@@
 \title{Sparsity Weak Lensing $3$-D Density Map Reconstruction:
-Reducing the line of sight smearing.}
+Reducing the line of sight smearing}
 %\author{Xiangchong Li}
@@
 removes the line of sight smear of structure.  2) The algorithm is able to
-detect halo with minimal mass limits of $10^{13.5} M_{\odot}/h$, $10^{14.3}
+detect halo with minimal mass limits of $10^{14.0} M_{\odot}/h$, $10^{14.7}
 M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq
-z< 0.6$) and high ($0.6\leq z< 0.9$) redshifts, respectively.  3) The estimated
-redshift of the halos detected from the reconstructed mass maps are lower than
-the true redshift by about $0.03$ for halos at low redshifts ($z\leq 0.4$). The
-relative redshift bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$.
+z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts, respectively, with a false
+detection of 0.022/deg$^2$.  3) The estimated redshift of the halos detected
+from the reconstructed mass maps are lower than the true redshift by about
+$0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshift bias is
+below $0.5\%$ for halos at $0.4<z\leq 0.85$.
 \end{abstract}
@@
         iation of $1.5$ pixels.
-        } \label{fig-atoms2D}
+        } \label{fig_atoms2D}
 \end{figure*}
@@
     \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The
-        corresponding $2$-D profiles are shown in Figure \ref{fig-atoms2D}.
+        corresponding $2$-D profiles are shown in Figure \ref{fig_atoms2D}.
         }
- \label{fig-atoms1D}
+ \label{fig_atoms1D}
 \end{figure}
@@
 
-The reconstruction of density map from shear measurements also receive considerable interest as it reaches the nonlinear scales.
-$2$-D density map reconstruction which recover an integration of projected mass along the line of sight has been well studied
-within the community \citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
-and applied to large-scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However, the
-reconstruction of $3$-D mass map is still a challenging task.
+The reconstruction of density map from shear measurements also receive
+considerable interest as it reaches the nonlinear scales.  $2$-D density map
+reconstruction which recover an integration of projected mass along the line of
+sight has been well studied within the community
+\citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
+and applied to large-scale surveys
+\citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However,
+the reconstruction of $3$-D mass map is still a challenging task.
 
@@
 \begin{equation}
-\hat{x}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{T\Phi} x)}_2^2+ \lambda C(x) \right\},
+\hat{x}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma-
+\mathbf{T\Phi} x)}_2^2+ \lambda C(x) \right\},
 \end{equation}
@@
      blue histogram is the normalized number distribution of the best photo-$z$
-         estimation. The vertical dashed lines are the boundaries of the redshift bins.
-         The galaxies are equal-number binned.
-        } \label{fig-bestpz}
+     estimation. The vertical dashed lines are the boundaries of the redshift
+     bins.  The galaxies are equal-number binned.
+        } \label{fig_bestpz}
 \end{figure}
@@
  \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.
-        }\label{fig-pdfpz}
+        }\label{fig_pdfpz}
 \end{figure}
@@
          correlation matrices equal one.
-        }\label{fig-corlensKer}
+        }\label{fig_corlensKer}
 \end{figure*}
@@
         on galaxy shape measurements are neglected in this simulation.
-        } \label{fig-lassoVsadaLasso}
+        } \label{fig_lassoVsadaLasso}
 \end{figure*}
@@
 The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the
-transverse plane are shown in Figure \ref{fig-atoms2D}. The $1$-D slices of the
-profiles are demonstrated in Figure \ref{fig-atoms1D}. Note that these profiles
+transverse plane are shown in Figure \ref{fig_atoms2D}. The $1$-D slices of the
+profiles are demonstrated in Figure \ref{fig_atoms1D}. Note that these profiles
 are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The
@@
 
-Figure \ref{fig-bestpz} shows the histogram of the best Machine Learning and
+Figure \ref{fig_bestpz} shows the histogram of the best Machine Learning and
 photo-Z \citep[MLZ]{MLZ-TPZ2013} photometric redshift estimation from
@@
 according to the photo-$z$ best estimation, and the boundaries of the bins are
-shown as vertical dashed lines in Figure \ref{fig-bestpz}. Figure \ref{fig-pdfpz}
+shown as vertical dashed lines in Figure \ref{fig_bestpz}. Figure \ref{fig_pdfpz}
 shows the average probability density function (PDF) for galaxies in each
@@
 
-The left panel of Figure \ref{fig-corlensKer} shows the lensing kernels for
+The left panel of Figure \ref{fig_corlensKer} shows the lensing kernels for
 lenses at five different redshifts as functions of source galaxy redshift bins.
@@
 photometric redshifts with redshift uncertainties shown in Figure
-\ref{fig-pdfpz}.  As shown by the dashed lines in the left panel of Figure
-\ref{fig-corlensKer}, the lensing kernels converge to zero for source redshifts
+\ref{fig_pdfpz}.  As shown by the dashed lines in the left panel of Figure
+\ref{fig_corlensKer}, the lensing kernels converge to zero for source redshifts
 lower than the lens redshift if the uncertainties on the source galaxy
@@
 Comparing the correlation matrices shown in the middle panel and the right
-panel of Figure \ref{fig-corlensKer}, we conclude that the photo-$z$
+panel of Figure \ref{fig_corlensKer}, we conclude that the photo-$z$
 uncertainties further increase the correlations between lensing kernels at
@@
  \centering
- \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
+ \includegraphics[width=0.5\textwidth]{shapeMeasurementError-HSCY1.pdf}
  \caption{The histograms of the HSC-like shape measurement error (including
@@
         }
- \label{fig-noiseHistogram}
+ \label{fig_noiseHistogram}
 \end{figure}
@@
  \centering
- \includegraphics[width=0.45\textwidth]{noise_std_map_pix.pdf}
+ \includegraphics[width=0.5\textwidth]{noise_std_map_pix.pdf}
  \caption{The standard deviation pixel map of the HSC-like shape measurement error for the fifth source galaxy bin
         ($0.69 \leq z < 0.80 $).
-        } \label{fig-noistdmap}
+        } \label{fig_noistdmap}
 \end{figure}
@@
  \centering
- \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
+ \includegraphics[width=1.0\textwidth]{peak_scatters_f3-1.pdf}
  \caption{The left panel shows the stacked $2$-D distribution of the deviations
@@
      are based on the NFW dictionary with $\lambda=3.5$.
-     } \label{fig-detoffsets}
+     } \label{fig_detoffsets}
 \end{figure*}
@@
  \centering
- \includegraphics[width=0.95\textwidth]{detfalseRate_f3-1.pdf}
- \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
+ \includegraphics[width=1.0\textwidth]{detfalseRate_f3-1.pdf}
+ \includegraphics[width=1.0\textwidth]{detfalseRate_f3-3.pdf}
  \caption{The upper panels show the halo detection rate and the number of false
@@
      low panels show the results for $\lambda=5.0$.
-        } \label{fig-detFalsRateNFW}
+        } \label{fig_detFalsRateNFW}
 \end{figure*}
@@
 linear operation on the transverse plane, whereas the grids in the line of sight
-direction follow equal number binning as shown in Figure \ref{fig-bestpz}.
+direction follow equal number binning as shown in Figure \ref{fig_bestpz}.
 
@@
 column vectors are highly correlated even in the absence of photometric
-redshift uncertainties because, as shown in Figure \ref{fig-corlensKer}, the
+redshift uncertainties because, as shown in Figure \ref{fig_corlensKer}, the
 lensing kernels for lenses at different redshifts are highly correlated.
@@
 sight direction even in the absence of noise on shear measurements.  Figure
-\ref{fig-lassoVsadaLasso} shows the reconstructions of a single halo's mass map
+\ref{fig_lassoVsadaLasso} shows the reconstructions of a single halo's mass map
 with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$.
 The noises on shear measurements are not included in the simulation.  The left
-panel of Figure \ref{fig-lassoVsadaLasso} is the reconstruction with the lasso
+panel of Figure \ref{fig_lassoVsadaLasso} is the reconstruction with the lasso
 algorithm, which shows a significant smear along the line of sight.
@@
  \centering
- \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
+ \includegraphics[width=0.5\textwidth]{peak_histograms.pdf}
  \caption{The histograms of detected peak values from all of the simulations.
@@
      results of reconstructions from pure noise fields.
-    }\label{fig-peakHist}
- \includegraphics[width=0.45\textwidth]{detfalse_threshold.pdf}
- \caption{Number of detections for true peaks (solid lines) and false
-     peaks (dashed lines) as functions of selection thresholds.
-     The lines with different colors are the results of reconstructions
-     with the NFW dictionary penalized with different regularization
-     parameters: $\lambda=3.5,4.0,5.0$.
-    }\label{fig-detfalse_threshold}
+    }\label{fig_peakHist}
 \end{figure}
@@
     and upper boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively.
-        } \label{fig-NFWvsPM}
+        } \label{fig_NFWvsPM}
 \end{figure*}
@@
 HSC-like shape estimation error on galaxy level is shown in Figure
-\ref{fig-noiseHistogram}.  The corresponding histogram of the shape error on
+\ref{fig_noiseHistogram}.  The corresponding histogram of the shape error on
 the pixel level after smoothing and pixelization is also shown in
-\ref{fig-noiseHistogram}, and the standard deviation map of the noise is
-demonstrated in Figure \ref{fig-noistdmap}.  \citep{HSC1-photoz}.
+\ref{fig_noiseHistogram}, and the standard deviation map of the noise is
+demonstrated in Figure \ref{fig_noistdmap}.  \citep{HSC1-photoz}.
 
@@
  \centering
- \includegraphics[width=0.95\textwidth]{detfalseRate_f1-1.pdf}
- \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
+ \includegraphics[width=1.0\textwidth]{detfalseRate_f1-1.pdf}
+ \includegraphics[width=1.0\textwidth]{detfalseRate_f1-3.pdf}
  \caption{The upper panels show the halo detection rate and the number of false
@@
      upper panels.  The lower panels show the results for $\lambda=5.0$.
-        }\label{fig-detFalsRatePM}
+        }\label{fig_detFalsRatePM}
 \end{figure*}
@@
 peak positions from the input halos' positions is shown in the left panel of
-Figure \ref{fig-detoffsets}.
+Figure \ref{fig_detoffsets}.
 
@@
 (in the pixel unit), and if the closest peak lay inside the region denoted with
-the dashed box in the left panel of Figure \ref{fig-detoffsets}, we take it as
+the dashed box in the left panel of Figure \ref{fig_detoffsets}, we take it as
 a true peak detection of the input halo. Other detected peaks, which include both
 positive and negative peaks, are taken as false peaks. The right
-panel of Figure \ref{fig-detoffsets} shows the average redshift of true
+panel of Figure \ref{fig_detoffsets} shows the average redshift of true
 detections for each halo. The estimated redshifts are lower than the true
@@
 
-Figure \ref{fig-detFalsRateNFW} shows the detection rate (left panels) and the
+Figure \ref{fig_detFalsRateNFW} shows the detection rate (left panels) and the
 number of false peaks per square degree (right panel) for each simulated halo.
@@
 
-Figure \ref{fig-peakHist} shows the histograms, which are normalized by the
+Figure \ref{fig_peakHist} shows the histograms, which are normalized by the
 number of simulations, for all detected peaks with different penalization
@@
 pure noise fields for comparison. From the left panels of Figure
-\ref{fig-NFWvsPM}, which show the $3$-D density maps reconstructed with
+\ref{fig_NFWvsPM}, which show the $3$-D density maps reconstructed with
 different penalization parameters for a halo with $M_{200}=10^{15.02}
@@
 
-We note that when detecting galaxy clusters from the weak lensing mass maps in
-real observations\citep{HSC1-massMap-cluster}, peaks greater than an ad-hoc
-threshold is chosen as galaxy cluster candidates to suppress the number of
-false detection. Figure \ref{fig-detfalse_threshold} shows the numbers of true
-detections and false detections as functions of detection thresholds.
-
 \subsection{Point mass atoms}
 \label{subsec:test-pm}
+
+\begin{figure*}
+ \includegraphics[width=1.0\textwidth]{detfalse_threshold.pdf}
+ \caption{The left panel and the middle panel show the halo detection rates
+     with different input masses and redshifts. The detections are performed on
+     the mass maps reconstructed with $\lambda=5.0$, and the detection
+     thresholds are set to $1.5\sigma$ and $3.0\sigma$ of the peak's standard
+     deviation of the noise field, respectively. The right panel shows the
+     numbers of false peaks per square degree as a function of selection
+     thresholds. The corresponding false peaks per square degree for thresholds
+     of $1.5\sigma$ and $3.0\sigma$ are about $0.022~\rm{deg}^{-2}$ and
+     $0.004~\rm{deg}^{-2}$.
+    }\label{fig_detfalse_threshold}
+\end{figure*}
 
@@
 
-Figure \ref{fig-detFalsRatePM} shows the detection rate (left panels) and the
+Figure \ref{fig_detFalsRatePM} shows the detection rate (left panels) and the
 number of false peaks per square degree (right panel) for each setup of halo
@@
 $\lambda=3.5$ (upper panel) and $\lambda=5.0$ (lower panel). The right panels
-of Figure \ref{fig-NFWvsPM} show the $3$-D density maps reconstructed with
+of Figure \ref{fig_NFWvsPM} show the $3$-D density maps reconstructed with
 different penalization parameters for a halo with $M_{200}=10^{15.02}
@@
 
-As demonstrated in the right panels of Figure \ref{fig-NFWvsPM}, the mass
+As demonstrated in the right panels of Figure \ref{fig_NFWvsPM}, the mass
 reconstructions with the point mass dictionary tend to assign masses to
@@
 sparsely distributes in the $3$-D space, the density field is reconstructed
-using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}.
-
-The method is tested with realistic simulations using HSC-like shape estimation
-error and HSC-like photo-$z$ uncertainty. The results are summarized as follows:
+using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}. The method is
+tested with realistic simulations using HSC-like shape estimation error and
+HSC-like photo-$z$ uncertainty.
+
+We will apply the method to the shear measurements of the HSC survey
+\citep{HSC1-catalog,FPFSHSC1-Li2020} to perform galaxy cluster detection in our
+future work.  Here, we note that, when detecting galaxy clusters from the weak
+lensing mass maps in real observations \citep{HSC1-massMap-cluster}, peaks
+higher than an ad-hoc threshold is chosen as galaxy cluster candidates to
+suppress the number of false detections. The threshold is set to a few times
+the peak's standard deviation of the noise field (shear estimation error
+field). We use different detection thresholds to detect peaks from the mass
+maps reconstructed with $\lambda=5.0$. The left and middle panels of Figure
+\ref{fig_detfalse_threshold} show the detection rates for halos with different
+mass and redshift with detection thresholds set to $1.5\sigma$ and $3.0\sigma$
+of the noise field, respectively. The right panel of Figure
+\ref{fig_detfalse_threshold} shows the numbers of false detections as a
+function of detection thresholds.
+
+The findings of this paper are summarized as follows:
 \begin{enumerate}
- \item The solution of the lasso algorithm suffers from a smear of structure in
+ \item The lasso algorithm's solution suffers from a smear of structure in
      the line of sight direction even in the absence of shape noise, and the
@@
      structure.
- \item The algorithm is able to detect halo with minimal mass
-     limits of $10^{13.5} M_{\odot}/h$, $10^{14.3} M_{\odot}/h$, $10^{15.0}
-     M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high
-     ($0.6\leq z< 0.9$) redshifts, respectively.
- \item The estimated redshift
-     of the halos detected from the reconstructed mass maps are lower than the
-     true redshift by about $0.03$ for halos at low redshifts ($z\leq 0.4$).
-     The relative redshift bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$.
+ \item The algorithm is able to detect halo with minimal mass limits of
+     $10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$
+     for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z<
+     0.85$) redshifts, respectively, with a false detection of 0.022/deg$^2$.
+ \item The estimated redshifts of the halos detected from the reconstructed mass
+     maps are lower than the true redshift by about $0.03$ for halos at low
+     redshifts ($z\leq 0.4$).  The relative redshift bias is below $0.5\%$ for
+     halos at $0.4<z\leq 0.85$.
 \end{enumerate}
-
-We will apply the method to the shear measurements of the HSC survey
-\citep{HSC1-catalog,FPFSHSC1-Li2020} to perform galaxy cluster detection in our
-future work.
 

### 2020-12-02 demo/makeNoiseCat.py
more noise catalogs

@@ -6,12 +6,15 @@ import numpy as np
 import astropy.table as astTab
 import astropy.io.fits as pyfits
 
-datDir  =   "/work/xiangchong.li/work/S16ACatalogs/"
+if False:
+    #GW
+    datDir  =   "/work/xiangchong.li/work/S16ACatalogs/"
+else:
+    #sshfsGW
+    datDir  =   "/home/xiangchong/work/gw_ipmu/work/S16ACatalogs/"
 tn      =   '9347.fits'
 
 def rotCatalog(e1, e2, phi=None):
-    if phi  ==  None:
-        phi = 2.0 * np.pi * np.random.rand(len(e1))
     cs      =   np.cos(phi)
     ss      =   np.sin(phi)
     e1_rot  =   e1 * cs + e2 * ss
@@ -72,7 +75,7 @@ def main():
     cdf     =   np.empty(shape=(nobj, nbin), dtype=float)
     np.cumsum(pdata, axis=1, out=cdf)
 
-    mRange  =   range(100,1000)
+    mRange  =   range(1000,2500)
     names   =   ('raH','decH','raR','decR','g1n','g2n','zbest','ztrue')
 
     for imock in mRange:
@@ -84,7 +87,8 @@ def main():
         r           =   np.random.random(size=nobj)
         for i in range(nobj):
             tzmc[i] =   np.interp(r[i], cdf[i], poz_bins)
-        g1n,g2n     =   rotCatalog(g1,g2)
+        phi = 2.0 * np.pi * np.random.rand(nobj)
+        g1n,g2n     =   rotCatalog(g1,g2,phi)
         tableMock['raH']    =   ra
         tableMock['decH']   =   dec
         tableMock['raR']    =   raR
@@ -96,6 +100,7 @@ def main():
         tableMock.write('HSC-obs/20200328/cats/sim%d.fits' %imock,overwrite=True)
         del tableMock
         del g1n,g2n
+        del phi
         del tzmc
         gc.collect()
     return

### 2020-12-02 demo/haloSimStamp.py
pure noise map on point mass reconstructions

@@ -71,7 +71,7 @@ class haloSimStampRunner(TaskRunner):
     def getTargetList(parsedCmd, **kwargs):
         # number of halos
         #idRange=range(64)
-        idRange=[10000000]
+        idRange=[640000]
         return [(ref, kwargs) for ref in idRange]
 
 def unpickle(factory, args, kwargs):
@@ -105,18 +105,20 @@ class haloSimStampBatchTask(BatchPoolTask):
             ss  =   pyascii.read(self.config.haloName)[Id]
             iz  =   ss['iz']
             im  =   ss['im']
+            nsim=   100
             self.pixelize_Sigma(ss)
         else:
             # Noise field
             ss  =   None
             iz  =   800
             im  =   800
+            nsim=   1000
         pool.storeSet(ss=ss)
         outDirH =   os.path.join(self.config.outDir,'halo%d%d'%(iz,im))
         if not os.path.isdir(outDirH):
             os.mkdir(outDirH)
         pool.storeSet(outDirH=outDirH)
-        pool.map(self.process,range(100,1000))
+        pool.map(self.process,range(nsim))
         return
 
     def pixelize_Sigma(self,ss):

### 2020-12-02 demo/massMapStamp.py

@@ -48,7 +48,7 @@ class massMapStampBatchConfig(pexConfig.Config):
                 default='planck-cosmo/config-pix96-nl20.ini',
                 doc = 'configuration file name')
     outDir  =   pexConfig.Field(dtype=str,
-                default='planck-cosmo/sparse-f3-3-2/',
+                default='planck-cosmo/sparse-f1-3-2/',
                 doc = 'output directory')
     pixDir  =   pexConfig.Field(dtype=str,
                 default='planck-cosmo/pix96-ns10/',
@@ -70,7 +70,7 @@ class massMapStampRunner(TaskRunner):
     def getTargetList(parsedCmd, **kwargs):
         # number of halos
         #idRange=range(64)
-        idRange=[10000000]
+        idRange=[640000]
         return [(ref, kwargs) for ref in idRange]
 
 def unpickle(factory, args, kwargs):
@@ -99,22 +99,24 @@ class massMapStampBatchTask(BatchPoolTask):
         pool.storeSet(haloName=self.config.haloName)
         pool.storeSet(configName=self.config.configName)
         pool.storeSet(pixDir=self.config.pixDir)
-        if Id<5e4:
+        if Id<640000:
             # halo field
             ss  =   pyascii.read(self.config.haloName)[Id]
             iz  =   ss['iz']
             im  =   ss['im']
+            nsim=   100
         else:
             # Noise field
             ss  =   None
-            iz  =   800
-            im  =   800
+            iz  =   int(Id//800)
+            im  =   int(Id%800)
+            nsim=   1000
         pool.storeSet(ss=ss)
         outDirH =   os.path.join(self.config.outDir,'halo%d%d'%(iz,im))
         if not os.path.isdir(outDirH):
             os.mkdir(outDirH)
         pool.storeSet(outDirH=outDirH)
-        resList =   pool.map(self.process,range(1000))
+        resList =   pool.map(self.process,range(nsim))
         resList =   [x for x in resList if x is not None]
 
         # peak catalogs list
@@ -234,20 +236,25 @@ class massMapStampBatchTask(BatchPoolTask):
         sigmafname  =   os.path.join(cache.pixDir,'pixStd.fits')
         lkfname     =   'planck-cosmo/lensing_kernel-pz-nl20.fits'
 
+        nframe      =   1
+        if nframe==1:
+            rs_base=0.
+        else:
+            rs_base=0.12
[…]

### 2020-12-02 python/halolet.py

@@ -109,6 +109,8 @@ class nfwShearlet2D():
         for izl in range(self.nzl):
             rz      =   self.rs_base/self.cosmo.Dc(0.,self.zlBin[izl])*60.*180./np.pi
             for ifr in range(self.nframe)[::-1]:
+                # For each lens redshfit bins, we begin from the
+                # frame with largest angular scale radius
                 rs  =   (ifr+1)*rz
                 if rs<self.resolve_lim:
                     self.rs_frame[izl,ifr]=0.

### 2020-12-03 demo/massMapStamp.py
reorganizing

@@ -69,8 +69,8 @@ class massMapStampRunner(TaskRunner):
     @staticmethod
     def getTargetList(parsedCmd, **kwargs):
         # number of halos
-        #idRange=range(64)
-        idRange=[640000]
+        idRange=range(64)
+        #idRange=[640000]
         return [(ref, kwargs) for ref in idRange]
 
 def unpickle(factory, args, kwargs):
@@ -83,7 +83,7 @@ class massMapStampBatchTask(BatchPoolTask):
     _DefaultName = "massMapStampBatch"
     def __reduce__(self):
         """Pickler"""
-        return unpickle, (self.__class__, [], dict(config=self.config, name=self._name,
+        return unpickle, (self.__class__,[],dict(config=self.config, name=self._name,
                 parentTask=self._parentTask, log=self.log))
     def __init__(self,**kwargs):
         BatchPoolTask.__init__(self, **kwargs)
@@ -109,7 +109,7 @@ class massMapStampBatchTask(BatchPoolTask):
             # Noise field
             ss  =   None
             iz  =   int(Id//800)
-            im  =   int(Id%800)
+            im  =   800
             nsim=   1000
         pool.storeSet(ss=ss)
         outDirH =   os.path.join(self.config.outDir,'halo%d%d'%(iz,im))

### 2020-12-03 notebook/nfw_halo.py

@@ -1,471 +1,0 @@
-# Copyright (c) 2012-2018 by the GalSim developers team on GitHub
-# https://github.com/GalSim-developers
-#
-# This file is part of GalSim: The modular galaxy image simulation toolkit.
-# https://github.com/GalSim-developers/GalSim
-#
-# GalSim is free software: redistribution and use in source and binary forms,
-# with or without modification, are permitted provided that the following
-# conditions are met:
-#
-# 1. Redistributions of source code must retain the above copyright notice, this
-#    list of conditions, and the disclaimer given in the accompanying LICENSE
-#    file.
-# 2. Redistributions in binary form must reproduce the above copyright notice,
-#    this list of conditions, and the disclaimer given in the documentation
-#    and/or other materials provided with the distribution.
-#
-"""@file nfw_halo.py The "lensing engine" for drawing shears from an NFW halo.
-"""
-
-import numpy as np
-
-from .position import PositionD
-from .angle import arcsec
-from . import integ
-from . import utilities
-from .errors import GalSimRangeError, GalSimIncompatibleValuesError
-
-class Cosmology(object):
-    """Basic cosmology calculations.
-
-    Cosmology calculates expansion function E(a) and angular diameter distances Da(z) for a
-    LambdaCDM universe.  Radiation is assumed to be zero and Dark Energy constant with w = -1 (no
-    quintessence), but curvature is arbitrary.
-
-    Based on Matthias Bartelmann's libastro.
-
-    @param omega_m      Present day energy density of matter relative to critical density.
-                        [default: 0.3]
-    @param omega_lam    Present day density of Dark Energy relative to critical density.
-                        [default: 0.7]
-    """
-    def __init__(self, omega_m=0.3, omega_lam=0.7):
-        # no quintessence, no radiation in this universe!
-        self.omega_m = omega_m
-        self.omega_lam = omega_lam
-        self.omega_c = (1. - omega_m - omega_lam)
-        #self.omega_r = 0
-
-    def __repr__(self):
-        return "galsim.Cosmology(omega_m=%r, omega_lam=%r)"%(self.omega_m, self.omega_lam)
-    def __str__(self):
[…]

### 2020-12-05 doc/paper_ms_method_HSCY1/massmap_sim.tex
detection as function of threshold and lambda 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd35.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd40.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd50.pdf separate tex file into sub tex files 	modified:   doc/paper_ms_method_HSCY1/ms.tex 	new file:   doc/paper_ms_method_HSCY1/massmap_sim.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_NFW_results.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex peak histograms(normalized) and fit noises' peak histograms to Gaussia

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{shapeMeasurementError-HSCY1.pdf}
 \caption{The solid lines show the histograms of the HSC-like shape measurement
     error (including both from shape noise and photon noise) on the first
     component of shear ($g_1$) for galaxies (blue lines) and smoothed pixels
     (orange lines). The dashed lines are the best-fit Gaussian distributions
     to the corresponding histograms.
    }
 \label{fig_noiseHistogram}
\end{figure}

The $\Lambda$CDM cosmology used in this paper is from the best-fit result of
the final full-mission Planck observation of the cosmic microwave background
(CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$,
$\Omega_\Lambda=0.685$ \citep{cmb-Planck2018-Cosmology}.

We sample halos in a two-dimensional redshift-mass plane. The redshift-mass
plane is evenly divided into eight redshift bins and eight mass bins. We
randomly shift the input halo redshifts and halo masses from the bins' centers
by a small amount. The concentration of the NFW halo is set as a function of
the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
\citet{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}
The weak-lensing shear fields of these NFW halos are simulated according to
\citet{haloModel-TJ2003-3pt}. The shear distortions are applied to one hundred
realizations of galaxy catalogs with the HSC-like shape measurement error and
photo-$z$ uncertainty.

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{noise_std_map_pix.pdf}
 \caption{The standard deviation pixel map of the HSC-like shape measurement
     error for the fifth source galaxy bin ($0.69 \leq z < 0.80 $).
        } \label{fig_noistdmap}
\end{figure}

The mock galaxy catalogs are generated using the HSC S16A shape catalog
\citep{HSC1-catalog}.  We use the galaxies in a one square degree region at the
center of tract 9347 \citep{HSC1-data}.  The galaxies' positions are randomized
to distribute homogeneously  in the one-square degree stamp statistically. We
randomly assign its redshift for each galaxy following the MLZ photo-$z$
probability distribution function \citep{HSC1-photoz}.

By randomly rotating the galaxies in the shape catalog, we simulate the
HSC-like shape estimation errors with different realizations.  The histogram of
the first component of the HSC-like shape estimation error on galaxy level is
shown in Figure \ref{fig_noiseHistogram}.  The corresponding histogram of the
shape measurement error on the pixel level after the smoothing and pixelization is
also shown in \ref{fig_noiseHistogram}. The standard deviation map of the
noise is demonstrated in Figure \ref{fig_noistdmap}. As demonstrated in Figure
\ref{fig_noiseHistogram}, even though the shape measurement error on the galaxy
level does not fully follow Gaussian distribution, the error is well described
by Gaussian distribution after the smoothing and pixelization.

### 2020-12-05 doc/paper_ms_method_HSCY1/ms.tex
detection as function of threshold and lambda 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd35.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd40.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd50.pdf separate tex file into sub tex files 	modified:   doc/paper_ms_method_HSCY1/ms.tex 	new file:   doc/paper_ms_method_HSCY1/massmap_sim.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_NFW_results.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex peak histograms(normalized) and fit noises' peak histograms to Gaussia

@@
 This paper is organized as follows.
-In Section \ref{sec:Method}, we propose the new method for $3$-D density map
+In Section \ref{sec_Method}, we propose the new method for $3$-D density map
 reconstruction.
-In Section \ref{sec:Test}, we test the novel algorithm on HSC-like simulations.
-In Section \ref{sec:Sum}, we summarize and discuss the future development of
+In Section \ref{sec_Test}, we test the novel algorithm on HSC-like simulations.
+In Section \ref{sec_Sum}, we summarize and discuss the future development of
 the method.
@@
 \section{Methodology}
-\label{sec:Method}
-
-\begin{figure}[!t]
+\label{sec_Method}
+
+\begin{figure}
  \centering
@@
 
-We first review the lensing process in section \ref{subsec:method-delta2shear}.
+We first review the lensing process in Section \ref{subsec_method_delta2shear}.
 Then, we introduce the dictionary used to model the foreground density maps in
-section \ref{subsec:method-dictionary}.
-
-Subsequently, in section \ref{subsec:method-Systematics}, we discuss several
+Section \ref{subsec_method_dictionary}.
+
+Subsequently, in Section \ref{subsec_method_Systematics}, we discuss several
 systematic effects from observations which include photo-$z$ uncertainty
-(section \ref{subsec:method-photoz}), smoothing (section
-\ref{subsec:method-smoothing}), masking(section \ref{subsec:method-msknoise}),
-and pixelization (section \ref{subsec:method-pixel}).
-
-Finally, we solve the mass reconstruction problem in section
-\ref{subsec:method-reconstruction} using the adaptive lasso algorithm
+(Section \ref{subsec_method_photoz}), smoothing (Section
+\ref{subsec_method_smoothing}), masking(Section \ref{subsec_method_msknoise}),
+and pixelization (Section \ref{subsec_method_pixel}).
+
+Finally, we solve the mass reconstruction problem in Section
+\ref{subsec_method_reconstruction} using the adaptive lasso algorithm
 \citep{AdaLASSO-Zou2006} optimized with the FISTA algorithm
@@
 \subsection{Lensing}
-\label{subsec:method-delta2shear}
-
-\begin{figure}[!t]
+\label{subsec_method_delta2shear}
+
+\begin{figure}
  \centering
@@
 from observations. The systematic errors will be discussed in Section
-\ref{subsec:method-Systematics}.
+\ref{subsec_method_Systematics}.
 
@@
 \subsection{Dictionary}
-\label{subsec:method-dictionary}
-
-\begin{figure*}[!t]
+\label{subsec_method_dictionary}
+
+The density contrast field is modeled as a summation of basis atoms in the
+dictionary:
+\begin{equation}\label{eq-x2delta}
+\delta(\vec{r}) = \sum_{s=1}^{N} \int d^3 r' \phi_s(\vec{r}-\vec{r'}) x_s(\vec{r'}),
+\end{equation}
+where $\phi_s(\vec{r})$ are the basis atoms of the dictionary. The basis atoms
+have `$N$' different scale frames, and the atoms in each scale frame are
+shifted by $\vec{r'}$ to form models at different spatial positions.
+$x_s(\vec{r'})$ is the projection coefficients of the density contrast field
+onto the basis atoms.
+
+We propose to use the multi-scale NFW atoms, denoted as
+$\{\phi_1,...,\phi_N\}$, as the basis atoms of our dictionary.  On the
+transverse plane, the NFW atoms follow surface density profiles of the NFW
+halos \citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and
+truncation radius $c \theta_\alpha$ , where $c$ is the concentration of the NFW
+halos.  As the scales of halos are much smaller than the reachable redshift
+resolution, we neglect the depth of halo on the line of sight direction and set
+the NFW atoms' profiles in the line of sight direction to $1$-D Dirac delta
+functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. The
+multi-scale NFW atoms are defined as
+\begin{equation}
+\begin{split}
+\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 }
+F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
+&  (s=1..N)
+\end{split}
+\end{equation}
+where
+\begin{equation}
+F(x)=
+\begin{cases}
+-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccosh
+\left(\frac{x^2+c}{x(1+c)}\right)}{(1-x^2)^{3/2}}  & (x<1),\\
+\frac{\sqrt{c^2-1}}{3(1+c)} (1+\frac{1}{c+1}) & (x=1),\\
+-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} +
+\frac{\arccos\left(\frac{x^2+c}{x(1+c)}\right)}{(x^2-1)^{3/2}} & (1<x\leq c),\\
+0& (x>c).
+\end{cases}
+\end{equation}
+$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for the NFW atoms in
+different scale frames.
+
+To simplify the notation, we compress the projection coefficients into a column
+vector:
+$x=\begin{pmatrix}
+x_{0}\\
+x_{1}\\
+...\\
+x_{N}
+\end{pmatrix}$,
+and compress the dictionary transform operator to a row vector:
+\begin{equation}
+\mathbf{\Phi}=\begin{pmatrix}
+\int d^3r\phi_0(\vec{r}) ~\int d^3r \phi_1(\vec{r})~ ...~\int d^3r \phi_{N}(\vec{r})
+\end{pmatrix}.
+\end{equation}
+We substitute eq. (\ref{eq-x2delta}) into eq.(\ref{eq-delta2gammat}) and get
+\begin{equation}\label{eq-x2gammat}
+\gamma_L=\mathbf{Q}\mathbf{\Phi} x.
+\end{equation}
+
+In this paper, a dictionary constructed with point mass atoms is used to
+compare with the dictionary of multi-scale atoms.  The point mass atoms is a
+$3$-D Dirac function defined as follows
+\begin{equation}
+\phi_{\rm{PM}}(\vec{r})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
+\end{equation}
+
+The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the
+transverse plane are shown in Figure \ref{fig_atoms2D}. The $1$-D slices of the
+profiles are demonstrated in Figure \ref{fig_atoms1D}. Note that these profiles
+are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The
+smoothing operation is discussed in Section \ref{subsec_method_smoothing}, and
+the pixelization operation is discussed in Section \ref{subsec_method_pixel}.
+
+\subsection{Systematics}
+\label{subsec_method_Systematics}
+
+The observed shear measurements are deviated from the physical shear prediction
+due to the systematic errors from observations. The influence of systematics is
+carefully studied and incorporated into the forward modeling in this Section.
+
+\subsubsection{Photo-$z$ Uncertainty}
+\label{subsec_method_photoz}
+
+\begin{figure*}
 \centering
@@
 \end{figure*}
-
-The density contrast field is modeled as a summation of basis atoms in the
-dictionary:
-\begin{equation}\label{eq-x2delta}
-\delta(\vec{r}) = \sum_{s=1}^{N} \int d^3 r' \phi_s(\vec{r}-\vec{r'}) x_s(\vec{r'}),
-\end{equation}
-where $\phi_s(\vec{r})$ are the basis atoms of the dictionary. The basis atoms
-have `$N$' different scale frames, and the atoms in each scale frame are
-shifted by $\vec{r'}$ to form models at different spatial positions.
-$x_s(\vec{r'})$ is the projection coefficients of the density contrast field
-onto the basis atoms.
-
-We propose to use the multi-scale NFW atoms, denoted as
-$\{\phi_1,...,\phi_N\}$, as the basis atoms of our dictionary.  On the
-transverse plane, the NFW atoms follow surface density profiles of the NFW
-halos \citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and
-truncation radius $c \theta_\alpha$ , where $c$ is the concentration of the NFW
-halos.  As the scales of halos are much smaller than the reachable redshift
-resolution, we neglect the depth of halo on the line of sight direction and set
-the NFW atoms' profiles in the line of sight direction to $1$-D Dirac delta
-functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. The
-multi-scale NFW atoms are defined as
-\begin{equation}
-\begin{split}
-\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 }
-F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
-&  (s=1..N)
-\end{split}
-\end{equation}
-where
-\begin{equation}
-F(x)=
-\begin{cases}
--\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccosh
-\left(\frac{x^2+c}{x(1+c)}\right)}{(1-x^2)^{3/2}}  & (x<1),\\
-\frac{\sqrt{c^2-1}}{3(1+c)} (1+\frac{1}{c+1}) & (x=1),\\
--\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} +
-\frac{\arccos\left(\frac{x^2+c}{x(1+c)}\right)}{(x^2-1)^{3/2}} & (1<x\leq c),\\
-0& (x>c).
-\end{cases}
-\end{equation}
-$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for the NFW atoms in
-different scale frames.
-
-To simplify the notation, we compress the projection coefficients into a column
-vector:
-$x=\begin{pmatrix}
-x_{0}\\
-x_{1}\\
-...\\
-x_{N}
-\end{pmatrix}$,
-and compress the dictionary transform operator to a row vector:
-\begin{equation}
-\mathbf{\Phi}=\begin{pmatrix}
-\int d^3r\phi_0(\vec{r}) ~\int d^3r \phi_1(\vec{r})~ ...~\int d^3r \phi_{N}(\vec{r})
-\end{pmatrix}.
-\end{equation}
-We substitute eq. (\ref{eq-x2delta}) into eq.(\ref{eq-delta2gammat}) and get
-\begin{equation}\label{eq-x2gammat}
-\gamma_L=\mathbf{Q}\mathbf{\Phi} x.
-\end{equation}
-
-In this paper, a dictionary constructed with point mass atoms is used to
-compare with the dictionary of multi-scale atoms.  The point mass atoms is a
-$3$-D Dirac function defined as follows
-\begin{equation}
-\phi_{\rm{PM}}(\vec{r})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
-\end{equation}
-
-The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the
-transverse plane are shown in Figure \ref{fig_atoms2D}. The $1$-D slices of the
-profiles are demonstrated in Figure \ref{fig_atoms1D}. Note that these profiles
-are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The
-smoothing operation is discussed in Section \ref{subsec:method-smoothing}, and
-the pixelization operation is discussed in Section \ref{subsec:method-pixel}.
-
-\subsection{Systematics}
-\label{subsec:method-Systematics}
-
-The observed shear measurements are deviated from the physical shear prediction
-due to the systematic errors from observations. The influence of systematics is
-carefully studied and incorporated into the forward modeling in this section.
-
-\subsubsection{Photo-$z$ Uncertainty}
-\label{subsec:method-photoz}
 
@@
 \subsubsection{Smoothing}
-\label{subsec:method-smoothing}
-
-\begin{figure}[!t]
- \centering
- \includegraphics[width=0.5\textwidth]{shapeMeasurementError-HSCY1.pdf}
- \caption{The histograms of the HSC-like shape measurement error (including
-         both from shape noise and from photon noise) on the first component of
-         shear ($g_1$) for galaxies (blue lines) and smoothed pixels (orange
-         lines). The solid steps are the sampled histograms, and the dashed
-         lines are the normalized Gaussian distributions that have the same
-         standard deviations as the corresponding histograms.
-        }
- \label{fig_noiseHistogram}
-\end{figure}
+\label{subsec_method_smoothing}
 
@@
 
-As we will discuss in Section \ref{subsec:method-pixel}, the smoothed shear
+As we will discuss in Section \ref{subsec_method_pixel}, the smoothed shear
 field is pixelized into equally spaced grids. We note that another widely used
@@
 
-\begin{figure}[!t]
- \centering
- \includegraphics[width=0.5\textwidth]{noise_std_map_pix.pdf}
- \caption{The standard deviation pixel map of the HSC-like shape measurement error for the fifth source galaxy bin
-        ($0.69 \leq z < 0.80 $).
-        } \label{fig_noistdmap}
-\end{figure}
-
 \subsubsection{Masking}
-\label{subsec:method-msknoise}
-
-\begin{figure*}[!t]
- \centering
- \includegraphics[width=1.0\textwidth]{peak_scatters_f3-1.pdf}
- \caption{The left panel shows the stacked $2$-D distribution of the deviations
-     of detected peak positions from the centers of the corresponding input
-     halos. The $x$-axis is for the deviated distance in the transverse plane,
-     and the $y$-axis is for the deviation of the redshift. For each
-     simulation, the positive peak inside the dashed black box with the
-     minimal offset (in the pixel unit) from the input halo's position is
-     taken as a true detection. The right panel focuses on the deviation of
-     detected peaks in the line of sight direction. The $x$-axis is the input
-     halo redshifts, and the $y$-axis is the redshift of the detected peak. The
-     `$\cross$' denotes the average redshift of detected peaks for each halo
-     over different noise realizations, and the error-bars are the
-     uncertainties of the average redshifts. The deep gray area is for the
-     relative redshift bias less than $0.05$, and the light gray area is for
-     the relative redshift bias less than $0.5$. These results in this figure
-     are based on the NFW dictionary with $\lambda=3.5$.
-     } \label{fig_detoffsets}
-\end{figure*}
+\label{subsec_method_msknoise}
 
@@
 \subsubsection{Pixelization}
-\label{subsec:method-pixel}
-
-\begin{figure*}[!t]
- \centering
- \includegraphics[width=1.0\textwidth]{detfalseRate_f3-1.pdf}
- \includegraphics[width=1.0\textwidth]{detfalseRate_f3-3.pdf}
- \caption{The upper panels show the halo detection rate and the number of false
-     peaks per square degree for mass map reconstructed with the NFW atoms. The
-     penalization parameter is set to $\lambda=3.5$ for the upper panels.  The
-     low panels show the results for $\lambda=5.0$.
-        } \label{fig_detFalsRateNFW}
-\end{figure*}
+\label{subsec_method_pixel}
 
@@
 \subsection{Density map reconstruction}
-\label{subsec:method-reconstruction}
+\label{subsec_method_reconstruction}
 
@@
 \subsubsection{FISTA}
-
-\begin{figure}[!t]
- \centering
- \includegraphics[width=0.5\textwidth]{peak_histograms.pdf}
- \caption{The histograms of detected peak values from all of the simulations.
-     The solid lines with different colors are the results of reconstructions
-     with the NFW dictionary penalized with different regularization
-     parameters: $\lambda=3.5,4.0,5.0$. The dashed lines are the corresponding
-     results of reconstructions from pure noise fields.
-    }\label{fig_peakHist}
-\end{figure}
 
@@
 \section{Tests}
-\label{sec:Test}
-
-\begin{figure*}[!t]
+\label{sec_Test}
+
+This Section simulates weak-lensing shear fields induced by a group of NFW
+halos with various halo masses and redshifts. The shear fields are used to
+distort the HSC mock shape catalogs with different realizations of the HSC-like
+shape measurement errors and photo-$z$ uncertainties (Section \ref{subsec_Sims}).
+
+Then, we test our algorithm using the simulations with different setups of the
+regularization parameter. We also compare the results of our algorithm, which
+uses the NFW dictionary (Section \ref{subsec_test-nfw}), with the point mass
+dictionary (Section \ref{subsec_test-pm}).
+
+\subsection{Simulations}
+\label{subsec_Sims}
+\input{massmap_sim.tex}
+
+\subsection{NFW atoms}
+\label{subsec_test-nfw}
+\input{sparse_NFW_results.tex}
+
+\subsection{Point mass atoms}
+\label{subsec_test-pm}
+\input{sparse_PointMass_results.tex}
+
+\begin{figure*}
 \centering
@@
 
-This section simulates weak-lensing shear fields induced by a group of halos
-with various halo masses and redshifts. The shear fields are used to distort
-the HSC mock shape catalogs with different realizations of the HSC-like shape
-measurement error and photo-$z$ uncertainty (Section \ref{subsec:Sims}).
-
-Then, we test our algorithm using the simulations with different setups of the
-regularization parameter. We also compare the results of our algorithm, which
-uses the NFW dictionary (Section \ref{subsec:test-nfw}), with the point mass
-dictionary (Section \ref{subsec:test-pm}).
-
-The $\Lambda$CDM cosmology used for the simulations is from the best fitting
-result of the final full-mission Planck observation of the cosmic microwave
-background (CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$,
-$\Omega_\Lambda=0.685$ \citep{cmb-Planck2018-Cosmology}.
-
-\subsection{Simulations}
-\label{subsec:Sims}
-
-We sample halos in a two-dimensional redshift-mass plane. The redshift-mass
-plane is evenly divided into eight redshift bins and eight mass bins. We
-randomly shift the input halo redshifts and halo masses from the bins' centers
-by a small amount. The concentration of the NFW halo is set as a function of
-the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
-\citet{c-M_Magneticum-Ragagnin2019}
-\begin{equation}
-c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
-\end{equation}
-The weak-lensing shear fields of these NFW halos are simulated according to
-\citet{haloModel-TJ2003-3pt}. The shear distortions are applied to one hundred
-realizations of galaxy catalogs with the HSC-like shape measurement error and
-photo-$z$ uncertainty.
-
-The galaxy catalogs are simulated using the HSC S16A shape catalog
-\citep{HSC1-catalog}.  We use galaxies in a one square degree region at the
-center of tract 9347 \citep{HSC1-data}.  The galaxies' positions are randomized
-to have a homogeneous distribution statistically in the one-square
-degree stamp. We randomly assign its redshift for each galaxy following the
-MLZ photo-$z$ probability distribution function from By randomly rotating the
-galaxies in the shape catalog, we simulate the HSC-like shape estimation error
-with different realizations.  The histogram of the first component of the
-HSC-like shape estimation error on galaxy level is shown in Figure
-\ref{fig_noiseHistogram}.  The corresponding histogram of the shape error on
-the pixel level after smoothing and pixelization is also shown in
-\ref{fig_noiseHistogram}, and the standard deviation map of the noise is
-demonstrated in Figure \ref{fig_noistdmap}.  \citep{HSC1-photoz}.
-
-\subsection{NFW atoms}
-\label{subsec:test-nfw}
-
-\begin{figure*}[!ht]
- \centering
- \includegraphics[width=1.0\textwidth]{detfalseRate_f1-1.pdf}
- \includegraphics[width=1.0\textwidth]{detfalseRate_f1-3.pdf}
- \caption{The upper panels show the halo detection rate and the number of false
-     peak per square degree for mass map reconstructed with the point mass
-     dictionary. The penalization paramter is set to $\lambda=3.5$ for the
-     upper panels.  The lower panels show the results for $\lambda=5.0$.
-        }\label{fig_detFalsRatePM}
-\end{figure*}
-
-In this subsection, we test the performance of our algorithm with the default
-setup that models the matter density field with multi-scale NFW atoms. The
-dictionary is constructed with three frames of different NFW comoving scale
-radius: $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc.  The
-truncation radius (concentration) is set to four times the scale radius for the
-atoms in the dictionary.
-
-We test the algorithm with different regularization parameters for the
-preliminary lasso estimation which range from $3.5$ to $5.0$. The
-regularization parameter for the adaptive lasso is set to
-$\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\tau+1}$.
-Here, we note that both the preliminary lasso estimation and the final adaptive
-estimation select the modes with signal to noise ratios (SNRs) greater than
-$\lambda_{\rm{ls}}$ in each iteration. While the final adaptive lasso
-estimation further enhances the growth of the modes with preliminary
-estimations greater than $\lambda_{\rm{ls}}$.
-
-This paper does not go beyond the resolution limit defined by the Gaussian
-smoothing kernel with the scale: $1.\arcmin 5$ and the pixel scale
-that equals $1\arcmin$. We smooth the reconstructed density with the same
-Gaussian kernel in each lens redshift plane.
-
-We detect the peaks on the density map after the reconstruction. The stacked
-$2$-D histogram, from all of the simulations, for the offsets of the detected
-peak positions from the input halos' positions is shown in the left panel of
-Figure \ref{fig_detoffsets}.
-
-For each simulation, we find the positive peak closest to the input position
-(in the pixel unit), and if the closest peak lay inside the region denoted with
-the dashed box in the left panel of Figure \ref{fig_detoffsets}, we take it as
-a true peak detection of the input halo. Other detected peaks, which include both
-positive and negative peaks, are taken as false peaks. The right
-panel of Figure \ref{fig_detoffsets} shows the average redshift of true
-detections for each halo. The estimated redshifts are lower than the true
-redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
-For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.
-
-Figure \ref{fig_detFalsRateNFW} shows the detection rate (left panels) and the
-number of false peaks per square degree (right panel) for each simulated halo.
-The figure include results of different penalization parameters: $\lambda=3.5$
-(upper panel) and $\lambda=5.0$ (lower panel).  We find that with the increase
-of the penalization parameter, the detection rate decreases. On the other hand,
-the number of false peaks also decreases.
-
-Figure \ref{fig_peakHist} shows the histograms, which are normalized by the
-number of simulations, for all detected peaks with different penalization
-parameters. We also plot the corresponding histograms for peaks detected from
-pure noise fields for comparison. From the left panels of Figure
-\ref{fig_NFWvsPM}, which show the $3$-D density maps reconstructed with
-different penalization parameters for a halo with $M_{200}=10^{15.02}
-~h^{-1}M_{\odot}$ at redshift $0.164$ , we also find that the number of false
-peaks significantly decreases as the penalization parameter increases.
-
-\subsection{Point mass atoms}
-\label{subsec:test-pm}
-
-\begin{figure*}
- \includegraphics[width=1.0\textwidth]{detfalse_threshold.pdf}
- \caption{The left panel and the middle panel show the halo detection rates
-     with different input masses and redshifts. The detections are performed on
-     the mass maps reconstructed with $\lambda=5.0$, and the detection
-     thresholds are set to $1.5\sigma$ and $3.0\sigma$ of the peak's standard
-     deviation of the noise field, respectively. The right panel shows the
-     numbers of false peaks per square degree as a function of selection
-     thresholds. The corresponding false peaks per square degree for thresholds
-     of $1.5\sigma$ and $3.0\sigma$ are about $0.022~\rm{deg}^{-2}$ and
-     $0.004~\rm{deg}^{-2}$.
-    }\label{fig_detfalse_threshold}
-\end{figure*}
-
-In this subsection, we show the results for the setup, which substitutes the
-default NFW dictionary with the point mass dictionary, to compare with the
-default setup.  The regularization parameter for the preliminary lasso is set
-to $3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
-propose to incorporate external group information into different adaptive lasso
-penalization weights by setting the penalization weights for projection
-coefficients in the same group to the average of the adaptive weights in this
-group, we smooth the preliminary lasso estimation in each lens redshift bin
-with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc. The smoothed
-preliminary lasso estimation is denoted as $\hat{x}^{\rm{ls}}_{\rm{sm}}$, and
-the penalization weights are set to $1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.
-The regularization parameter for the adaptive lasso is set to
-$\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.
-
-As we have done on the NFW dictionary's reconstruction, we smooth the
-reconstructed density maps with the Gaussian kernel (scale radius equals
-$1.\arcmin 5$) in each lens redshift plane.
-
-Figure \ref{fig_detFalsRatePM} shows the detection rate (left panels) and the
-number of false peaks per square degree (right panel) for each setup of halo
-mass and redshift.
-This figure includes results of different penalization parameters:
-$\lambda=3.5$ (upper panel) and $\lambda=5.0$ (lower panel). The right panels
-of Figure \ref{fig_NFWvsPM} show the $3$-D density maps reconstructed with
-different penalization parameters for a halo with $M_{200}=10^{15.02}
-~h^{-1}M_{\odot}$ at redshift $0.164$.
-Comparing with the results of the NFW dictionary, we find that the number of
-false peaks in the mass map reconstructed with the point mass dictionary is
-much larger than the NFW dictionary.
-
-As demonstrated in the right panels of Figure \ref{fig_NFWvsPM}, the mass
-reconstructions with the point mass dictionary tend to assign masses to
-several different redshift bins in the neighboring region of the halo center.
-While the NFW dictionary produces consistent mass reconstructions.
-Since the NFW atoms' profiles are more consistent with the mass profiles of the
-input halos than the profile of a point mass, there are less false structures
-reconstructed with the NFW dictionary.
-
 \section{Summary}
-\label{sec:Sum}
+\label{sec_Sum}
 

### 2020-12-05 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
detection as function of threshold and lambda 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd35.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd40.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd50.pdf separate tex file into sub tex files 	modified:   doc/paper_ms_method_HSCY1/ms.tex 	new file:   doc/paper_ms_method_HSCY1/massmap_sim.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_NFW_results.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex peak histograms(normalized) and fit noises' peak histograms to Gaussia

\begin{figure*}
 \centering
 \includegraphics[width=1.0\textwidth]{peak_histograms_NFW.pdf}
 \caption{The histograms of detected peak values (normalized) from all of the
     simulations.  The solid red steps are the results from reconstructions
     with the NFW dictionary penalized with different regularization
     parameters: $\lambda=3.5,4.0,5.0$. The dashed blue steps are the
     corresponding results of the reconstructions from $1000$ realizations of
     pure noise fields. The gray lines are the best-fit Gaussian distributions
     to the noises' peak histograms.
    }\label{fig_peakHist}
\end{figure*}

In this subsection, we test the performance of our algorithm with the default
setup that models the matter density field with multi-scale NFW atoms. The
dictionary is constructed with three frames of different NFW comoving scale
radius: $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc.  The
truncation radii (concentration) are set to four times the comoving scale radii
for the atoms in the dictionary. We note that each frame of our dictionary
fixes the scale radius in the comoving space; therefore, the NFW atoms have
different angular radii in different lens redshift bins.

We test the algorithm with different regularization parameters for the
preliminary lasso estimation, which are $3.5$, $4.0$, and $5.0$. The
corresponding regularization parameters for the adaptive lasso are set to
$\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\tau+1}$.  Here, we note that both the
preliminary lasso estimation and the final adaptive lasso estimation select the
pixels with the signal-to-noise ratios (SNRs) greater than $\lambda_{\rm{ls}}$
in each gradient descent iteration. While the final adaptive lasso estimation
further enhances the growth of the pixels with preliminary estimations greater
than $\lambda_{\rm{ls}}$.

This paper does not go beyond the resolution limit defined by the Gaussian
smoothing kernel with a standard deviation of $1.\arcmin 5$ and the $1\arcmin$
pixel scale as discussed in Section \ref{subsec_method_smoothing} and Section
\ref{subsec_method_pixel}, respectively.  Therefore, we smooth the
reconstructed density with the same Gaussian kernel in each lens redshift
plane.

The left panels of Figure \ref{fig_NFWvsPM} demonstrates the $3$-D density maps
reconstructed with different penalization parameters for a halo with
$M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$.  As we can see from
the reconstructed maps, the adaptive lasso algorithm sets most of the
reconstructed pixels to zero and only keeps the pixels with large amplitudes.
Therefore, it is straightforward to identify the peaks on the reconstructed
sparse density map.  Figure \ref{fig_peakHist} shows the histograms for the
detected peaks with different penalization parameters.

We simulate $1000$ realizations of pure noise fields and perform the
same reconstructions on these noise fields to study the noise properties. Figure
\ref{fig_peakHist} shows the histograms of peaks detected from the
pure noise fields. , we also find that the number of false
peaks significantly decreases as the penalization parameter increases.

\begin{figure*}
 \centering
 \includegraphics[width=1.0\textwidth]{peak_scatters_NFW_lbd35.pdf}
 \caption{The left panel shows the stacked $2$-D distribution of the deviations
     of detected peak positions from the centers of the corresponding input
     halos. The $x$-axis is for the deviated distance in the transverse plane,
     and the $y$-axis is for the deviation of the redshift. For each
     simulation, the positive peak inside the dashed black box with the minimal
     offset (in the pixel unit) from the input halo's position is taken as a
     true detection. The right panel focuses on the deviation of detected peaks
     in the line of sight direction. The $x$-axis is the input halo redshifts,
     and the $y$-axis is the redshift of the detected peak. The `$\cross$'
     denotes the average redshift of detected peaks for each halo over
     different noise realizations, and the error-bars are the uncertainties of
     the average redshifts. The deep gray area is for the relative redshift
     bias less than $0.05$, and the light gray area is for the relative
     redshift bias less than $0.5$. These results in this figure are based on
     the NFW dictionary with $\lambda=3.5$.
     } \label{fig_detoffsets}
\end{figure*}

The stacked $2$-D histogram, from all of the simulations, for the offsets of
the detected peak positions from the input halos' positions is shown in the
left panel of Figure \ref{fig_detoffsets}.

For each simulation, we find the positive peak closest to the input position
(in the pixel unit). If the closest peak lay inside the region denoted with
the dashed box in the left panel of Figure \ref{fig_detoffsets}, we take it as
a true peak detection of the input halo. Other detected peaks, which include both
positive and negative peaks, are taken as false peaks. The right
panel of Figure \ref{fig_detoffsets} shows the average redshift of true
detections for each halo. The estimated redshifts are lower than the true
redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.

\begin{figure*}
 \centering
 \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd35.pdf}
 \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd40.pdf}
 \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd50.pdf}
 \caption{The upper panels show the halo detection rate and the number of false
     peaks per square degree for mass map reconstructed with the NFW atoms. The
     penalization parameter is set to $\lambda=3.5$ for the upper panels.  The
     low panels show the results for $\lambda=5.0$.
        } \label{fig_detFalsRateNFW}
\end{figure*}

Figure \ref{fig_detFalsRateNFW} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each simulated halo.
The figure include results of different penalization parameters: $\lambda=3.5$
(upper panel) and $\lambda=5.0$ (lower panel).  We find that with the increase
of the penalization parameter, the detection rate decreases. On the other hand,
the number of false peaks also decreases.

### 2020-12-05 doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex
detection as function of threshold and lambda 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd35.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd40.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd50.pdf separate tex file into sub tex files 	modified:   doc/paper_ms_method_HSCY1/ms.tex 	new file:   doc/paper_ms_method_HSCY1/massmap_sim.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_NFW_results.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex peak histograms(normalized) and fit noises' peak histograms to Gaussia

In this subsection, we show the results for the setup, which substitutes the
default NFW dictionary with the point mass dictionary, to compare with the
default setup.  The regularization parameter for the preliminary lasso is set
to $3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
propose to incorporate external group information into different adaptive lasso
penalization weights by setting the penalization weights for projection
coefficients in the same group to the average of the adaptive weights in this
group, we smooth the preliminary lasso estimation in each lens redshift bin
with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc. The smoothed
preliminary lasso estimation is denoted as $\hat{x}^{\rm{ls}}_{\rm{sm}}$, and
the penalization weights are set to $1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.
The regularization parameter for the adaptive lasso is set to
$\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.

As we have done on the NFW dictionary's reconstruction, we smooth the
reconstructed density maps with the Gaussian kernel (scale radius equals
$1.\arcmin 5$) in each lens redshift plane.

Figure \ref{fig_detFalsRatePM} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each setup of halo
mass and redshift.
This figure includes results of different penalization parameters:
$\lambda=3.5$ (upper panel) and $\lambda=5.0$ (lower panel). The right panels
of Figure \ref{fig_NFWvsPM} show the $3$-D density maps reconstructed with
different penalization parameters for a halo with $M_{200}=10^{15.02}
~h^{-1}M_{\odot}$ at redshift $0.164$.
Comparing with the results of the NFW dictionary, we find that the number of
false peaks in the mass map reconstructed with the point mass dictionary is
much larger than the NFW dictionary.

As demonstrated in the right panels of Figure \ref{fig_NFWvsPM}, the mass
reconstructions with the point mass dictionary tend to assign masses to
several different redshift bins in the neighboring region of the halo center.
While the NFW dictionary produces consistent mass reconstructions.
Since the NFW atoms' profiles are more consistent with the mass profiles of the
input halos than the profile of a point mass, there are less false structures
reconstructed with the NFW dictionary.

### 2020-12-06 doc/paper_ms_method_HSCY1/ms.tex
revising the paper

@@
 \usepackage{amsmath,amsthm,amsfonts,amssymb,bm}
-% for big dot
+\usepackage{physics,commath}
+
+\usepackage{listings}
+\hypersetup{breaklinks}
+\usepackage{color}
+\usepackage{graphicx,subfigure}
+\usepackage{multirow}
+
+\usepackage{textcomp}
+\usepackage{epstopdf}
+\usepackage{natbib}
+\usepackage{algorithm,algcompatible}
+\usepackage[-]{callouts}
+
 \makeatletter
@@
 \newcommand{\argmin}{\mathop{\rm arg~min}\limits}
-
-\usepackage{listings}
-\usepackage{physics}
-\usepackage{multirow}
-\usepackage{color}
-\usepackage{graphicx,subfigure}
-\renewcommand\thesubfigure{(\roman{subfigure})}
-
-\usepackage{textcomp}
-\usepackage{epstopdf}
-\usepackage{natbib}
-\usepackage{commath}
-\hypersetup{breaklinks}
 
@@
 
-\usepackage{algorithm,algcompatible}
-\usepackage[-]{callouts}
-
-%\DeclareMathOperator*{\argmax}{\arg\!\max}
 \algnewcommand\INPUT{\item[\textbf{Input:}]}
@@
 
+\renewcommand\thesubfigure{(\roman{subfigure})}
 \newcommand{\includezraphics}[1]{
@@
     \arrow { -6., -4}{ -6., 4}
-\note {-6.,4.5}{$\huge{z}$}
+    \note {-6.,4.5}{$\mathbf{z}$}
     \end{annotate}
@@
 \makeatother
-%\newcommand{\jcap}{JCAP}
 
 \begin{document}
-\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction:
+\title{$3$-D Weak Lensing Mass Map Reconstruction:
 Reducing the line of sight smearing}
-%\author{Xiangchong Li}
-%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
-%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-%University of Tokyo, Kashiwa 277-8583, Japan}
-%\author{Masamune Oguri}
-%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
-%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-%University of Tokyo, Kashiwa 277-8583, Japan}
-%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
-%\author{Wentao Luo}
-%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-%University of Tokyo, Kashiwa 277-8583, Japan}
-%\author{HSC Collaboration}
-%\noaffiliation
-%\email{xiangchong.li@ipmu.jp}
+% \author{Xiangchong Li}
+% \affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
+% \affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
+% University of Tokyo, Kashiwa 277-8583, Japan}
+% \author{Masamune Oguri}
+% \affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
+% \affiliation{Kavli Institute for the Physics and Mathematics of the Universe
+% (WPI),\\
+% University of Tokyo, Kashiwa 277-8583, Japan}
+% \affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo
+% 113-0033, Japan}
+% \author{Wentao Luo}
+% \affiliation{Kavli Institute for the Physics and Mathematics of the Universe
+% (WPI),\\
+% University of Tokyo, Kashiwa 277-8583, Japan}
+% \email{xiangchong.li@ipmu.jp}
 
@@
         columns are the multi-scale NFW atoms.  The smoothing kernel is
-        Gaussian with a standard dev
-        iation of $1.5$ pixels.
+        Gaussian with a standard dev iation of $1.5$ pixels.
     } \label{fig_atoms2D}
@@
 \begin{figure}
- \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
+ \includegraphics[width=0.45\textwidth]{nfwlet-atom-1D.pdf}
     \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The
@@
  \centering
- \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
+ \includegraphics[width=0.45\textwidth]{photo-z_binning.pdf}
  \caption{The source galaxies are binned into $10$ redshift bins according to
@@
  \centering
- \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
+ \includegraphics[width=0.45\textwidth]{mlz-poz.pdf}
  \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.
@@
 \caption{The density map reconstructions with the lasso (left) and the adaptive
-        lasso (right) algorithms. The input density map is from a NFW halo with
-        mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso
-        reconstruction smears the density field along the line of sight
-        direction (vertical direction in the plots).  The vertical direction is
-        the line of sight direction, and the lower boundaries and upper
-        boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively. Noises
-        on galaxy shape measurements are neglected in this simulation.
+    lasso (right) algorithms. The vertical direction is the line of sight
+    direction, and the lower boundaries and upper boundaries of the boxes are
+    $z=0.01$ and $z=0.85$, respectively. Noises on galaxy shape measurements
+    are neglected in the simulation.  The input halo mass is $M_{200}=10^{15}
+    ~h^{-1}M_{\odot}$, and its redshift is $z=0.35$. The lasso reconstruction
+    smears the density field along the line of sight direction.
     } \label{fig_lassoVsadaLasso}
@@
 
-The observed galaxies have random irregular (unequally-spaced) spatial
-distribution. To boost the computational speed, we smooth the shear
-measurements from galaxy shapes and pixelize the smoothed measurements onto
-regular grids.  After the pixelization, the fast Fourier transform (FFT) can be
-directly conducted on the transverse plane in each source redshift bin.
+The observed galaxies have random yet unequally-spaced spatial distribution. To
+boost the computational speed, we smooth the shear measurements from galaxy
+shapes and pixelize the smoothed measurements onto regular grids.  After the
+pixelization, the fast Fourier transform (FFT) can be directly conducted on the
+transverse plane in each source redshift bin.
 
@@
 $\theta_i$ are the shear, photometric reshift, and transverse position of the
-`$i$-th' galaxy in the catalog.
+$i$-th galaxy in the catalog.
 
@@
 \begin{equation}
-\hat{x'}^{\rm{lasso}}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{A'} x')}_2^2+ \lambda_{\rm{ls}} \norm{x'}^1_1\right\},
+\hat{x'}^{\rm{lasso}}=\argmin_{x} \left\{
+\frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{A'} x')}_2^2+
+\lambda \norm{x'}^1_1\right\},
 \end{equation}
 where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and
-$l^2$ norm, respectively.  $\lambda_{ls}$ denotes the penalization parameter
+$l^2$ norm, respectively.  $\lambda$ denotes the penalization parameter
 for the lasso estimation.
@@
 \hat{x'}=\argmin_{x'} \left\{ \frac{1}{2} \norm{\Sigma^{-\frac{1}{2}}(\gamma-\mathbf{A'}x')}^2_2 +
-\hat{w}\lambda_{\rm{als}} \norm{x'}^1_1\right\}.
+\hat{w}\lambda_{\rm{ada}} \norm{x'}^1_1\right\}.
 \end{equation}
-Here, $\lambda_{\rm{als}}$ is the penalization parameter for the adaptive
-lasso.  We note that $\lambda_{\rm{als}}$ does not need to be the same as the
+Here, $\lambda_{\rm{ada}}$ is the penalization parameter for the adaptive
+lasso.  We note that $\lambda_{\rm{ada}}$ does not need to be the same as the
 penalization parameter for the preliminary lasso estimation
-($\lambda_{\rm{ls}}$).
+($\lambda$).
 
@@
 (\gamma_{\beta}-A'_{\beta j}x'_{j})\\
-&+ \lambda_{\rm{als}} \hat{w_\beta} \abs{x'_\beta}.
+&+ \lambda_{\rm{ada}} \hat{w_\beta} \abs{x'_\beta}.
 \end{split}
@@
 \STATE $x'^{(1)} = 0$
-\STATE $\hat{w}=1$, $\lambda=\lambda_{\rm{ls}}$
+\STATE $\hat{w}=1$
 \STATE $t^{(1)}=1$,$i=1$, $j=1$
@@
 \STATE \textbf{Reinitialization:}
-\STATE $\hat{w}=\abs{\hat{x'}^{\rm{lasso}}}^{-2}$, $\lambda=\lambda_{\rm{als}}$
+\STATE $\hat{w}=\abs{\hat{x'}^{\rm{lasso}}}^{-2}$, $\lambda \leftarrow
+\lambda_{\rm{ada}}$
 \STATE $\hat{x'}^{(1)} = x'^{(N_{\rm{iter}})}$
@@
 
-\begin{figure*}
-\centering
-\subfigure[NFW: $\lambda=3.5$]{
-        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
-        }
-\subfigure[Point Mass: $\lambda=3.5$]{
-        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
-        }
-\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
-        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
-        }
-\subfigure[Point Mass: $\lambda=5.0$]{
-        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
-        }
-\caption{The results of density maps reconstruction with the point mass
-    dictionary (left) and the NFW dictionary (right) with $\lambda=3.5$ (upper)
-    and $\lambda=5.0$ (lower). The input density map is from a NFW halo with
-    mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The
-    vertical direction is the line of sight direction, and the lower boundaries
-    and upper boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively.
-        } \label{fig_NFWvsPM}
-\end{figure*}
-
 \section{Summary}
@@
 method models $3$-D density contrast maps as summations of NFW atoms with
-difference comoving radius.  With the prior assumption that the clumpy mass
-sparsely distributes in the $3$-D space, the density field is reconstructed
+different comoving radii.  With the prior assumption that the clumpy masses
+sparsely distribute in the $3$-D space, the density map is reconstructed
 using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}. The method is
-tested with realistic simulations using HSC-like shape estimation error and
-HSC-like photo-$z$ uncertainty.
+tested with realistic simulations using HSC-like shape estimation errors and
+photo-$z$ uncertainties.
+
+The findings of this paper are summarized as follows:
+
+(i) The lasso algorithm's solution suffers from a smear of structure in the
+line of sight direction even in the absence of shape noise, and the adaptive
+lasso algorithm significantly removes the line of sight smear of structure.
+
+(ii) The algorithm is able to detect halo with minimal mass limits of
+$10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for
+the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$)
+redshifts, respectively, with a false detection of 0.022/deg$^2$.
+
+(iii)The estimated redshifts of the halos detected from the reconstructed mass
+maps are lower than the true redshift by about $0.03$ for halos at low
+redshifts ($z\leq 0.4$).  The relative redshift bias is below $0.5\%$ for halos
+at $0.4<z\leq 0.85$.
 
@@
 \citep{HSC1-catalog,FPFSHSC1-Li2020} to perform galaxy cluster detection in our
-future work.  Here, we note that, when detecting galaxy clusters from the weak
-lensing mass maps in real observations \citep{HSC1-massMap-cluster}, peaks
-higher than an ad-hoc threshold is chosen as galaxy cluster candidates to
-suppress the number of false detections. The threshold is set to a few times
-the peak's standard deviation of the noise field (shear estimation error
-field). We use different detection thresholds to detect peaks from the mass
-maps reconstructed with $\lambda=5.0$. The left and middle panels of Figure
-\ref{fig_detfalse_threshold} show the detection rates for halos with different
-mass and redshift with detection thresholds set to $1.5\sigma$ and $3.0\sigma$
-of the noise field, respectively. The right panel of Figure
-\ref{fig_detfalse_threshold} shows the numbers of false detections as a
-function of detection thresholds.
-
-The findings of this paper are summarized as follows:
-\begin{enumerate}
- \item The lasso algorithm's solution suffers from a smear of structure in
-     the line of sight direction even in the absence of shape noise, and the
-     adaptive lasso algorithm significantly removes the line of sight smear of
-     structure.
- \item The algorithm is able to detect halo with minimal mass limits of
-     $10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$
-     for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z<
-     0.85$) redshifts, respectively, with a false detection of 0.022/deg$^2$.
- \item The estimated redshifts of the halos detected from the reconstructed mass
-     maps are lower than the true redshift by about $0.03$ for halos at low
-     redshifts ($z\leq 0.4$).  The relative redshift bias is below $0.5\%$ for
-     halos at $0.4<z\leq 0.85$.
-\end{enumerate}
+future work.
 
 \section*{Acknowledgements}
-We thank Yin Li and Jiaxin Han for useful discussions.
+XL thank Yin Li and Jiaxin Han for useful discussions.
 
-This work was supported by Global Science Graduate Course (GSGC) program of
+XL was supported by Global Science Graduate Course (GSGC) program of
 University of Tokyo and JSPS KAKENHI (JP19J22222).

### 2020-12-06 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
revising the paper

@@
+\begin{figure*}
+\centering
+\subfigure[NFW: $\lambda=3.5$]{
+        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
+    }
+\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
+        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
+    }
+\caption{The density maps reconstructed from the mock galaxy shape catalog with
+    the NFW dictionary. The penalization parameters are $\lambda=3.5$ (left)
+    and $\lambda=5.0$ (right).  The input halo mass is $M_{200}=10^{15.02}
+    ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The vertical direction
+    is the line of sight direction. The boxes' lower boundaries and upper
+    boundaries of correspond to $z=0.01$ and $z=0.85$, respectively.
+    } \label{fig_NFW3D}
+\end{figure*}
+
+In this subsection, we test the performance of our algorithm with the default
+setup that models the matter density field with multi-scale NFW atoms. The
+dictionary is constructed with three frames of different NFW scale radii in the
+comoving coordinate: $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$
+Mpc.  The truncation radii are set to four times the comoving scale radii for
+the atoms in the dictionary (concentration equals four) . We note that each
+frame of our dictionary fixes the scale radius in the comoving space;
+therefore, the NFW atoms have different angular radii in different lens
+redshift bins.
+
+We test the algorithm with different regularization parameters ($\lambda$) for
+the preliminary lasso estimation, which are $3.5$, $4.0$, and $5.0$. The
+corresponding regularization parameters for the final adaptive lasso estimations
+are set to $\lambda_{\rm{ada}}=\lambda^{\tau+1}$.  Here, we note that both the
+preliminary lasso estimation and the final adaptive lasso estimation select the
+pixels with the signal-to-noise ratios (SNRs) greater than $\lambda$ in each
+gradient descent iteration. While the final adaptive lasso estimation further
+enhances the growth of the pixels with preliminary estimations greater than
+$\lambda$.
+
+This paper does not go beyond the resolution limit defined by the Gaussian
+smoothing kernel with a standard deviation of $1.\arcmin 5$ and the $1\arcmin$
+pixel scale as discussed in Section \ref{subsec_method_smoothing} and Section
+\ref{subsec_method_pixel}, respectively.  Therefore, we smooth the
+reconstructed density with the same Gaussian kernel in each lens redshift
+plane.
+
+Figure \ref{fig_NFW3D} shows the $3$-D density maps reconstructed with
+different penalization parameters for a halo with $M_{200}=10^{15.02}
+~h^{-1}M_{\odot}$ at redshift $0.164$.  As we can see from the reconstructed
+density maps, the adaptive lasso algorithm sets most of the reconstructed
+pixels to zero and only keeps the pixels with large amplitudes.  We identify
+the peaks on the reconstructed sparse density map.
+
 \begin{figure*}
@@
  \includegraphics[width=1.0\textwidth]{peak_histograms_NFW.pdf}
- \caption{The histograms of detected peak values (normalized) from all of the
-     simulations.  The solid red steps are the results from reconstructions
+ \caption{The number per square degree histograms of detected peak values from
+     all of the simulations.  The solid red steps result from reconstructions
      with the NFW dictionary penalized with different regularization
@@
 
-In this subsection, we test the performance of our algorithm with the default
-setup that models the matter density field with multi-scale NFW atoms. The
-dictionary is constructed with three frames of different NFW comoving scale
-radius: $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc.  The
-truncation radii (concentration) are set to four times the comoving scale radii
-for the atoms in the dictionary. We note that each frame of our dictionary
-fixes the scale radius in the comoving space; therefore, the NFW atoms have
-different angular radii in different lens redshift bins.
+Following \citet{WL-massMap-Glimpse2D-Lanusse2016}, we normalize detected peaks
+in the $l$-th lens redshift plane to account for the peak amplitude difference
+due to the difference in the norm of the lensing kernels for different redshift
+bins:
+\begin{equation}
+\delta^{\rm{n}}_{\rm{peak}}(\vec{\theta},z_l)=\delta_{\rm{peak}}(\vec{\theta},z_l)/\mathcal{R}_{l}^{\frac{1}{2}},
+\end{equation}
+where the normalization matrix is defined as
+\begin{equation}
+\mathcal{R}_{l}=\sum_s K^2(z_l,z_s).
+\end{equation}
+The solid steps in Figure \ref{fig_peakHist} show the histograms for the
+normalized peaks with different penalization parameters. Also, we simulate
+$1000$ realizations of pure noise fields and perform the reconstructions on
+these noise fields to study the noise properties. The dashed steps in Figure
+\ref{fig_peakHist} show the histograms of normalized peaks detected from the
+pure noise fields. The solid lines in Figure \ref{fig_peakHist} show the
+best-fit Gaussian distributions to the noise peaks' histograms.
 
-We test the algorithm with different regularization parameters for the
-preliminary lasso estimation, which are $3.5$, $4.0$, and $5.0$. The
-corresponding regularization parameters for the adaptive lasso are set to
-$\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\tau+1}$.  Here, we note that both the
-preliminary lasso estimation and the final adaptive lasso estimation select the
-pixels with the signal-to-noise ratios (SNRs) greater than $\lambda_{\rm{ls}}$
-in each gradient descent iteration. While the final adaptive lasso estimation
-further enhances the growth of the pixels with preliminary estimations greater
-than $\lambda_{\rm{ls}}$.
+Figure \ref{fig_peakHist} tells that the densities of peaks (including both
+true and false peaks) are suppressed as the penalization parameter $\lambda$
+increases. Moreover, we find the standard deviation of noise peaks slightly
+decreases as $\lambda$ increases. As a result, for a higher detection threshold
+($\lambda=5.0$), we find a clearer peak number excess for mass maps
+reconstructed from mock catalogs comparing with the noise peak histogram .
 
-This paper does not go beyond the resolution limit defined by the Gaussian
-smoothing kernel with a standard deviation of $1.\arcmin 5$ and the $1\arcmin$
-pixel scale as discussed in Section \ref{subsec_method_smoothing} and Section
-\ref{subsec_method_pixel}, respectively.  Therefore, we smooth the
-reconstructed density with the same Gaussian kernel in each lens redshift
-plane.
-
-The left panels of Figure \ref{fig_NFWvsPM} demonstrates the $3$-D density maps
-reconstructed with different penalization parameters for a halo with
-$M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$.  As we can see from
-the reconstructed maps, the adaptive lasso algorithm sets most of the
-reconstructed pixels to zero and only keeps the pixels with large amplitudes.
-Therefore, it is straightforward to identify the peaks on the reconstructed
-sparse density map.  Figure \ref{fig_peakHist} shows the histograms for the
-detected peaks with different penalization parameters.
-
-We simulate $1000$ realizations of pure noise fields and perform the
-same reconstructions on these noise fields to study the noise properties. Figure
-\ref{fig_peakHist} shows the histograms of peaks detected from the
-pure noise fields. , we also find that the number of false
-peaks significantly decreases as the penalization parameter increases.
+The $2$-D histogram, stacked from all of the simulations, for the offsets of
+the detected peak positions from the input halos' positions is shown in the
+left panel of Figure \ref{fig_detoffsets}. We see a clustering of peaks close
+to the input halo's position on the stacked position histogram.  For each stamp
+simulation, we find the positive peak closest to the input position (in the
+pixel unit). If the closest peak lay inside the region denoted with the dashed
+box in the left panel of Figure \ref{fig_detoffsets}, we take it as a true peak
+detection of the input halo. Other identified peaks, which include both positive
+and negative peaks, are taken as false detections.
 
@@
 
-The stacked $2$-D histogram, from all of the simulations, for the offsets of
-the detected peak positions from the input halos' positions is shown in the
-left panel of Figure \ref{fig_detoffsets}.
+The right panel of Figure \ref{fig_detoffsets} shows the average redshift of
+true detections for each halo. The estimated redshifts are lower than the true
+redshifts by about $0.03$ for halos in the low-redshift range ($z\leq
+0.4$).  For halos at $0.4<z\leq 0.85$, the relative redshift bias is below
+$0.5\%$.
 
-For each simulation, we find the positive peak closest to the input position
-(in the pixel unit). If the closest peak lay inside the region denoted with
-the dashed box in the left panel of Figure \ref{fig_detoffsets}, we take it as
-a true peak detection of the input halo. Other detected peaks, which include both
-positive and negative peaks, are taken as false peaks. The right
-panel of Figure \ref{fig_detoffsets} shows the average redshift of true
-detections for each halo. The estimated redshifts are lower than the true
-redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
-For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.
+We select peaks with values greater than an ad-hoc threshold as candidates of
+galaxy clusters following \citet{HSC1-massMap-cluster}.  The threshold is set
+to a few times the standard deviation of the noise peaks. We use different
+detection thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters
+from the mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and
+middle columns of Figure \ref{fig_detFalsRateNFW} show the detection rates for
+halos in the (mass, redshift) planes with detection thresholds set to
+$1.5\sigma$ and $3.0\sigma$ of the noise field, respectively. The right column
+of Figure \ref{fig_detFalsRateNFW} shows the corresponding numbers of false
+detections per square degree as functions of detection thresholds. The first,
+second, and third rows of Figure \ref{fig_detFalsRateNFW} correspond to the
+$lambda=3.5,4.0,5.0$, respectively.
+
+Figure \ref{fig_detFalsRateNFW} tells that the false peak density is suppressed
+as the detection threshold increases. Also, the detection rate of halo
+significantly decreases. We decide to set the detection threshold to
+$1.5\sigma$ and set the penalization parameter $\lambda$ to $5.0$ since such a
+setup suppresses the false detection to $0.022$ while keeping a good halo
+detection rate. In summary, The algorithm is able to detect halo with minimal
+mass limits of $10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0}
+M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high
+($0.6\leq z< 0.85$) redshifts, respectively.
 
@@
  \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd50.pdf}
- \caption{The upper panels show the halo detection rate and the number of false
-     peaks per square degree for mass map reconstructed with the NFW atoms. The
-     penalization parameter is set to $\lambda=3.5$ for the upper panels.  The
-     low panels show the results for $\lambda=5.0$.
+ \caption{The detection rate and false peak density for different $\lambda$ and
+     detection thresholds. The first, second, and third rows correspond to the
+     results with $lambda=3.5,4.0,5.0$, respectively. The left and middle columns
+     are the halo detection rates for detection thresholds equal $1.5\sigma$ and
+     $3.0\sigma$, respectively. The right column is the density of false peaks as
+     a function of detection threshold.
     } \label{fig_detFalsRateNFW}
 \end{figure*}
-
-Figure \ref{fig_detFalsRateNFW} shows the detection rate (left panels) and the
-number of false peaks per square degree (right panel) for each simulated halo.
-The figure include results of different penalization parameters: $\lambda=3.5$
-(upper panel) and $\lambda=5.0$ (lower panel).  We find that with the increase
-of the penalization parameter, the detection rate decreases. On the other hand,
-the number of false peaks also decreases.

### 2020-12-06 doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex
revising the paper

@@
-In this subsection, we show the results for the setup, which substitutes the
-default NFW dictionary with the point mass dictionary, to compare with the
-default setup.  The regularization parameter for the preliminary lasso is set
-to $3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
+We substitute the default NFW dictionary with the point mass dictionary and
+reconstruct the mass map from the mock galaxy shape catalog, to compare with
+the default setup.
+
+The regularization parameter ($\lambda$) for the preliminary lasso is set to
+$3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
 propose to incorporate external group information into different adaptive lasso
@@
 preliminary lasso estimation is denoted as $\hat{x}^{\rm{ls}}_{\rm{sm}}$, and
-the penalization weights are set to $1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.
+the penalization weights are set to
+$\hat{w}=1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.
 The regularization parameter for the adaptive lasso is set to
-$\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.
-
+$\lambda_{\rm{ada}}=\lambda$.
 As we have done on the NFW dictionary's reconstruction, we smooth the
@@
 
-Figure \ref{fig_detFalsRatePM} shows the detection rate (left panels) and the
-number of false peaks per square degree (right panel) for each setup of halo
-mass and redshift.
-This figure includes results of different penalization parameters:
-$\lambda=3.5$ (upper panel) and $\lambda=5.0$ (lower panel). The right panels
-of Figure \ref{fig_NFWvsPM} show the $3$-D density maps reconstructed with
-different penalization parameters for a halo with $M_{200}=10^{15.02}
-~h^{-1}M_{\odot}$ at redshift $0.164$.
-Comparing with the results of the NFW dictionary, we find that the number of
-false peaks in the mass map reconstructed with the point mass dictionary is
-much larger than the NFW dictionary.
+As demonstrated in Figure \ref{fig_PM3D}, the mass reconstructions with the
+point mass dictionary tend to assign masses to several different redshift bins
+in the neighboring region of the halo's center.  In contrast, as demonstrated in
+Figure \ref{fig_NFW3D}, the NFW dictionary manages to perform consistent mass
+reconstructions.  We think the problem of the point mass dictionary originates
+from the fact that the profile of the point mass atom in the transverse plane
+is much more compact than the profile of the input halos, especially at low
+redshift.
 
-As demonstrated in the right panels of Figure \ref{fig_NFWvsPM}, the mass
-reconstructions with the point mass dictionary tend to assign masses to
-several different redshift bins in the neighboring region of the halo center.
-While the NFW dictionary produces consistent mass reconstructions.
-Since the NFW atoms' profiles are more consistent with the mass profiles of the
-input halos than the profile of a point mass, there are less false structures
-reconstructed with the NFW dictionary.
+\begin{figure*}
+\centering
+\subfigure[Point Mass: $\lambda=3.5$]{
+        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
+        }
+\subfigure[Point Mass: $\lambda=5.0$]{
+        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
+        }
+\caption{The density maps reconstructed from the mock galaxy shape catalog with
+    the point mass dictionary. The penalization parameters are $\lambda=3.5$
+    (left) and $\lambda=5.0$ (right).  The input halo mass is
+    $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The
+    vertical direction is the line of sight direction. The boxes' lower
+    boundaries and upper boundaries of correspond to $z=0.01$ and $z=0.85$,
+    respectively.
+    } \label{fig_PM3D}
+\end{figure*}

### 2020-12-06 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
small changes

@@
      corresponding results of the reconstructions from $1000$ realizations of
-     pure noise fields. The gray lines are the best-fit Gaussian distributions
+     pure noise catalogs. The gray lines are the best-fit Gaussian distributions
      to the noises' peak histograms.
@@
 
-Following \citet{WL-massMap-Glimpse2D-Lanusse2016}, we normalize detected peaks
-in the $l$-th lens redshift plane to account for the peak amplitude difference
-due to the difference in the norm of the lensing kernels for different redshift
-bins:
+Following \citet{WL-massMap-Glimpse2D-Lanusse2016}, we normalize the detected
+peaks in the $l$-th ($l=1...20$) lens redshift plane to account for the peak
+amplitude difference due to the difference in the norm of the lensing kernels
+for different redshift bins:
 \begin{equation}
@@
 \end{equation}
-The solid steps in Figure \ref{fig_peakHist} show the histograms for the
+The solid steps in Figure \ref{fig_peakHist} show the histograms of the
 normalized peaks with different penalization parameters. Also, we simulate
-$1000$ realizations of pure noise fields and perform the reconstructions on
-these noise fields to study the noise properties. The dashed steps in Figure
+$1000$ realizations of pure noise catalogs and perform the reconstructions on
+these noise catalogs to study the noise properties. The dashed steps in Figure
 \ref{fig_peakHist} show the histograms of normalized peaks detected from the
-pure noise fields. The solid lines in Figure \ref{fig_peakHist} show the
+pure noise catalogs. The solid lines in Figure \ref{fig_peakHist} show the
 best-fit Gaussian distributions to the noise peaks' histograms.
@@
 halos in the (mass, redshift) planes with detection thresholds set to
-$1.5\sigma$ and $3.0\sigma$ of the noise field, respectively. The right column
-of Figure \ref{fig_detFalsRateNFW} shows the corresponding numbers of false
-detections per square degree as functions of detection thresholds. The first,
-second, and third rows of Figure \ref{fig_detFalsRateNFW} correspond to the
-$lambda=3.5,4.0,5.0$, respectively.
+$1.5\sigma$ and $3.0\sigma$ of the noise peaks' distributions, respectively.
+The right column of Figure \ref{fig_detFalsRateNFW} shows the corresponding
+numbers of false detections per square degree as functions of detection
+thresholds. The first, second, and third rows of Figure
+\ref{fig_detFalsRateNFW} correspond to the $lambda=3.5,4.0,5.0$, respectively.
 
@@
  \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd50.pdf}
- \caption{The detection rate and false peak density for different $\lambda$ and
-     detection thresholds. The first, second, and third rows correspond to the
-     results with $lambda=3.5,4.0,5.0$, respectively. The left and middle columns
-     are the halo detection rates for detection thresholds equal $1.5\sigma$ and
-     $3.0\sigma$, respectively. The right column is the density of false peaks as
-     a function of detection threshold.
+ \caption{The detection rates and false peak densities for different
+     penalization parameters and detection thresholds. The first, second, and
+     third rows correspond to the results with $\lambda=3.5,4.0,5.0$,
+     respectively. The left and middle columns are the halo detection rates for
+     detection thresholds equal $1.5\sigma$ and $3.0\sigma$, respectively. The
+     right column shows the density of false peaks as a function of detection
+     threshold.
     } \label{fig_detFalsRateNFW}

### 2020-12-07 doc/paper_ms_method_HSCY1/ms.tex
commit

@@
     \arrow { -6., -4}{ -6., 4}
-    \note {-6.,4.5}{$\mathbf{z}$}
+    \note {-6.,4.5}{$\mathbf{z_l}$}
     \end{annotate}
@@
 density fields have a sparse spatial distribution, the density fields are
-reconstructed using an oracle algorithm: adaptive lasso. Our method is tested
+reconstructed using an oracle algorithm: adaptive lasso. The method is tested
 with realistic simulations using the HSC-like shape estimation error and
@@
 solution suffers from a smear of structure in the line of sight direction even
-in the absence of shape noise. The adaptive lasso algorithm significantly
-removes the line of sight smear of structure.  2) The algorithm is able to
-detect halo with minimal mass limits of $10^{14.0} M_{\odot}/h$, $10^{14.7}
-M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq
-z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts, respectively, with a false
-detection of 0.022/deg$^2$.  3) The estimated redshift of the halos detected
-from the reconstructed mass maps are lower than the true redshift by about
-$0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshift bias is
-below $0.5\%$ for halos at $0.4<z\leq 0.85$.
+in the absence of shape noise. In contrast, the adaptive lasso algorithm
+efficiently removes the line of sight smear of structure.  2) The algorithm is
+able to detect halo with minimal mass limits of $10^{14.0} M_{\odot}/h$,
+$10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median
+($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts, respectively, with a
+false detection of 0.022/deg$^2$.  3) The estimated redshift of the halos
+detected from the reconstructed mass maps are lower than the true redshift by
+about $0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshift
+bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$.
 \end{abstract}
@@
 \delta, \end{equation} where $\mathbf{T}$ is used to denote the linear
-transformation operator, which includes not only physical lensing effect but
+transformation operator, which includes not only the physical lensing effect but
 also systematic effects from observations (e.g., pixelization and smoothing of
@@
 The primary goal of most weak-lensing surveys is to constrain the cosmology
-model through $2$-point correlations. The studies include galaxy$-$galaxy
+model through the $2$-point correlations. The studies include galaxy$-$galaxy
 lensing, which cross-correlating the shear field ($\gamma$) with the positions
@@
 The reconstruction of density map from shear measurements also receive
-considerable interest as it reaches the nonlinear scales.  $2$-D density map
-reconstruction which recover an integration of projected mass along the line of
+considerable interest as it reaches the nonlinear scales. The $2$-D density map
+reconstruction which recovers an integration of projected mass along the line of
 sight has been well studied within the community
@@
 where $\mathbf{\Phi}$ is the transformation operator from the projection
-coefficient field to the density contrast, and $x$ denotes the parameters.
-\citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field in Fourier
-space, which is equivalent to model the mass field with sinusoidal functions.
-On the other hand, \citet{LSS-massMap-Glimpse3D-Leonard2014} models the mass
-field with Starlets \citep{Starlet-Starck2015}.
+coefficient field to the density contrast, and $x$ denotes the projection
+coefficients. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density
+field in Fourier space, which is equivalent to modeling the mass field with
+sinusoidal functions.  On the other hand,
+\citet{LSS-massMap-Glimpse3D-Leonard2014} model the mass field with Starlets
+\citep{Starlet-Starck2015}.
 
@@
 covariance matrix of the error on the shear measurements ($\Sigma$).} measuring
-the residuals between the prediction and the data, while $C(x)$ is the
-regularization term measuring the deviation of the estimation of the parameter
-($x$) from the prior assumptions. The $l^p$ norm is defined as
+the difference between the prediction and the data, while $C(x)$ is the
+regularization term measuring the deviation of the coefficient estimation
+($x$) from the prior assumption. The $l^p$ norm is defined as
 \begin{equation}
@@
 \end{equation}
-Such estimation prefers the parameters that are able to describe the
-observations and align with the prior assumptions.  The regularization
-parameter $\lambda$ adjusts the relative weight between the observations and
-prior assumptions in the optimization process.
+Such penalized estimation prefers the parameters that are able to describe the
+observations and align with the prior assumption. The regularization
+parameter $\lambda$ adjusts the relative weight between the data and
+prior assumption in the optimization process.
 
@@
 
-\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version
-of $l^1$ lasso regulation ($C=\norm{x}^1_1$) to find a sparse solution in the
-Starlets dictionary space \citep{Starlet-Starck2015}.
+\citet{LSS-massMap-Glimpse3D-Leonard2014} propose the Glimpse algorithm, which
+uses a derivative version of $l^1$ lasso regulation ($C=\norm{x}^1_1$) to find
+a sparse solution in the Starlet dictionary space \citep{Starlet-Starck2015}.
 \citet{LSS-massMap-Glimpse3D-Leonard2014} apply a greedy coordinate descent
@@
 minimum of a non-convex loss function penalized with the firm thresholding
-function. \citet{LSS-massMap-Glimpse3D-Leonard2014} significantly reduce the
-smearing along the line of sight. However, the stability of the non-convex
+function. The Glimpse algorithm reduces the smearing along the line of sight
+since the coordinate descent algorithm forces the structure to grow only on the
+most related lens redshift plane.  However, the stability of the non-convex
 optimization and greedy coordinate descent algorithm has not been fully
-justified. Moreover, the Starlets functions are not designed to model the
-profile of clumpy mass in the universe.
+justified. Moreover, the Starlet dictionary are not designed to model the
+profile of clumpy mass in the universe, and the Starlet dictionary does not
+account for the angular scale difference at different lens redshifts.
 
@@
 estimator that smears the structure along the line of sight, the adaptive lasso
-can significantly reduce the smearing effect.
+can efficiently reduce the smearing effect.
 
@@
 without relying on any greedy coordinate descent approaches. The stability of
-this convex optimization has been well studied.
+this convex optimization has been justified.
 
@@
 \end{equation}
-We substitute eq. (\ref{eq-x2delta}) into eq.(\ref{eq-delta2gammat}) and get
+We substitute eq. (\ref{eq-x2delta}) into eq. (\ref{eq-delta2gammat}) and get
 \begin{equation}\label{eq-x2gammat}
@@
 \begin{equation}
-\gamma_L \rightarrow \mathbf{Q} \gamma_L,
+\gamma_L \rightarrow \mathbf{P} \gamma_L,
 \end{equation}
@@
 distort the HSC mock shape catalogs with different realizations of the HSC-like
-shape measurement errors and photo-$z$ uncertainties (Section \ref{subsec_Sims}).
+shape measurement error and photo-$z$ uncertainty (Section \ref{subsec_Sims}).
 
@@
 using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}. The method is
-tested with realistic simulations using HSC-like shape estimation errors and
-photo-$z$ uncertainties.
+tested with realistic simulations using HSC-like shape estimation error and
+photo-$z$ uncertainty.
 
@@
 line of sight direction even in the absence of shape noise, and the adaptive
-lasso algorithm significantly removes the line of sight smear of structure.
+lasso algorithm efficiently removes the line of sight smear of structure.
 

### 2020-12-07 doc/paper_ms_method_HSCY1/ms.tex
correct many typos

@@
-\documentclass[twocolumn]{aastex62}
+\documentclass[twocolumn]{aastex63}
 \emergencystretch=1.em
@@
 \usepackage{color}
-\usepackage{graphicx,subfigure}
+\usepackage{graphicx}
 \usepackage{multirow}
@@
 
-\renewcommand\thesubfigure{(\roman{subfigure})}
 \newcommand{\includezraphics}[1]{
     \begin{annotate}{
-    \includegraphics[width=0.43\textwidth]{#1}}{0.45}
-    \arrow { -6., -4}{ -6., 4}
-    \note {-6.,4.5}{$\mathbf{z_l}$}
+        \includegraphics[width=0.95\textwidth]{#1}
+    }{1.0}
+    \arrow { -3., -2}{ -3., 2}
+    \note {-3.,2.5}{z}
     \end{annotate}
@@
 the difference between the prediction and the data, while $C(x)$ is the
-regularization term measuring the deviation of the coefficient estimation
-($x$) from the prior assumption. The $l^p$ norm is defined as
+regularization term measuring the deviation of the coefficient estimation ($x$)
+from the prior assumption. The $l^p$ norm is defined as
 \begin{equation}
@@
 
-We first review the lensing process in Section \ref{subsec_method_delta2shear}.
+We first review the lensing effect in Section \ref{subsec_method_delta2shear}.
 Then, we introduce the dictionary used to model the foreground density maps in
@@
 \end{equation}
-where $K(z_l,z_s)$ is the lensing kernel defined as
+where $K(z_l,z_s)$ is the lensing kernel:
 \begin{equation}
@@
 As shown in \citet{massMap-KS1993}, the shear field is related to the kappa
-field at the same redshift plane via
+field at the same source redshift plane via
 \begin{equation}\label{eq-kappa2gamma}
@@
 \end{equation}
-Here we denote the physical shear distortion field as $\gamma_L$ and we note
-that the final observed shear measurements are influenced by systematic errors
-from observations. The systematic errors will be discussed in Section
-\ref{subsec_method_Systematics}.
+Here we denote the physical shear distortion as $\gamma_L$, and we note
+that it is not the final shear measurement since the final shear
+measurement is influenced by systematic errors from observations. The
+systematic errors will be discussed in Section \ref{subsec_method_Systematics}.
 
@@
 have `$N$' different scale frames, and the atoms in each scale frame are
-shifted by $\vec{r'}$ to form models at different spatial positions.
-$x_s(\vec{r'})$ is the projection coefficients of the density contrast field
-onto the basis atoms.
+shifted by $\vec{r'}$ to form models at different positions in the comoving
+coordinates.  $x_s(\vec{r'})$ is the projection coefficient of the density
+contrast field onto the basis atoms at the comoving coordinate: $\vec{r'}$.
 
@@
 transverse plane, the NFW atoms follow surface density profiles of the NFW
-halos \citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and
-truncation radius $c \theta_\alpha$ , where $c$ is the concentration of the NFW
+halos \citep{haloModel-TJ2003-3pt} with comoving scale radii $r_s$ and
+truncation radius $c r_s$, where $c$ is the concentration of the NFW
 halos.  As the scales of halos are much smaller than the reachable redshift
@@
 \begin{split}
-\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 }
-F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
-&  (s=1..N)
+\phi_s(\vec{r}_{\theta},z) =&\frac{f}{2 \pi r_s^2 }
+F(|\vec{r}_{\theta}|/r_s) \delta_D(z),\\
+&  (s=1...N)
 \end{split}
 \end{equation}
-where
+where $\vec{r}_\theta$ is the comoving position in the transverse plane,
 \begin{equation}
@@
 $f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for the NFW atoms in
-different scale frames.
+different scale frames. Then, we write the basis atoms into the angular
+separation coordinates:
+\begin{equation}
+\begin{split}
+\phi_s(\vec{\theta},z) =&\frac{f \chi(z)^2}{2 \pi r_s^2 }
+F(|\vec{\theta}|\chi(z)/r_s) \delta_D(z),\\
+& (s=1...N)
+\end{split}
+\end{equation}
+where $\chi(z)$ is the comoving distance at the redshift $z$.
 
@@
 \begin{equation}
-\phi_{\rm{PM}}(\vec{r})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
+\phi_{\rm{PM}}(\vec{\theta},z) = \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
 \end{equation}
@@
 
-The observed shear measurements are deviated from the physical shear prediction
-due to the systematic errors from observations. The influence of systematics is
-carefully studied and incorporated into the forward modeling in this Section.
+The observed shear measurement is deviated from the physical shear prediction
+due to the systematic errors from the observation. The influence of systematics is
+carefully studied and incorporated into the forward modeling in this subsection.
 
-\subsubsection{Photo-$z$ Uncertainty}
+\subsubsection{Photo-z Uncertainty}
 \label{subsec_method_photoz}
@@
 \begin{figure*}
+\begin{minipage}[c]{1.0\columnwidth}
+    \includezraphics{delta-3-7-pz-nn-lasso.pdf}
     \centering
-\subfigure[lasso]{\includezraphics{delta-3-7-pz-nn-lasso.pdf}}
-\subfigure[adaptive lasso]{\includezraphics{delta-3-7-pz-nn-alasso.pdf}}
+    \small lasso
+\end{minipage}
+\begin{minipage}[c]{1.0\columnwidth}
+    \includezraphics{delta-3-7-pz-nn-alasso.pdf}
+    \centering
+    \small adaptive lasso
+\end{minipage}
 \caption{The density map reconstructions with the lasso (left) and the adaptive
@@
 The photometric redshifts of source galaxies in the current large-scale survey
-are estimated with a limited number of board photometric bands (e.g., $9$ bands
+are estimated with a limited number of broad photometric bands (e.g., $9$ bands
 for KIDS$+$VIKING survey \citep{KIDS_VIKING-Hildebrant2020}, $5$ bands for DES
 survey and HSC survey). As a result, the estimated redshifts of galaxies suffer
-from much larger uncertainties than redshifts estimated with spectroscopic
+from much larger uncertainty than the redshifts estimated with spectroscopic
 observations. Such photo-$z$ uncertainty smears the lensing kernels
-statistically since a galaxy with a best fit photo-$z$ estimation of $z_s$ has
+statistically since a galaxy with a best-fit photo-$z$ estimation of $z_s$ has
 possibilities of being actually located at different redshifts ($z$). The
-probability function for the photo-$z$ uncertainty is denoted as $P(z|z_s)$,
+probability function is denoted as $P(z|z_s)$,
 and the expected shear distortion on the galaxy is
@@
 \end{equation}
-the photo-$z$ uncertainty changes the shear as
+we express the influence of photo-$z$ uncertainty on the shear signal as
 \begin{equation}
-\gamma_L \rightarrow \mathbf{P} \gamma_L,
+\gamma_L \rightarrow \mathbf{P} \gamma_L.
 \end{equation}
-where we use $\rightarrow$ to denote the changes of shear by the systematic
-operator.
 
@@
 \citep{HSC1-data}. These Galaxies are divided into ten source galaxy bins
-according to the photo-$z$ best estimation, and the boundaries of the bins are
+according to the photo-$z$ best-fit estimation, and the boundaries of the bins are
 shown as vertical dashed lines in Figure \ref{fig_bestpz}. Figure \ref{fig_pdfpz}
@@
 The left panel of Figure \ref{fig_corlensKer} shows the lensing kernels for
-lenses at five different redshifts as functions of source galaxy redshift bins.
-The dashed lines are the lensing kernel for spectroscopic redshifts with
-neglectable redshift uncertainty. The solid lines are the lensing kernel for
+lenses at five different redshifts as functions of source galaxy redshifts.
+The dashed lines are the lensing kernels for spectroscopic redshifts with
+neglectable redshift uncertainties. The solid lines are the lensing kernels for
 photometric redshifts with redshift uncertainties shown in Figure
@@
 \ref{fig_corlensKer}, the lensing kernels converge to zero for source redshifts
-lower than the lens redshift if the uncertainties on the source galaxy
-redshift estimations are neglectable. However, as demonstrated by the solid
+lower than the lens redshift if the uncertainty on the source galaxy
+redshift estimation are neglectable. However, as demonstrated by the solid
 lines in the same panel, for the source redshifts with large photo-$z$
@@
 
-The middle and right panels show the correlation between lensing kernels for
+The middle and right panels show the correlations between lensing kernels for
 lenses at different redshifts. The middle panel is for spect-$z$, and the right
@@
 panel of Figure \ref{fig_corlensKer}, we conclude that the photo-$z$
-uncertainties further increase the correlations between lensing kernels at
+uncertainty slightly increases the correlations between lensing kernels at
 different lens plane.
@@
 
-The observed galaxies have random yet unequally-spaced spatial distribution. To
-boost the computational speed, we smooth the shear measurements from galaxy
-shapes and pixelize the smoothed measurements onto regular grids.  After the
-pixelization, the fast Fourier transform (FFT) can be directly conducted on the
-transverse plane in each source redshift bin.
+The observed galaxies have a random yet unequally-spaced spatial distribution
+in the transverse plane. To boost the computational speed, we smooth the shear
+measurements from galaxies and pixelize the smoothed shear field onto a regular
+grid. After the pixelization, the fast Fourier transform (FFT) can be directly
+conducted on the transverse plane in each source redshift bin.  Another benefit
+of smoothing is that it reduces the bias from the aliasing effect in the
+pixelization process as the smoothing kernel reduces the amplitude of the shear
+signal at the high frequency.
 
@@
 
-Since the smoothing kernel is normalized by definition:
+By definition, the smoothing kernel is normalized as
 \begin{equation}
-\int d^3r W(\vec{r})=1,
+\int d^3r W(\vec{r})=1.
 \end{equation}
-with the approximation that the density of galaxy number - $n(\vec{r})$ -
-varies slowly at the smoothing scale, the
-smoothed galaxy number density:
+With the approximation that the density of galaxy number - $n(\vec{r})$ -
+varies slowly at the smoothing scale, the smoothed galaxy number density,
+which is defined as
 \begin{equation}\label{eq-numDesSmooth}
@@
 equals the galaxy number density: $n_{\rm{sm}}(\vec{r})=n(\vec{r})$.
-We note that the galaxy number density experience a steep drop on the boundary
+However, the galaxy number density experience a steep drop on the boundary
 of the survey, therefore the smoothed galaxy number density does not equal the
@@
 \end{equation}
-and the smoothing procedure influence the shear signal through
+and the smoothing procedure influence the shear signal by
 \begin{equation}
@@
 
-We define the masking window function according to the smoothed number density
-(defined in eq. (\ref{eq-numDesSmooth})) of the galaxies:
+We define the masking window function according to the smoothed galaxy number
+density (defined in eq. (\ref{eq-numDesSmooth})):
 \begin{equation}
@@
 \end{equation}
-The mask changes the shear measurements though
+The mask changes the shear measurements by
 \begin{equation}\label{eq-delta2gamma-final}
@@
 pixel with index $\alpha$, where $\alpha=1...N_\theta \times N_\theta \times
-N_s$. The grids on the transverse planes are equally spaced with a pixel size of
-$1\arcmin$.  Fast Fourier transform (FFT) can be used to boost the speed of
-linear operation on the transverse plane, whereas the grids in the line of sight
-direction follow equal number binning as shown in Figure \ref{fig_bestpz}.
+N_s$. The grids on the transverse planes are equally spaced with a pixel size
+of $1\arcmin$. While the grids in the line of sight direction follow
+equal number binning as shown in Figure \ref{fig_bestpz}.
 
@@
 We term the column vectors of the forward transform matrix $\mathbf{A}$ as the
-effective basis atoms. We note that the effective basis atoms have different
-$l^2$ norm. The $l^2$ norm of the $i'th$ column vectors of the effective basis
-atoms are $\mathcal{N}_{i}=\sum_\alpha A_{i\alpha}A_{i\alpha}$. Before solving
-the density map reconstruction problem, we normalize the column vectors of the
-transform matrix through a rescaling:
+effective basis atoms. The $l^2$ norm of the $i$-th column vectors weighted by
+the inverse of the noise covariance matrix's diagonal elements is defined as
+\begin{equation}
+\mathcal{N}_{i}=\sum_\alpha A_{i\alpha}A_{i\alpha}/\Sigma_{\alpha\alpha}.
+\end{equation}
+
+We note that the effective basis atoms have different weighted $l^2$ norm.
+Before solving the density map reconstruction problem, we normalize the column
+vectors of the transform matrix through a rescaling:
 \begin{equation}
@@
 A'_{\alpha\beta}&=A_{\alpha\beta}/\mathcal{N}_{\alpha}^{\frac{1}{2}},\\
-x'_{\beta}&=x_{\beta}\mathcal{N}_{\beta}^{\frac{1}{2}}.\\
+x'_{\beta}&=x_{\beta}\mathcal{N}_{\beta}^{\frac{1}{2}},\\
 \end{split}
 \end{equation}
+to make the projection coefficients have the same weighted $l^2$ norm.
+Such normalization boosts the speed of the gradient descent iterations
+in the next subsection.
 
@@
 Therefore, the lasso algorithm cannot select the consistent mass in the line of
-sight direction, and the reconstructed mass suffers from smears in the line of
-sight direction even in the absence of noise on shear measurements.  Figure
-\ref{fig_lassoVsadaLasso} shows the reconstructions of a single halo's mass map
-with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$.
-The noises on shear measurements are not included in the simulation.  The left
-panel of Figure \ref{fig_lassoVsadaLasso} is the reconstruction with the lasso
-algorithm, which shows a significant smear along the line of sight.
+sight direction, and the reconstructed mass suffers from smearing in the line
+of sight direction even in the absence of noise on shear measurements and
+photo-$z$ uncertainty .
+
+Figure \ref{fig_lassoVsadaLasso} shows the reconstructions of a single halo's
+mass map with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift
+$0.35$. The shear measurement error and photo-$z$ uncertainty are not included
+in the simulation.  The left panel of Figure \ref{fig_lassoVsadaLasso} is the
+reconstruction with the lasso algorithm, which shows a significant smear along
+the line of sight.
 
@@
 \end{equation}
-Here, $\lambda_{\rm{ada}}$ is the penalization parameter for the adaptive
-lasso.  We note that $\lambda_{\rm{ada}}$ does not need to be the same as the
-penalization parameter for the preliminary lasso estimation
-($\lambda$).
+Here $\lambda_{\rm{ada}}$ is the penalization parameter for the adaptive lasso,
+which does not need to be the same as the penalization parameter for the
+preliminary lasso estimation ($\lambda$).
 
@@
 (FISTA) to solve the lasso problem.  Since the lasso's loss function and the
-adaptive lasso's loss function only differ in their penalization terms. The
-FISTA is also applicable to the adaptive lasso problem. We apply the FISTA to
-solve both the preliminary lasso estimation and the final adaptive lasso
-estimation.
+adaptive lasso's loss function only differ in their penalization terms, the
+FISTA is also applicable to solve the adaptive lasso problem. In this paper, we
+apply the FISTA to solve both the preliminary lasso estimation and the final
+adaptive lasso estimation.
 
@@
 The soft thresholding is a part of the lasso algorithm. It selects the
-estimations with amplitude larger than $\lambda$, and shrink the estimations by
+modes with an amplitude greater than $\lambda$, and shrink the selected
+estimations by
 $\lambda$.

### 2020-12-07 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
correct many typos

@@
-\begin{figure*}
+\begin{figure*}[!t]
+\begin{minipage}[c]{1.0\columnwidth}
+\includegraphics[width=0.95\textwidth]{pixel_histograms_halo17_NFW_lbd35.pdf}
+    \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
     \centering
-\subfigure[NFW: $\lambda=3.5$]{
-        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
-    }
-\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
-        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
-    }
-\caption{The density maps reconstructed from the mock galaxy shape catalog with
-    the NFW dictionary. The penalization parameters are $\lambda=3.5$ (left)
-    and $\lambda=5.0$ (right).  The input halo mass is $M_{200}=10^{15.02}
-    ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The vertical direction
-    is the line of sight direction. The boxes' lower boundaries and upper
-    boundaries of correspond to $z=0.01$ and $z=0.85$, respectively.
+    \small NFW: $\lambda=3.5$
+\end{minipage}
+\begin{minipage}[c]{1.0\columnwidth}
+\includegraphics[width=0.95\textwidth]{pixel_histograms_halo17_NFW_lbd50.pdf}
+    \includezraphics{delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
+    \centering
+    \small
+    NFW: $\lambda=5.0$
+\end{minipage}
+\caption{The lower panels show the density maps reconstructed from the mock
+    galaxy shape catalog with the NFW dictionary. The upper panels show the
+    pixels' number histograms.  The penalization parameters are $\lambda=3.5$
+    (left) and $\lambda=5.0$ (right).  The input halo mass is
+    $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The
+    vertical direction is the line of sight direction. The boxes' lower
+    boundaries and upper boundaries of correspond to $z=0.01$ and $z=0.85$,
+    respectively.
     } \label{fig_NFW3D}
@@
 the atoms in the dictionary (concentration equals four) . We note that each
-frame of our dictionary fixes the scale radius in the comoving space;
+frame of our dictionary fixes the scale radius in the comoving coordinates;
 therefore, the NFW atoms have different angular radii in different lens
@@
 the preliminary lasso estimation, which are $3.5$, $4.0$, and $5.0$. The
-corresponding regularization parameters for the final adaptive lasso estimations
-are set to $\lambda_{\rm{ada}}=\lambda^{\tau+1}$.  Here, we note that both the
-preliminary lasso estimation and the final adaptive lasso estimation select the
-pixels with the signal-to-noise ratios (SNRs) greater than $\lambda$ in each
-gradient descent iteration. While the final adaptive lasso estimation further
-enhances the growth of the pixels with preliminary estimations greater than
-$\lambda$.
+corresponding regularization parameters for the final adaptive lasso
+estimations are set to $\lambda_{\rm{ada}}=\lambda^{\tau+1}$.  Here, we note
+that both the preliminary lasso estimation and the final adaptive lasso
+estimation select the pixels with the signal-to-noise ratios (SNRs) greater
+than $\lambda$ in each gradient descent iteration and estimate the density in
+the selected pixels. While the final adaptive lasso estimation further enhances
+the growth of the pixels with preliminary estimations greater than $\lambda$.
 
@@
 different penalization parameters for a halo with $M_{200}=10^{15.02}
-~h^{-1}M_{\odot}$ at redshift $0.164$.  As we can see from the reconstructed
-density maps, the adaptive lasso algorithm sets most of the reconstructed
-pixels to zero and only keeps the pixels with large amplitudes.  We identify
-the peaks on the reconstructed sparse density map.
+~h^{-1}M_{\odot}$ at redshift $0.164$. Also, the pixels' histograms are shown
+in Figure \ref{fig_NFW3D}. From these plots, we conclude that the adaptive
+lasso algorithm sets most of the reconstructed pixels to zero and only keeps
+the modes strongly related to the data. Moreover, the reconstructed density maps
+do not suffer from the line of sight smearing. After the reconstruction for
+each simulation, we identify the peaks on the sparse density map.
 

### 2020-12-09 doc/paper_ms_method_HSCY1/ms.tex
revise writing

@@
 \begin{abstract}
-A new method is developed to reconstruct $3$-D density contrast maps from
-photometric weak-lensing shear measurements. The $3$-D density contrast maps
-are modeled as a summation of the NFW basis atoms, which have $2$-D multi-scale
-NFW surface density profiles on the transverse plane and $1$-D Dirac delta
-functions in the line of sight direction. With the prior assumption that the
-density fields have a sparse spatial distribution, the density fields are
-reconstructed using an oracle algorithm: adaptive lasso. The method is tested
-with realistic simulations using the HSC-like shape estimation error and
-photo-$z$ uncertainty.  Our findings are summarized as follows: 1) The lasso
-solution suffers from a smear of structure in the line of sight direction even
-in the absence of shape noise. In contrast, the adaptive lasso algorithm
-efficiently removes the line of sight smear of structure.  2) The algorithm is
-able to detect halo with minimal mass limits of $10^{14.0} M_{\odot}/h$,
-$10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median
-($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts, respectively, with a
-false detection of 0.022/deg$^2$.  3) The estimated redshift of the halos
-detected from the reconstructed mass maps are lower than the true redshift by
-about $0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshift
-bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$.
+A new method is developed to reconstruct three-dimensional density contrast
+maps from photometric weak-lensing shear measurements. The three-dimensional
+density contrast maps are modeled as a summation of the NFW basis atoms, which
+have two-dimensional multi-scale NFW surface density profiles on the transverse
+plane and one-dimensional Dirac delta functions in the line of sight direction.
+With the prior assumption that the density fields have a sparse spatial
+distribution, the density fields are reconstructed using an oracle algorithm:
+adaptive lasso. The method is tested with realistic simulations using the
+HSC-like shape estimation error and photometric redshift uncertainty.  Our
+findings are summarized as follows: 1) The lasso solution suffers from a smear
+of structure in the line of sight direction even in the absence of shape noise.
+In contrast, the adaptive lasso algorithm efficiently removes the line of sight
+smear of structure.  2) The algorithm is able to detect halo with minimal mass
+limits of $10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0}
+M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high
+($0.6\leq z< 0.85$) redshifts, respectively, with a false detection of
+0.022/deg$^2$.  3) The estimated redshift of the halos detected from the
+reconstructed mass maps are lower than the true redshift by about $0.03$ for
+halos at low redshifts ($z\leq 0.4$). The relative redshift bias is below
+$0.5\%$ for halos at $0.4<z\leq 0.85$.
 \end{abstract}
@@
 \delta, \end{equation} where $\mathbf{T}$ is used to denote the linear
-transformation operator, which includes not only the physical lensing effect but
-also systematic effects from observations (e.g., pixelization and smoothing of
-the shear field in the transverse plane, photo-$z$ uncertainty).
+transformation operator, which includes not only the physical lensing effect
+but also systematic effects from observations (e.g., pixelization and smoothing
+of the shear field in the transverse plane, photometric redshift
+uncertainty).
 
@@
 The reconstruction of density map from shear measurements also receive
-considerable interest as it reaches the nonlinear scales. The $2$-D density map
-reconstruction which recovers an integration of projected mass along the line of
-sight has been well studied within the community
+considerable interest as it reaches the nonlinear scales. The two-dimensional
+($2$-D) density map reconstruction which recovers an integration of projected
+mass along the line of sight has been well studied within the community
 \citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
@@
 \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However,
-the reconstruction of $3$-D mass map is still a challenging task.
+the reconstruction of three-dimensional ($3$-D) mass map is still a challenging
+task.
 
@@
 Subsequently, in Section \ref{subsec_method_Systematics}, we discuss several
-systematic effects from observations which include photo-$z$ uncertainty
-(Section \ref{subsec_method_photoz}), smoothing (Section
-\ref{subsec_method_smoothing}), masking(Section \ref{subsec_method_msknoise}),
-and pixelization (Section \ref{subsec_method_pixel}).
+systematic effects from observations which include photometric redshift
+(photo-$z$) uncertainty (Section \ref{subsec_method_photoz}), smoothing
+(Section \ref{subsec_method_smoothing}), masking(Section
+\ref{subsec_method_msknoise}), and pixelization (Section
+\ref{subsec_method_pixel}).
 
@@
 
-Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}),
+Combining eq. (\ref{eq-delta2kappa}) with eq. (\ref{eq-kappa2gamma}),
 the expectation of lensing shear signal is
@@
 halos \citep{haloModel-TJ2003-3pt} with comoving scale radii $r_s$ and
-truncation radius $c r_s$, where $c$ is the concentration of the NFW
-halos.  As the scales of halos are much smaller than the reachable redshift
-resolution, we neglect the depth of halo on the line of sight direction and set
-the NFW atoms' profiles in the line of sight direction to $1$-D Dirac delta
+truncation radius $c r_s$, where $c$ is the concentration of the NFW halos.  As
+the scales of halos are much smaller than the reachable redshift resolution, we
+neglect the depth of halo on the line of sight direction and set the NFW atoms'
+profiles in the line of sight direction to one-dimensional ($1$-D) Dirac delta
 functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. The
@@
     $z=0.01$ and $z=0.85$, respectively. Noises on galaxy shape measurements
-    are neglected in the simulation.  The input halo mass is $M_{200}=10^{15}
-    ~h^{-1}M_{\odot}$, and its redshift is $z=0.35$. The lasso reconstruction
-    smears the density field along the line of sight direction.
+    are neglected in the simulation.  The input halo's virial mass is
+    $M_{200}=10^{15} ~h^{-1}M_{\odot}$, and its redshift is $z=0.35$. The lasso
+    reconstruction smears the density field along the line of sight direction.
     } \label{fig_lassoVsadaLasso}
@@
 Figure \ref{fig_lassoVsadaLasso} shows the reconstructions of a single halo's
-mass map with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift
+mass map with virial mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift
 $0.35$. The shear measurement error and photo-$z$ uncertainty are not included

### 2020-12-20 python/haloSim.py
Papers to read (science) 	new file:   doc/ref/clusterDet_weaklens.md Pixelation has to be changed to     pix -> smooth instead of     smooth -> pix since the previous operation is too slow. Now we can use FFT to smooth after pixelation. TODO: How much aliasing power is caused? 	modified:   notebook/s19/pixelation.ipynb 	modified:   python/haloSim.py 	modified:   python/halolet.py 	modified:   python/pixel3D.py

@@ -581,29 +581,39 @@ def haloCS02SigmaAtom(r_s,ngrid,c=9.,smooth_scale=-1,fou=True):
     else:
         return np.real(np.fft.ifft2(atomFou))
 
-def GausAtom(sigma,ngrid,fou=True):
-    """ Normalized Gaussian in a postage stamp
-    @param ngrid      number of pixel in x and y directions.
-    @param sigma      scale factortor of the Gaussian function
+def GausAtom(sigma,ny,nx=None,fou=True,lnorm=2):
     """
-    if sigma>0.1:
-        x,y =   np.meshgrid(np.fft.fftfreq(ngrid),np.fft.fftfreq(ngrid))
+    Normalized Gaussian in a postage stamp
+    normalized by l2 norm
+    Parameters:
+    --------------
+    ny:     int
+    number of pixel y directions.
+    nx:     int [default=None]
+    number of pixel x directions.
+    sigma:  float
+    scale factortor of the Gaussian function
+    """
+    if nx is None:
+        nx=ny
+    if sigma>0.:
+        x,y =   np.meshgrid(np.fft.fftfreq(nx),np.fft.fftfreq(ny))
         if fou:
             x  *=   (2*np.pi);y*=(2*np.pi)
             rT  =   np.sqrt(x**2+y**2)
             fun =   np.exp(-(rT*sigma)**2./2.)
-            norm=   np.sqrt(np.sum(fun**2.))/ngrid
+            norm=   (np.sum(fun**lnorm)/(nx*ny))**(1./lnorm)
         else:
-            x  *=   (ngrid);y*=(ngrid)
+            x  *=   (nx);y*=(ny)
             rT  =   np.sqrt(x**2+y**2)
             fun =   1./np.sqrt(2.*np.pi)/sigma*np.exp(-(rT/sigma)**2./2.)
-            norm=   np.sqrt(np.sum(fun**2.))
+            norm=   (np.sum(fun**lnorm))**(1./lnorm)
         return  fun/norm
     else:
         if fou:
-            return np.ones((ngrid,ngrid))
+            return np.ones((ny,nx))
         else:
-            out =   np.zeros((ngrid,ngrid))
+            out =   np.zeros((ny,nx))
             out[0,0]=1
             return out
 

### 2020-12-20 python/halolet.py

@@ -48,7 +48,7 @@ class massmap_ks2D():
 class nfwShearlet2D():
     """
     A Class for 2D nfwlet transform
-    Consding the typical scale of the redshift plane
+    with different angular scale in different redshift plane
     --------
 
     Construction Keywords

### 2020-12-20 python/pixel3D.py

@@ -112,7 +112,7 @@ class cartesianGrid3D():
         self.pozPdfAve=None
         return
 
-    def pixelize_data(self,x,y,z,v,ws=None):
+    def pixelize_data(self,x,y,z,v,ws=None,method='FFT'):
         """pixelize catalog into the cartesian grid
         Parameters:
         -------------
@@ -126,9 +126,33 @@ class cartesianGrid3D():
             measurements.
         ws: array [defalut: None]
             weights.
+        method: string [default: FFT]
+            method used to convolve with smoothing kernel
         """
+
         if ws is None:
             ws=np.ones(len(x))/0.25**2.
+        if self.sigma>0. and method=='sample':
+            return self._pixelize_data_sample(x,y,z,v,ws)
+        else:
+            return self._pixelize_data_FFT(x,y,z,v,ws)
+
+    def _pixelize_data_FFT(self,x,y,z,v,ws=None):
+        dataOut=numpy.histogramdd((x,y,z),bins=(self.xbound,self.ybound,self.zbound), weights=v*ws)[0]
+        weightOut=numpy.histogramdd((x,y,z),bins=(self.xbound,self.ybound,self.zbound), weights=ws)[0]
+        dataOut=dataOut/weightOut
+        assert dataOut.shape==self.shape
+        varOut=np.zeros(self.shape,dtype=float)
+        # truncate the smoothing kernel
+        # to 3 times of sigma
+        if self.sigma>0:
+            rsig=int(self.sigma/self.delta*3+1)
+        else:
+            pass
+
+        return
+
+    def _pixelize_data_sample(self,x,y,z,v,ws=None):
         xbin=np.int_((x-self.xbound[0])/self.delta)
         ybin=np.int_((y-self.ybound[0])/self.delta)
         if z is None:
@@ -140,6 +164,7 @@ class cartesianGrid3D():
         if self.sigma>0:
             rsig=int(self.sigma/self.delta*3+1)
         else:
+            raise ValueError("smoothing scale should be larger than zero")
             return
         for iz in range(self.shape[0]):
             if z is not None:

### 2020-12-22 doc/paper_ms_method_HSCY1/ms.tex
add slides

--- 2020-12-07 doc/paper_ms_method_HSCY1/ms.tex
@@
 the foreground density contrast field ($\delta$) through a linear
-transformation: \begin{equation} \label{eq-intro-delta2shear} \gamma=\mathbf{T}
-\delta, \end{equation} where $\mathbf{T}$ is used to denote the linear
+transformation:
+\begin{equation} \label{eq-intro-delta2shear}
+    \gamma=\mathbf{T} \delta,
+\end{equation}
+where $\mathbf{T}$ is used to denote the linear
 transformation operator, which includes not only the physical lensing effect but

### 2020-12-22 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex

@@
 
-We select peaks with values greater than an ad-hoc threshold as candidates of
-galaxy clusters following \citet{HSC1-massMap-cluster}.  The threshold is set
-to a few times the standard deviation of the noise peaks. We use different
-detection thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters
-from the mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and
-middle columns of Figure \ref{fig_detFalsRateNFW} show the detection rates for
-halos in the (mass, redshift) planes with detection thresholds set to
-$1.5\sigma$ and $3.0\sigma$ of the noise peaks' distributions, respectively.
-The right column of Figure \ref{fig_detFalsRateNFW} shows the corresponding
-numbers of false detections per square degree as functions of detection
-thresholds. The first, second, and third rows of Figure
-\ref{fig_detFalsRateNFW} correspond to the $lambda=3.5,4.0,5.0$, respectively.
+With the intent to suppress false detections, we select peaks with values
+greater than an ad-hoc threshold as candidates of galaxy clusters following
+\citet{HSC1-massMap-cluster}.  The threshold is set to a few times the standard
+deviation of the noise peaks. We use different detection thresholds
+($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters from the mass maps
+reconstructed with $\lambda=3.5,4.0,5.0$. The left and middle columns of Figure
+\ref{fig_detFalsRateNFW} show the detection rates for halos in the (mass,
+redshift) planes with detection thresholds set to $1.5\sigma$ and $3.0\sigma$
+of the noise peaks' distributions, respectively.  The right column of Figure
+\ref{fig_detFalsRateNFW} shows the corresponding numbers of false detections
+per square degree as functions of detection thresholds. The first, second, and
+third rows of Figure \ref{fig_detFalsRateNFW} correspond to the
+$lambda=3.5,4.0,5.0$, respectively.
 

### 2020-12-22 doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex

@@
 group, we smooth the preliminary lasso estimation in each lens redshift bin
-with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc. The smoothed
+with a top-hat filter of comoving diameter: $0.25~h^{-1}$ Mpc. The smoothed
 preliminary lasso estimation is denoted as $\hat{x}^{\rm{ls}}_{\rm{sm}}$, and
@@
 $\hat{w}=1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.
-The regularization parameter for the adaptive lasso is set to
-$\lambda_{\rm{ada}}=\lambda$.
-As we have done on the NFW dictionary's reconstruction, we smooth the
-reconstructed density maps with the Gaussian kernel (scale radius equals
-$1.\arcmin 5$) in each lens redshift plane.
 
@@
 \centering
-\subfigure[Point Mass: $\lambda=3.5$]{
+\begin{minipage}[c]{1.0\columnwidth}
     \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
-        }
-\subfigure[Point Mass: $\lambda=5.0$]{
+    \centering
+    \small Point Mass: $\lambda=3.5$
+\end{minipage}
+\begin{minipage}[c]{1.0\columnwidth}
     \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
-        }
+    \centering
+    \small Point Mass: $\lambda=5.0$
+\end{minipage}
 \caption{The density maps reconstructed from the mock galaxy shape catalog with

### 2020-12-22 python/haloSim.py
try on small patch of XMM

@@ -546,20 +546,28 @@ class nfw_lensTJ03():
 """
 The following functions are used for halolet construction
 """
-def haloCS02SigmaAtom(r_s,ngrid,c=9.,smooth_scale=-1,fou=True):
+def haloCS02SigmaAtom(r_s,ny,nx=None,c=9.,smooth_scale=-1,fou=True):
     """Make haloTJ03 atom from Fourier space as CS02.
     https://arxiv.org/pdf/astro-ph/0206508.pdf
     Eq.(81) Eq.(82)
-    @param r_s        scale radius [unit of pixel].
-    @param ngrid      number of pixel in x and y directions.
-    @param c          truncation ratio (concentration)
-    @param fou        in Fourier space
+    Parameters:
+    -----------
+    r_s     [float]
+            scale radius (in unit of pixel).
+    ny,nx   [int]
+            number of pixel in y and x directions.
+    c       [float]
+            truncation ratio (concentration)
+    fou     [bool]
+            in Fourier space
     """
-    x,y=np.meshgrid(np.fft.fftfreq(ngrid),np.fft.fftfreq(ngrid))
+    if nx is None:
+        nx=ny
+    x,y=np.meshgrid(np.fft.fftfreq(nx),np.fft.fftfreq(ny))
     x*=(2*np.pi);y*=(2*np.pi)
     rT=np.sqrt(x**2+y**2)
     if r_s<=0.1:
-        atomFou=np.ones((ngrid,ngrid))
+        atomFou=np.ones((ny,nx))
     else:
         A= 1./(np.log(1+c)-c/(1.+c))
         r=rT*r_s
@@ -573,7 +581,7 @@ def haloCS02SigmaAtom(r_s,ngrid,c=9.,smooth_scale=-1,fou=True):
         atomFou[~mask]=1.+A*(c+c**3/(6*(1 + c))+1/4.*(-2.*c-c**2.-2*np.log(1+c)))*r0**2.
     if smooth_scale>.1:
         atomFou =   atomFou*np.exp(-(rT*smooth_scale)**2./2.)
-    norm = np.sqrt(np.sum(atomFou*np.conj(atomFou)))/ngrid
+    norm = np.sqrt(np.sum(atomFou*np.conj(atomFou)/nx/ny))
     # Normalize
     atomFou=atomFou/norm
     if fou:

### 2020-12-22 python/halolet.py

@@ -45,16 +45,17 @@ class massmap_ks2D():
             gOMap    =   np.fft.ifft2(gOMap)
         return gOMap
 
+
 class nfwShearlet2D():
     """
     A Class for 2D nfwlet transform
     with different angular scale in different redshift plane
     --------
 
-    Construction Keywords
+    Construction Parser
     -------
     nframe  :   number of frames
-    ngrid   :   size of the field (pixel)
+    ny,nx   :   size of the field (pixel)
     smooth_scale:   scale radius of Gaussian smoothing kernal (pixel)
 
     Methods
@@ -114,7 +115,8 @@ class nfwShearlet2D():
                 rs  =   (ifr+1)*rz
                 if rs<self.resolve_lim:
                     self.rs_frame[izl,ifr]=0.
-                    iAtomF=haloSim.GausAtom(sigma=self.smooth_scale,ngrid=self.ny,fou=True)
+                    # l2 normalized gaussian
+                    iAtomF=haloSim.GausAtom(sigma=self.smooth_scale,ny=self.ny,nx=self.nx,fou=True)
                     self.fouaframesDelta[izl,ifr]=iAtomF             # Fourier Space
                     iAtomF=self.ks2D.transform(iAtomF,outFou=True)
                     self.fouaframes[izl,ifr]=iAtomF             # Fourier Space
@@ -122,7 +124,7 @@ class nfwShearlet2D():
                     break
                 else:
                     self.rs_frame[izl,ifr]=rs
-                    iAtomF=haloSim.haloCS02SigmaAtom(r_s=rs,ngrid=self.ny,c=4.,\
+                    iAtomF=haloSim.haloCS02SigmaAtom(r_s=rs,ny=self.ny,nx=self.nx,c=4.,\
                             smooth_scale=self.smooth_scale)
                     self.fouaframesDelta[izl,ifr]=iAtomF             # Fourier Space
                     iAtomF=   self.ks2D.transform(iAtomF,outFou=True)
@@ -202,226 +204,3 @@ class nfwShearlet2D():
                     break
         return dataOut
 
-class nfwlet2D():
-    """
-    A Class for 2D nfwlet transform
-    --------
-
-    Construction Keywords
-    -------
-    nframe  :   number of frames
-    ngrid   :   size of the field (pixel)
-    smooth_scale:   scale radius of Gaussian smoothing kernal (pixel)
-
-    Methods
-    --------
[…]

### 2020-12-22 python/sparseBase.py

@@ -437,474 +437,3 @@ class massmapSparsityTaskNew():
     def write(self):
         pyfits.writeto(self.outFname,self.deltaR.real,overwrite=True)
         return
-
-class massmapSparsityTask():
-    def __init__(self,parser):
-        #display
-        self.display_iframe=0
-        if parser.has_option('file','fieldN'):
-            self.fieldN =   parser.get('file','fieldN')
-        else:
-            self.fieldN =   'test'
-        if parser.has_option('file','outDir'):
-            self.outDir =   parser.get('file','outDir')
-        else:
-            self.outDir =   './'
-
-        #sparse
-        self.aprox_method    =   parser.get('sparse','aprox_method')
-        self.lbd    =   parser.getfloat('sparse','lbd') #   For Sparsity
-        if parser.has_option('sparse','tau'):           #   For Total Square Variance
-            self.tau   =   parser.getfloat('sparse','tau')
-        else:
-            self.tau   =   0.
-        self.nframe     =   parser.getint('sparse','nframe')
-        minframe   =   parser.getint('sparse','minframe')
-        # Do debug?
-        if parser.has_option('sparse','debugList'):
-            self.debugList  =   np.array(json.loads(parser.get('sparse','debugList')))
-            self.debugRatios=[]
-            self.debugDeltas=[]
-            self.debugAlphas=[]
-        else:
-            debugList=[]
-
-        ##transverse plane
-        self.ny     =   parser.getint('transPlane','ny')
-        self.nx     =   parser.getint('transPlane','nx')
-        ##lens z axis
-        self.nlp    =   parser.getint('lensZ','nlp')
-
-        if self.nlp<=1:
-            self.zlMin  =   0.
-            self.zlscale=   1.
-        else:
-            self.zlMin  =   parser.getfloat('lensZ','zlMin')
-            self.zlscale=   parser.getfloat('lensZ','zlscale')
-        self.zlBin      =   zMeanBin(self.zlMin,self.zlscale,self.nlp)
-
-        ##source z axis
-        self.nz     =   parser.getint('sourceZ','nz')
-        if self.nz<=1:
-            self.zMin   =   0.05
-            self.zscale =   2.5
[…]

### 2021-01-04 python/sparseBase.py
match the positive peaks with the camira and WHL15 cluster catalogs

@@ -395,7 +395,8 @@ class massmapSparsityTaskNew():
         for irun in range(niter):
             dalphaR =   -self.mu*self.quad_gradient(self.alphaR).real
             Xp1 =   self.alphaR+dalphaR
-            Xp1 =   soft_thresholding_nn(Xp1,thresholds)
+            #Xp1 =   soft_thresholding_nn(Xp1,thresholds)
+            Xp1 =   soft_thresholding(Xp1,thresholds)
             tnTmp= (1.+np.sqrt(1.+4*tn**2.))/2.
             ratio= (tn-1.)/tnTmp
             self.alphaR=Xp1+(ratio*(Xp1-Xp0))

### 2021-01-06 doc/paper_ms_method_HSCY1/massmap_method.tex
change the introduction

--- 2020-12-09 doc/paper_ms_method_HSCY1/ms.tex
@@
-\documentclass[twocolumn]{aastex63}
-\emergencystretch=1.em
-
-\usepackage{amsmath,amsthm,amsfonts,amssymb,bm}
-\usepackage{physics,commath}
-
-\usepackage{listings}
-\hypersetup{breaklinks}
-\usepackage{color}
-\usepackage{graphicx}
-\usepackage{multirow}
-
-\usepackage{textcomp}
-\usepackage{epstopdf}
-\usepackage{natbib}
-\usepackage{algorithm,algcompatible}
-\usepackage[-]{callouts}
-
-\makeatletter
-\newcommand*\bigcdot{\mathpalette\bigcdot@{.5}}
-\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
-\newcommand{\argmax}{\mathop{\rm arg~max}\limits}
-\newcommand{\argmin}{\mathop{\rm arg~min}\limits}
-
-\DeclareMathOperator{\arccosh}{arccosh}
-\newcommand \redColor{\color{red}}
-
-\renewcommand\labelenumi{(\roman{enumi})}
-\renewcommand\theenumi\labelenumi
-
-\algnewcommand\INPUT{\item[\textbf{Input:}]}
-\algnewcommand\OUTPUT{\item[\textbf{Output:}]}
-
-\newcommand{\includezraphics}[1]{
-    \begin{annotate}{
-        \includegraphics[width=0.95\textwidth]{#1}
-    }{1.0}
-    \arrow { -3., -2}{ -3., 2}
-    \note {-3.,2.5}{z}
-    \end{annotate}
-}
-
-\makeatother
-
-\begin{document}
-\title{$3$-D Weak Lensing Mass Map Reconstruction:
-Reducing the line of sight smearing}
-% \author{Xiangchong Li}
-% \affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
-% \affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
-% University of Tokyo, Kashiwa 277-8583, Japan}
-% \author{Masamune Oguri}
-% \affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
-% \affiliation{Kavli Institute for the Physics and Mathematics of the Universe
-% (WPI),\\
-% University of Tokyo, Kashiwa 277-8583, Japan}
-% \affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo
-% 113-0033, Japan}
-% \author{Wentao Luo}
-% \affiliation{Kavli Institute for the Physics and Mathematics of the Universe
-% (WPI),\\
-% University of Tokyo, Kashiwa 277-8583, Japan}
-% \email{xiangchong.li@ipmu.jp}
-
-\begin{abstract}
-A new method is developed to reconstruct three-dimensional density contrast
-maps from photometric weak-lensing shear measurements. The three-dimensional
-density contrast maps are modeled as a summation of the NFW basis atoms, which
-have two-dimensional multi-scale NFW surface density profiles on the transverse
-plane and one-dimensional Dirac delta functions in the line of sight direction.
-With the prior assumption that the density fields have a sparse spatial
-distribution, the density fields are reconstructed using an oracle algorithm:
-adaptive lasso. The method is tested with realistic simulations using the
-HSC-like shape estimation error and photometric redshift uncertainty.  Our
-findings are summarized as follows: 1) The lasso solution suffers from a smear
-of structure in the line of sight direction even in the absence of shape noise.
-In contrast, the adaptive lasso algorithm efficiently removes the line of sight
-smear of structure.  2) The algorithm is able to detect halo with minimal mass
-limits of $10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0}
-M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high
-($0.6\leq z< 0.85$) redshifts, respectively, with a false detection of
-0.022/deg$^2$.  3) The estimated redshift of the halos detected from the
-reconstructed mass maps are lower than the true redshift by about $0.03$ for
-halos at low redshifts ($z\leq 0.4$). The relative redshift bias is below
-$0.5\%$ for halos at $0.4<z\leq 0.85$.
-\end{abstract}
-
-\section{Introduction}
-
-\begin{figure*}[!t] \includegraphics[width=1.\textwidth]{nfwlet-atom-2D.pdf}
-    \caption{The smoothed pixelized basis atoms. The upper row shows the basis
-        atoms in Fourier space, and the lower row shows the basis atoms in Real
-        space.  The leftmost column is the point mass atom, and the other
-        columns are the multi-scale NFW atoms.  The smoothing kernel is
-        Gaussian with a standard dev iation of $1.5$ pixels.
-    } \label{fig_atoms2D}
-\end{figure*}
-
-\begin{figure}
- \includegraphics[width=0.45\textwidth]{nfwlet-atom-1D.pdf}
-    \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The
-        corresponding $2$-D profiles are shown in Figure \ref{fig_atoms2D}.
-    }
- \label{fig_atoms1D}
-\end{figure}
-
-Weak lensing refers to the phenomenon that light from distant galaxies is
-distorted by the intervening inhomogeneous density distribution along the line
-of sight due to gravity's influence.
-As a result of the light distortion, the shapes of the background galaxies are
-coherently distorted. The lensing effect imprints the information of
-foreground mass density distribution to the background galaxy images and offers
-a direct probe into the mass density distribution in our universe
-\citep[see][for recent reviews]{revKilbinger15,revRachel17}.
-
 The expected shear measurements ($\gamma$) on distant galaxies are related to
 the foreground density contrast field ($\delta$) through a linear
-transformation: \begin{equation} \label{eq-intro-delta2shear} \gamma=\mathbf{T}
-\delta, \end{equation} where $\mathbf{T}$ is used to denote the linear
-transformation operator, which includes not only the physical lensing effect
-but also systematic effects from observations (e.g., pixelization and smoothing
-of the shear field in the transverse plane, photometric redshift
-uncertainty).
-
-Several large-scale surveys target to study the weak-lensing effect at a high
-precision level (e.g., HSC \citep{HSC1-data}, KIDS \citep{KIDS13}, DES
-\citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, NGRST
-\citep{WFIRST15}).
-
-The primary goal of most weak-lensing surveys is to constrain the cosmology
-model through the $2$-point correlations. The studies include galaxy$-$galaxy
-lensing, which cross-correlating the shear field ($\gamma$) with the positions
-of foreground galaxies
-\citep{gglens-GAMA-Han2014,gglens-BossCFHTMore2015,gglens-DES1}, and cosmic
-shear which auto-correlates the shear measurements
-\citep{cosmicShearRealKids450,cosmicShear-DES1,cosmicShear_HSC1_Chiaki2019,cosmicShear_HSC1_Hamana2019}.
-Since the shear is directly related to the foreground matter distribution as
-shown in eq. (\ref{eq-intro-delta2shear}), Galaxy$-$galaxy lensing probes into
-the correlation between the matter field and galaxy field. On the other hand,
-cosmic shear probes into the auto-correlation of matter field.
-
-The reconstruction of density map from shear measurements also receive
-considerable interest as it reaches the nonlinear scales. The two-dimensional
-($2$-D) density map reconstruction which recovers an integration of projected
-mass along the line of sight has been well studied within the community
-\citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
-and applied to large-scale surveys
-\citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However,
-the reconstruction of three-dimensional ($3$-D) mass map is still a challenging
-task.
+transformation:
+\begin{equation} \label{eq-intro-delta2shear}
+    \gamma=\mathbf{T} \delta,
+\end{equation}
+where $\mathbf{T}$ is used to denote the linear transformation operator, which
+includes not only the physical lensing effect but also systematic effects from
+observations (e.g., pixelization and smoothing of the shear field in the
+transverse plane, photo-$z$ uncertainty).
 
@@
 
-This paper is organized as follows.
-In Section \ref{sec_Method}, we propose the new method for $3$-D density map
-reconstruction.
-In Section \ref{sec_Test}, we test the novel algorithm on HSC-like simulations.
-In Section \ref{sec_Sum}, we summarize and discuss the future development of
-the method.
-
-\section{Methodology}
-\label{sec_Method}
-
 \begin{figure}
@@
 Subsequently, in Section \ref{subsec_method_Systematics}, we discuss several
-systematic effects from observations which include photometric redshift
-(photo-$z$) uncertainty (Section \ref{subsec_method_photoz}), smoothing
-(Section \ref{subsec_method_smoothing}), masking(Section
-\ref{subsec_method_msknoise}), and pixelization (Section
-\ref{subsec_method_pixel}).
+systematic effects from observations which include photo-$z$ uncertainty
+(Section \ref{subsec_method_photoz}), smoothing (Section
+\ref{subsec_method_smoothing}), masking(Section \ref{subsec_method_msknoise}),
+and pixelization (Section \ref{subsec_method_pixel}).
 
@@
 With the approximation that the density of galaxy number - $n(\vec{r})$ -
-varies slowly at the smoothing scale, the smoothed galaxy number density,
-which is defined as
+varies slowly at the smoothing scale, the smoothed galaxy number density (in
+unit of number per pixel), which is defined as
 \begin{equation}\label{eq-numDesSmooth}
@@
 \end{algorithm}
-
-\section{Tests}
-\label{sec_Test}
-
-This Section simulates weak-lensing shear fields induced by a group of NFW
-halos with various halo masses and redshifts. The shear fields are used to
-distort the HSC mock shape catalogs with different realizations of the HSC-like
-shape measurement error and photo-$z$ uncertainty (Section \ref{subsec_Sims}).
-
-Then, we test our algorithm using the simulations with different setups of the
-regularization parameter. We also compare the results of our algorithm, which
-uses the NFW dictionary (Section \ref{subsec_test-nfw}), with the point mass
-dictionary (Section \ref{subsec_test-pm}).
-
-\subsection{Simulations}
-\label{subsec_Sims}
-\input{massmap_sim.tex}
-
-\subsection{NFW atoms}
-\label{subsec_test-nfw}
-\input{sparse_NFW_results.tex}
-
-\subsection{Point mass atoms}
-\label{subsec_test-pm}
-\input{sparse_PointMass_results.tex}
-
-\section{Summary}
-\label{sec_Sum}
-
-We develop a novel method to reconstruct $3$-D density contrast maps from
-weak-lensing shear measurements and photometric redshift estimations.  Our
-method models $3$-D density contrast maps as summations of NFW atoms with
-different comoving radii.  With the prior assumption that the clumpy masses
-sparsely distribute in the $3$-D space, the density map is reconstructed
-using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}. The method is
-tested with realistic simulations using HSC-like shape estimation error and
-photo-$z$ uncertainty.
-
-The findings of this paper are summarized as follows:
-
-(i) The lasso algorithm's solution suffers from a smear of structure in the
-line of sight direction even in the absence of shape noise, and the adaptive
-lasso algorithm efficiently removes the line of sight smear of structure.
-
-(ii) The algorithm is able to detect halo with minimal mass limits of
-$10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for
-the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$)
-redshifts, respectively, with a false detection of 0.022/deg$^2$.
-
-(iii)The estimated redshifts of the halos detected from the reconstructed mass
-maps are lower than the true redshift by about $0.03$ for halos at low
-redshifts ($z\leq 0.4$).  The relative redshift bias is below $0.5\%$ for halos
-at $0.4<z\leq 0.85$.
-
-We will apply the method to the shear measurements of the HSC survey
-\citep{HSC1-catalog,FPFSHSC1-Li2020} to perform galaxy cluster detection in our
-future work.
-
-\section*{Acknowledgements}
-XL thank Yin Li and Jiaxin Han for useful discussions.
-
-XL was supported by Global Science Graduate Course (GSGC) program of
-University of Tokyo and JSPS KAKENHI (JP19J22222).
-\bibliographystyle{aasjournal}
-\bibliography{citation}
-
-\end{document}

### 2021-01-06 doc/paper_ms_method_HSCY1/ms.tex
change the introduction

@@
 \begin{document}
-\title{$3$-D Weak Lensing Mass Map Reconstruction:
-Reducing the line of sight smearing}
+\title{Cluster Detection from three-dimensional Lensing Mass Map}
 % \author{Xiangchong Li}
@@
 \begin{abstract}
-A new method is developed to reconstruct $3$-D density contrast maps from
-photometric weak-lensing shear measurements. The $3$-D density contrast maps
-are modeled as a summation of the NFW basis atoms, which have $2$-D multi-scale
-NFW surface density profiles on the transverse plane and $1$-D Dirac delta
-functions in the line of sight direction. With the prior assumption that the
-density fields have a sparse spatial distribution, the density fields are
-reconstructed using an oracle algorithm: adaptive lasso. The method is tested
-with realistic simulations using the HSC-like shape estimation error and
-photo-$z$ uncertainty.  Our findings are summarized as follows: 1) The lasso
-solution suffers from a smear of structure in the line of sight direction even
-in the absence of shape noise. In contrast, the adaptive lasso algorithm
-efficiently removes the line of sight smear of structure.  2) The algorithm is
-able to detect halo with minimal mass limits of $10^{14.0} M_{\odot}/h$,
-$10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median
-($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts, respectively, with a
-false detection of 0.022/deg$^2$.  3) The estimated redshift of the halos
-detected from the reconstructed mass maps are lower than the true redshift by
-about $0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshift
-bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$.
+A new method is developed to reconstruct three-dimensional mass maps from
+photometric weak-lensing shear measurements. The three-dimensional mass map is
+modeled as a summation of the NFW basis atoms, which have two-dimensional
+multi-scale NFW surface density profiles on the transverse plane and
+one-dimensional Dirac delta functions in the line of sight direction.  The
+adaptive lasso algorithm is applied to find a sparse reconstruction of the mass
+maps.
+We study the performance of cluster detection from the reconstruction mass map
+with simulations that applies shear field from isolated halo to HSC-like galaxy
+shapes and photometric redshifts.
+Our findings are summarized as follows:
+1) The lasso solution suffers from a smear of structure in the line of sight
+direction even in the absence of shape noise, and in contrast, the adaptive
+lasso algorithm efficiently removes the line of sight smear.
+2) The algorithm is able to detect halo with minimal mass limits of $10^{14.0}
+M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low
+($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts,
+respectively, with a false detection of 0.022/deg$^2$.
+3) The estimated redshift of the halos detected from the reconstructed mass
+maps are lower than the true redshift by about $0.03$ for halos at low
+redshifts ($z\leq 0.4$). The relative redshift bias is below $0.5\%$ for halos
+at $0.4<z\leq 0.85$.
 \end{abstract}
@@
 Weak lensing refers to the phenomenon that light from distant galaxies is
-distorted by the intervening inhomogeneous density distribution along the line
-of sight due to gravity's influence.
-As a result of the light distortion, the shapes of the background galaxies are
-coherently distorted. The lensing effect imprints the information of
-foreground mass density distribution to the background galaxy images and offers
-a direct probe into the mass density distribution in our universe
-\citep[see][for recent reviews]{revKilbinger15,revRachel17}.
-
-The expected shear measurements ($\gamma$) on distant galaxies are related to
-the foreground density contrast field ($\delta$) through a linear
-transformation:
-\begin{equation} \label{eq-intro-delta2shear}
-    \gamma=\mathbf{T} \delta,
-\end{equation}
-where $\mathbf{T}$ is used to denote the linear
-transformation operator, which includes not only the physical lensing effect but
-also systematic effects from observations (e.g., pixelization and smoothing of
-the shear field in the transverse plane, photo-$z$ uncertainty).
-
-Several large-scale surveys target to study the weak-lensing effect at a high
+weakly yet coherently distorted by the intervening inhomogeneous density
+distribution along the line of sight due to gravity's influence.  As a result,
+the shapes of the background galaxies are distorted and the information of the
+foreground mass distribution is imprinted to the background galaxy images. Weak
+lensing offers a direct probe into the mass distribution, including both
+visible matter and invisible dark matter, in our universe \citep[see][for
+recent reviews]{revKilbinger15,revRachel17}.
+Several large-scale surveys focus on studying the weak-lensing effect at a high
 precision level (e.g., HSC \citep{HSC1-data}, KIDS \citep{KIDS13}, DES
@@
 
-The primary goal of most weak-lensing surveys is to constrain the cosmology
-model through the $2$-point correlations. The studies include galaxy$-$galaxy
-lensing, which cross-correlating the shear field ($\gamma$) with the positions
-of foreground galaxies
-\citep{gglens-GAMA-Han2014,gglens-BossCFHTMore2015,gglens-DES1}, and cosmic
-shear which auto-correlates the shear measurements
-\citep{cosmicShearRealKids450,cosmicShear-DES1,cosmicShear_HSC1_Chiaki2019,cosmicShear_HSC1_Hamana2019}.
-Since the shear is directly related to the foreground matter distribution as
-shown in eq. (\ref{eq-intro-delta2shear}), Galaxy$-$galaxy lensing probes into
-the correlation between the matter field and galaxy field. On the other hand,
-cosmic shear probes into the auto-correlation of matter field.
+% The primary goal of most weak-lensing surveys is to constrain the cosmology
+% model through the $2$-point correlations. The studies include galaxy$-$galaxy
+% lensing, which cross-correlating the shear field ($\gamma$) with the positions
+% of foreground galaxies
+% \citep{gglens-GAMA-Han2014,gglens-BossCFHTMore2015,gglens-DES1}, and cosmic
+% shear which auto-correlates the shear measurements
+% \citep{cosmicShearRealKids450,cosmicShear-DES1,cosmicShear_HSC1_Chiaki2019,cosmicShear_HSC1_Hamana2019}.
+% Since the shear is directly related to the foreground matter distribution as
+% shown in eq. (\ref{eq-intro-delta2shear}), Galaxy$-$galaxy lensing probes into
+% the correlation between the matter field and galaxy field. On the other hand,
+% cosmic shear probes into the auto-correlation of matter field.
 
-The reconstruction of density map from shear measurements also receive
-considerable interest as it reaches the nonlinear scales. The $2$-D density map
-reconstruction which recovers an integration of projected mass along the line of
-sight has been well studied within the community
+The reconstruction of density map from shear measurements has received
+considerable interest since
+we can constrain the cosmology model using the peak counts, which are
+identified from the weak lensing mass map
+\citep{WL-massMap-peakcounts-Jain2000,WL-massMap-peakcountsAna-Fan2010,WL-massMap-peakcountsFM-Lin2016}.
+Moreover, we can directly detect massive clusters through
+identifying high signal-to-noise (SNR) peaks on the mass map without any
+reference to the mass-to-light ratio
+\citep{WL-massMap-clusDet-Schneider1996,WL-massMap-clusDet-Hamana2004}.
+
+The two-dimensional ($2$-D) density map reconstruction which recovers an
+integration of projected mass along the line of sight has been well studied
+within the community
 \citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
 and applied to large-scale surveys
-\citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However,
-the reconstruction of $3$-D mass map is still a challenging task.
+\citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}.
+Galaxy clusters are detected from the $2$-D mass map
+\citep{WL-massMap-clusDet-CFHT-Shan2012,WL-massMap-clusDet-HSC-Miyazaki2018,WL-massMap-clusDet-HSC-Hamana2020};
+however, cross matching with some (e.g., optically selected) cluster
+catalog is needed to assign the redshift and extract its physical parameter
+(such as mass) for each cluster selected from $2$-D mass map.
 
-To fully reconstruct the $3$-D mass density distribution ($\delta$) from the
-photometric shear observations ($\gamma$), the density contrast field is
-modeled as a summation of basis atoms in a model dictionary:
-\begin{equation} \label{eq-intro-dict}
- \delta= \mathbf{\Phi} x,
-\end{equation}
-where $\mathbf{\Phi}$ is the transformation operator from the projection
-coefficient field to the density contrast, and $x$ denotes the projection
-coefficients. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density
-field in Fourier space, which is equivalent to modeling the mass field with
-sinusoidal functions.  On the other hand,
-\citet{LSS-massMap-Glimpse3D-Leonard2014} model the mass field with Starlets
-\citep{Starlet-Starck2015}.
+On the other hand, \citet{WL-clusDet-Hennawi2005} propose to detect clusters
+from smoothed shear measurements after convolving tomographic shear
+measurements with $3$-D filters that match the tangential shears induced by
+multi-scale NFW halos.
+Alternatively, we can directly reconstruct $3$-D mass maps taking advantage of
+photometric redshift (photo-$z$) information
+\citep{LSS-massMap-Wiener-Simon2009,WL-massMap-VanderPlas2011}; however, these
+methods either do not have enough spatial resolution to identify clusters, or
+they suffer from smears along the line of sight direction, which need to be
+overcome for practical searches of clusters in 3D mass maps.
 
-The projection coefficients are estimated by optimizing a regularized loss
-function. The estimator is generally defined as
-\begin{equation}
-\hat{x}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma-
-\mathbf{T\Phi} x)}_2^2+ \lambda C(x) \right\},
-\end{equation}
-where $\norm{\Sigma^{-\frac{1}{2}}(\gamma - \mathbf{T\Phi} x)}_2^2$ is the
-$l^2$ chi-square term\footnote{weighted by the inverse of the diagonal
-covariance matrix of the error on the shear measurements ($\Sigma$).} measuring
-the difference between the prediction and the data, while $C(x)$ is the
-regularization term measuring the deviation of the coefficient estimation
-($x$) from the prior assumption. The $l^p$ norm is defined as
-\begin{equation}
-\norm{x}_p=(\sum_{i} |x|^p_i)^{\frac{1}{p}}.
-\end{equation}
-Such penalized estimation prefers the parameters that are able to describe the
-observations and align with the prior assumption. The regularization
-parameter $\lambda$ adjusts the relative weight between the data and
-prior assumption in the optimization process.
-
-\citet{LSS-massMap-Wiener-Simon2009} propose to use the Wiener filter, which is
-also known as $l^2$ ridge regulation ($C=\norm{x}^2_2$), to find a regularized
-solution in Fourier space. \citet{HSC1-massMaps} apply the method of
-\citet{LSS-massMap-Wiener-Simon2009} to the first-year data of the Hyper
-Suprime-Cam Survey \citep{HSC1-data}.  However, the density maps reconstructed
-by this method suffer from smearing along the line of sight direction with a
-standard deviation of $\sigma_z=0.2 \sim 0.3$.
-
-\citet{LSS-massMap-Glimpse3D-Leonard2014} propose the Glimpse algorithm, which
-uses a derivative version of $l^1$ lasso regulation ($C=\norm{x}^1_1$) to find
-a sparse solution in the Starlet dictionary space \citep{Starlet-Starck2015}.
-\citet{LSS-massMap-Glimpse3D-Leonard2014} apply a greedy coordinate descent
-algorithm, which selects the steepest coordinate in each iteration, to find the
-minimum of a non-convex loss function penalized with the firm thresholding
-function. The Glimpse algorithm reduces the smearing along the line of sight
-since the coordinate descent algorithm forces the structure to grow only on the
-most related lens redshift plane.  However, the stability of the non-convex
-optimization and greedy coordinate descent algorithm has not been fully
-justified. Moreover, the Starlet dictionary are not designed to model the
-profile of clumpy mass in the universe, and the Starlet dictionary does not
-account for the angular scale difference at different lens redshifts.
-
-$N$-body simulations have shown that the dark matter is distributed in halos
-connected by filaments, and the density profile of a single halo follows the
-NFW function \citep{halo-NFW1997ApJ}.  We construct a model dictionary with the
-multi-scale NFW atoms.  The atoms follow multi-scale surface density profiles
-of the NFW functions \citep{haloModel-TJ2003-3pt} on the transverse plane.
-Following \citet{LSS-massMap-Glimpse3D-Leonard2014}, we neglect the depth of
-halos since the resolution scale of the reconstruction in the line of sight
-direction is much larger than the halo scale. Therefore, we set the NFW atoms'
-profile in the line of sight direction as the Dirac delta function.  Moreover,
-we assume that the halos are sparsely distributed in the universe.  With the
-sparsity prior, the adaptive lasso regularization \citep{AdaLASSO-Zou2006} is
-used to reconstruct the density field.  We find that, in contrast to the lasso
-estimator that smears the structure along the line of sight, the adaptive lasso
-can efficiently reduce the smearing effect.
-
-Compared with \citet{LSS-massMap-Glimpse3D-Leonard2014}, our dictionary is
-built up to describe the clumpy mass in the universe with a clear physical
-motivation. Furthermore, the adaptive lasso algorithm is strictly convex and
-can be directly optimized with the FISTA algorithm \citep{FISTA-Beck2009}
-without relying on any greedy coordinate descent approaches. The stability of
-this convex optimization has been justified.
+In this paper, we develop a novel method for high-resolution $3$-D mass map
+reconstruction that are free from line of sight smears and study the
+performance of cluster detection from the reconstructed mass maps.  The $3$-D
+mass map is modeled as a summation of the NFW \citep{halo-NFW1997ApJ} basis
+atoms, which have $2$-D multi-scale NFW surface density profiles on the
+transverse plane and one-dimensional Dirac delta functions in the line of sight
+direction. The adaptive lasso algorithm \citep{AdaLASSO-Zou2006} is applied to
+find a sparse reconstruction of the mass maps.
 
@@
 reconstruction.
-In Section \ref{sec_Test}, we test the novel algorithm on HSC-like simulations.
+In Section \ref{sec_Test}, we study the cluster detection from the
+reconstructed mass map using isolated halo simulations with the HSC
+observational condition.
 In Section \ref{sec_Sum}, we summarize and discuss the future development of
@@
 
-\section{Methodology}
+\section{$3$-D Mass Map Reconstruction}
 \label{sec_Method}
+\input{massmap_method.tex}
 
-\begin{figure}
- \centering
- \includegraphics[width=0.45\textwidth]{photo-z_binning.pdf}
- \caption{The source galaxies are binned into $10$ redshift bins according to
-     their Machine Learning and photo-Z (MLZ) best photo-$z$ estimation. The
-     blue histogram is the normalized number distribution of the best photo-$z$
-     estimation. The vertical dashed lines are the boundaries of the redshift
-     bins.  The galaxies are equal-number binned.
-        } \label{fig_bestpz}
-\end{figure}
-
-We first review the lensing process in Section \ref{subsec_method_delta2shear}.
-Then, we introduce the dictionary used to model the foreground density maps in
-Section \ref{subsec_method_dictionary}.
-
-Subsequently, in Section \ref{subsec_method_Systematics}, we discuss several
-systematic effects from observations which include photo-$z$ uncertainty
-(Section \ref{subsec_method_photoz}), smoothing (Section
-\ref{subsec_method_smoothing}), masking(Section \ref{subsec_method_msknoise}),
-and pixelization (Section \ref{subsec_method_pixel}).
-
-Finally, we solve the mass reconstruction problem in Section
-\ref{subsec_method_reconstruction} using the adaptive lasso algorithm
-\citep{AdaLASSO-Zou2006} optimized with the FISTA algorithm
-\citep{FISTA-Beck2009}.
-
-\subsection{Lensing}
-\label{subsec_method_delta2shear}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.45\textwidth]{mlz-poz.pdf}
- \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.
-        }\label{fig_pdfpz}
-\end{figure}
-
-The lensing convergence map at the comoving distance $\chi_s$ caused by the
-foreground inhomogeneous density distribution at the comoving distance $\chi_l$
-($\chi_l< \chi_s$) along the line of sight is
-\begin{equation}
-\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s}
-\frac{\delta(\vec{\theta},\chi_l)}{a(\chi_l)},
-\end{equation}
-where $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
-at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the
-matter density parameter, $c$ is the speed of light, and $a(\chi_l)$ is the
-scale parameter at the lens position.
-
-After substituting comoving distance ($\chi$) with redshift ($z$), we have
-\begin{equation}\label{eq-delta2kappa}
-\kappa(\vec{\theta},z_s)=\int_0^{z_s} dz_l K(z_l,z_s)\delta(\vec{\theta},z_l).
-\end{equation}
-where $K(z_l,z_s)$ is the lensing kernel defined as
-\begin{equation}
-K(z_l,z_s) =
-\begin{cases}
-\frac{3H_0\Omega_M}{2 c} \frac{\chi_l \chi_{sl} (1+z_l)}{\chi_{s} E\left(z_l\right)} & (z_s>z_l),\\
-0&(z_s \leq z_l),
-\end{cases}
-\end{equation}
-where $E(z)$ is the Hubble parameter as a function of redshift, in units of $H_0$.
-
-\begin{figure*}[!t]
- \centering
- \includegraphics[width=1.\textwidth]{lensing_kernel.pdf}
- \caption{The left panel shows the lensing kernels for five different lens
-         redshifts. The dashed lines are the kernels for spectroscopic redshift,
-         which assumes that the source galaxies' redshifts are precisely
-         estimated. The solid lines are for photometric redshifts, which
-         accounts for the influence of photometric redshift uncertainty. The
-         other two panels show the correlation between lensing kernels of
-         different lens redshifts. The middle panel is for spectroscopic
-         redshift, and the right panel is for photometric redshifts. The
-         lensing kernels are normalized so that the diagonal elements of the
-         correlation matrices equal one.
-        }\label{fig_corlensKer}
-\end{figure*}
-
-As shown in \citet{massMap-KS1993}, the shear field is related to the kappa
-field at the same redshift plane via
-\begin{equation}\label{eq-kappa2gamma}
-\gamma_L(\vec{\theta},z_s) = \int  d^2 \theta' D(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s),
-\end{equation}
-where
-\begin{equation}
-D(\vec{\theta})=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2}.
-\end{equation}
-Here we denote the physical shear distortion field as $\gamma_L$ and we note
-that the final observed shear measurements are influenced by systematic errors
-from observations. The systematic errors will be discussed in Section
-\ref{subsec_method_Systematics}.
-
-Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}),
-the expectation of lensing shear signal is
-\begin{equation}\label{eq-delta2gammat}
-\gamma_L(\vec{\theta},z_s) = \int_0^{z_s} dz_l K(z_l,z_s) \int d^2 \theta' \vec{D}(\vec{\theta}-\vec{\theta'}) \delta(\vec{\theta'},z_l).
-\end{equation}
-
-To simplify the expression, we define the lensing transform operator as
-\begin{equation}
-\mathbf{Q}=\int_0^{z_s} dz_l K(z_l,z_s) \int d^2 \theta'  \vec{D}(\vec{\theta}-\vec{\theta'}),
-\end{equation}
-and eq. (\ref{eq-delta2gammat}) is simplified to
-\begin{equation} \label{eq-delta2gammat-simp}
-\gamma_L=\mathbf{Q}\delta.
-\end{equation}
-
-\subsection{Dictionary}
-\label{subsec_method_dictionary}
-
-The density contrast field is modeled as a summation of basis atoms in the
-dictionary:
-\begin{equation}\label{eq-x2delta}
-\delta(\vec{r}) = \sum_{s=1}^{N} \int d^3 r' \phi_s(\vec{r}-\vec{r'}) x_s(\vec{r'}),
-\end{equation}
-where $\phi_s(\vec{r})$ are the basis atoms of the dictionary. The basis atoms
-have `$N$' different scale frames, and the atoms in each scale frame are
-shifted by $\vec{r'}$ to form models at different spatial positions.
-$x_s(\vec{r'})$ is the projection coefficients of the density contrast field
-onto the basis atoms.
-
-We propose to use the multi-scale NFW atoms, denoted as
-$\{\phi_1,...,\phi_N\}$, as the basis atoms of our dictionary.  On the
-transverse plane, the NFW atoms follow surface density profiles of the NFW
-halos \citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and
-truncation radius $c \theta_\alpha$ , where $c$ is the concentration of the NFW
-halos.  As the scales of halos are much smaller than the reachable redshift
-resolution, we neglect the depth of halo on the line of sight direction and set
-the NFW atoms' profiles in the line of sight direction to $1$-D Dirac delta
-functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. The
-multi-scale NFW atoms are defined as
-\begin{equation}
-\begin{split}
-\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 }
-F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
-&  (s=1..N)
-\end{split}
-\end{equation}
-where
-\begin{equation}
-F(x)=
-\begin{cases}
--\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccosh
-\left(\frac{x^2+c}{x(1+c)}\right)}{(1-x^2)^{3/2}}  & (x<1),\\
-\frac{\sqrt{c^2-1}}{3(1+c)} (1+\frac{1}{c+1}) & (x=1),\\
--\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} +
-\frac{\arccos\left(\frac{x^2+c}{x(1+c)}\right)}{(x^2-1)^{3/2}} & (1<x\leq c),\\
-0& (x>c).
-\end{cases}
-\end{equation}
-$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for the NFW atoms in
-different scale frames.
-
-To simplify the notation, we compress the projection coefficients into a column
-vector:
-$x=\begin{pmatrix}
-x_{0}\\
-x_{1}\\
-...\\
-x_{N}
-\end{pmatrix}$,
-and compress the dictionary transform operator to a row vector:
-\begin{equation}
-\mathbf{\Phi}=\begin{pmatrix}
-\int d^3r\phi_0(\vec{r}) ~\int d^3r \phi_1(\vec{r})~ ...~\int d^3r \phi_{N}(\vec{r})
-\end{pmatrix}.
-\end{equation}
-We substitute eq. (\ref{eq-x2delta}) into eq. (\ref{eq-delta2gammat}) and get
-\begin{equation}\label{eq-x2gammat}
-\gamma_L=\mathbf{Q}\mathbf{\Phi} x.
-\end{equation}
-
-In this paper, a dictionary constructed with point mass atoms is used to
-compare with the dictionary of multi-scale atoms.  The point mass atoms is a
-$3$-D Dirac function defined as follows
-\begin{equation}
-\phi_{\rm{PM}}(\vec{r})= \delta_D(\theta_1) \delta_D(\theta_2) \delta_D(z).
-\end{equation}
-
-The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the
-transverse plane are shown in Figure \ref{fig_atoms2D}. The $1$-D slices of the
-profiles are demonstrated in Figure \ref{fig_atoms1D}. Note that these profiles
-are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The
-smoothing operation is discussed in Section \ref{subsec_method_smoothing}, and
-the pixelization operation is discussed in Section \ref{subsec_method_pixel}.
-
-\subsection{Systematics}
-\label{subsec_method_Systematics}
-
-The observed shear measurements are deviated from the physical shear prediction
-due to the systematic errors from observations. The influence of systematics is
-carefully studied and incorporated into the forward modeling in this Section.
-
-\subsubsection{Photo-$z$ Uncertainty}
-\label{subsec_method_photoz}
-
-\begin{figure*}
-\centering
-\subfigure[lasso]{\includezraphics{delta-3-7-pz-nn-lasso.pdf}}
-\subfigure[adaptive lasso]{\includezraphics{delta-3-7-pz-nn-alasso.pdf}}
-\caption{The density map reconstructions with the lasso (left) and the adaptive
-    lasso (right) algorithms. The vertical direction is the line of sight
-    direction, and the lower boundaries and upper boundaries of the boxes are
-    $z=0.01$ and $z=0.85$, respectively. Noises on galaxy shape measurements
-    are neglected in the simulation.  The input halo mass is $M_{200}=10^{15}
-    ~h^{-1}M_{\odot}$, and its redshift is $z=0.35$. The lasso reconstruction
-    smears the density field along the line of sight direction.
-    } \label{fig_lassoVsadaLasso}
-\end{figure*}
-
-The photometric redshifts of source galaxies in the current large-scale survey
-are estimated with a limited number of board photometric bands (e.g., $9$ bands
-for KIDS$+$VIKING survey \citep{KIDS_VIKING-Hildebrant2020}, $5$ bands for DES
-survey and HSC survey). As a result, the estimated redshifts of galaxies suffer
-from much larger uncertainties than redshifts estimated with spectroscopic
-observations. Such photo-$z$ uncertainty smears the lensing kernels
-statistically since a galaxy with a best fit photo-$z$ estimation of $z_s$ has
-possibilities of being actually located at different redshifts ($z$).  The
-probability function for the photo-$z$ uncertainty is denoted as $P(z|z_s)$,
-and the expected shear distortion on the galaxy is
-\begin{equation}\label{eq-delta2gamma-poz}
-\int dz_s P(z|z_s) \gamma_L(\vec{\theta},z_s).
-\end{equation}
-With the definition of photo-$z$ smearing operator:
-\begin{equation}
-\mathbf{P} = \int dz_s P(z|z_s),
-\end{equation}
-the photo-$z$ uncertainty changes the shear as
-\begin{equation}
-\gamma_L \rightarrow \mathbf{P} \gamma_L,
-\end{equation}
-where we use $\rightarrow$ to denote the changes of shear by the systematic
-operator.
-
-Figure \ref{fig_bestpz} shows the histogram of the best Machine Learning and
-photo-Z \citep[MLZ]{MLZ-TPZ2013} photometric redshift estimation from
-\cite{HSC1-photoz} for galaxies in the tract 9347 of the HSC S16A data release
-\citep{HSC1-data}. These Galaxies are divided into ten source galaxy bins
-according to the photo-$z$ best estimation, and the boundaries of the bins are
-shown as vertical dashed lines in Figure \ref{fig_bestpz}. Figure \ref{fig_pdfpz}
-shows the average probability density function (PDF) for galaxies in each
-redshift bin.
-
-The left panel of Figure \ref{fig_corlensKer} shows the lensing kernels for
-lenses at five different redshifts as functions of source galaxy redshift bins.
-The dashed lines are the lensing kernel for spectroscopic redshifts with
-neglectable redshift uncertainty. The solid lines are the lensing kernel for
-photometric redshifts with redshift uncertainties shown in Figure
-\ref{fig_pdfpz}.  As shown by the dashed lines in the left panel of Figure
-\ref{fig_corlensKer}, the lensing kernels converge to zero for source redshifts
-lower than the lens redshift if the uncertainties on the source galaxy
-redshift estimations are neglectable. However, as demonstrated by the solid
-lines in the same panel, for the source redshifts with large photo-$z$
-uncertainties, the lensing kernels do not converge to zero at redshifts lower
-than the lens redshift. This is because the galaxies with photo-$z$ estimations
-lower than the lens redshifts may be actually located at higher redshifts due
-to the photo-$z$ uncertainties.
-
-The middle and right panels show the correlation between lensing kernels for
-lenses at different redshifts. The middle panel is for spect-$z$, and the right
-panel is for photo-$z$.  As demonstrated in the middle panel, the lensing
-kernels are highly correlated even though the redshift estimation is precise.
-Comparing the correlation matrices shown in the middle panel and the right
-panel of Figure \ref{fig_corlensKer}, we conclude that the photo-$z$
-uncertainties further increase the correlations between lensing kernels at
-different lens plane.
-
-\subsubsection{Smoothing}
-\label{subsec_method_smoothing}
-
-The observed galaxies have random yet unequally-spaced spatial distribution. To
-boost the computational speed, we smooth the shear measurements from galaxy
-shapes and pixelize the smoothed measurements onto regular grids.  After the
-pixelization, the fast Fourier transform (FFT) can be directly conducted on the
-transverse plane in each source redshift bin.
-
-The smoothing is conducted by convolving the shear measurements with a
-smoothing kernel:
-\begin{equation}
-\gamma_{\rm{sm}} (\vec{\theta})  = \frac{\sum_i
-W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) \gamma_i}{\sum_i
-W(\vec{\theta}-\vec{{\theta}}_i,z-z_i) },
-\end{equation}
-where $W(\vec{\theta},z)$ is a $3$-D smoothing kernel. $\gamma_i$, $z_i$ and
-$\theta_i$ are the shear, photometric reshift, and transverse position of the
-$i$-th galaxy in the catalog.
-
-$W(\vec{\theta},z)$ can be decomposed into a transverse component
-$W_T(\vec{\theta})$ and a line of sight component
-$W_\times(z)$ as
-\begin{equation}
-W(\vec{\theta},z)=W_T(\vec{\theta}) W_\times (z).
-\end{equation}
-In this paper, we use an isotropic $2$-D Gaussian kernel and a $1$-D top-hat
-kernel to smooth the measurements in the transverse plane and the line of sight
-direction. These components of the smoothing kernel are
-\begin{equation}
-\begin{split}
-W_T(\vec{\theta}) &=\frac{1}{2\pi\beta^2}\exp(-\frac{|\vec{\theta}|}{2\beta^2}),\\
-W_\times (z) &=
-\begin{cases}
-1/\Delta z& (|z|<\Delta z/2),\\
-0& else.
-\end{cases}
-\end{split}
-\end{equation}
-In this paper, we set $\beta=1.\arcmin5$.
-
-Since the smoothing kernel is normalized by definition:
-\begin{equation}
-\int d^3r W(\vec{r})=1,
-\end{equation}
-with the approximation that the density of galaxy number - $n(\vec{r})$ -
-varies slowly at the smoothing scale, the
-smoothed galaxy number density:
-\begin{equation}\label{eq-numDesSmooth}
-n_{\rm{sm}}(\vec{r})=\sum_i W(\vec{\theta}-\vec{\theta_i},z-z_i),
-\end{equation}
-equals the galaxy number density: $n_{\rm{sm}}(\vec{r})=n(\vec{r})$.
-We note that the galaxy number density experience a steep drop on the boundary
-of the survey, therefore the smoothed galaxy number density does not equal the
-galaxy number density close to the boundary of the survey.
-
-The smoothing operator is defined as
-\begin{equation}
-\mathbf{W} = \int d^3 r' W(\vec{r}-\vec{r'}),
-\end{equation}
-and the smoothing procedure influence the shear signal through
-\begin{equation}
-\gamma_L \rightarrow \mathbf{W} \gamma_L.
-\end{equation}
-
-As we will discuss in Section \ref{subsec_method_pixel}, the smoothed shear
-field is pixelized into equally spaced grids. We note that another widely used
-scheme is to average the shear measurements in each pixel.  Such a scenario is
-equivalent to resampling the shear field smoothed with a $3$-D top-hat kernel
-with the same scale as the pixels.
-
-\subsubsection{Masking}
-\label{subsec_method_msknoise}
-
-In real observations, shear measurements are available in a finite region of
-the sky, and the boundary of the region is always irregular. Moreover, many
-isolated sub-regions near the bright stars are masked out since the light from
-bright stars tends to influence the shear measurements on neighboring galaxies.
-
-We define the masking window function according to the smoothed number density
-(defined in eq. (\ref{eq-numDesSmooth})) of the galaxies:
-\begin{equation}
- M(\vec{r})=
-\begin{cases}
-0 & n_{\rm{sm}}>1,\\
-1 & \rm{else}.
-\end{cases}
-\end{equation}
-The mask changes the shear measurements though
-\begin{equation}\label{eq-delta2gamma-final}
-\gamma_L(\vec{\theta},z) \rightarrow M(\vec{\theta},z) \gamma_L(\vec{\theta},z),
-\end{equation}
-We define the masking operator as
-\begin{equation}
-\mathbf{M}= \int d^3 r' M(\vec{r'}) \delta_D(\vec{r}-\vec{r'}),
-\end{equation}
-where $\delta_D(\vec{r})$ is $3$-D Dirac delta function. The shear is
-influenced by the masking by
-$\gamma_L \rightarrow \mathbf{M} \gamma_L$.
-
-The final observed shear field, taking into account all of the systematics as
-mentioned above from observations, is
-\begin{equation}\label{eq-x2gamma-final}
-\gamma =\mathbf{M} \mathbf{W} \mathbf{P} \mathbf{Q} \mathbf{\Phi} x.
-\end{equation}
-For simplicity, we denote $\mathbf{A}=\mathbf{M} \mathbf{W} \mathbf{P}
-\mathbf{Q} \mathbf{\Phi} $ and
-eq. (\ref{eq-x2gamma-final}) is written as
-\begin{equation}\label{eq-x2gamma-simple}
-\gamma=\mathbf{A} x.
-\end{equation}
-
-\subsubsection{Pixelization}
-\label{subsec_method_pixel}
-
-We pixelize the smoothed shear field into an $N_\theta \times N_\theta \times
-N_s$ grid, where $N_\theta$ is the number of pixels for the two orthogonal axes
-of the transverse plane and $N_s$ is the number of pixels for the line of sight
-axis. $\gamma_{\alpha}$ denotes the smoothed shear measurements recorded on the
-pixel with index $\alpha$, where $\alpha=1...N_\theta \times N_\theta \times
-N_s$. The grids on the transverse planes are equally spaced with a pixel size of
-$1\arcmin$.  Fast Fourier transform (FFT) can be used to boost the speed of
-linear operation on the transverse plane, whereas the grids in the line of sight
-direction follow equal number binning as shown in Figure \ref{fig_bestpz}.
-
-Similarly, we pixelize each scale frame of the projection coefficient field $x$
-into an $N_\theta \times N_\theta \times N_l$ grid. The pixelization on the
-transverse plane for each scale frame is the same as that of the
-smoothed shear field on the transverse plane. At the same time, the projection
-coefficient field is pixelized into equal spaced grids in the line of sight
-direction ranging from redshift $0.01$ to redshift $0.85$. Here, we use $N_l$
-to denote the number of the lens planes and $x_{\beta}$ to denote the
-projection parameter indexed as $\beta$, where $\beta=1...N_\theta \times
-N_\theta \times N_l \times N$. The corresponding pixelized elements of the
-forward transform matrix $\mathbf{A}$ is denoted as $A_{\alpha\beta}$.
-
-We term the column vectors of the forward transform matrix $\mathbf{A}$ as the
-effective basis atoms. We note that the effective basis atoms have different
-$l^2$ norm. The $l^2$ norm of the $i'th$ column vectors of the effective basis
-atoms are $\mathcal{N}_{i}=\sum_\alpha A_{i\alpha}A_{i\alpha}$. Before solving
-the density map reconstruction problem, we normalize the column vectors of the
-transform matrix through a rescaling:
-\begin{equation}
-\begin{split}
-A'_{\alpha\beta}&=A_{\alpha\beta}/\mathcal{N}_{\alpha}^{\frac{1}{2}},\\
-x'_{\beta}&=x_{\beta}\mathcal{N}_{\beta}^{\frac{1}{2}}.\\
-\end{split}
-\end{equation}
-
-\subsection{Density map reconstruction}
-\label{subsec_method_reconstruction}
-
-\subsubsection{Adaptive lasso}
-
-The lasso algorithm uses $l^1$ norm of the projection coefficient field to
-regularize the modeling, and the estimator is defined as
-\begin{equation}
-\hat{x'}^{\rm{lasso}}=\argmin_{x} \left\{
-\frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{A'} x')}_2^2+
-\lambda \norm{x'}^1_1\right\},
-\end{equation}
-where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and
-$l^2$ norm, respectively.  $\lambda$ denotes the penalization parameter
-for the lasso estimation.
-
-The lasso algorithm selects the parameters relevant to the measurements and
-simultaneously estimates the value of the selected parameters.  However, it has
-been shown by \citet{AdaLASSO-Zou2006} that when the column vectors of the
-transforming matrix $\mathbf{A'}$ are highly correlated, the lasso cannot
-select the relevant parameters from the parameter space consistently.
-Moreover, the estimated parameters are biased due to the shrinkage in the lasso
-regression. We note that, for the density map reconstruction problem, the
-column vectors are highly correlated even in the absence of photometric
-redshift uncertainties because, as shown in Figure \ref{fig_corlensKer}, the
-lensing kernels for lenses at different redshifts are highly correlated.
-Therefore, the lasso algorithm cannot select the consistent mass in the line of
-sight direction, and the reconstructed mass suffers from smears in the line of
-sight direction even in the absence of noise on shear measurements.  Figure
-\ref{fig_lassoVsadaLasso} shows the reconstructions of a single halo's mass map
-with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$.
-The noises on shear measurements are not included in the simulation.  The left
-panel of Figure \ref{fig_lassoVsadaLasso} is the reconstruction with the lasso
-algorithm, which shows a significant smear along the line of sight.
-
-\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm, which uses
-adaptive weights to penalize different projection coefficients in the $l^1$
-penalty. The adaptive lasso algorithm is a two-steps process. In the first
-step, the lasso is used to estimate the parameters, and the preliminary
-estimation of the lasso is denoted as $\hat{x'}^{\rm{lasso}}$. In the second
-step, the preliminary lasso estimation is used to weight the penalization. The
-weight on penalty is defined as
-\begin{equation}
-\hat{w}= \frac{1}{\abs{\hat{x'}^{\rm{lasso}}}^\tau},
-\end{equation}
-where we set the hyper-parameter $\tau$ to $2$.  The adaptive lasso estimator is
-expressed as
-\begin{equation}\label{eq-lossFun}
-\hat{x'}=\argmin_{x'} \left\{ \frac{1}{2} \norm{\Sigma^{-\frac{1}{2}}(\gamma-\mathbf{A'}x')}^2_2 +
-\hat{w}\lambda_{\rm{ada}} \norm{x'}^1_1\right\}.
-\end{equation}
-Here, $\lambda_{\rm{ada}}$ is the penalization parameter for the adaptive
-lasso.  We note that $\lambda_{\rm{ada}}$ does not need to be the same as the
-penalization parameter for the preliminary lasso estimation
-($\lambda$).
-
-We rewrite the loss function with the Einstein notation:
-\begin{equation}
-\begin{split}
-L(x')&=\frac{1}{2}(\Sigma^{-1})_{\alpha\beta}(\gamma^{*}_{\alpha}-A'^{*}_{\alpha i}x'_{i})
-(\gamma_{\beta}-A'_{\beta j}x'_{j})\\
-&+ \lambda_{\rm{ada}} \hat{w_\beta} \abs{x'_\beta}.
-\end{split}
-\end{equation}
-To simplify the notification in future, we define the quadruple term in the
-loss function as $G(x')$:
-\begin{equation}
-G(x')=\frac{1}{2}\Sigma^{-1}_{\alpha\beta}(\gamma^{*}_{\alpha}-A'^{*}_{\alpha
-i}x'_{i}) (\gamma_{\beta}-A'_{\beta j}x'_{j}).
-\end{equation}
-
-\subsubsection{FISTA}
-
-\citet{FISTA-Beck2009} propose the Fast Iterative Soft Thresholding Algorithm
-(FISTA) to solve the lasso problem.  Since the lasso's loss function and the
-adaptive lasso's loss function only differ in their penalization terms. The
-FISTA is also applicable to the adaptive lasso problem. We apply the FISTA to
-solve both the preliminary lasso estimation and the final adaptive lasso
-estimation.
-
-Here we start from the lasso preliminary estimation. The coefficients are
-initialized as $x_i^{(1)}=0$. According to the FISTA algorithm, we iteratively
-update the projection coefficient field ($x$). Taking the $n$'th iteration as
-an example, a temporary update is first calculated as
-\begin{equation}
-x'^{(n+1)}_{i}=\mathrm{ST}_{\lambda} \left(x'^{(n)}_{i} -\mu \partial_i G(x'^{(n)})\right),
-\end{equation}
-where $\mathrm{ST}$ is the soft thresholding function defined as
-\begin{equation}
-\mathrm{ST}_{\lambda} \left(x'\right) = \mathrm{sign} (x') \max \left(\abs{x'}-\lambda,0\right).
-\end{equation}
-The soft thresholding is a part of the lasso algorithm. It selects the
-estimations with amplitude larger than $\lambda$, and shrink the estimations by
-$\lambda$.
-$\mu$ is the step size of the gradient descent iteration.  $\partial_i
-G(x'^{(n)})$ refers to the $i$'th element of the gradient vector of $G$ at
-point $x'^{(n)}$:
-\begin{equation}
-\partial_i G(x'^{(n)})=\Sigma^{-1}_{\alpha\beta}\Re\left(A'^{*}_{\alpha i}(\gamma_{\beta}-A'_{\beta j}x'_{j})\right),
-\end{equation}
-where $\Re\left( \bullet \right)$ is the function returns the real part of the
-input function. The FISTA algorithm requires an additional update amounting to a
-weighted average between
-$x'^{(n+1)}$ and $x'^{(n)}$:
-\begin{equation}
-\begin{split}
-t^{(n+1)}&=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2},\\
-x'^{(n+1)} &\leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)}),
-\end{split}
-\end{equation}
-where the relative weight is initialized as $t^{(1)}=1$.
-
-The FISTA algorithm converges as long as the gradient descent step size $\mu$
-satisfies
-\begin{equation}
- 0< \mu < \frac{1}{ \norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }},
-\end{equation}
-where $\norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }$ refers to
-the spectrum norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1}
-\mathbf{A}$. The spectral norm is estimated by simulating a large number of
-random vectors with $l^2$ norms equal one with different realizations. The
-matrix operator $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is
-subsequently applied to each random vector and get a corresponding transformed
-vector. The spectral norm of the matrix $\mathbf{A^{\dagger}}
-\mathbf{\Sigma}^{-1} \mathbf{A}$ is determined as the maximum $l^2$ norm of the
-transformed vectors.
-
-As summarized in Algorithm \ref{alg-1}, we first initial the projection
-coefficients as zero and use the FISTA algorithm to find the global minimum of
-the lasso loss function. Such a global minimum is the preliminary estimation.
-We then use the preliminary lasso estimation to weight the coefficients and
-construct the adaptive lasso loss function. Finally, we set the preliminary
-lasso estimation as the warm start of the adaptive lasso estimation and use the
-FISTA algorithm again to find the adaptive lasso loss function's global minimum,
-which is the final solution.
-
-\begin{algorithm}[H]
-\renewcommand{\thealgorithm}{}
-\label{alg-1}
-\caption{Our Algorithm}
-\begin{algorithmic}[1]
-\INPUT $\gamma$: Pixelized complex $3$-D array of shear
-\OUTPUT  $\delta$: $3$-D array of density contrast
-\STATE Normalize column vectors of $\mathbf{A}$
-\STATE Estimate step size $\mu$ and $\mathbf{\Sigma}$
-\STATE \textbf{Initialization:}
-\STATE $x'^{(1)} = 0$
-\STATE $\hat{w}=1$
-\STATE $t^{(1)}=1$,$i=1$, $j=1$
-\WHILE{$j \leq 2$}
-    \WHILE{$i \leq N_{\rm{iter}}$}
-        \STATE \# soft thresholding
-        \STATE $x'^{(n+1)}_{i}=\mathrm{ST}_{\hat{w}\lambda} \left(x'^{(n)}_{i} -\mu \partial_i G(x'^{(n)})\right)$
-        \STATE \# FISTA algorithm
-        \STATE $t^{(n+1)}=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2}$
-        \STATE $x'^{(n+1)} \leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)})$
-        \STATE $i=i+1$
-    \ENDWHILE
-\STATE \textbf{Reinitialization:}
-\STATE $\hat{w}=\abs{\hat{x'}^{\rm{lasso}}}^{-2}$, $\lambda \leftarrow
-\lambda_{\rm{ada}}$
-\STATE $\hat{x'}^{(1)} = x'^{(N_{\rm{iter}})}$
-\STATE $t^{(1)}=1$, $i=1$
-\STATE $j=j+1$
-\ENDWHILE
-\STATE $\delta=\mathbf{\Phi}\mathcal{N}^{-\frac{1}{2}}x'^{(N_{\rm{iter}})}$
-\end{algorithmic}
-\end{algorithm}
-
-\section{Tests}
+\section{Cluster Detection}
 \label{sec_Test}

### 2021-01-06 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
change the introduction

--- 2020-12-07 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
@@
 that both the preliminary lasso estimation and the final adaptive lasso
-estimation select the pixels with the signal-to-noise ratios (SNRs) greater
-than $\lambda$ in each gradient descent iteration and estimate the density in
-the selected pixels. While the final adaptive lasso estimation further enhances
-the growth of the pixels with preliminary estimations greater than $\lambda$.
+estimation select the pixels with the SNRs greater than $\lambda$ in each
+gradient descent iteration and estimate the density in the selected pixels.
+While the final adaptive lasso estimation further enhances the growth of the
+pixels with preliminary estimations greater than $\lambda$.
 
@@
 
-We select peaks with values greater than an ad-hoc threshold as candidates of
-galaxy clusters following \citet{HSC1-massMap-cluster}.  The threshold is set
-to a few times the standard deviation of the noise peaks. We use different
-detection thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters
-from the mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and
-middle columns of Figure \ref{fig_detFalsRateNFW} show the detection rates for
-halos in the (mass, redshift) planes with detection thresholds set to
-$1.5\sigma$ and $3.0\sigma$ of the noise peaks' distributions, respectively.
-The right column of Figure \ref{fig_detFalsRateNFW} shows the corresponding
-numbers of false detections per square degree as functions of detection
-thresholds. The first, second, and third rows of Figure
-\ref{fig_detFalsRateNFW} correspond to the $lambda=3.5,4.0,5.0$, respectively.
+With the intent to suppress false detections, we select peaks with values
+greater than an ad-hoc threshold as candidates of galaxy clusters following
+\citet{WL-massMap-clusDet-HSC-Miyazaki2018}.  The threshold is set to a few
+times the standard deviation of the noise peaks. We use different detection
+thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters from the
+mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and middle columns
+of Figure \ref{fig_detFalsRateNFW} show the detection rates for halos in the
+(mass, redshift) planes with detection thresholds set to $1.5\sigma$ and
+$3.0\sigma$ of the noise peaks' distributions, respectively.  The right column
+of Figure \ref{fig_detFalsRateNFW} shows the corresponding numbers of false
+detections per square degree as functions of detection thresholds. The first,
+second, and third rows of Figure \ref{fig_detFalsRateNFW} correspond to the
+$lambda=3.5,4.0,5.0$, respectively.
 

### 2021-01-07 doc/paper_ms_method_HSCY1/massmap_sim.tex
add planck2018

@@
 (CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$,
-$\Omega_\Lambda=0.685$ \citep{cmb-Planck2018-Cosmology}.
+$\Omega_\Lambda=0.685$, $\sigma_8=0.811$, $n_s=0.965$
+\citep{cmb-Planck2018-Cosmology}.
 
@@
 by a small amount. The concentration of the NFW halo is set as a function of
-the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
+the halo's virial mass ($M_{200}$) and redshift ($z_{h}$) according to
 \citet{c-M_Magneticum-Ragagnin2019}
 \begin{equation}
-c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
+c_{h}=6.02\times\left(\frac{M_{200}}{10^{13} M_{\odot}}\right)^{-0.12}
+\left(\frac{1.47}{1.+z_h}\right)^{0.16}.
 \end{equation}

### 2021-01-08 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
add detection density to paper
add discussion on the detection number density

@@
 \end{figure*}
+
+According to the detection rate measured from the simulation, we predict the
+number density of detected cluster using the halo mass function of
+\citet{haloMass-Tinker2008}. We use HMF \citep{hmf-Murray2013}, an open-source
+package, to calculate the halo mass function.  The predicted halo detection
+number density for the setup ($\lambda=5$, $1.5\sigma$ detection threshold) is
+shown in Figure \ref{fig_detNum}. The expected cluster number density in total
+is $0.49$ $\deg^{-2}$, which is $78.4$ clusters for the first year HSC shear
+catalog \citep{HSC1-catalog} with a survey area of $\sim 160 \deg^2$.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{detNum_zm.pdf}
+ \caption{The expected number density of detected clusters per square degree as
+     a function of halo's virial mass and redshift. The number density in total
+     is $0.49~\deg^{-2}$.
+     } \label{fig_detNum}
+\end{figure}

### 2021-01-08 doc/paper_ms_method_HSCY1/massmap_method.tex

@@
 halos \citep{haloModel-TJ2003-3pt} with comoving scale radii $r_s$ and
-truncation radius $c r_s$, where $c$ is the concentration of the NFW halos.  As
-the scales of halos are much smaller than the reachable redshift resolution, we
-neglect the depth of halo on the line of sight direction and set the NFW atoms'
-profiles in the line of sight direction to one-dimensional ($1$-D) Dirac delta
-functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. The
+concentration $c$. In this paper, we apply a hard truncation on the NFW
+profiles at the virial radius: $c r_s$, the influence of different truncation
+forms \citep{haloTrunc-Oguri2011} on the mass map reconstruction is left to our
+future work.
+
+As the scales of halos are much smaller than the reachable redshift resolution,
+we neglect the depth of halo on the line of sight direction and set the NFW
+atoms' profiles in the line of sight direction to one-dimensional ($1$-D) Dirac
+delta functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. The
 multi-scale NFW atoms are defined as
@@
 lenses at five different redshifts as functions of source galaxy redshifts.
-The dashed lines are the lensing kernels for spectroscopic redshifts with
-neglectable redshift uncertainties. The solid lines are the lensing kernels for
-photometric redshifts with redshift uncertainties shown in Figure
-\ref{fig_pdfpz}. As shown by the dashed lines in the left panel of Figure
-\ref{fig_corlensKer}, the lensing kernels converge to zero for source redshifts
-lower than the lens redshift if the uncertainty on the source galaxy
-redshift estimation are neglectable. However, as demonstrated by the solid
-lines in the same panel, for the source redshifts with large photo-$z$
-uncertainties, the lensing kernels do not converge to zero at redshifts lower
-than the lens redshift. This is because the galaxies with photo-$z$ estimations
-lower than the lens redshifts may be actually located at higher redshifts due
-to the photo-$z$ uncertainties.
+The results include both the lensing kernels for spectroscopic redshifts with
+neglectable redshift uncertainties and photometric redshifts with redshift
+uncertainties shown in Figure \ref{fig_pdfpz}. As shown by the dashed lines in
+the left panel of Figure \ref{fig_corlensKer}, the lensing kernels converge to
+zero for source redshifts lower than the lens redshift if the uncertainty on
+the source galaxy redshift estimation are neglectable. However, as demonstrated
+by the solid lines in the same panel, for the source redshifts with large
+photo-$z$ uncertainties, the lensing kernels do not converge to zero at
+redshifts lower than the lens redshift. This is because the galaxies with
+photo-$z$ estimations lower than the lens redshifts may be actually located at
+higher redshifts due to the photo-$z$ uncertainties.
 

### 2021-01-08 doc/paper_ms_method_HSCY1/massmap_sim.tex

@@
 randomly shift the input halo redshifts and halo masses from the bins' centers
-by a small amount. The concentration of the NFW halo is set as a function of
-the halo's virial mass ($M_{200}$) and redshift ($z_{h}$) according to
+by a small amount. In the simulation, we set the non-linear over-density
+($\Delta_{\rm{vir}}$) to $200$, and $M_{200}$ refers to the virial mass. The
+concentration of the NFW halo is set to as a function of the halo's virial mass
+($M_{200}$) and redshift ($z_{h}$) according to
 \citet{c-M_Magneticum-Ragagnin2019}
@@
 \end{equation}
+The halos are truncated at the virial radius.
 The weak-lensing shear fields of these NFW halos are simulated according to

### 2021-01-08 doc/paper_ms_method_HSCY1/ms.tex

@@
 maps.
-We study the performance of cluster detection from the reconstruction mass map
-with simulations that applies shear field from isolated halo to HSC-like galaxy
-shapes and photometric redshifts.
+We study the performance of three-dimensional cluster detection from the
+reconstructed mass map with simulations that applies shear distortions from
+isolated halo to HSC-like galaxy shapes with realistic photometric redshift
+uncertainties .
 Our findings are summarized as follows:
-1) The lasso solution suffers from a smear of structure in the line of sight
-direction even in the absence of shape noise, and in contrast, the adaptive
-lasso algorithm efficiently removes the line of sight smear.
+1) The lasso reconstructed suffers from a smear of structure in the line of
+sight direction even in the absence of shape noise, and in contrast, the
+adaptive lasso algorithm efficiently removes the line of sight smear.
 2) The algorithm is able to detect halo with minimal mass limits of $10^{14.0}
@@
 \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}.
-Galaxy clusters are detected from the $2$-D mass map
+Cluster detection from $2$-D mass maps has been widely studied and applied to
+these large-scale weak-lensing surveys
 \citep{WL-massMap-clusDet-CFHT-Shan2012,WL-massMap-clusDet-HSC-Miyazaki2018,WL-massMap-clusDet-HSC-Hamana2020};
@@
 
-On the other hand, \citet{WL-clusDet-Hennawi2005} propose to detect clusters
-from smoothed shear measurements after convolving tomographic shear
-measurements with $3$-D filters that match the tangential shears induced by
-multi-scale NFW halos.
-Alternatively, we can directly reconstruct $3$-D mass maps taking advantage of
-photometric redshift (photo-$z$) information
+On the other hand, we can directly reconstruct $3$-D mass maps taking advantage
+of photometric redshift (photo-$z$) information
 \citep{LSS-massMap-Wiener-Simon2009,WL-massMap-VanderPlas2011}; however, these
@@
 they suffer from smears along the line of sight direction, which need to be
-overcome for practical searches of clusters in 3D mass maps.
+overcome for practical searches of clusters in 3D mass maps.  Alternatively,
+\citet{WL-clusDet-Hennawi2005} propose to perform a maximum-likelihood
+detection of clusters, by convolving tomographic shear measurements with $3$-D
+filters that match the tangential shears induced by multi-scale NFW halos,
+without fully reconstruct the $3$-D mass maps.
 
 In this paper, we develop a novel method for high-resolution $3$-D mass map
-reconstruction that are free from line of sight smears and study the
-performance of cluster detection from the reconstructed mass maps.  The $3$-D
+reconstruction that are free from line of sight smears.  The $3$-D
 mass map is modeled as a summation of the NFW \citep{halo-NFW1997ApJ} basis
@@
 find a sparse reconstruction of the mass maps.
+
+We study the performance of cluster detection from the reconstructed mass maps
+using simulations applying shear distortions from isolated halos to HSC-like
+galaxy shapes with realistic photo-$z$ uncertainties.
 

### 2021-01-08 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex

@@
 shown in Figure \ref{fig_detNum}. The expected cluster number density in total
-is $0.49$ $\deg^{-2}$, which is $78.4$ clusters for the first year HSC shear
-catalog \citep{HSC1-catalog} with a survey area of $\sim 160 \deg^2$.
+is $0.49$ $\deg^{-2}$, which corresponds to $78.4$ clusters for the first year
+HSC shear catalog \citep{HSC1-catalog} with a survey area of $\sim 160 \deg^2$.
+The expected number of detections is similar to the number of $2$-D cluster
+detections on the first year HSC shape catalog \citep{HSC1-massMap-cluster}.
 

### 2021-01-08 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
small revision on paper

@@
 \end{equation}
-The solid steps in Figure \ref{fig_peakHist} show the histograms of the
-normalized peaks with different penalization parameters. Also, we simulate
-$1000$ realizations of pure noise catalogs and perform the reconstructions on
-these noise catalogs to study the noise properties. The dashed steps in Figure
-\ref{fig_peakHist} show the histograms of normalized peaks detected from the
-pure noise catalogs. The solid lines in Figure \ref{fig_peakHist} show the
-best-fit Gaussian distributions to the noise peaks' histograms.
+In Figure \ref{fig_peakHist}, we show the stacked histograms of the
+normalized peaks with different penalization parameters. Here, we stack the
+histograms from $100$ realizations of all halos sampled in the redshift-mass
+plane.
+Also, we simulate $1000$ realizations of pure noise catalogs and perform the
+reconstructions on these noise catalogs to study the noise properties.  The
+histograms of normalized peaks detected from the pure noise catalogs are shown
+in Figure \ref{fig_peakHist} and we show the best-fit Gaussian functions of the
+noise peaks' histograms.
 

### 2021-01-09 doc/paper_ms_method_HSCY1/ms.tex
update summary

@@
 \begin{abstract}
-A new method is developed to reconstruct three-dimensional mass maps from
-photometric weak-lensing shear measurements. The three-dimensional mass map is
-modeled as a summation of the NFW basis atoms, which have two-dimensional
-multi-scale NFW surface density profiles on the transverse plane and
-one-dimensional Dirac delta functions in the line of sight direction.  The
-adaptive lasso algorithm is applied to find a sparse reconstruction of the mass
-maps.
+A new method is developed to reconstruct high-resoluion three-dimensional mass
+maps from photometric weak-lensing shear measurements. The three-dimensional
+mass map is modeled as a summation of the NFW basis atoms, which have
+two-dimensional multi-scale NFW surface density profiles on the transverse
+plane and one-dimensional Dirac delta functions in the line of sight direction.
+The adaptive lasso algorithm is applied to find a sparse reconstruction of the
+mass maps.
 We study the performance of three-dimensional cluster detection from the
@@
 ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts,
-respectively, with a false detection of 0.022/deg$^2$.
+respectively, with an average false detection of 0.022/deg$^2$.
 3) The estimated redshift of the halos detected from the reconstructed mass
@@
 redshifts ($z\leq 0.4$). The relative redshift bias is below $0.5\%$ for halos
-at $0.4<z\leq 0.85$.
+at $0.4<z\leq 0.85$. The standard deviation of the redshift estimation is $0.092$.
 \end{abstract}
@@
 \citep{WL-massMap-clusDet-CFHT-Shan2012,WL-massMap-clusDet-HSC-Miyazaki2018,WL-massMap-clusDet-HSC-Hamana2020};
-however, cross matching with some (e.g., optically selected) cluster
-catalog is needed to assign the redshift and extract its physical parameter
-(such as mass) for each cluster selected from $2$-D mass map.
+however, cross matching with some (e.g., optically selected) cluster catalog is
+needed to assign the redshift and extract its physical parameter (such as mass)
+for each cluster selected from $2$-D mass map.
 
@@
 
-We develop a novel method to reconstruct $3$-D density contrast maps from
-weak-lensing shear measurements and photometric redshift estimations.  Our
-method models $3$-D density contrast maps as summations of NFW atoms with
-different comoving radii.  With the prior assumption that the clumpy masses
-sparsely distribute in the $3$-D space, the density map is reconstructed
-using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}. The method is
-tested with realistic simulations using HSC-like shape estimation error and
-photo-$z$ uncertainty.
+We have developed a novel method to reconstruct high-resolution $3$-D density
+contrast maps from weak-lensing shear measurements and photometric redshift
+estimations.  Our method models $3$-D density contrast maps as summations of
+NFW atoms with different comoving radii.  With the prior assumption that the
+clumpy masses sparsely distribute in the $3$-D space, the density map is
+reconstructed using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}.
+We find that the lasso algorithm's solution suffers from a smear of structure
+in the line of sight direction even in the absence of galaxy shape noise, and
+the adaptive lasso algorithm efficiently removes the line of sight smear of
+structure.
 
-The findings of this paper are summarized as follows:
+We study the performance of cluster detection from the reconstructed $3$-D mass
+maps using simulations that apply shear distortions from isolated NFW halos to
+HSC-like shapes and photo-$z$ uncertainties.  We conclude that the algorithm is
+able to detect halo with minimal mass limits of $10^{14.0} M_{\odot}/h$,
+$10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median
+($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts, respectively, with an
+average false detection of 0.022 deg$^{-2}$. The estimated redshifts of the halos
+detected from the reconstructed mass maps are lower than the true redshift by
+about $0.03$ for halos at low redshifts ($z\leq 0.4$).  The relative redshift
+bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$. The standard deviation of
+the redshift estimation is $0.092$.
 
-(i) The lasso algorithm's solution suffers from a smear of structure in the
-line of sight direction even in the absence of shape noise, and the adaptive
-lasso algorithm efficiently removes the line of sight smear of structure.
-
-(ii) The algorithm is able to detect halo with minimal mass limits of
-$10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for
-the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$)
-redshifts, respectively, with a false detection of 0.022/deg$^2$.
-
-(iii)The estimated redshifts of the halos detected from the reconstructed mass
-maps are lower than the true redshift by about $0.03$ for halos at low
-redshifts ($z\leq 0.4$).  The relative redshift bias is below $0.5\%$ for halos
-at $0.4<z\leq 0.85$.
-
-We will apply the method to the shear measurements of the HSC survey
-\citep{HSC1-catalog,FPFSHSC1-Li2020} to perform galaxy cluster detection in our
-future work.
+We will apply the $3$-D mass map reconstruction to the shear measurements of
+the HSC survey \citep[e.g.,][]{HSC1-catalog,FPFSHSC1-Li2020} to perform galaxy
+cluster detection in our future work.
 

### 2021-01-09 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
update summary
typo correction in paper

@@
 true detections for each halo. The estimated redshifts are lower than the true
-redshifts by about $0.03$ for halos in the low-redshift range ($z\leq
-0.4$).  For halos at $0.4<z\leq 0.85$, the relative redshift bias is below
-$0.5\%$.
+redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
+For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$. The
+standard deviation of the redshift estimation is $0.092$.
 
@@
 of Figure \ref{fig_detFalsRateNFW} show the detection rates for halos in the
-(mass, redshift) planes with detection thresholds set to $1.5\sigma$ and
+redshift-mass planes with detection thresholds set to $1.5\sigma$ and
 $3.0\sigma$ of the noise peaks' distributions, respectively.  The right column
 of Figure \ref{fig_detFalsRateNFW} shows the corresponding numbers of false
-detections per square degree as functions of detection thresholds. The first,
-second, and third rows of Figure \ref{fig_detFalsRateNFW} correspond to the
-$lambda=3.5,4.0,5.0$, respectively.
+detections per square degree as functions of detection thresholds.
 
@@
 setup suppresses the false detection to $0.022$ while keeping a good halo
-detection rate. In summary, The algorithm is able to detect halo with minimal
-mass limits of $10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0}
-M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high
-($0.6\leq z< 0.85$) redshifts, respectively.
+detection rate.
+In summary, The algorithm is able to detect halo with minimal mass limits of
+$10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for
+the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$)
+redshifts, respectively.
 

### 2021-01-13 doc/paper_ms_method_HSCY1/massmap_method.tex
typo correction in paper
some minor corrections

@@
 where $\norm{\Sigma^{-\frac{1}{2}}(\gamma - \mathbf{T\Phi} x)}_2^2$ is the
-$l^2$ chi-square term\footnote{weighted by the inverse of the diagonal
-covariance matrix of the error on the shear measurements ($\Sigma$).} measuring
-the difference between the prediction and the data, while $C(x)$ is the
-regularization term measuring the deviation of the coefficient estimation ($x$)
-from the prior assumption. The $l^p$ norm is defined as
+$l^2$ chi-square term\footnote{The term chi-square is weighted by the inverse
+of the diagonal covariance matrix of the error on the shear measurements
+($\Sigma$).} measuring the difference between the prediction and the data,
+while $C(x)$ is the regularization term measuring the deviation of the
+coefficient estimation ($x$) from the prior assumption. The $l^p$ norm is
+defined as
 \begin{equation}
-\norm{x}_p=(\sum_{i} |x|^p_i)^{\frac{1}{p}}.
+\norm{x}_p=\left(sum_{i} |x|^p_i\right)^{\frac{1}{p}}.
 \end{equation}
@@
 halos since the resolution scale of the reconstruction in the line of sight
-direction is much larger than the halo scale. Therefore, we set the NFW atoms'
-profile in the line of sight direction as the Dirac delta function.  Moreover,
-we assume that the halos are sparsely distributed in the universe.  With the
-sparsity prior, the adaptive lasso regularization \citep{AdaLASSO-Zou2006} is
-used to reconstruct the density field.  We find that, in contrast to the lasso
-estimator that smears the structure along the line of sight, the adaptive lasso
-can efficiently reduce the smearing effect.
+direction is much larger than the halo scale. Therefore, we set the profile of
+the NFW atoms in the line of sight direction as the Dirac delta function.
+Moreover, we assume that the halos are sparsely distributed in the universe.
+With the sparsity prior, the adaptive lasso regularization
+\citep{AdaLASSO-Zou2006} is used to reconstruct the density field.  We find
+that, in contrast to the lasso estimator that smears the structure along the
+line of sight, the adaptive lasso can efficiently reduce the smearing effect.
 
@@
 We first review the lensing effect in Section \ref{subsec_method_delta2shear}.
-Then, we introduce the dictionary used to model the foreground density maps in
+We then introduce the dictionary used to model the foreground density maps in
 Section \ref{subsec_method_dictionary}.
@@
  \includegraphics[width=0.45\textwidth]{mlz-poz.pdf}
- \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.
+ \caption{The average PDF of MLZ photo-$z$ PDFs for $10$ source redshift bins defined
+         in Figure \ref{fig_bestpz}.
         }\label{fig_pdfpz}
@@
 where $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
-at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the
-matter density parameter, $c$ is the speed of light, and $a(\chi_l)$ is the
-scale parameter at the lens position.
+at the position of lens, $H_0$ is the Hubble constant, $\Omega_M$ is the matter
+density parameter, $c$ is the speed of light, $\chi_{sl}$ is the comoving
+distance between source and lens plane, and $a(\chi_l)$ is the scale parameter
+at the lens position.
 
@@
 \end{equation}
-where $E(z)$ is the Hubble parameter as a function of redshift, in units of $H_0$.
+where $E(z)$ is the Hubble constant as a function of redshift, in units of $H_0$.
 
@@
 \end{equation}
-Here we denote the physical shear distortion as $\gamma_L$, and we note
-that it is not the final shear measurement since the final shear
-measurement is influenced by systematic errors from observations. The
-systematic errors will be discussed in Section \ref{subsec_method_Systematics}.
+Here we denote the physical shear distortion as $\gamma_L$, which is not the
+final shear measurement since the final shear measurement is influenced by
+systematic errors from observations. The systematic errors will be discussed in
+Section \ref{subsec_method_Systematics}.
 
@@
 As the scales of halos are much smaller than the reachable redshift resolution,
-we neglect the depth of halo on the line of sight direction and set the NFW
-atoms' profiles in the line of sight direction to one-dimensional ($1$-D) Dirac
-delta functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. The
-multi-scale NFW atoms are defined as
+we neglect the depth of halo on the line of sight direction and set the
+profiles of the NFW atoms in the line of sight direction to one-dimensional
+($1$-D) Dirac delta functions as suggested by
+\citep{LSS-massMap-Glimpse3D-Leonard2014}. The multi-scale NFW atoms are
+defined as
 \begin{equation}
@@
 F(|\vec{r}_{\theta}|/r_s) \delta_D(z),\\
-&  (s=1...N)
+&  (s=1,...,N)
 \end{split}
@@
 $f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for the NFW atoms in
-different scale frames. Then, we write the basis atoms into the angular
+different scale frames. We then write the basis atoms into the angular
 separation coordinates:
@@
 F(|\vec{\theta}|\chi(z)/r_s) \delta_D(z),\\
-& (s=1...N)
+& (s=1,...,N)
 \end{split}
@@
 compare with the dictionary of multi-scale atoms. The point mass atoms is a
-$3$-D Dirac function defined as follows
+$3$-D Dirac function defined as
 \begin{equation}
@@
     $z=0.01$ and $z=0.85$, respectively. Noises on galaxy shape measurements
-    are neglected in the simulation.  The input halo's virial mass is
+    are neglected in the simulation.  The input mass of halo is
     $M_{200}=10^{15} ~h^{-1}M_{\odot}$, and its redshift is $z=0.35$. The lasso
@@
 The photometric redshifts of source galaxies in the current large-scale survey
-are estimated with a limited number of broad photometric bands (e.g., $9$ bands
+are estimated with a limited number of broad photometric bands e.g., $9$ bands
 for KIDS$+$VIKING survey \citep{KIDS_VIKING-Hildebrant2020}, $5$ bands for DES
-survey and HSC survey). As a result, the estimated redshifts of galaxies suffer
+survey and HSC survey. As a result, the estimated redshifts of galaxies suffer
 from much larger uncertainty than the redshifts estimated with spectroscopic
@@
 The results include both the lensing kernels for spectroscopic redshifts with
-neglectable redshift uncertainties and photometric redshifts with redshift
+negligible redshift uncertainties and photometric redshifts with redshift
 uncertainties shown in Figure \ref{fig_pdfpz}. As shown by the dashed lines in
@@
 zero for source redshifts lower than the lens redshift if the uncertainty on
-the source galaxy redshift estimation are neglectable. However, as demonstrated
+the source galaxy redshift estimation are negligible. However, as demonstrated
 by the solid lines in the same panel, for the source redshifts with large
@@
 \end{equation}
-In this paper, we set $\beta=1.\arcmin5$.
+In this paper, we set $\beta=1\farcm5$.
 
@@
 \end{equation}
-With the approximation that the density of galaxy number - $n(\vec{r})$ -
+With the approximation that the density of galaxy number $n(\vec{r})$
 varies slowly at the smoothing scale, the smoothed galaxy number density (in
@@
 We define the masking window function according to the smoothed galaxy number
-density (defined in eq. (\ref{eq-numDesSmooth})):
+density defined in eq. (\ref{eq-numDesSmooth}):
 \begin{equation}
@@
 \begin{cases}
-0 & n_{\rm{sm}}>1,\\
-1 & \rm{else}.
+1 & n_{\rm{sm}}\geq 1,\\
+0 & \rm{else}.
 \end{cases}
@@
 axis. $\gamma_{\alpha}$ denotes the smoothed shear measurements recorded on the
-pixel with index $\alpha$, where $\alpha=1...N_\theta \times N_\theta \times
+pixel with index $\alpha$, where $\alpha=1,...,N_\theta \times N_\theta \times
 N_s$. The grids on the transverse planes are equally spaced with a pixel size
-of $1\arcmin$. While the grids in the line of sight direction follow
+of $1\arcmin$. The grids in the line of sight direction follow
 equal number binning as shown in Figure \ref{fig_bestpz}.
@@
 to denote the number of the lens planes and $x_{\beta}$ to denote the
-projection parameter indexed as $\beta$, where $\beta=1...N_\theta \times
-N_\theta \times N_l \times N$. The corresponding pixelized elements of the
-forward transform matrix $\mathbf{A}$ is denoted as $A_{\alpha\beta}$.
+projection parameter indexed as $\beta$, where $\beta=1,...,N_\theta \times
+N_\theta \times N_l \times N$, where $N$ is the number of NFW dictionary
+frames. The corresponding pixelized elements of the forward transform matrix
+$\mathbf{A}$ is denoted as $A_{\alpha\beta}$.
 
@@
 effective basis atoms. The $l^2$ norm of the $i$-th column vectors weighted by
-the inverse of the noise covariance matrix's diagonal elements is defined as
+the inverse of the diagonal elements the noise covariance matrix is defined as
 \begin{equation}
@@
 of sight direction even in the absence of noise on shear measurements and
-photo-$z$ uncertainty .
+photo-$z$ uncertainty.
 
-Figure \ref{fig_lassoVsadaLasso} shows the reconstructions of a single halo's
-mass map with virial mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift
-$0.35$. The shear measurement error and photo-$z$ uncertainty are not included
-in the simulation.  The left panel of Figure \ref{fig_lassoVsadaLasso} is the
-reconstruction with the lasso algorithm, which shows a significant smear along
-the line of sight.
+Figure \ref{fig_lassoVsadaLasso} shows the reconstructions of the mass map of a
+single halo with halo mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift
+$0.35$. In this paper, we set the non-linear over-density ($\Delta_{\rm{vir}}$)
+to $200$, and use $M_{200}$ to denote the halo mass. The shear measurement
+error and photo-$z$ uncertainty are not included in the simulation.  The left
+panel of Figure \ref{fig_lassoVsadaLasso} is the reconstruction with the lasso
+algorithm, which shows significant smearing along the line of sight.
 
@@
 \citet{FISTA-Beck2009} propose the Fast Iterative Soft Thresholding Algorithm
-(FISTA) to solve the lasso problem.  Since the lasso's loss function and the
-adaptive lasso's loss function only differ in their penalization terms, the
-FISTA is also applicable to solve the adaptive lasso problem. In this paper, we
-apply the FISTA to solve both the preliminary lasso estimation and the final
-adaptive lasso estimation.
+(FISTA) to solve the lasso problem. Since the loss functions of the lasso and
+the adaptive lasso only differ in their penalization terms, the FISTA is also
+applicable to solve the adaptive lasso problem. In this paper, we apply the
+FISTA to solve both the preliminary lasso estimation and the final adaptive
+lasso estimation.
 
@@
 initialized as $x_i^{(1)}=0$. According to the FISTA algorithm, we iteratively
-update the projection coefficient field ($x$). Taking the $n$'th iteration as
+update the projection coefficient field ($x$). Taking the $n$-th iteration as
 an example, a temporary update is first calculated as
@@
 $\mu$ is the step size of the gradient descent iteration.  $\partial_i
-G(x'^{(n)})$ refers to the $i$'th element of the gradient vector of $G$ at
+G(x'^{(n)})$ refers to the $i$-th element of the gradient vector of $G$ at
 point $x'^{(n)}$:
@@
 
-As summarized in Algorithm \ref{alg-1}, we first initial the projection
+As summarized in Algorithm \ref{alg-1}, we first initialize the projection
 coefficients as zero and use the FISTA algorithm to find the global minimum of

### 2021-01-13 doc/paper_ms_method_HSCY1/massmap_sim.tex
small revision on paper
some minor corrections

@@
 plane is evenly divided into eight redshift bins and eight mass bins. We
-randomly shift the input halo redshifts and halo masses from the bins' centers
-by a small amount. In the simulation, we set the non-linear over-density
-($\Delta_{\rm{vir}}$) to $200$, and $M_{200}$ refers to the virial mass. The
-concentration of the NFW halo is set to as a function of the halo's virial mass
-($M_{200}$) and redshift ($z_{h}$) according to
+randomly shift the input halo redshifts and halo masses from the bin centers
+by a small amount. The concentration of the NFW halo is set to as a function of
+the halo mass ($M_{200}$) and redshift ($z_{h}$) according to
 \citet{c-M_Magneticum-Ragagnin2019}
@@
 \citep{HSC1-catalog}.  We use the galaxies in a one square degree region at the
-center of tract 9347 \citep{HSC1-data}.  The galaxies' positions are randomized
-to distribute homogeneously  in the one-square degree stamp statistically. We
+center of tract 9347 \citep{HSC1-data}. The average galaxy number density in
+this region is $22.94~\rm{arcmin}^{-2}$. The positions of galaxies are randomized to
+distribute homogeneously  in the one-square degree stamp statistically. We
 randomly assign its redshift for each galaxy following the MLZ photo-$z$
@@
 shape measurement error on the pixel level after the smoothing and pixelization is
-also shown in \ref{fig_noiseHistogram}. The standard deviation map of the
+also shown in Figure \ref{fig_noiseHistogram}. The standard deviation map of the
 noise is demonstrated in Figure \ref{fig_noistdmap}. As demonstrated in Figure

### 2021-01-13 doc/paper_ms_method_HSCY1/ms.tex
some minor corrections

@@
 \begin{document}
-\title{Cluster Detection from three-dimensional Lensing Mass Map}
+\title{A new method cluster Detection from three-dimensional weak lensing mass map}
 % \author{Xiangchong Li}
@@
 mass maps.
-We study the performance of three-dimensional cluster detection from the
-reconstructed mass map with simulations that applies shear distortions from
-isolated halo to HSC-like galaxy shapes with realistic photometric redshift
-uncertainties .
-Our findings are summarized as follows:
-1) The lasso reconstructed suffers from a smear of structure in the line of
-sight direction even in the absence of shape noise, and in contrast, the
-adaptive lasso algorithm efficiently removes the line of sight smear.
-2) The algorithm is able to detect halo with minimal mass limits of $10^{14.0}
-M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low
+We study the performance of three-dimensional detection of clusters of galaxies
+from the reconstructed mass map with simulations that apply shear distortions
+from isolated halo to HSC-like galaxy shapes with realistic photometric
+redshift uncertainties .
+We find that the adaptive lasso algorithm efficiently removes the line of sight
+smearing, in contrast to the lasso reconstruction that suffers from  the line
+of sight smearing even in the absence of shape noise.
+The algorithm is able to detect halo with minimal mass limits of $10^{14.0}
+h^{-1}M_{\odot}$, $10^{14.7} h^{-1}M_{\odot}$, $10^{15.0} h^{-1}M_{\odot}$ for the low
 ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts,
 respectively, with an average false detection of 0.022/deg$^2$.
-3) The estimated redshift of the halos detected from the reconstructed mass
-maps are lower than the true redshift by about $0.03$ for halos at low
+The estimated redshift of the halos detected from the reconstructed mass maps
+are slightly lower than the true redshift by about $0.03$ for halos at low
 redshifts ($z\leq 0.4$). The relative redshift bias is below $0.5\%$ for halos
-at $0.4<z\leq 0.85$. The standard deviation of the redshift estimation is $0.092$.
+at $0.4<z\leq 0.85$. The standard deviation of the redshift estimation is
+$0.092$.
 \end{abstract}
@@
         columns are the multi-scale NFW atoms.  The smoothing kernel is
-        Gaussian with a standard dev iation of $1.5$ pixels.
+        Gaussian with a standard deviation of $1.5$ pixels.
     } \label{fig_atoms2D}
@@
 weakly yet coherently distorted by the intervening inhomogeneous density
-distribution along the line of sight due to gravity's influence.  As a result,
-the shapes of the background galaxies are distorted and the information of the
-foreground mass distribution is imprinted to the background galaxy images. Weak
-lensing offers a direct probe into the mass distribution, including both
-visible matter and invisible dark matter, in our universe \citep[see][for
-recent reviews]{revKilbinger15,revRachel17}.
+distribution along the line of sight due to the influence of gravity.  As a
+result, the shapes of the background galaxies are distorted such that the
+information of the foreground mass distribution is imprinted to the background
+galaxy images. Weak lensing offers a direct probe into the mass distribution,
+including both visible matter and invisible dark matter, in our universe
+\citep[see][for recent reviews]{revKilbinger15,revRachel17}.
 Several large-scale surveys focus on studying the weak-lensing effect at a high
-precision level (e.g., HSC \citep{HSC1-data}, KIDS \citep{KIDS13}, DES
+precision level e.g., HSC \citep{HSC1-data}, KIDS \citep{KIDS13}, DES
 \citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, NGRST
-\citep{WFIRST15}).
+\citep{WFIRST15}.
 
@@
 \citep{WL-massMap-peakcounts-Jain2000,WL-massMap-peakcountsAna-Fan2010,WL-massMap-peakcountsFM-Lin2016}.
-Moreover, we can directly detect massive clusters through
+Moreover, we can directly detect massive clusters of galaxies through
 identifying high signal-to-noise (SNR) peaks on the mass map without any
@@
 needed to assign the redshift and extract its physical parameter (such as mass)
-for each cluster selected from $2$-D mass map.
+for each cluster selected from $2$-D mass maps.
 
-On the other hand, we can directly reconstruct $3$-D mass maps taking advantage
-of photometric redshift (photo-$z$) information
+On the other hand, we can directly reconstruct three-dimensional ($3$-D) mass
+maps taking advantage of photometric redshift (photo-$z$) information
 \citep{LSS-massMap-Wiener-Simon2009,WL-massMap-VanderPlas2011}; however, these
 methods either do not have enough spatial resolution to identify clusters, or
-they suffer from smears along the line of sight direction, which need to be
+they suffer from smearing along the line of sight direction, which need to be
 overcome for practical searches of clusters in 3D mass maps.  Alternatively,
@@
 In this paper, we develop a novel method for high-resolution $3$-D mass map
-reconstruction that are free from line of sight smears.  The $3$-D
+reconstruction that are free from line of sight smearing.  The $3$-D
 mass map is modeled as a summation of the NFW \citep{halo-NFW1997ApJ} basis
@@
 
-Then, we test our algorithm using the simulations with different setups of the
+We then test our algorithm using the simulations with different setups of the
 regularization parameter. We also compare the results of our algorithm, which
@@
 reconstructed using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006}.
-We find that the lasso algorithm's solution suffers from a smear of structure
+We find that the lasso algorithm uffers from smearing of structure
 in the line of sight direction even in the absence of galaxy shape noise, and
-the adaptive lasso algorithm efficiently removes the line of sight smear of
+the adaptive lasso algorithm efficiently removes the line of sight smearing of
 structure.
@@
 HSC-like shapes and photo-$z$ uncertainties.  We conclude that the algorithm is
-able to detect halo with minimal mass limits of $10^{14.0} M_{\odot}/h$,
-$10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median
-($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts, respectively, with an
-average false detection of 0.022 deg$^{-2}$. The estimated redshifts of the halos
-detected from the reconstructed mass maps are lower than the true redshift by
-about $0.03$ for halos at low redshifts ($z\leq 0.4$).  The relative redshift
-bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$. The standard deviation of
-the redshift estimation is $0.092$.
+able to detect halo with minimal mass limits of $10^{14.0} h^{-1}M_{\odot}$,
+$10^{14.7} h^{-1}M_{\odot}$, $10^{15.0} h^{-1}M_{\odot}$ for the low ($z<0.3$),
+median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts, respectively,
+with an average false detection of 0.022 deg$^{-2}$. The estimated redshifts of
+the halos detected from the reconstructed mass maps are slightly lower than the
+true redshift by about $0.03$ for halos at low redshifts ($z\leq 0.4$).  The
+relative redshift bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$. The
+standard deviation of the redshift estimation is $0.092$.
 
@@
 \section*{Acknowledgements}
-XL thank Yin Li and Jiaxin Han for useful discussions.
+We thank Yin Li and Jiaxin Han for useful discussions.
 
-XL was supported by Global Science Graduate Course (GSGC) program of
-University of Tokyo and JSPS KAKENHI (JP19J22222).
+XL was supported by Global Science Graduate Course (GSGC) program of University
+of Tokyo and JSPS KAKENHI (JP19J22222).
+
+This work was supported in part by Japan Science and Technology Agency (JST)
+CREST JPMHCR1414, and by JST AIP Acceleration Research Grant No. JP20317829,
+Japan. This work was supported in part by the World Premier International
+Research Center Initiative (WPI Initiative), MEXT, Japan, and JSPS KAKENHI
+Grant Nos. JP18K03693, JP20H00181, JP20H05856.
+
 \bibliographystyle{aasjournal}

### 2021-01-16 python/pixel3D.py
update pixelization code

@@ -1,6 +1,7 @@
 import os
 import json
 import cosmology
+import haloSim
 import numpy as np
 from configparser import ConfigParser
 
@@ -112,7 +113,7 @@ class cartesianGrid3D():
         self.pozPdfAve=None
         return
 
-    def pixelize_data(self,x,y,z,v,ws=None,method='FFT'):
+    def pixelize_data(self,x,y,z,v,ws=None,method='FFT',ave=True):
         """pixelize catalog into the cartesian grid
         Parameters:
         -------------
@@ -129,43 +130,43 @@ class cartesianGrid3D():
         method: string [default: FFT]
             method used to convolve with smoothing kernel
         """
-
+        if z is None:
+            # This is for 2D pixeliztion
+            assert self.shape[0]==1
         if ws is None:
-            ws=np.ones(len(x))/0.25**2.
+            # equal weight
+            ws=np.ones(len(x))
         if self.sigma>0. and method=='sample':
             return self._pixelize_data_sample(x,y,z,v,ws)
         else:
             return self._pixelize_data_FFT(x,y,z,v,ws)
 
     def _pixelize_data_FFT(self,x,y,z,v,ws=None):
-        dataOut=numpy.histogramdd((x,y,z),bins=(self.xbound,self.ybound,self.zbound), weights=v*ws)[0]
-        weightOut=numpy.histogramdd((x,y,z),bins=(self.xbound,self.ybound,self.zbound), weights=ws)[0]
-        dataOut=dataOut/weightOut
-        assert dataOut.shape==self.shape
-        varOut=np.zeros(self.shape,dtype=float)
-        # truncate the smoothing kernel
-        # to 3 times of sigma
+        # pixelize value field
+        dataOut =   np.histogramdd((z,y,x),bins=(self.zbound,self.ybound,self.xbound), weights=v*ws)[0]
+        # pixelize weight field
+        weightOut=  np.histogramdd((z,y,x),bins=(self.zbound,self.ybound,self.xbound), weights=ws)[0]
         if self.sigma>0:
-            rsig=int(self.sigma/self.delta*3+1)
-        else:
-            pass
-
-        return
+            # Gaussian Kernel in Fourier space (normalized in configuration space)
+            gausKer =   haloSim.GausAtom(ny=ny,nx=nx,sigma=self.sigma/self.delta,fou=True,lnorm=2.)
+            norm    =   gausKer[0,0]
+            gausKer /=  norm
[…]

### 2021-01-18 doc/paper_ms_method_HSCY1/ms.tex
add citation for original paper for 3Ddet

@@
 maps taking advantage of photometric redshift (photo-$z$) information
-\citep{LSS-massMap-Wiener-Simon2009,WL-massMap-VanderPlas2011}; however, these
-methods either do not have enough spatial resolution to identify clusters, or
-they suffer from smearing along the line of sight direction, which need to be
-overcome for practical searches of clusters in 3D mass maps.  Alternatively,
-\citet{WL-clusDet-Hennawi2005} propose to perform a maximum-likelihood
-detection of clusters, by convolving tomographic shear measurements with $3$-D
-filters that match the tangential shears induced by multi-scale NFW halos,
-without fully reconstruct the $3$-D mass maps.
+\citep{massMap3D-Hu2002,massMap3D-Bacon2003,LSS-massMap-Wiener-Simon2009,WL-massMap-VanderPlas2011};
+however, these methods either do not have enough spatial resolution to identify
+clusters, or they suffer from smearing along the line of sight direction, which
+need to be overcome for practical searches of clusters in 3D mass maps.
+Alternatively, \citet{WL-clusDet-Hennawi2005} propose to perform a
+maximum-likelihood detection of clusters, by convolving tomographic shear
+measurements with $3$-D filters that match the tangential shears induced by
+multi-scale NFW halos, without fully reconstruct the $3$-D mass maps.
 

### 2021-01-18 doc/paper_ms_method_HSCY1/sim_NFW_results.tex
delete unused figures

--- 2021-01-09 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
@@
     galaxy shape catalog with the NFW dictionary. The upper panels show the
-    pixels' number histograms.  The penalization parameters are $\lambda=3.5$
-    (left) and $\lambda=5.0$ (right).  The input halo mass is
+    number histograms of pixel values.  The penalization parameters are
+    $\lambda=3.5$ (left) and $\lambda=5.0$ (right).  The input halo mass is
     $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The
-    vertical direction is the line of sight direction. The boxes' lower
-    boundaries and upper boundaries of correspond to $z=0.01$ and $z=0.85$,
+    vertical direction is the line of sight direction. The lower boundaries and
+    upper boundaries of the boxes correspond to $z=0.01$ and $z=0.85$,
     respectively.
@@
 This paper does not go beyond the resolution limit defined by the Gaussian
-smoothing kernel with a standard deviation of $1.\arcmin 5$ and the $1\arcmin$
+smoothing kernel with a standard deviation of $1\farcm5$ and the $1\arcmin$
 pixel scale as discussed in Section \ref{subsec_method_smoothing} and Section
@@
 different penalization parameters for a halo with $M_{200}=10^{15.02}
-~h^{-1}M_{\odot}$ at redshift $0.164$. Also, the pixels' histograms are shown
-in Figure \ref{fig_NFW3D}. From these plots, we conclude that the adaptive
-lasso algorithm sets most of the reconstructed pixels to zero and only keeps
-the modes strongly related to the data. Moreover, the reconstructed density maps
-do not suffer from the line of sight smearing. After the reconstruction for
-each simulation, we identify the peaks on the sparse density map.
+~h^{-1}M_{\odot}$ at redshift $0.164$. Also, the histograms of pixel values are
+shown in Figure \ref{fig_NFW3D}. From these plots, we conclude that the
+adaptive lasso algorithm sets most of the reconstructed pixels to zero and only
+keeps the modes strongly related to the data. Moreover, the reconstructed
+density maps do not suffer from the line of sight smearing. After the
+reconstruction for each simulation, we identify the peaks on the sparse density
+map.
 
@@
      pure noise catalogs. The gray lines are the best-fit Gaussian distributions
-     to the noises' peak histograms.
+     to the histograms of noise peaks.
     }\label{fig_peakHist}
@@
 histograms of normalized peaks detected from the pure noise catalogs are shown
-in Figure \ref{fig_peakHist} and we show the best-fit Gaussian functions of the
+in Figure \ref{fig_peakHist} along with the best-fit Gaussian functions of the
 noise peaks' histograms.
 
-Figure \ref{fig_peakHist} tells that the densities of peaks (including both
+Figure \ref{fig_peakHist} indicates that the densities of peaks (including both
 true and false peaks) are suppressed as the penalization parameter $\lambda$
@@
 The $2$-D histogram, stacked from all of the simulations, for the offsets of
-the detected peak positions from the input halos' positions is shown in the
+the detected peak positions from the positions of input halos is shown in the
 left panel of Figure \ref{fig_detoffsets}. We see a clustering of peaks close
-to the input halo's position on the stacked position histogram.  For each stamp
+to the position of the input halo on the stacked position histogram.  For each stamp
 simulation, we find the positive peak closest to the input position (in the
@@
      simulation, the positive peak inside the dashed black box with the minimal
-     offset (in the pixel unit) from the input halo's position is taken as a
-     true detection. The right panel focuses on the deviation of detected peaks
-     in the line of sight direction. The $x$-axis is the input halo redshifts,
-     and the $y$-axis is the redshift of the detected peak. The `$\cross$'
-     denotes the average redshift of detected peaks for each halo over
+     offset (in the pixel unit) from the position of the input halo is taken as
+     a true detection. The right panel focuses on the deviation of detected
+     peaks in the line of sight direction. The $x$-axis is the input halo
+     redshifts, and the $y$-axis is the redshift of the detected peak. The
+     cross denotes the average redshift of detected peaks for each halo over
      different noise realizations, and the error-bars are the uncertainties of
@@
 The right panel of Figure \ref{fig_detoffsets} shows the average redshift of
-true detections for each halo. The estimated redshifts are lower than the true
-redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
-For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$. The
-standard deviation of the redshift estimation is $0.092$.
+true detections for each halo. The estimated redshifts are slightly lower than
+the true redshifts by about $0.03$ for halos in the low-redshift range ($z\leq
+0.4$).  For halos at $0.4<z\leq 0.85$, the relative redshift bias is below
+$0.5\%$. The standard deviation of the redshift estimation is $0.092$.
 
 With the intent to suppress false detections, we select peaks with values
-greater than an ad-hoc threshold as candidates of galaxy clusters following
-\citet{WL-massMap-clusDet-HSC-Miyazaki2018}.  The threshold is set to a few
-times the standard deviation of the noise peaks. We use different detection
-thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters from the
-mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and middle columns
-of Figure \ref{fig_detFalsRateNFW} show the detection rates for halos in the
-redshift-mass planes with detection thresholds set to $1.5\sigma$ and
-$3.0\sigma$ of the noise peaks' distributions, respectively.  The right column
-of Figure \ref{fig_detFalsRateNFW} shows the corresponding numbers of false
-detections per square degree as functions of detection thresholds.
+greater than an ad-hoc threshold as candidates of galaxy clusters.  The
+threshold is set to a few times the standard deviation of the noise peaks. We
+use different detection thresholds ($1.5\sigma$ and $3.0\sigma$) to detect
+galaxy clusters from the mass maps reconstructed with $\lambda=3.5,4.0,5.0$.
+The left and middle columns of Figure \ref{fig_detFalsRateNFW} show the
+detection rates for halos in the redshift-mass planes with detection thresholds
+set to $1.5\sigma$ and $3.0\sigma$ of the noise peak distributions,
+respectively.  The right column of Figure \ref{fig_detFalsRateNFW} shows the
+corresponding numbers of false detections per square degree as functions of
+detection thresholds.
 
-Figure \ref{fig_detFalsRateNFW} tells that the false peak density is suppressed
+Figure \ref{fig_detFalsRateNFW} indicates that the false peak density is suppressed
 as the detection threshold increases. Also, the detection rate of halo
@@
 In summary, The algorithm is able to detect halo with minimal mass limits of
-$10^{14.0} M_{\odot}/h$, $10^{14.7} M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for
-the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high ($0.6\leq z< 0.85$)
-redshifts, respectively.
+$10^{14.0} h^{-1}M_{\odot}$, $10^{14.7} h^{-1}M_{\odot}$, $10^{15.0}
+h^{-1}M_{\odot}$ for the low ($z<0.3$), median ($0.3\leq z< 0.6$) and high
+($0.6\leq z< 0.85$) redshifts, respectively.
 
@@
 shown in Figure \ref{fig_detNum}. The expected cluster number density in total
-is $0.49$ $\deg^{-2}$, which corresponds to $78.4$ clusters for the first year
-HSC shear catalog \citep{HSC1-catalog} with a survey area of $\sim 160 \deg^2$.
-The expected number of detections is similar to the number of $2$-D cluster
-detections on the first year HSC shape catalog \citep{HSC1-massMap-cluster}.
+is $0.49$ $\deg^{-2}$, which is much higher than the false detection rate of
+0.022 deg$^{-2}$. This cluster number density corresponds to $78.4$ clusters
+for the first year HSC shear catalog \citep{HSC1-catalog} with a survey area of
+$\sim 160 \deg^2$.  The expected number of detections is similar to the number
+of $2$-D cluster detections on the first year HSC shape catalog
+\citep{HSC1-massMap-cluster}.
 
@@
  \caption{The expected number density of detected clusters per square degree as
-     a function of halo's virial mass and redshift. The number density in total
+     a function of halo mass and redshift. The number density in total
      is $0.49~\deg^{-2}$.

### 2021-01-18 doc/paper_ms_method_HSCY1/sim_PointMass_results.tex
delete unused figures

--- 2020-12-22 doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex
@@
 point mass dictionary tend to assign masses to several different redshift bins
-in the neighboring region of the halo's center.  In contrast, as demonstrated in
+in the neighboring region of the halo center.  In contrast, as demonstrated in
 Figure \ref{fig_NFW3D}, the NFW dictionary manages to perform consistent mass
-reconstructions.  We think the problem of the point mass dictionary originates
+reconstructions. The problem of the point mass dictionary presumably originates
 from the fact that the profile of the point mass atom in the transverse plane
@@
     $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The
-    vertical direction is the line of sight direction. The boxes' lower
-    boundaries and upper boundaries of correspond to $z=0.01$ and $z=0.85$,
+    vertical direction is the line of sight direction. The lower boundaries and
+    the upper boundaries of the boxes correspond to $z=0.01$ and $z=0.85$,
     respectively.

### 2021-01-20 python/pixel3D.py
implete TAN project into pixel3D

@@ -24,69 +24,56 @@ def four_pi_G_over_c_squared():
     return fourpiGoverc2
 
 class cartesianGrid3D():
-    # pixel3D.cartesianGrid3D
+    """
+    pixlize in a TAN(Gnomonic)-prjected Cartesian Grid
+    """
     def __init__(self,parser):
         """
         Parameters:
         -------------
         parser: parser
         """
-        # Transverse celestial plane
-        # the unit in the configuration
-        # the input data is in unit of degree
+        # The unit of angle in the configuration
         unit=parser.get('transPlane','unit')
+        # It is necessary to do the scaling as the input data is in unit of
+        # degree
         if unit=='degree':
-            ratio=1.
+            self.ratio=1.
         elif unit=='arcmin':
-            ratio=1./60.
+            self.ratio=1./60.
         elif unit=='arcsec':
-            ratio=1./60./60.
-
-        ## ra
-        delta=parser.getfloat('transPlane','scale')*ratio
-        xmin=parser.getfloat('transPlane','xmin')*ratio
-        nx=parser.getint('transPlane','nx')
-        assert nx>=1
-        xmax=xmin+delta*(nx+0.1)
-        xbound=np.arange(xmin,xmax,delta)
-        xcgrid=(xbound[:-1]+xbound[1:])/2.
-        assert len(xcgrid)==nx
-        self.xbound=xbound
-        self.xcgrid=xcgrid
-        ## dec
-        ymin=parser.getfloat('transPlane','ymin')*ratio
-        ny=parser.getint('transPlane','ny')
-        assert ny>=1
-        ymax=ymin+delta*(ny+0.1)
-        ybound=np.arange(ymin,ymax,delta)
-        ycgrid=(ybound[:-1]+ybound[1:])/2.
-        assert len(ycgrid)==ny
-        self.ybound=ybound
-        self.ycgrid=ycgrid
-        self.delta=delta
-        ## Gaussian smoothing
-        self.sigma=parser.getfloat('transPlane','smooth_scale')*ratio
-
-        # line-of-signt direction
-        # background plane
-        if parser.has_option('sourceZ','zbound'):
-            zbound=np.array(json.loads(parser.get('sourceZ','zbound')))
-            nz=len(zbound)-1
+            self.ratio=1./60./60.
[…]
